### 2021-06-24 paper-correlations.tex
Initial commit

\documentclass[reprint,amsmath,amssymb,aps,pre]{revtex4-1}
% Latex
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% Xelatex
%\usepackage{polyglossia}
%\usepackage{fontspec}
%\setdefaultlanguage{english}
%\setmainfont{DejaVu Sans}
%\setsansfont{DejaVu Sans}
%\setmonofont{DejaVu Sans Mono}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{algpseudocode}

\definecolor{light-gray}{gray}{0.95}
\newcommand{\code}[1]{\colorbox{light-gray}{\texttt{#1}}}
% When cleveref fails to do its job
\newcommand{\apref}[1]{Appendix \ref{#1}}

\begin{document}
%*Corresponding author: Kirill M. Gerke, Tel.: +79661877715, E-mail: kg@ifz.ru,
%Address: Schmidt Institute of Physics of the Earth of Russian Academy of
%Sciences, Bolshaya Gruzinskaya str. 10/1, Moscow, 123242, Russia
\author{Vasily Postnicov}
\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of Sciences, Moscow, 123242, Russia}
\author{Alexey I. Samarin}
\altaffiliation{Computational Mathematics and Cybernetics, Lomonosov Moscow State University, Moscow, 119991, Russia}
\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of Sciences, Moscow, 123242, Russia}
\author{Marina V. Karsanina}
\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of Sciences, Moscow, 123242, Russia}
\author{Efim V. Lavrukhin}
\altaffiliation{Computational Mathematics and Cybernetics, Lomonosov Moscow State University, Moscow, 119991, Russia}
\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of Sciences, Moscow, 123242, Russia}
\author{Kirill M. Gerke}
\email[E-mail:]{kg@ifz.ru}
\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of Sciences, Moscow, 123242, Russia}

\title{Something about correlation functions}

\begin{abstract}
  What have we done?
\end{abstract}

\maketitle

\section{Overview of supported functions and modules.}
\label{oversec}
\verb+CorrelationFunctions.jl+ is capable to compute the following correlation
functions:
\begin{itemize}
\item Lineal-path function $L_2$.
\item Two-point function $S_2$.
\item Cluster function $C_2$.
\item Surface-surface function $F_{ss}$.
\item Surface-void function $F_{sv}$.
\item Pore size function $P$.
\item Chord length function $p$.
\end{itemize}

These correlation functions are calculated using two different approaches (when
applicable). The first approach is implemented in the module \code{Directional}
and the second approach is in the module \code{Map}. The former approach (called
the scan approach) calculates correlation functions along specified directions
which can include axial and diagonal directions. The results of computations can
be provided to the user separately for each requested direction or averaged over
multiple directions. The latter approach (called the map approach) calculates a
``correlation map'' which stores the values of a correlation function in all
directions. The scan and map approaches are described in \cref{scansec} and
\cref{mapsec} respectively.

Our package takes one-, two- or three-dimensional arrays of any element type
(usually we restrict ourselves to integer numbers of type \code{Int} or
\code{Int8}) and treats them as homogeneous anisotropic media.

Correlation functions can be computed using closed walls (CW) and periodic
boundary conditions. \textbf{TODO: Describe them}.

\section{The scan approach.}
\label{scansec}
In this approach, the input array is cut in parallel slices (``scanned'') along
each requested direction. Each slice is then analyzed independently as
one-dimensional system and the result is accumulated into \code{CorrelationData}
structure. In the following sections we provide the algorithms for computation
of the functions given in \cref{oversec}.

Generally a correlation function $F(\bm{r})$ is defined as a probability
$p(\bm{r})$ of event $A$ which can occur when a line segment of length
$|\bm{r}|$ and parallel to $\bm{r}$ is randomly dropped into the input
array. Examples of $A$ include an event that the whole segment lies in some
phase $i$ or that it touches an interface between phases with both of its ends
and so on.

The probability $p(\bm{r})$ can be expressed as
\begin{equation*}
  p(\bm{r}) = \frac{\text{Number of successful trials $S(\bm{r})$}}
  {\text{Total number of trials $N(\bm{r})$}}
\end{equation*}

In the scan approach we fix one direction $\bm{e}$ and accumulate the values of
$S(\bm{r})$ and $N(\bm{r})$ so that $\bm{r} \parallel \bm{e}$ into two arrays
\code{success} and \code{total} respectively. We then calculate \code{success}
and \code{total} for all directions and construct a \code{CorrelationData}
structure which holds two dictionaries with key-value pairs
\code{(direction, success)} and \code{(direction, total)}. With this information
it's easy to calculate a correlation function for each combination of
correlation length and direction.

\subsection{Lineal-path function}
Lineal-path function $L_2^{(i)}(\bm{r})$ is defined as the probability that a
line segment with the length $|\bm{r}|$ and paralel to $\bm{r}$ lies wholly in
the phase $i$ when randomly thrown into the input array. This function for a
one-dimensional array is computed using the algorithm described in
\apref{linpathalg}. A multidimensional arrays is firstly cut in slices as
described above and \code{l2} function is calculated for each slice returning
\code{success} and \code{total} arrays. These arrays are then accumulated as
described in \cref{scansec} for final calculation of $L_2^{(i)}(\bm{r})$
function.

\subsection{Two-point function}
Two-point correlation function $S_2^{(i)}(\bm{r})$ is defined as the probability
that both ends of a line segment with the length $|\bm{r}|$ and paralel to
$\bm{r}$ lie in the phase $i$ when the segment is randomly thrown into the input
array. This can be expressed using the following formula:
\begin{equation*}
  S_2^{(i)}(\bm{r}) = \langle I^{(i)}(\bm{x}) I^{(i)}(\bm{x} + \bm{r}) \rangle
\end{equation*}
where $I^{(i)}(\bm{x})$ is an indicator function for the phase $i$:
\begin{equation*}
I^{(i)}(\bm{x}) = \left\{
\begin{array}{ll}
  1 & \quad \bm{x} \in \text{phase $i$} \\
  0 & \quad \text{otherwise}
\end{array}
\right.
\end{equation*}

Two-point function is so heaviliy used internally in the package so we propose a
bit more general definition for it:
\begin{equation*}
  S_2^{\chi}(\bm{r}) = \langle \chi(\bm{x}, \bm{x} + \bm{r}) \rangle
\end{equation*}
where $\chi(\bm{x})$ is some arbitrary indicator (or membership) function. and
$\bm{x} \in \mathbb{R}^{2n}$ where $n$ is dimensionality of the input array. The
vector $\bm{x}$ is constructed as $(\bm{x_1}, \bm{x_2})$ where $\bm{x_1}$ and
$\bm{x_2}$ are the coordinates of the both ends of a line segment thrown into
the input array.

If $\chi(\bm{x})$ can be expressed as
$\chi(\bm{x}) = \chi_1(\bm{x_1})\chi_2(\bm{x_2})$ (what we call
\code{SeparableIndicator} in our package) we use the following algorithm to
calculate the array \code{success} for one-dimensional slice:
\begin{algorithmic}[1]
  \Procedure{s2sep}{$array, \chi_1, \chi_2, periodic$}
  \If{$!periodic$}
    \State $array \gets array \odot zeros(length(array))$ \Comment{$\odot$
      denotes concatenation and $zeros(n)$ returns an array with $n$ zeros.}
  \EndIf
  \State $ind1 \gets \chi_1(array)$ \Comment{apply $\chi_1$ element-wise to $array$}
  \State $ind2 \gets \chi_2(array)$ \Comment{apply $\chi_2$ element-wise to $array$}
  \State $ft1 \gets rfft(ind1)$ \Comment{$rfft$ is fast Fourier transform for
    real-valued data}
  \State $ft2 \gets rfft(ind2)$
  \State $s2ft \gets ft1 \cdot \overline{ft2}$ \Comment{multiply element-wise}
  \State $success \gets irfft(s2ft)$ \Comment{$irfft$ is inverse of $rfft$}
  \State \textbf{return} $success$
  \EndProcedure
\end{algorithmic}

If $\chi(\bm{x})$ cannot be expressed in this way (what we call
\code{InseparableIndicator}) the algorithm is slightly different:
\begin{algorithmic}[1]
  \Procedure{s2insep}{$array, \chi, periodic$}
    \State $len \gets length(array)$
    \If{$periodic$}
      \State $array \gets array \odot array$
    \EndIf
    \State $success \gets zeros(len)$
    \For{$shift \gets 0,len-1$}
      \State $array2 \gets subseq(array, shift)$
      \Comment{$subseq$ returns subsequence of $array$ from the $shift$-th element
        to the end.}
      \State $array[shift] \gets sum(map(\chi, array, array2))$
    \EndFor
    \State \textbf{return} $success$
  \EndProcedure
\end{algorithmic}

The array \code{total} is obtained in the same way as in $L_2$ function because
it depends only on correlation lengths and the length of the input array.

The efficiency of \code{s2sep} is $O(n\:log\,n)$ and efficiency of
\code{s2insep} is $O(n^2)$ where $n$ is the length of the array.

\subsection{Cluster function}
The cluster correlation function $C_2^{(i)}(\bm{r})$ is defined as the
probability that both ends of a line segment with the length $|\bm{r}|$ and
paralel to $\bm{r}$ lie in the same cluster of the phase $i$ when the segment is
randomly thrown into the input array.

The algorithm for calculation of the array \code{success} for
$C_2^{(i)}(\bm{r})$ for one-dimensional slice is straightforward:
\begin{algorithmic}[1]
  \Procedure{c2}{$array, phase, periodic$}
  \State $ind \gets array = phase$ \Comment{$array$ is compared with $phase$
    element-wise}
  \State $clusters \gets clusterize(ind)$
  \Comment{$clusterize(x)$ selects clusters from the array
    $x$. Each cluster gets its own unique integer identificator. The
    identificator $0$ is reserved for the void phase.}
  \State $\chi(x,y) \gets (x = y \ne 0)$
  \State \textbf{return} $s2insep(clusters, \chi, periodic)$
  \EndProcedure
\end{algorithmic}

\subsection{Surface-surface and surface-void functions}
The surface-surface correlation function $F_{ss}^{(i)}(\bm{r})$ is defined as
the probability that both ends of a line segment with the length $|\bm{r}|$ and
paralel to $\bm{r}$ touch the interface of the phase $i$ when the segment is
randomly thrown into the input array. This can be expressed using the following
formula:
\begin{equation*}
  F_{ss}^{(i)}(\bm{r}) = \langle |\nabla I^{(i)}(\bm{x})| |\nabla I^{(i)}(\bm{x}
  + \bm{r})| \rangle
\end{equation*}
where $I^{(i)}(\bm{x})$ is an indicator function for the phase $i$.

The algorithm for calculation of the array \code{success} for
$F_{ss}^{(i)}(\bm{r})$ for one-dimensional slice is also straightforward:
\begin{algorithmic}[1]
  \Procedure{surfsurf}{$array, phase, periodic$}
    \State $ind \gets array = phase$ \Comment{$array$ is compared with $phase$
      element-wise}
    \State $edge \gets \text{Detect edges in $ind$}$
    \State \textbf{return} $s2sep(edge, identity, identity, periodic)$
    \Comment{$identity(x) = x$}
  \EndProcedure
\end{algorithmic}

The surface-void correlation function $F_{sv}^{(i)}(\bm{r})$is defined as
follows:
\begin{equation*}
  F_{sv}^{(i)}(\bm{r}) = \langle |\nabla I^{(i)}(\bm{x})| I^{(void)}(\bm{x}
  + \bm{r}) \rangle
\end{equation*}

The algorithm for calculation of the array \code{success} for
$F_{sv}^{(i)}(\bm{r})$ for one-dimensional slice is very similar to the previous
one:
\begin{algorithmic}[1]
  \Procedure{surfvoid}{$array, phase, periodic$}
    \State $ind \gets array = phase$ \Comment{$array$ is compared with $phase$
      element-wise}
    \State $edge \gets \text{Detect edges in $ind$}$
    \State $indices \gets \text{Array of all indices in $array$}$
    \State $\chi_1(x) \gets edge[x]$
    \State $\chi_2(x) \gets array[x] = 0$ \Comment{$0$ is a value which designates the
      void phase}
    \State \textbf{return} $s2sep(indices, \chi_1, \chi_2, periodic)$
  \EndProcedure
\end{algorithmic}

The edges are extracted by calculating $|S(array)|$ where $S$ is the Sobel
operator. \textbf{TODO: Cite our first paper}.

\subsection{Pore size function}
The pore size correlation function $P(r)dr$ is defined as the probability that a
randomly chosen point in the input array lies at a distance between
$r$ and $r + dr$ from the nearest point on the pore-solid interface.

As you can see this function cannot be obtained from one-dimensional slices.

\section{The map approach.}
\label{mapsec}
Text

\appendix
\section{Algorithm of computation of lineal-phase function}
\label{linpathalg}
The algorithm below calculates $L_2^{(phase)}$ correlation function for
one-dimensional array $array$. The result is an array of $L_2$ values for
correlation lengths from $0$ to $maxlen-1$. If $periodic$ is true (resp. false)
then periodic (resp. CW) boundary conditions are used. The entry point of the
algorithm is the function L2. The efficiency of the proposed algorithm is $O(n)$
where $n$ is the length of the array.

\begin{algorithmic}[1]
  \Procedure{countruns}{$array, len, phase$}
    \State $runslist \gets [\quad]$
    \State $runs \gets 0$
    \ForAll{$x \in array$}
      \If{$x = phase$}
        \State $runs \gets runs + 1$
      \ElsIf{$runs \ne 0$}
        \State $runslist \gets runs:runslist$
        \State $runs \gets 0$
      \EndIf
    \EndFor
    \If{$runs \ne 0$}
      \State $runslist \gets runs:runslist$
    \EndIf
    \State \textbf{return} $runslist$
  \EndProcedure
  \\
  \Procedure{updateruns}{$array, runs, n$}
    \For{$idx = 1,n$}
      \State $array[idx] \gets array[idx] + runs$
      \State $runs \gets runs - 1$
    \EndFor
  \EndProcedure
  \\
  \Procedure{updateperiodic}{$array, first, last, n$}
    \State $sum \gets first + last$
    \State $n \gets \min(n, sum)$
    \For{$idx = 1,n$}
      \State $a \gets \min(idx - 1, first, last, sum - (idx - 1))$
      \State $array[idx] \gets array[idx] + a$
    \EndFor
  \EndProcedure
  \\
  \Procedure{l2}{$array, phase, maxlen, periodic$}
    \State $success \gets zeros(maxlen)$
    \State $total \gets zeros(maxlen)$
    \State $len \gets length(array)$
    \State $nupdates \gets \min(len, maxlen)$
    \State $runs \gets countruns(array, maxlen, phase)$
    \ForAll{$run \in runs$}
      \State $updateruns(success, run, \min(run, maxlen))$
    \EndFor
    \If{$periodic$}
      \State $first \gets first(array)$
      \State $last \gets last(array)$
      \If{$first = last$}
        \State $updateperiodic(success, first, last, nupdates)$
      \EndIf
      \State Increment $total[\text{from} \, 1 \, \text{to} \, nupdates]$ by
      $len$
    \Else
      \State $updateruns(total, len, nupdates)$
    \EndIf
    \State \textbf{return} $success$ divided by $total$ element-wise.  
  \EndProcedure
\end{algorithmic}
\end{document}

### 2021-06-24 paper-correlations.tex
More on pore size function

@@
 \newcommand{\apref}[1]{Appendix \ref{#1}}
+\DeclareMathOperator*{\argmin}{arg\,min}
 
@@
 multiple directions. The latter approach (called the map approach) calculates a
-``correlation map'' which stores the values of a correlation function in all
+``correlation map'' which holds the values of a correlation function in all
 directions. The scan and map approaches are described in \cref{scansec} and
@@
 
-As you can see this function cannot be obtained from one-dimensional slices.
+As you can see this function cannot be obtained from one-dimensional slices. We
+calculate it using distance transform. For each point $\bm{x}$ distance
+transform $\mathcal{D}(\bm{x})$ is defined as
+\begin{equation*}
+  \mathcal{D}(\bm{x})= \left\{
+  \begin{array}{ll}
+    0 & \quad \bm{x} \in \text{solid phase} \\
+    \argmin\limits_{y \in \text{solid phase}} \rho(\bm{x},\bm{y}) & \quad \text{otherwise}
+  \end{array}
+\right.
+\end{equation*}
+
+Our algorithm for calculating $P(r)$ for a two-phase system is the following:
+\begin{algorithmic}[1]
+  \Procedure{poresize}{$array, nbins$}
+    \State $d \gets dist(array)$ \Comment{$dist$ calculates
+      $\mathcal{D}(\bm{x})$ for each element of $array$}
+    \State $f(x) \gets x \ne 0$
+    \State $positive \gets filter(d, f)$
+    \State Bin values in $positive$ to $nbins$ bins to compute a histogram $H$
+    \State \textbf{return} $H$
+  \EndProcedure
+\end{algorithmic}
 

### 2021-06-25 paper-correlations.tex
Some text regarding chord-length function and verification

@@
 
+\subsection{Chord length function}
+The chord length function $p^{(i)}(\bm{r})d\bm{r}$ is defined as the probability of
+finding a chord of length between $|\bm{r}|$ and $|\bm{r} + d\bm{r}|$ and
+paralled to $\bm{r}$ in phase $i$. A chords is a line segment between
+intersections of an infinitely long line with the two-phase interface. This
+function, again, can be calculated by cutting slices from a multidimensional
+array. The algorithm is as follows:
+\begin{algorithmic}[1]
+  \Procedure{chordlength}{$array, phase, nbins$}
+    \State $lengths \gets [\quad]$
+    \State $ind \gets array = phase$ \Comment{$array$ is compared with $phase$
+      element-wise}
+    \State $edgephase \gets maximum(array) + 1$ \Comment{``bogus'' phase for the
+      interface of the phase $phase$}
+    \State $edge \gets edgephase \cdot [\text{Detect edges in $ind$}]$ \Comment{We
+      use distance transform here}
+    \State $combo = min(edge + array, edgephase)$ \Comment{Combine the original
+      array and the interface for the phase $phase$}
+    \ForAll{$direction \in \{\text{Requested directions}\}$}
+      \ForAll{$slice \in \{\text{Slices parallel to $direction$}\}$}
+        \State $len \gets 0$
+        \State $startonedge \gets false$
+        \ForAll{$x \in slice$}
+          \If{$x = edgephase$}
+            \Comment{Edge found}
+            \If{$len > 1 \land startonedge$}
+              \State $lengths \gets (len-1):lengths$
+            \EndIf
+            \State $len \gets 0$
+            \State $startonedge \gets true$
+          \ElsIf{$x \ne phase$}
+            \State $startonedge \gets false$
+          \EndIf
+          \State $len \gets len + 1$
+        \EndFor
+      \EndFor
+    \EndFor
+    \State Bin elements in $lengths$ to $nbins$ bins to compute a histogram $H$
+    \State \textbf{return} $H$
+  \EndProcedure
+\end{algorithmic}
+
 \section{The map approach.}
@@
 Text
+
+\section{Verifying our algorithms}
+To verify our package we use random datasets of overlapping spheres with radii
+$R$ and centers placed in points generated by Poisson point process with a
+parameter $\lambda$. For these datasets correlation functions can be given in
+closed-form expressions for one-, two- and three-dimensional cases. For the sake
+of testing we obtain a collection of spheres in a square (the number of
+dimensions $n = 2$) or cube ($n = 3$) with the side $s$ using the following
+algorithm:
+\begin{algorithmic}[1]
+  \Procedure{spheres}{$s, n, R, \lambda$}
+    \State $nspheres \gets poisson(\lambda s^n)$ \Comment{$poisson(\lambda)$
+      generates random numbers with Poisson distribution with parameter
+      $\lambda$.}
+    \State Generate $nspheres$ random points which are uniformly distributes in
+    a cube ($n = 3$) or square ($n = 2$) with a side $s$
+    \State Draw spheres of radius $R$ in those points. Store the result in an
+    array $output$.
+    \State \textbf{return} $output$
+  \EndProcedure
+\end{algorithmic}
 

### 2021-06-25 paper-correlations.tex
Add section about testing

@@
 \usepackage{algpseudocode}
+\usepackage{graphicx}
+\usepackage{subcaption}
 
@@
 \newcommand{\apref}[1]{Appendix \ref{#1}}
-\DeclareMathOperator*{\argmin}{arg\,min}
 
@@
 which can include axial and diagonal directions. The results of computations can
-be provided to the user separately for each requested direction or averaged over
-multiple directions. The latter approach (called the map approach) calculates a
-``correlation map'' which holds the values of a correlation function in all
-directions. The scan and map approaches are described in \cref{scansec} and
-\cref{mapsec} respectively.
+be provided to the user separately for each requested direction or averaged
+across multiple directions. The latter approach (called the map approach)
+calculates a ``correlation map'' which holds the values of a correlation
+function in all directions. The scan and map approaches are described in
+\cref{scansec} and \cref{mapsec} respectively.
 
@@
 \end{equation*}
-where $\chi(\bm{x})$ is some arbitrary indicator (or membership) function. and
+where $\chi(\bm{x})$ is some arbitrary indicator (or membership) function and
 $\bm{x} \in \mathbb{R}^{2n}$ where $n$ is dimensionality of the input array. The
@@
     \State $\chi_1(x) \gets edge[x]$
-    \State $\chi_2(x) \gets array[x] = 0$ \Comment{$0$ is a value which designates the
+    \State $\chi_2(x) \gets array[x] = 0$ \Comment{$0$ is a value reserved for the
       void phase}
@@
     0 & \quad \bm{x} \in \text{solid phase} \\
-    \argmin\limits_{y \in \text{solid phase}} \rho(\bm{x},\bm{y}) & \quad \text{otherwise}
+    \min\limits_{y \in \text{solid phase}} \rho(\bm{x},\bm{y}) & \quad \text{otherwise}
   \end{array}
@@
 paralled to $\bm{r}$ in phase $i$. A chords is a line segment between
-intersections of an infinitely long line with the two-phase interface. This
-function, again, can be calculated by cutting slices from a multidimensional
-array. The algorithm is as follows:
+intersections of an infinitely long line with the interface of the phase
+$i$. This function, again, can be calculated by cutting slices from a
+multidimensional array. The algorithm is as follows:
 \begin{algorithmic}[1]
@@
 \section{Verifying our algorithms}
-To verify our package we use random datasets of overlapping spheres with radii
-$R$ and centers placed in points generated by Poisson point process with a
-parameter $\lambda$. For these datasets correlation functions can be given in
-closed-form expressions for one-, two- and three-dimensional cases. For the sake
-of testing we obtain a collection of spheres in a square (the number of
-dimensions $n = 2$) or cube ($n = 3$) with the side $s$ using the following
-algorithm:
+To verify our package we use random datasets of overlapping disks (the number of
+dimensions $n = 2$) or balls ($n = 3$) with radii $R$ and centers placed in
+points generated by Poisson point process with a parameter $\lambda$. For these
+datasets correlation functions can be given in closed-form expressions for one-,
+two- and three-dimensional cases. For the sake of testing we obtain a collection
+of disks (resp. balls) in a square (resp. cube) with the side $s$ using the
+following algorithm:
 \begin{algorithmic}[1]
-  \Procedure{spheres}{$s, n, R, \lambda$}
-    \State $nspheres \gets poisson(\lambda s^n)$ \Comment{$poisson(\lambda)$
+  \label{testdata}
+  \Procedure{testdata}{$s, n, R, \lambda$}
+    \State $nballs \gets poisson(\lambda s^n)$ \Comment{$poisson(\lambda)$
       generates random numbers with Poisson distribution with parameter
       $\lambda$.}
-    \State Generate $nspheres$ random points which are uniformly distributes in
+    \State Generate $nballs$ random points which are uniformly distributes in
     a cube ($n = 3$) or square ($n = 2$) with a side $s$
-    \State Draw spheres of radius $R$ in those points. Store the result in an
-    array $output$.
+    \State Draw balls (disks) of radius $R$ in those points. Store the result in
+    an array $output$.
     \State \textbf{return} $output$
@@
 \end{algorithmic}
+
+In two-dimensional case we test functions $L_2(r)$, $S_2(r)$, $F_{ss}(r)$ and
+$F_{sv}(r)$ using parameters $R = 100$, $\lambda = 4\cdot10^{-5}$ and
+$s = 5000$. The correlation functions are calculated in two axial directions
+with periodic boundary conditions and the result is averaged across the
+directions. Instead of taking one realization of Poisson process we take 15
+realizations and average results over them. The result can be seen on
+\cref{fig:2d}.
+
+For pore size function $P(r)$ and chord length function $p(\bm{r})$ a slightly
+different approach is required. We take a single realization of Poisson point
+process with the same parameters $R$ and $\lambda$ in a square with the side
+$s = 20000$ (resp. $s = 12000$) and calculate histograms for Pore size
+(resp. Chord length) function. Chord length function is calculated in two axial
+directions. The theoretical values are integrated over bin ranges and compared
+with the number of elements in those bins. The results are presented on
+\cref{fig:pscl}.
+
+In three-dimensional case the approach for testing is still the same but with
+different parameters to speed up calculations. We choose $R = 20$,
+$\lambda = 3\cdot10^{-5}$ and $s = 500$. The correlation functions are
+calculated in three axial directions with periodic boundary conditions and the
+result is also averaged across the directions as in two-dimensional
+case. We take six realizations of Poisson process for averaging the results
+which are presented on \cref{fig:3d}.
+
+Pore size and chord length functions are calculated using the side of a cube
+$s = 700$. The results are presented on \cref{fig:pscl}.
+
+The results for three-dimensional case are seemingly worse than for
+two-dimensional case. This can be explained by a reduced number of realizations
+of Poisson process and smaller value of $s$.
+
+\onecolumngrid
+\begin{figure*}[t]
+  \centering
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/l2-2d.png}
+    \caption[]{{\small Lineal-path correlation function}}
+    \label{fig:l2-2d}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/s2-2d.png}
+    \caption[]{{\small Two-point correlation function}}
+    \label{fig:s2-2d}
+  \end{subfigure}
+  \vskip\baselineskip
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/ss-2d.png}
+    \caption[]{{\small Surface-surface correlation function}}
+    \label{fig:ss-2d}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/sv-2d.png}
+    \caption[]{{\small Surface-void correlation function}}
+    \label{fig:sv-2d}
+  \end{subfigure}
+  \caption[]{\small A comparison of calculated values of $L_2(r)$, $S_2(r)$,
+    $F_{ss}(r)$ and $F_{sv}(r)$ with theoretical values for overlapping disks.}
+  \label{fig:2d}
+\end{figure*}
+
+\begin{figure*}[t]
+  \centering
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/l2-3d.png}
+    \caption[]{{\small Lineal-path correlation function}}
+    \label{fig:l2-3d}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/s2-3d.png}
+    \caption[]{{\small Two-point correlation function}}
+    \label{fig:s3-3d}
+  \end{subfigure}
+  \vskip\baselineskip
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/ss-3d.png}
+    \caption[]{{\small Surface-surface correlation function}}
+    \label{fig:ss-3d}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/sv-3d.png}
+    \caption[]{{\small Surface-void correlation function}}
+    \label{fig:sv-3d}
+  \end{subfigure}
+  \caption[]{\small A comparison of calculated values of $L_2(r)$, $S_2(r)$,
+    $F_{ss}(r)$ and $F_{sv}(r)$ with theoretical values for overlapping balls.}
+  \label{fig:3d}
+\end{figure*}
+
+\begin{figure*}[t]
+  \centering
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/ps-2d.png}
+    \caption[]{{\small Pore size correlation function (2D)}}
+    \label{fig:ps-2d}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/cl-2d.png}
+    \caption[]{{\small Chord length correlation function (2D)}}
+    \label{fig:cl-2d}
+  \end{subfigure}
+  \vskip\baselineskip
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/ps-3d.png}
+    \caption[]{{\small Pore size correlation function (3D)}}
+    \label{fig:ps-3d}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/cl-3d.png}
+    \caption[]{{\small Chord length correlation function (3D)}}
+    \label{fig:cl-3d}
+  \end{subfigure}
+  \caption[]{\small A comparison of calculated values of $P(r)$ and $p(r)$
+    with theoretical values for overlapping disks (\cref{fig:ps-2d} and
+    \cref{fig:cl-2d}) and balls(\cref{fig:ps-3d} and \cref{fig:cl-3d}).}
+  \label{fig:pscl}
+\end{figure*}
+\twocolumngrid
 

### 2021-06-28 timings/timings.jl
Time of execution for different functions

@@ -1,0 +1,35 @@
+using ValueNoise
+using CorrelationFunctions
+using Statistics
+using DelimitedFiles
+
+getdata(side, :: Val{2}) =
+    [value_noise(5x/side, 5y/side, 0.0, 5, 34365) < 0.5 for x in 1:side, y in 1:side]
+
+getdata(side, :: Val{3}) =
+    [value_noise(5x/side, 5y/side, 5z/side, 5, 34365) < 0.5 for x in 1:side, y in 1:side, z in 1:side]
+
+#const data_2d = [getdata(side, Val(2)) for side in 1000:1000:10000]
+const data_3d = [getdata(side, Val(3)) for side in 50:50:500]
+
+function calculate_time!(fn, dim)
+    sides = Vector{Int}(undef, 0)
+    times = Vector{Float64}(undef, 0)
+    data_arrays = (dim == 2) ? data_2d : data_3d
+
+    for data in data_arrays
+        side = size(data, 1)
+        push!(sides, side)
+        println(side)
+        #time = sum(let time = time_ns(); fn(data, 1); time_ns() - time end for i in 1:5) / 5
+        time = sum(let time = time_ns(); fn(data, 1); time_ns() - time end for i in 1:2) / 2
+        push!(times, time / 10^9)
+    end
+
+    res = hcat(sides, times)
+    open("/home/vasily/timings/$(fn)-$(dim)d.dat", "w") do io
+        writedlm(io, res)
+    end
+    
+    return res
+end

### 2021-06-29 paper-correlations.tex
Add a section about actual execution times for Directional module

@@
 
-The efficiency of \code{s2sep} is $O(n\:log\,n)$ and efficiency of
+The efficiency of \code{s2sep} is $O(n\log n)$ and efficiency of
 \code{s2insep} is $O(n^2)$ where $n$ is the length of the array.
@@
 The edges are extracted by calculating $|S(array)|$ where $S$ is the Sobel
-operator. \textbf{TODO: Cite our first paper}.
+operator. \textbf{TODO: Cite our first paper}. Algorithmic efficiency of these
+algorithms are $O(n\log n)$ because it's implemented using \code{s2sep} and
+filtering to extract edges is $O(n)$.
 
@@
 \end{algorithmic}
+Algorithmic efficiency is $O(n)$ where $n$ is the number of elements in the
+input array.
 
@@
 $i$. This function, again, can be calculated by cutting slices from a
-multidimensional array. The algorithm is as follows:
+multidimensional array. The algorithm which works in $O(n)$ time where $n$ is
+the number of elements in the input is as follows:
 \begin{algorithmic}[1]
@@
 
+\section{Efficiency of our algorithms}
+
+To measure efficiecy of our algorithms we use a machine with the following
+configuration:
+\begin{itemize}
+\item \textbf{CPU}: AMD Ryzen 5 1600X running at 2200~MHz
+\item \textbf{Memory}: 32~Gb DDR4-2400 memory
+\item \textbf{GPU}: \textbf{Insert nvidia gpu here}
+\end{itemize}
+
+We generate two (resp. three) dimensional square (resp. cubic) binary arrays
+with different number of elements. The arrays are filled with thresholded value
+noise using \code{ValueNoise.jl} package and this code:
+\begin{verbatim}
+using ValueNoise
+
+getdata(side, dims :: Integer) =
+    getdata(side, Val(dims))
+
+getdata(side, :: Val{2}) =
+    [value_noise(5x/side,
+                 5y/side,
+                 0.0,
+                 5, 34365) < 0.5
+     for x in 1:side, y in 1:side]
+
+getdata(side, :: Val{3}) =
+    [value_noise(5x/side,
+                 5y/side,
+                 5z/side,
+                 5, 34365) < 0.5
+     for x in 1:side, y in 1:side, z in 1:side]
+\end{verbatim}
+An example of a two-dimensional image generated in this way is on
+\cref{fig:valuenoise}. The function \code{getdata} generates the same image
+sampled with different resolutions. For two-dimensional case we generate ten
+arrays with the side of a square $s = 1000, 2000, \dots, 10000$ pixels and
+measure execution time for each function. For three-dimensional case we measure
+execution time for ten cubic arrays with the side $s = 50, 100, \dots, 500$. The
+result for \code{Directional} module is on \cref{fig:timings}. All functions are
+calculated with default values of optional arguments (that is: closed walls
+boundary conditions and computation along axial directions).
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=.3\textwidth]{images/timing-image.png}
+  \caption[]{{\small An example of 2D image used in timing measurements}}
+  \label{fig:valuenoise}
+\end{figure}
+
+\onecolumngrid
+\begin{figure*}[t]
+  \centering
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/time-2d.png}
+    \caption[]{{\small Two-dimensional case}}
+    \label{fig:timings-2d}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/time-3d.png}
+    \caption[]{{\small Three-dimensional case}}
+    \label{fig:timings-3d}
+  \end{subfigure}
+  \caption[]{\small Execution times for different functions from
+    \code{Directional} module.}
+  \label{fig:timings}
+\end{figure*}
+\twocolumngrid
+
 \appendix

### 2021-06-29 timings/plot-timings.py

@@ -1,0 +1,40 @@
+#!/usr/local/bin/python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+names2d = [
+    'l2-2d.dat', 's2-2d.dat',
+    'surfsurf-2d.dat', 'surfvoid-2d.dat',
+    'pore_size-2d.dat', 'chord_length-2d.dat'
+]
+
+names3d = [
+    'l2-3d.dat', 's2-3d.dat',
+    'surfsurf-3d.dat', 'surfvoid-3d.dat',
+    'pore_size-3d.dat', 'chord_length-3d.dat'
+]
+
+markers = [
+    '.', 'o', 's', 'p', '^', 'v'
+]
+
+data2d = [np.loadtxt(name) for name in names2d]
+data3d = [np.loadtxt(name) for name in names3d]
+
+labels = [
+    'Lineal-path function', 'Two-point function',
+    'Surface-surface function', 'Surface-void function',
+    'Pore size function', 'Chord length function'
+]
+
+plt.figure(dpi = 300)
+
+for data, marker in zip(data3d, markers):
+    data[:, 0] = data[:, 0] ** 3
+    plt.plot(data[:, 0], data[:, 1], marker = marker)
+
+plt.legend(labels)
+plt.xlabel('Number of voxels')
+plt.ylabel('Time of execution, seconds')
+plt.savefig('time-3d.png')

### 2021-06-29 paper-correlations.tex
Write a section about execution time

@@
 \cref{fig:valuenoise}. The function \code{getdata} generates the same image
-sampled with different resolutions. For two-dimensional case we generate ten
-arrays with the side of a square $s = 1000, 2000, \dots, 10000$ pixels and
-measure execution time for each function. For three-dimensional case we measure
-execution time for ten cubic arrays with the side $s = 50, 100, \dots, 500$. The
-result for \code{Directional} module is on \cref{fig:timings}. All functions are
-calculated with default values of optional arguments (that is: closed walls
-boundary conditions and computation along axial directions).
+sampled with different resolutions.
+
+To measure efficiency of \code{Directional} module we generate ten arrays with
+a side of a square $s = 1000, 2000, \dots, 10000$ pixels for two-dimensional
+case and ten arrays with a side of a cube $s = 50, 100, \dots, 500$ voxels for
+three-dimensional case and calculate execution time for each function. All
+functions are calculated with default values of optional arguments (that is:
+closed walls boundary conditions and computation along axial directions).
+
+To measure efficiency of \code{Map} module we follow the same procedure but with
+seven arrays usings squares with a side $s = 1000, 2000, \dots, 7000$ pixels and
+cubes with a side $s = 50, 100, \dots, 350$ voxels.
+
+The measurements of execution time is on \cref{fig:timings}.
+
+\textbf{TODO: alogithmic efficiency for two and three dimensions as a function
+  of number of elements.}
 
@@
     \includegraphics[width=\textwidth]{images/time-2d.png}
-    \caption[]{{\small Two-dimensional case}}
+    \caption[]{{\small Two-dimensional case, module \code{Directional}}}
     \label{fig:timings-2d}
@@
     \includegraphics[width=\textwidth]{images/time-3d.png}
-    \caption[]{{\small Three-dimensional case}}
+    \caption[]{{\small Three-dimensional case, module \code{Directional}}}
     \label{fig:timings-3d}
   \end{subfigure}
-  \caption[]{\small Execution times for different functions from
-    \code{Directional} module.}
+    \vskip\baselineskip
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/time-2d-map.png}
+    \caption[]{{\small Two-dimensional case, module \code{Map}}}
+    \label{fig:timings-2d-map}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/time-3d-map.png}
+    \caption[]{{\small Three-dimensional case, module \code{Map}}}
+    \label{fig:timings-3d-map}
+  \end{subfigure}
+  \caption[]{\small Execution times for different correlation functions.}
   \label{fig:timings}

### 2021-07-02 paper-correlations.tex
Remove confusing TODO
Add some words about GPU

@@
 \item \textbf{Memory}: 32~Gb DDR4-2400 memory
-\item \textbf{GPU}: \textbf{Insert nvidia gpu here}
+\item \textbf{GPU}: Nvidia GeForce GTX 1650 with 4~Gb video memory
 \end{itemize}
@@
 seven arrays usings squares with a side $s = 1000, 2000, \dots, 7000$ pixels and
-cubes with a side $s = 50, 100, \dots, 350$ voxels.
+cubes with a side $s = 50, 100, \dots, 350$ voxels. The surface-void correlation
+functions on \cref{fig:timings-2d-gpu} and \cref{fig:timings-3d-gpu} are
+calculates with a lesser number of sides because it's too demanding in video
+memory.
 
-The measurements of execution time is on \cref{fig:timings}.
+Also many functions in \code{Map} module can utilize Nvidia's GPUs using the
+CUDA library. For example, two-point correlation function uses FFT transform
+optimized for Nvidia GPUs and provided in \code{CUDA.FFT} package. The choice
+between CPU or GPU version is made depending on type of input array. If it's
+\code{CuArray} rather than generic \code{AbstractArray} then CUDA implementation
+is chosen.
 
-\textbf{TODO: alogithmic efficiency for two and three dimensions as a function
-  of number of elements.}
+The measurements of execution time is on \cref{fig:timings}. As you can see, GPU
+versions (when available) are faster than CPU versions and limited only by
+amount of video memory. Functions in \code{Directional} are slower (with
+exception of the lineal-path function) but are also useful in media
+reconstruction algorithms which utilize simulated annealing.
 
@@
     \includegraphics[width=\textwidth]{images/time-2d-map.png}
-    \caption[]{{\small Two-dimensional case, module \code{Map}}}
+    \caption[]{{\small Two-dimensional case, module \code{Map}, CPU}}
     \label{fig:timings-2d-map}
@@
     \includegraphics[width=\textwidth]{images/time-3d-map.png}
-    \caption[]{{\small Three-dimensional case, module \code{Map}}}
+    \caption[]{{\small Three-dimensional case, module \code{Map}, CPU}}
     \label{fig:timings-3d-map}
+  \end{subfigure}
+  \vskip\baselineskip
+    \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/time-2d-gpu.png}
+    \caption[]{{\small Two-dimensional case, module \code{Map}, GPU}}
+    \label{fig:timings-2d-gpu}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/time-3d-gpu.png}
+    \caption[]{{\small Three-dimensional case, module \code{Map}, GPU}}
+    \label{fig:timings-3d-gpu}
   \end{subfigure}

### 2021-07-02 timings/plot-timings.py

@@ -4,28 +4,31 @@ import numpy as np
 import matplotlib.pyplot as plt
 
 names2d = [
-    'l2-2d.dat', 's2-2d.dat',
-    'surfsurf-2d.dat', 'surfvoid-2d.dat',
-    'pore_size-2d.dat', 'chord_length-2d.dat'
+    'gpu/s2-2d.dat',
+    'gpu/surfsurf-2d.dat',
+    'gpu/surfvoid-2d.dat',
+    'gpu/c2-2d.dat',
 ]
 
 names3d = [
-    'l2-3d.dat', 's2-3d.dat',
-    'surfsurf-3d.dat', 'surfvoid-3d.dat',
-    'pore_size-3d.dat', 'chord_length-3d.dat'
+    'gpu/s2-3d.dat',
+    'gpu/surfsurf-3d.dat',
+    'gpu/surfvoid-3d.dat',
+    'gpu/c2-3d.dat',
 ]
 
 markers = [
-    '.', 'o', 's', 'p', '^', 'v'
+    '.', 'o', 's', 'p'
 ]
 
 data2d = [np.loadtxt(name) for name in names2d]
 data3d = [np.loadtxt(name) for name in names3d]
 
 labels = [
-    'Lineal-path function', 'Two-point function',
-    'Surface-surface function', 'Surface-void function',
-    'Pore size function', 'Chord length function'
+    'Two-point function',
+    'Surface-surface function',
+    'Surface-void function',
+    'Cluster function'
 ]
 
 plt.figure(dpi = 300)

### 2021-07-07 paper-correlations.tex
Change few words

@@
 \item \textbf{Memory}: 32~Gb DDR4-2400 memory
-\item \textbf{GPU}: Nvidia GeForce GTX 1650 with 4~Gb video memory
+\item \textbf{GPU}: Nvidia Tesla V100 with 32~Gb video memory
 \end{itemize}
@@
 We generate two (resp. three) dimensional square (resp. cubic) binary arrays
-with different number of elements. The arrays are filled with thresholded value
-noise using \code{ValueNoise.jl} package and this code:
-\begin{verbatim}
-using ValueNoise
-
-getdata(side, dims :: Integer) =
-    getdata(side, Val(dims))
-
-getdata(side, :: Val{2}) =
-    [value_noise(5x/side,
-                 5y/side,
-                 0.0,
-                 5, 34365) < 0.5
-     for x in 1:side, y in 1:side]
-
-getdata(side, :: Val{3}) =
-    [value_noise(5x/side,
-                 5y/side,
-                 5z/side,
-                 5, 34365) < 0.5
-     for x in 1:side, y in 1:side, z in 1:side]
-\end{verbatim}
-An example of a two-dimensional image generated in this way is on
-\cref{fig:valuenoise}. The function \code{getdata} generates the same image
-sampled with different resolutions.
+with different number of elements. Each element $a_{ij}$ (resp. $a_{ijk}$) of a
+two-dimensional (resp. three-dimensional) array is calculated as follows:
+\begin{align*}
+  a_{ij} & = \left\{
+  \begin{array}{ll}
+    0 & \quad vn(5i/s, 5j/s, 0, 5, 34365) < 0.5 \\
+    1 & \quad \text{otherwise}
+  \end{array}
+  \right. \\
+  a_{ijk} & = \left\{
+  \begin{array}{ll}
+    0 & \quad vn(5i/s, 5j/s, 5k/s, 5, 34365) < 0.5 \\
+    1 & \quad \text{otherwise}
+  \end{array}
+  \right.
+\end{align*}
+Here $vn(x,y,z,o,s)$ is a value noise function. We fix a number of
+octaves $o = 5$ and a random seed $s = 34365$. The particular implementation for
+our measurements was taken from \code{ValueNoise.jl} package. An example of a
+two-dimensional image generated in this way is on \cref{fig:valuenoise}.
 
@@
 
-To measure efficiency of \code{Map} module we follow the same procedure but with
-seven arrays usings squares with a side $s = 1000, 2000, \dots, 7000$ pixels and
-cubes with a side $s = 50, 100, \dots, 350$ voxels. The surface-void correlation
-functions on \cref{fig:timings-2d-gpu} and \cref{fig:timings-3d-gpu} are
-calculates with a lesser number of sides because it's too demanding in video
-memory.
-
-Also many functions in \code{Map} module can utilize Nvidia's GPUs using the
-CUDA library. For example, two-point correlation function uses FFT transform
-optimized for Nvidia GPUs and provided in \code{CUDA.FFT} package. The choice
-between CPU or GPU version is made depending on type of input array. If it's
-\code{CuArray} rather than generic \code{AbstractArray} then CUDA implementation
-is chosen.
+With the \code{Map} module we follow the same procedure. Many functions in
+\code{Map} can utilize Nvidia's GPUs using the CUDA library. For example,
+two-point correlation function uses FFT transform optimized for Nvidia GPUs and
+provided in \code{CUDA.FFT} package. We provide execution times for bot CPU and
+GPU. The choice between CPU or GPU version is made depending on type of input
+array. If it's \code{CuArray} rather than generic \code{AbstractArray} then CUDA
+implementation is chosen.
 
@@
 amount of video memory. Functions in \code{Directional} are slower (with
-exception of the lineal-path function) but are also useful in media
+exception of the lineal-path function) but are also useful in medium
 reconstruction algorithms which utilize simulated annealing.

### 2021-07-08 paper-correlations.tex
Introduction

@@
 \author{Vasily Postnicov}
-\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of Sciences, Moscow, 123242, Russia}
+\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of
+  Sciences, Moscow, 123242, Russia}
 \author{Alexey I. Samarin}
-\altaffiliation{Computational Mathematics and Cybernetics, Lomonosov Moscow State University, Moscow, 119991, Russia}
-\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of Sciences, Moscow, 123242, Russia}
+\altaffiliation{Computational Mathematics and Cybernetics, Lomonosov Moscow
+  State University, Moscow, 119991, Russia}
+\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of
+  Sciences, Moscow, 123242, Russia}
+\author{Efim V. Lavrukhin}
+\altaffiliation{Computational Mathematics and Cybernetics, Lomonosov Moscow
+  State University, Moscow, 119991, Russia}
+\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of
+  Sciences, Moscow, 123242, Russia}
 \author{Marina V. Karsanina}
-\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of Sciences, Moscow, 123242, Russia}
-\author{Efim V. Lavrukhin}
-\altaffiliation{Computational Mathematics and Cybernetics, Lomonosov Moscow State University, Moscow, 119991, Russia}
-\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of Sciences, Moscow, 123242, Russia}
+\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of
+  Sciences, Moscow, 123242, Russia}
+\author{Mathieu Gravey}
+\altaffiliation{University of Lausanne, Faculty of Geosciences and Environment,
+  Institute of Earth Surface Dynamics, Lausanne, Switzerland}
 \author{Kirill M. Gerke}
 \email[E-mail:]{kg@ifz.ru}
-\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of Sciences, Moscow, 123242, Russia}
+\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of
+  Sciences, Moscow, 123242, Russia}
 
-\title{Something about correlation functions}
+\title{Evaluation of classical correlation functions from 2/3D images on CPU and
+  GPU architectures: introducing CorrelationFunctions.jl}
 
@@
 \maketitle
+
+\section{Background and motivation}
+Materials are ubiquitous both in nature and in industrial human activities, and
+their physical properties are interconnected to
+structure\cite{Torq_book}\cite{Sahimi_book}\cite{Adler_book}. The information
+about the structure usually comes in the way of 2D and 3D images obtained by
+microscopy, tomography and other related methodologies. This structural
+information can be used for numerous types of analysis, including simulations of
+different processes within studied materials or evaluation of their properties
+using so-called pore-scale modelling. Unlike computational modelling techniques
+a whole class of approximate methods exists including (rigorous) bounds that
+allows very fast estimations of physical properties albeit the bounds themselves
+are too wide to be applicable in majority of practical problems. Nonetheless, it
+is noteworthy that such bounds are originally based on structural descriptors in
+the form of correlation functions.
+
+Two ways exist to obtain correlation functions for a given structure at hand:
+measure them either experimentally with the help of scattering intensity or
+from digital images. None is perfect, as the first approach suffers from the
+limitation of CFs that can be obtained this way, while the second one provides
+information with limited resolution or/and resolution to field-of-view ratio. In
+addition to the resolution conundrum, the most useful imaging methods such as
+X-ray computed tomography (XCT) and scanning electron microscopy (SEM) provide
+gray-scale images (e.g., X-ray attenuation or electron back-scattering
+distributions) due to their underlying physical principles and require labeling
+of constituent phases (this is called segmentation) before computation of
+CFs. If properly segmented, high-resolution digital images do provide a
+possibility to compute any correlation function and, thus, possibility to
+address numerous fundamental and practical research problems.
+
+Correlation functions (CFs) as invaluable universal descriptors of structure are
+utilized in a multitude of scientific disciplines: material sciences, rock
+physics, soil physics and hydrology, cosmology and food engineering, biology and
+many others. Computed from 2D and 3D images, CFs can be applied to:
+\begin{enumerate}
+  \item to characterize the morphology and representativeness via correlation
+    lengths;
+  \item to perform stochastic reconstructions from experimentally measured CFs
+    or 2D to 3D reconstructions based on CFs that can be extracted from less
+    dimensions or through penetrable sphere model;
+  \item compare different structures to each other, including verification of
+    stochastic reconstructions;
+  \item compress structural information in the form of raw or parameterized CFs
+    with the possibility to recover the structure using stochastic
+    reconstruction
+  \item describe structural dynamics under different boundary conditions;
+  \item extract structural features for deep learning;
+  \item fuse multi-scale images and structural information as obtained by
+    different methods into a single digital model;
+  \item quantify spatial heterogeneity.
+\end{enumerate}
+
+Stochastic reconstruction is a separate huge topic, as this approach allows to
+solve an inverse problem and recover structure from known set of correlation
+functions. This ability for recovery serves as the basis for majority of usages
+in the list above. While it is necessary to compute CFs from digital images as a
+target set for stochastic reconstructions, they rely more on efficient
+recomputations or optimizations, e.g., re-evaluation during simulated
+annealing. Such optimizations are not the part of the computational package and
+are not considered in this work.
+
+There are different types of correlation functions that in general describe some
+probabilities. The main parameter of any correlation function is the number of
+points that are utilized to evaluate such a probability. While so-called
+$n$-point probability function\cite{Torq_book} will totally describe any
+structure in the limit of $n \rightarrow$ number of voxels/pixels on the image,
+computing or storing such a function is not practical. Based on information
+content, it was shown that increasing the number of point $n > 2$ only
+marginally improves the quality of the structure quantification and these
+improvements decay with increasing $n$. For stochastic reconstruction purposes
+computation of higher-order statistics will, arguably, not be balanced by
+increased number of points, but this is the topic of active research. For
+aforementioned reasons, we mainly focus on 2-point statistics, leaving the
+possibility to include higher order CFs in the future work. The simplest 2-point
+probability function ($S_2$ or autocorrelation) actually arise from small angle
+scattering experiments and measures the probability that both ends of line
+segment with a given length fall into the same phase. Other types include the
+probability of a whole line segment to fall into the phase ($L_2$ function) or
+to lie on the interface between phases ($F_{ss}$ function), and mainly originate
+from aforementioned bounds on physical properties such as permeability and
+elasticity. The general idea of computation of different 2-point CFs is shown in
+\cref{fig:functions}. All major details and numerous analytical cases can be
+found in seminal work of Torquato \cite{Torq_book}. To all CFs described in this
+book and applicable to digital images we shall refer as to classical correlation
+functions.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=.3\textwidth]{images/corr.png}
+  \caption[]{{\small WTF?}}
+  \label{fig:functions}
+\end{figure}
+
+While evaluation of correlation functions from 2D and 3D images was a topic of
+numerous research papers, the information is highly fragmented, especially in
+terms of algorithms and their implementation in the code. Some snippets of code
+are available for some functions, but they lack general API and are usually
+implemented in proprietary interpreted languages such as Matlab. Due to a recent
+leap forward in GPU-based computations, some papers describe computations on
+this architecture, but the code is usually not provided. All in all, the
+efficient and open-source single API solution utilizing both CPU and GPU
+architectures is currently absent.
+
+The aim of this paper is to establish a general open-source solution allowing to
+compute all classical correlation functions. This solution should be well
+documented with all computational algorithms explained, it should also leverage
+on recent advances in programming high-intensity computations and utilize both
+CPU and GPU power. Our answer in the form of \code{CorrelationFunctions.jl}
+package allows to compute numerous CFs easily under any operating system. The
+manuscript describing the package is organized as follows: in \cref{scansec} we
+provide all algorithmic details for CFs computation in directions (scanning
+method). \cref{mapsec} presents all algorithmic details for computing full CFs
+maps (map method, full 2-point statistics for a given image). In \cref{verisec}
+we verify the all computations based on known analytical
+solutions. \cref{effisec} deals with computational efficiency of our code, we
+compare computational times for 2D and 3D images of different sizes for scanning
+and map methods as evaluated using either CPU or GPU. In \cref{exasec} some
+application examples are provided, including CFs evaluation for multi-phase
+materials. Finally, \cref{sumsec} summarizes all results and outlines possible
+future improvements.
 
@@
 \section{Verifying our algorithms}
+\label{verisec}
 To verify our package we use random datasets of overlapping disks (the number of
@@
 \section{Efficiency of our algorithms}
-
+\label{effisec}
 To measure efficiecy of our algorithms we use a machine with the following
@@
 
+\section{Examples and applications}
+\label{exasec}
+Text
+
+\section{Summary}
+\label{sumsec}
+Text
+
 \appendix
@@
 \end{algorithmic}
+
+\onecolumngrid
+\bibliography{habib}
+\bibliographystyle{plain}
+\twocolumngrid
+
 \end{document}

### 2021-07-08 paper-correlations.tex
New shitplots

@@
 (usually we restrict ourselves to integer numbers of type \code{Int} or
-\code{Int8}) and treats them as homogeneous anisotropic media.
+\code{Int8}) and treats them as homogeneous anisotropic media. The package can
+understand two-phase as well as multiphase systems. Indeed, a multiphase system
+$A$ can be easily converted to a two-phase system $B$ by applying an indicator
+function $\chi(x)$ to each element of $A$ which can be written as $B = \chi(A)$.
 
@@
 two-point correlation function uses FFT transform optimized for Nvidia GPUs and
-provided in \code{CUDA.FFT} package. We provide execution times for bot CPU and
+provided in \code{CUDA.FFT} package. We provide execution times for both CPU and
 GPU. The choice between CPU or GPU version is made depending on type of input
 array. If it's \code{CuArray} rather than generic \code{AbstractArray} then CUDA
-implementation is chosen.
+implementation is chosen. Please note, that CPU versions are much slower, so we
+choose a different sides of squares ($s = 700, 1350, \dots, 7000$) and cubes
+($s = 10, 45, \dots, 350$) for evaluation of the performance.
 

### 2021-07-13 paper-correlations.tex
Minor edits + few words about cross-correlation functions

@@
 \item Chord length function $p$.
+\item Phase cross-correlation function $\rho_{ij}$
 \end{itemize}
@@
 one-dimensional array is computed using the algorithm described in
-\apref{linpathalg}. A multidimensional arrays is firstly cut in slices as
-described above and \code{l2} function is calculated for each slice returning
-\code{success} and \code{total} arrays. These arrays are then accumulated as
-described in \cref{scansec} for final calculation of $L_2^{(i)}(\bm{r})$
-function.
+\apref{linpathalg}. A multidimensional arrays is firstly cut in slices and
+\code{l2} function is calculated for each slice returning \code{success} and
+\code{total} arrays. These arrays are then accumulated as described in
+\cref{scansec} for final calculation of $L_2^{(i)}(\bm{r})$ function.
 
 \subsection{Two-point function}
+\label{sec:s2}
 Two-point correlation function $S_2^{(i)}(\bm{r})$ is defined as the probability
@@
 bit more general definition for it:
-\begin{equation*}
+\begin{equation}
   S_2^{\chi}(\bm{r}) = \langle \chi(\bm{x}, \bm{x} + \bm{r}) \rangle
-\end{equation*}
-where $\chi(\bm{x})$ is some arbitrary indicator (or membership) function and
-$\bm{x} \in \mathbb{R}^{2n}$ where $n$ is dimensionality of the input array. The
-vector $\bm{x}$ is constructed as $(\bm{x_1}, \bm{x_2})$ where $\bm{x_1}$ and
-$\bm{x_2}$ are the coordinates of the both ends of a line segment thrown into
-the input array.
+  \label{eq:s2gen}
+\end{equation}
+where $\chi(\bm{x_1}, \bm{x_2})$ can be understood as some arbitrary indicator
+(or membership) function on $\mathbb{R}^{2n}$ where $n$ is dimensionality of the
+input array. Vectors $\bm{x_1}$ and $\bm{x_2}$ are the coordinates of the both
+ends of a line segment thrown into the input array.
 
-If $\chi(\bm{x})$ can be expressed as
-$\chi(\bm{x}) = \chi_1(\bm{x_1})\chi_2(\bm{x_2})$ (what we call
+If $\chi(\bm{x_1}, \bm{x_2})$ can be expressed as
+$\chi(\bm{x_1}, \bm{x_2}) = \chi_1(\bm{x_1})\chi_2(\bm{x_2})$ (what we call
 \code{SeparableIndicator} in our package) we use the following algorithm to
-calculate the array \code{success} for one-dimensional slice:
+calculate the array \code{success} for one-dimensional slice $a$:
 \begin{algorithmic}[1]
-  \Procedure{s2sep}{$array, \chi_1, \chi_2, periodic$}
+  \Procedure{s2sep}{$a, \chi_1, \chi_2, periodic$}
   \If{$!periodic$}
-    \State $array \gets array \odot zeros(length(array))$ \Comment{$\odot$
+    \State $a \gets a \odot zeros(length(a))$ \Comment{$\odot$
       denotes concatenation and $zeros(n)$ returns an array with $n$ zeros.}
   \EndIf
-  \State $ind1 \gets \chi_1(array)$ \Comment{apply $\chi_1$ element-wise to $array$}
-  \State $ind2 \gets \chi_2(array)$ \Comment{apply $\chi_2$ element-wise to $array$}
-  \State $ft1 \gets rfft(ind1)$ \Comment{$rfft$ is fast Fourier transform for
+  \State $a_1 \gets \chi_1(a)$ \Comment{apply $\chi_1$ element-wise to $a$}
+  \State $a_2 \gets \chi_2(a)$ \Comment{apply $\chi_2$ element-wise to $a$}
+  \State $f_1 \gets rfft(a_1)$ \Comment{$rfft$ is fast Fourier transform for
     real-valued data}
-  \State $ft2 \gets rfft(ind2)$
-  \State $s2ft \gets ft1 \cdot \overline{ft2}$ \Comment{multiply element-wise}
-  \State $success \gets irfft(s2ft)$ \Comment{$irfft$ is inverse of $rfft$}
+  \State $f_2 \gets rfft(a_2)$
+  \State $f_{S_2} \gets f_1 \cdot \overline{f_2}$ \Comment{multiply element-wise}
+  \State $success \gets irfft(f_{S_2})$ \Comment{$irfft$ is inverse of $rfft$}
   \State \textbf{return} $success$
@@
 \begin{algorithmic}[1]
-  \Procedure{s2insep}{$array, \chi, periodic$}
-    \State $len \gets length(array)$
+  \Procedure{s2insep}{$a, \chi, periodic$}
+    \State $len \gets length(a)$
     \If{$periodic$}
-      \State $array \gets array \odot array$
+      \State $a \gets a \odot a$
     \EndIf
@@
     \For{$shift \gets 0,len-1$}
-      \State $array2 \gets subseq(array, shift)$
-      \Comment{$subseq$ returns subsequence of $array$ from the $shift$-th element
+      \State $a_2 \gets subseq(a, shift)$
+      \Comment{$subseq$ returns subsequence of $a$ from the $shift$-th element
         to the end.}
-      \State $array[shift] \gets sum(map(\chi, array, array2))$
+      \State $success[shift] \gets sum(map(\chi, a, a_2))$
     \EndFor
@@
 The algorithm for calculation of the array \code{success} for
-$C_2^{(i)}(\bm{r})$ for one-dimensional slice is straightforward:
+$C_2^{(i)}(\bm{r})$ for one-dimensional slice $a$ is straightforward:
 \begin{algorithmic}[1]
-  \Procedure{c2}{$array, phase, periodic$}
-  \State $ind \gets array = phase$ \Comment{$array$ is compared with $phase$
+  \Procedure{c2}{$a, phase, periodic$}
+  \State $a_1 \gets x = phase$ \Comment{$a$ is compared with $phase$
     element-wise}
-  \State $clusters \gets clusterize(ind)$
+  \State $c \gets clusterize(a_1)$
   \Comment{$clusterize(x)$ selects clusters from the array
@@
   \State $\chi(x,y) \gets (x = y \ne 0)$
-  \State \textbf{return} $s2insep(clusters, \chi, periodic)$
+  \State \textbf{return} $s2insep(c, \chi, periodic)$
   \EndProcedure
@@
 The algorithm for calculation of the array \code{success} for
-$F_{ss}^{(i)}(\bm{r})$ for one-dimensional slice is also straightforward:
+$F_{ss}^{(i)}(\bm{r})$ for one-dimensional slice $a$is also straightforward:
 \begin{algorithmic}[1]
-  \Procedure{surfsurf}{$array, phase, periodic$}
-    \State $ind \gets array = phase$ \Comment{$array$ is compared with $phase$
-      element-wise}
-    \State $edge \gets \text{Detect edges in $ind$}$
-    \State \textbf{return} $s2sep(edge, identity, identity, periodic)$
-    \Comment{$identity(x) = x$}
+  \Procedure{surfsurf}{$a, phase, periodic$}
+    \State $a_1 \gets a = phase$
+    \State $edge \gets \text{Detect edges in $a_1$}$
+    \State \textbf{return} $s2sep(edge, E, E, periodic)$
+    \Comment{$E(x) = x$}
   \EndProcedure
@@
 The algorithm for calculation of the array \code{success} for
-$F_{sv}^{(i)}(\bm{r})$ for one-dimensional slice is very similar to the previous
-one:
+$F_{sv}^{(i)}(\bm{r})$ for one-dimensional slice $a$ is very similar to the
+previous one:
 \begin{algorithmic}[1]
-  \Procedure{surfvoid}{$array, phase, periodic$}
-    \State $ind \gets array = phase$ \Comment{$array$ is compared with $phase$
-      element-wise}
-    \State $edge \gets \text{Detect edges in $ind$}$
-    \State $indices \gets \text{Array of all indices in $array$}$
+  \Procedure{surfvoid}{$a, phase, periodic$}
+    \State $a_1 \gets a = phase$
+    \State $edge \gets \text{Detect edges in $a_1$}$
+    \State $indices \gets \text{Array of all indices in $a$}$
     \State $\chi_1(x) \gets edge[x]$
-    \State $\chi_2(x) \gets array[x] = 0$ \Comment{$0$ is a value reserved for the
+    \State $\chi_2(x) \gets a[x] = 0$ \Comment{$0$ is a value reserved for the
       void phase}
@@
 
-The edges are extracted by calculating $|S(array)|$ where $S$ is the Sobel
+The edges are extracted by calculating $|S(a)|$ where $S$ is the Sobel
 operator. \textbf{TODO: Cite our first paper}. Algorithmic efficiency of these
@@
 
-Our algorithm for calculating $P(r)$ for a two-phase system is the following:
+Our algorithm for calculating $P(r)$ for a two-phase system $a$ is the
+following:
 \begin{algorithmic}[1]
-  \Procedure{poresize}{$array, nbins$}
-    \State $d \gets dist(array)$ \Comment{$dist$ calculates
-      $\mathcal{D}(\bm{x})$ for each element of $array$}
+  \Procedure{poresize}{$a, nbins$}
+    \State $d \gets dist(a)$ \Comment{$dist(a)$ calculates
+      $\mathcal{D}(\bm{x})$ for each element of $a$}
     \State $f(x) \gets x \ne 0$
-    \State $positive \gets filter(d, f)$
-    \State Bin values in $positive$ to $nbins$ bins to compute a histogram $H$
+    \State $d' \gets filter(f, d)$
+    \State Bin values in $d'$ to $nbins$ bins to compute a histogram $H$
     \State \textbf{return} $H$
@@
 finding a chord of length between $|\bm{r}|$ and $|\bm{r} + d\bm{r}|$ and
-paralled to $\bm{r}$ in phase $i$. A chords is a line segment between
+paralled to $\bm{r}$ in phase $i$. A chord is a line segment between
 intersections of an infinitely long line with the interface of the phase
@@
 \begin{algorithmic}[1]
-  \Procedure{chordlength}{$array, phase, nbins$}
+  \Procedure{chordlength}{$a, phase, nbins$}
     \State $lengths \gets [\quad]$
-    \State $ind \gets array = phase$ \Comment{$array$ is compared with $phase$
-      element-wise}
-    \State $edgephase \gets maximum(array) + 1$ \Comment{``bogus'' phase for the
+    \State $a_1 \gets a = phase$
+    \State $p' \gets maximum(a) + 1$ \Comment{``bogus'' phase for the
       interface of the phase $phase$}
-    \State $edge \gets edgephase \cdot [\text{Detect edges in $ind$}]$ \Comment{We
+    \State $edge \gets p' \cdot [\text{Detect edges in $a_1$}]$ \Comment{We
       use distance transform here}
-    \State $combo = min(edge + array, edgephase)$ \Comment{Combine the original
+    \State $a_2 = min(edge + a, p')$ \Comment{Combine the original
       array and the interface for the phase $phase$}
-    \ForAll{$direction \in \{\text{Requested directions}\}$}
-      \ForAll{$slice \in \{\text{Slices parallel to $direction$}\}$}
+    \ForAll{$dir \in \{\text{Requested directions}\}$}
+      \ForAll{$s \in \{\text{Slices of $a_2$ parallel to $dir$}\}$}
         \State $len \gets 0$
         \State $startonedge \gets false$
-        \ForAll{$x \in slice$}
-          \If{$x = edgephase$}
+        \ForAll{$x \in s$}
+          \If{$x = p'$}
             \Comment{Edge found}
@@
 \end{algorithmic}
+
+\subsection{Phase cross-corellation function}
+
+Phase cross-correlation function $\rho_{ij}(\bm{r})$ can be defined as
+\begin{equation*}
+  \rho_{ij}(\bm{r}) = \langle I^{(i)}(\bm{x}) I^{(j)}(\bm{x} + \bm{r}) \rangle
+\end{equation*}
+which can be rewritten as \cref{eq:s2gen} with $\chi(\bm{x_1}, \bm{x_2})$
+defined as follows:
+\begin{equation*}
+  \chi(\bm{x_1}, \bm{x_2}) = I^{(i)}(\bm{x}) I^{(j)}(\bm{x})
+\end{equation*}
+Now to calculate cross-correlation function we can use \code{s2sep} function
+described in \cref{sec:s2}.
 
@@
 Here $vn(x,y,z,o,s)$ is a value noise function. We fix a number of
-octaves $o = 5$ and a random seed $s = 34365$. The particular implementation for
-our measurements was taken from \code{ValueNoise.jl} package. An example of a
-two-dimensional image generated in this way is on \cref{fig:valuenoise}.
+octaves $o = 5$ and a random seed $s = 34365$. The particular implementation of
+value noise for our measurements was taken from \code{ValueNoise.jl} package. An
+example of a two-dimensional image generated in this way is on
+\cref{fig:valuenoise}.
 
@@
 The algorithm below calculates $L_2^{(phase)}$ correlation function for
-one-dimensional array $array$. The result is an array of $L_2$ values for
+one-dimensional array $a$. The result is an array of $L_2$ values for
 correlation lengths from $0$ to $maxlen-1$. If $periodic$ is true (resp. false)
@@
 \begin{algorithmic}[1]
-  \Procedure{countruns}{$array, len, phase$}
+  \Procedure{countruns}{$a, len, phase$}
     \State $runslist \gets [\quad]$
     \State $runs \gets 0$
-    \ForAll{$x \in array$}
+    \ForAll{$x \in a$}
       \If{$x = phase$}
@@
   \\
-  \Procedure{updateruns}{$array, runs, n$}
+  \Procedure{updateruns}{$a, runs, n$}
     \For{$idx = 1,n$}
-      \State $array[idx] \gets array[idx] + runs$
+      \State $a[idx] \gets a[idx] + runs$
       \State $runs \gets runs - 1$
@@
   \\
-  \Procedure{updateperiodic}{$array, first, last, n$}
+  \Procedure{updateperiodic}{$a, first, last, n$}
     \State $sum \gets first + last$
@@
       \State $a \gets \min(idx - 1, first, last, sum - (idx - 1))$
-      \State $array[idx] \gets array[idx] + a$
+      \State $a[idx] \gets a[idx] + a$
     \EndFor
@@
   \\
-  \Procedure{l2}{$array, phase, maxlen, periodic$}
+  \Procedure{l2}{$a, phase, maxlen, periodic$}
     \State $success \gets zeros(maxlen)$
     \State $total \gets zeros(maxlen)$
-    \State $len \gets length(array)$
+    \State $len \gets length(a)$
     \State $nupdates \gets \min(len, maxlen)$
-    \State $runs \gets countruns(array, maxlen, phase)$
+    \State $runs \gets countruns(a, maxlen, phase)$
     \ForAll{$run \in runs$}
@@
     \If{$periodic$}
-      \State $first \gets first(array)$
-      \State $last \gets last(array)$
+      \State $first \gets first(a)$
+      \State $last \gets last(a)$
       \If{$first = last$}

### 2021-10-12 paper-correlations.tex
Use more recent RevTex
Modify misleading line
Replace subcaption with subfigure

@@
 \usepackage{graphicx}
-\usepackage{subcaption}
+\usepackage{subfigure}
 
@@
   \centering
-  \includegraphics[width=.3\textwidth]{images/corr.png}
-  \caption[]{{\small WTF?}}
+  \includegraphics[width=0.9\linewidth]{images/corr.png}
+  \caption[]{WTF?}
   \label{fig:functions}
@@
 
-\onecolumngrid
 \begin{figure*}[t]
   \centering
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/l2-2d.png}
-    \caption[]{{\small Lineal-path correlation function}}
-    \label{fig:l2-2d}
-  \end{subfigure}
+  \subfigure[Lineal-path correlation function]{
+    \includegraphics[width=0.475\linewidth]{images/l2-2d.png}
+    \label{fig:l2-2d}}
   \hfill
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/s2-2d.png}
-    \caption[]{{\small Two-point correlation function}}
-    \label{fig:s2-2d}
-  \end{subfigure}
+  \subfigure[Two-point correlation function]{
+    \includegraphics[width=0.475\linewidth]{images/s2-2d.png}
+    \label{fig:s2-2d}}
   \vskip\baselineskip
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/ss-2d.png}
-    \caption[]{{\small Surface-surface correlation function}}
-    \label{fig:ss-2d}
-  \end{subfigure}
+  \subfigure[Surface-surface correlation function]{
+    \includegraphics[width=0.475\linewidth]{images/ss-2d.png}
+    \label{fig:ss-2d}}
   \hfill
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/sv-2d.png}
-    \caption[]{{\small Surface-void correlation function}}
-    \label{fig:sv-2d}
-  \end{subfigure}
-  \caption[]{\small A comparison of calculated values of $L_2(r)$, $S_2(r)$,
+  \subfigure[Surface-void correlation function]{
+    \includegraphics[width=0.475\linewidth]{images/sv-2d.png}
+    \label{fig:sv-2d}}
+  \caption[]{A comparison of calculated values of $L_2(r)$, $S_2(r)$,
     $F_{ss}(r)$ and $F_{sv}(r)$ with theoretical values for overlapping disks.}
@@
   \centering
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/l2-3d.png}
-    \caption[]{{\small Lineal-path correlation function}}
-    \label{fig:l2-3d}
-  \end{subfigure}
+  \subfigure[Lineal-path correlation function]{
+    \includegraphics[width=0.475\linewidth]{images/l2-3d.png}
+    \label{fig:l2-3d}}
   \hfill
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/s2-3d.png}
-    \caption[]{{\small Two-point correlation function}}
-    \label{fig:s3-3d}
-  \end{subfigure}
+  \subfigure[Two-point correlation function]{
+    \includegraphics[width=0.475\linewidth]{images/s2-3d.png}
+    \label{fig:s3-3d}}
   \vskip\baselineskip
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/ss-3d.png}
-    \caption[]{{\small Surface-surface correlation function}}
-    \label{fig:ss-3d}
-  \end{subfigure}
+  \subfigure[Surface-surface correlation function]{
+    \includegraphics[width=0.475\linewidth]{images/ss-3d.png}
+    \label{fig:ss-3d}}
   \hfill
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/sv-3d.png}
-    \caption[]{{\small Surface-void correlation function}}
-    \label{fig:sv-3d}
-  \end{subfigure}
-  \caption[]{\small A comparison of calculated values of $L_2(r)$, $S_2(r)$,
+  \subfigure[Surface-void correlation function]{
+    \includegraphics[width=0.475\linewidth]{images/sv-3d.png}
+    \label{fig:sv-3d}}
+  \caption[]{A comparison of calculated values of $L_2(r)$, $S_2(r)$,
     $F_{ss}(r)$ and $F_{sv}(r)$ with theoretical values for overlapping balls.}
@@
   \centering
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/ps-2d.png}
-    \caption[]{{\small Pore size correlation function (2D)}}
-    \label{fig:ps-2d}
-  \end{subfigure}
+  \subfigure[Pore size correlation function (2D)]{
+    \includegraphics[width=0.475\linewidth]{images/ps-2d.png}
+    \label{fig:ps-2d}}
   \hfill
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/cl-2d.png}
-    \caption[]{{\small Chord length correlation function (2D)}}
-    \label{fig:cl-2d}
-  \end{subfigure}
+  \subfigure[Chord length correlation function (2D)]{
+    \includegraphics[width=0.475\linewidth]{images/cl-2d.png}
+    \label{fig:cl-2d}}
   \vskip\baselineskip
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/ps-3d.png}
-    \caption[]{{\small Pore size correlation function (3D)}}
-    \label{fig:ps-3d}
-  \end{subfigure}
+  \subfigure[Pore size correlation function (3D)]{
+    \includegraphics[width=0.475\linewidth]{images/ps-3d.png}
+    \label{fig:ps-3d}}
   \hfill
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/cl-3d.png}
-    \caption[]{{\small Chord length correlation function (3D)}}
-    \label{fig:cl-3d}
-  \end{subfigure}
-  \caption[]{\small A comparison of calculated values of $P(r)$ and $p(r)$
+  \subfigure[Chord length correlation function (3D)]{
+    \includegraphics[width=0.475\linewidth]{images/cl-3d.png}
+    \label{fig:cl-3d}}
+  \caption[]{A comparison of calculated values of $P(r)$ and $p(r)$
     with theoretical values for overlapping disks (\cref{fig:ps-2d} and
@@
 \end{figure*}
-\twocolumngrid
 
@@
 \begin{itemize}
-\item \textbf{CPU}: AMD Ryzen 5 1600X running at 2200~MHz
+\item \textbf{CPU}: AMD Ryzen 5 1600X
 \item \textbf{Memory}: 32~Gb DDR4-2400 memory
@@
   \centering
-  \includegraphics[width=.3\textwidth]{images/timing-image.png}
-  \caption[]{{\small An example of 2D image used in timing measurements}}
+  \includegraphics[width=0.9\linewidth]{images/timing-image.png}
+  \caption[]{An example of 2D image used in timing measurements.}
   \label{fig:valuenoise}
@@
 
-\onecolumngrid
 \begin{figure*}[t]
   \centering
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/time-2d.png}
-    \caption[]{{\small Two-dimensional case, module \code{Directional}}}
-    \label{fig:timings-2d}
-  \end{subfigure}
+  \subfigure[Two-dimensional case, module \code{Directional}]{
+    \includegraphics[width=0.475\linewidth]{images/time-2d.png}
+    \label{fig:timings-2d}}
   \hfill
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/time-3d.png}
-    \caption[]{{\small Three-dimensional case, module \code{Directional}}}
-    \label{fig:timings-3d}
-  \end{subfigure}
+  \subfigure[Three-dimensional case, module \code{Directional}]{
+    \includegraphics[width=0.475\linewidth]{images/time-3d.png}
+    \label{fig:timings-3d}}
   \vskip\baselineskip
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/time-2d-map.png}
-    \caption[]{{\small Two-dimensional case, module \code{Map}, CPU}}
-    \label{fig:timings-2d-map}
-  \end{subfigure}
+  \subfigure[Two-dimensional case, module \code{Map}, CPU]{
+    \includegraphics[width=0.475\linewidth]{images/time-2d-map.png}
+    \label{fig:timings-2d-map}}
   \hfill
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/time-3d-map.png}
-    \caption[]{{\small Three-dimensional case, module \code{Map}, CPU}}
-    \label{fig:timings-3d-map}
-  \end{subfigure}
+  \subfigure[Three-dimensional case, module \code{Map}, CPU]{
+    \includegraphics[width=0.475\linewidth]{images/time-3d-map.png}
+    \label{fig:timings-3d-map}}
   \vskip\baselineskip
-    \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/time-2d-gpu.png}
-    \caption[]{{\small Two-dimensional case, module \code{Map}, GPU}}
-    \label{fig:timings-2d-gpu}
-  \end{subfigure}
+  \subfigure[Two-dimensional case, module \code{Map}, GPU]{
+    \includegraphics[width=0.475\linewidth]{images/time-2d-gpu.png}
+    \label{fig:timings-2d-gpu}}
   \hfill
-  \begin{subfigure}[b]{0.475\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/time-3d-gpu.png}
-    \caption[]{{\small Three-dimensional case, module \code{Map}, GPU}}
-    \label{fig:timings-3d-gpu}
-  \end{subfigure}
-  \caption[]{\small Execution times for different correlation functions.}
+  \subfigure[Three-dimensional case, module \code{Map}, GPU]{
+    \includegraphics[width=0.475\linewidth]{images/time-3d-gpu.png}
+    \label{fig:timings-3d-gpu}}
+  \caption[]{Execution times for different correlation functions.}
   \label{fig:timings}
 \end{figure*}
-\twocolumngrid
 

### 2022-04-05 paper-correlations.tex
Try to explain what periodic/non-periodic boundary conditions are

@@
 
-Correlation functions can be computed using closed walls (CW) and periodic
-boundary conditions. \textbf{TODO: Describe them}.
+Correlation functions can be computed using periodic and zero-padding boundary
+conditions. With periodic boundary conditions a correlation function is
+calculated as if the input array were periodically extended to infinity,
+i.e. $A_k = A_{k+N_k}$ where $N_k$ is the k-th array dimension. With
+zero-padding the input is extended with zeros, i.e. $A_k = 0$ when
+$0 < k < N_k$.
 
@@
 correlation lengths from $0$ to $maxlen-1$. If $periodic$ is true (resp. false)
-then periodic (resp. CW) boundary conditions are used. The entry point of the
+then periodic (resp. zero padding) boundary conditions are used. The entry point of the
 algorithm is the function L2. The efficiency of the proposed algorithm is $O(n)$

### 2022-04-18 paper-correlations.tex
Clearer description of algorithms

@@
-\documentclass[reprint,amsmath,amssymb,aps,pre]{revtex4-1}
+\documentclass[reprint,amsmath,amssymb,aps,pre,nofootinbib]{revtex4-1}
 % Latex
@@
 \code{SeparableIndicator} in our package) we use the following algorithm to
-calculate the array \code{success} for one-dimensional slice $a$:
+calculate the array \code{success} for one-dimensional slice $a$: \footnote{From
+here on $\odot$ denotes concatenation and $:$ denotes consing (joining an
+element in front of a list).}
 \begin{algorithmic}[1]
@@
   \If{$!periodic$}
-    \State $a \gets a \odot zeros(length(a))$ \Comment{$\odot$
-      denotes concatenation and $zeros(n)$ returns an array with $n$ zeros.}
+    \State $a \gets a \odot [0 \dots 0]$ \Comment{Pad with zeros to twice the
+      length of $a$.}
   \EndIf
@@
     \For{$shift \gets 0,len-1$}
-      \State $a_2 \gets subseq(a, shift)$
-      \Comment{$subseq$ returns subsequence of $a$ from the $shift$-th element
-        to the end.}
-      \State $success[shift] \gets sum(map(\chi, a, a_2))$
+      \State $a_2 \gets a[shift \dots]$
+      \Comment{Take elements with index bigger than $shift$.}
+      \State $success[shift] \gets sum(\chi(a, a_2))$
+      \Comment{Apply $\chi$ element-wise and take a sum.}
     \EndFor
@@
 
+For computation of cluster function we use \code{label\_components} function
+from \code{Image.jl} package which extracts connected comonents (clusters) from the
+binary array. Each cluster gets its own unique integer identificator. The
+identificator $0$ is reserved for the void phase.
+
 The algorithm for calculation of the array \code{success} for
@@
     element-wise}
-  \State $c \gets clusterize(a_1)$
-  \Comment{$clusterize(x)$ selects clusters from the array
-    $x$. Each cluster gets its own unique integer identificator. The
-    identificator $0$ is reserved for the void phase.}
+  \State $c \gets label\_components(a_1)$
   \State $\chi(x,y) \gets (x = y \ne 0)$

### 2022-04-18 real-data/plot-c2.py
Add plots for real data

@@ -1,0 +1,28 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+names = [
+    "BanderaBrown",
+    "Bentheimer",
+    "Berea",
+    "BSG",
+    "CastleGate",
+    "Kirby"
+]
+
+plt.figure(figsize = (10, 9), dpi = 300)
+plt.rc('font', size = 20)
+
+for name in names:
+    path = name + '_2d25um_binary.pbm-c2void.dat'
+    data = np.loadtxt(path)
+    plt.plot(data)
+
+plt.xlabel('Correlation length $r$')
+plt.ylabel('$C_2^{(void)}(r)$')
+plt.yscale('log')
+plt.legend(names)
+plt.savefig('../real-data-plots/real-c2void.png')
+#plt.show()

### 2022-04-18 real-data/plot-l2.py

@@ -1,0 +1,28 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+names = [
+    "BanderaBrown",
+    "Bentheimer",
+    "Berea",
+    "BSG",
+    "CastleGate",
+    "Kirby"
+]
+
+plt.figure(figsize = (10, 9), dpi = 300)
+plt.rc('font', size = 20)
+
+for name in names:
+    path = name + '_2d25um_binary.pbm-l2void.dat'
+    data = np.loadtxt(path)
+    plt.plot(data)
+
+plt.xlabel('Correlation length $r$')
+plt.ylabel('$L_2^{(void)}(r)$')
+plt.yscale('log')
+plt.legend(names)
+plt.savefig('../real-data-plots/real-l2void.png')
+#plt.show()

### 2022-04-18 real-data/plot-s2.py

@@ -1,0 +1,26 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+names = [
+    "BanderaBrown",
+    "Bentheimer",
+    "Berea",
+    "BSG",
+    "CastleGate",
+    "Kirby"
+]
+
+plt.figure(figsize = (10, 9), dpi = 300)
+plt.rc('font', size = 20)
+
+for name in names:
+    path = name + '_2d25um_binary.pbm-s2void.dat'
+    data = np.loadtxt(path)
+    plt.plot(data)
+
+plt.xlabel('Correlation length $r$')
+plt.ylabel('$S_2^{(void)}(r)$')
+plt.legend(names)
+plt.savefig('../real-data-plots/real-s2void.png')

### 2022-04-18 real-data/plot-ss.py

@@ -1,0 +1,28 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+names = [
+    "BanderaBrown",
+    "Bentheimer",
+    "Berea",
+    "BSG",
+    "CastleGate",
+    "Kirby"
+]
+
+plt.figure(figsize = (10, 9), dpi = 300)
+plt.rc('font', size = 20)
+
+for name in names:
+    path = name + '_2d25um_binary.pbm-surfsurf.dat'
+    data = np.loadtxt(path)
+    plt.plot(np.arange(10, 500), data[10:])
+
+plt.ticklabel_format(scilimits = (0, 0), axis = 'y')
+plt.xlabel('Correlation length $r$')
+plt.ylabel('$F_{ss}(r)$')
+plt.legend(names)
+plt.savefig('../real-data-plots/real-ss.png')
+#plt.show()

### 2022-04-18 real-data/plot-sv.py

@@ -1,0 +1,28 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+names = [
+    "BanderaBrown",
+    "Bentheimer",
+    "Berea",
+    "BSG",
+    "CastleGate",
+    "Kirby"
+]
+
+plt.figure(figsize = (10, 9), dpi = 300)
+plt.rc('font', size = 20)
+
+for name in names:
+    path = name + '_2d25um_binary.pbm-surfvoid.dat'
+    data = np.loadtxt(path)
+    plt.plot(data)
+
+plt.ticklabel_format(scilimits = (0, 0), axis = 'y')
+plt.xlabel('Correlation length $r$')
+plt.ylabel('$F_{sv}(r)$')
+plt.legend(names)
+plt.savefig('../real-data-plots/real-sv.png')
+#plt.show()

### 2022-04-18 paper-correlations.tex
Add plots for five functions

@@
 \label{exasec}
-Text
+After the verification of our computational approach based on analytical
+solution we can apply our algorithms to evaluate correlation functions for
+different porous media images, including real XCT and SEM images.
+
+For demonstration purposes, we computed correlation functions for images of
+sandstone found on Digital Rocks Portal \cite{DigitalRocks} all of which have
+dimensions $1000 \times 1000$. The result can be seen on \cref{fig:real-data}.
+
+\begin{figure*}[t]
+  \centering
+  \subfigure[$S_2^{(void)}$ correlation function.]{
+    \includegraphics[width=0.3\linewidth]{real-data-plots/real-s2void.png}
+    \label{fig:real-s2}}
+  \hfill
+  \subfigure[$L_2^{(void)}$ correlation function.]{
+    \includegraphics[width=0.3\linewidth]{real-data-plots/real-l2void.png}
+    \label{fig:real-l2}}
+  \subfigure[$C_2^{(void)}$ correlation function.]{
+    \includegraphics[width=0.3\linewidth]{real-data-plots/real-c2void.png}
+    \label{fig:real-c2}}
+  \vskip\baselineskip
+  \subfigure[$F_{ss}$ correlation function.]{
+    \includegraphics[width=0.3\linewidth]{real-data-plots/real-ss.png}
+    \label{fig:real-ss}}
+  \subfigure[$F_{sv}$ correlation function.]{
+    \includegraphics[width=0.3\linewidth]{real-data-plots/real-sv.png}
+    \label{fig:real-sv}}
+  \caption[]{Plots of correlation functions for images of sandstones.}
+  \label{fig:real-data}
+\end{figure*}
 

### 2022-04-26 paper-correlations.tex
Calculate CFs for 3D data

@@
 sandstone found on Digital Rocks Portal \cite{DigitalRocks} all of which have
-dimensions $1000 \times 1000$. The result can be seen on \cref{fig:real-data}.
+dimensions $1000 \times 1000 \times 1000$. The result can be seen on
+\cref{fig:real-data}.
 

### 2022-04-26 real-data/plot-c2.py

@@ -22,7 +22,7 @@ for name in names:
 
 plt.xlabel('Correlation length $r$')
 plt.ylabel('$C_2^{(void)}(r)$')
-plt.yscale('log')
+#plt.yscale('log')
 plt.legend(names)
 plt.savefig('../real-data-plots/real-c2void.png')
 #plt.show()

### 2022-05-31 paper-correlations.tex
fill map section

--- 2022-04-18 paper-correlations.tex
@@
-\documentclass[reprint,amsmath,amssymb,aps,pre,nofootinbib]{revtex4-1}
+\documentclass[reprint,amsmath,amssymb,aps,pre]{revtex4-1}
 % Latex
@@
 \usepackage{graphicx}
-\usepackage{subfigure}
+\usepackage{subcaption}
 
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{images/corr.png}
-  \caption[]{WTF?}
+  \includegraphics[width=.3\textwidth]{images/corr.png}
+  \caption[]{{\small WTF?}}
   \label{fig:functions}
@@
 
-Correlation functions can be computed using periodic and zero-padding boundary
-conditions. With periodic boundary conditions a correlation function is
-calculated as if the input array were periodically extended to infinity,
-i.e. $A_k = A_{k+N_k}$ where $N_k$ is the k-th array dimension. With
-zero-padding the input is extended with zeros, i.e. $A_k = 0$ when
-$0 < k < N_k$.
+Correlation functions can be computed using closed walls (CW) and periodic
+boundary conditions. \textbf{TODO: Describe them}.
 
@@
 The probability $p(\bm{r})$ can be expressed as
-\begin{equation*}
+\begin{equation}\label{eq:probability}
   p(\bm{r}) = \frac{\text{Number of successful trials $S(\bm{r})$}}
   {\text{Total number of trials $N(\bm{r})$}}
-\end{equation*}
+\end{equation}
 
@@
 \code{SeparableIndicator} in our package) we use the following algorithm to
-calculate the array \code{success} for one-dimensional slice $a$: \footnote{From
-here on $\odot$ denotes concatenation and $:$ denotes consing (joining an
-element in front of a list).}
+calculate the array \code{success} for one-dimensional slice $a$:
 \begin{algorithmic}[1]
@@
   \If{$!periodic$}
-    \State $a \gets a \odot [0 \dots 0]$ \Comment{Pad with zeros to twice the
-      length of $a$.}
+    \State $a \gets a \odot zeros(length(a))$ \Comment{$\odot$
+      denotes concatenation and $zeros(n)$ returns an array with $n$ zeros.}
   \EndIf
@@
     \For{$shift \gets 0,len-1$}
-      \State $a_2 \gets a[shift \dots]$
-      \Comment{Take elements with index bigger than $shift$.}
-      \State $success[shift] \gets sum(\chi(a, a_2))$
-      \Comment{Apply $\chi$ element-wise and take a sum.}
+      \State $a_2 \gets subseq(a, shift)$
+      \Comment{$subseq$ returns subsequence of $a$ from the $shift$-th element
+        to the end.}
+      \State $success[shift] \gets sum(map(\chi, a, a_2))$
     \EndFor
@@
 
-For computation of cluster function we use \code{label\_components} function
-from \code{Image.jl} package which extracts connected comonents (clusters) from the
-binary array. Each cluster gets its own unique integer identificator. The
-identificator $0$ is reserved for the void phase.
-
 The algorithm for calculation of the array \code{success} for
@@
     element-wise}
-  \State $c \gets label\_components(a_1)$
+  \State $c \gets clusterize(a_1)$
+  \Comment{$clusterize(x)$ selects clusters from the array
+    $x$. Each cluster gets its own unique integer identificator. The
+    identificator $0$ is reserved for the void phase.}
   \State $\chi(x,y) \gets (x = y \ne 0)$
@@
 \label{mapsec}
-Text
+
+In this approach we actively use fast Fourier transform (FFT)
+to compute some correlation function ($S_2, F_{ss}, F_{sv}, C_2$)
+in all directions.
+The FFT algorithm let us compute auto and cross-correlation fast,
+especially on GPU.
+
+Lineal-path function doesn't have FFT realization,
+therefore, we use different approach.
+
+\subsection{Lineal-path function}
+
+High-level algorithm:
+\begin{enumerate}
+  \item Chose a set of directions
+  \item for a direction in the set
+    \begin{enumerate}
+      \item align the image along the direction
+      \item scan the aligned image
+    \end{enumerate}
+\end{enumerate}
+
+Align and rotate - simple operations with linear computational complexity.
+Therefore, the complexity of the entire algorithm depends linearly 
+on the number of directions and on the size of the image.
+
+\subsection{Correlation map}
+
+\subsubsection{Auto- and cross-correlation using FFT}
+
+All subsequent functions are auto- or cross-correlations.
+Therefore, here we describe a method to compute them using FFT.
+
+\begin{algorithmic}[1]
+  \Procedure{cross\_correlation}{$a, b$}
+    \State $A \gets rfft(a)$\Comment{Real fast Fourie transform}
+    \State $B \gets rfft(b)$
+    \ForAll{$i \in CartesianIndices(A)$}
+      \State $C[i] \gets conj(A[i]) \cdot B[i]$
+    \EndFor
+    \State $c = irfft(C)$ 
+    \Comment{inverse rfft}
+    \State \textbf{return} $c$
+  \EndProcedure
+\end{algorithmic}
+
+One can use cross-correlation to compute auto-correlation,
+but special function would permorm better.
+
+\begin{algorithmic}[1]
+  \Procedure{auto\_correlation}{$a$}
+    \State $A \gets rfft(a)$
+    \ForAll{$i \in CartesianIndices(A)$}
+      \State $C[i] \gets |A[i]|^2$
+    \EndFor
+    \State $c = irfft(C)$ 
+    \State \textbf{return} $c$
+  \EndProcedure
+\end{algorithmic}
+
+CartesianIndices --- all indices of multidimensional array,
+therefore, the for loop describe elementwise operations
+and have linear computational complexity $O(n)$.
+For both functions computational complexity is $O(n\ log(n))$.
+
+It is worth noting, that the FFT approach imply
+periodic boundary conditions by design.
+
+\subsubsection{Total number of trials}
+
+$auto\_correlation$ and $cross\_correlation$ return non-negative number
+of success trials \cref{eq:probability}.
+To compute probability we need to count total number of trials.
+This value depends on boundary conditions.
+We realize two types: periodic and non-periodic (flat).
+
+\begin{algorithmic}[1]
+  \Procedure{total}{$a, periodic$}
+    \State $m, n \gets size(a)$
+    \If{periodic}
+      \ForAll{$i \in range(0, m - 1)$}
+        \ForAll{$j \in range(0, n - 1)$}
+          \State $total[i, j] \gets m \cdot n$
+        \EndFor
+      \EndFor
+    \Else
+      \ForAll{$i \in range(-m + 1, m - 1)$}
+        \ForAll{$j \in range(-n + 1, n - 1)$}
+          \State $i' \gets mod(i, 2m - 1)$
+          \State $j' \gets mod(j, 2n - 1)$
+          \State $total[i', j'] \gets |m - i| \cdot |n - j|$
+        \EndFor
+      \EndFor
+    \EndIf
+    \State \textbf{return} $total$
+  \EndProcedure
+\end{algorithmic}
+
+Described function is for 2D images,
+for 1D and 3D images realization is similar.
+
+if n is the number of pixels, then computational complexity
+of this funciton is $O(n)$.
+
+\subsubsection{Two-point funciton}
+
+We realize two boundary conditions: periodic and non-periodic (flat).
+For non-periodic boundary conditions one need to double image size
+by padding new values with zeros.
+Thus, if original image is $(m \times n)$,
+then expanded image will have size $(2m - 1 \times 2n - 1)$.
+
+\begin{algorithmic}[1]
+  \Procedure{s2\_map}{$a, phase, periodic$}
+    \State $a_1 \gets a = phase$
+    \If{periodic}
+      \State $a_2 \gets a_1$
+    \Else
+      \State $a_2 \gets expand(a_1)$\Comment{double image size by padding new values with zeros}
+    \EndIf
+
+    \State $success \gets AUTO\_CORRELATION(a_2)$
+
+    \State $total \gets TOTAL(a, periodic)$
+
+    \ForAll{$i \in CartesianIndices(success)$}
+      \State $s2[i] \gets success[i]\ /\ total[i]$
+    \EndFor
+
+    \State \textbf{return} $s2$
+  \EndProcedure
+\end{algorithmic}
+
+if n is the number of pixels, then computational complexity
+of this funciton is $O(n\ log(n))$.
+
+\subsubsection{Phase cross-correlation funciton}
+
+\begin{algorithmic}[1]
+  \Procedure{cc\_map}{$a, b, periodic$}
+    \If{periodic}
+      \State $a_1 \gets a$
+      \State $b_1 \gets b$
+    \Else
+      \State $a_1 \gets expand(a)$
+      \State $b_1 \gets expand(b)$
+    \EndIf
+
+    \State $success \gets CROSS\_CORRELATION(a_1, b_1)$
+
+    \State $total \gets TOTAL(a, periodic)$
+
+    \ForAll{$i \in CartesianIndices(success)$}
+      \State $cc[i] \gets success[i]\ /\ total[i]$
+    \EndFor
+
+    \State \textbf{return} $cc$
+  \EndProcedure
+\end{algorithmic}
+
+if n is the number of pixels, then computational complexity
+of this funciton is $O(n\ log(n))$.
+
+\subsection{Surface-surface function}
+
+Computation of surface-surface function consists of two steps 
+\textcolor{red}{[link to surface paper]}:
+\begin{enumerate}
+  \item extracting surface $M = \nabla I(a)$
+  \item computing $F_{ss} = S_2(M)$
+\end{enumerate}
+
+For surface extraction we use `imgradient' function
+and Sobel kernel as default kernel, 
+both defined in ImageFiltering.jl package \textcolor{red}{[add link]}.
+
+\begin{algorithmic}[1]
+  \Procedure{surf\_surf}{$a, phase, periodic, kernel$}
+    \State $a_1 \gets a = phase$
+    \State $M \gets imgradient(a_1, kernel)$
+    \State $Fss = S2\_MAP(M, periodic)$
+    \State \textbf{return} $Fss$
+  \EndProcedure
+\end{algorithmic}
+
+if n is the number of pixels, then computational complexity
+of this funciton is $O(n\ log(n))$.
+
+\subsection{Surface-void function}
+
+Computation of surface-void function consists of three steps 
+\textcolor{red}{[link to surface paper]}:
+\begin{enumerate}
+  \item extracting surface $M = \nabla I(a)$
+  \item extracting void phase $V = I_v(a)$
+  \item computing $F_{sv} = cross\_correlation(M, V)$
+\end{enumerate}
+
+\begin{algorithmic}[1]
+  \Procedure{surf\_void}{$a, phase, periodic, kernel$}
+    \State $a_1 \gets a = phase$
+    \State $M \gets imgradient(a_1, kernel)$
+    \State $V \gets a = 0$
+    \State $Fsv = CC\_MAP(M, V, periodic)$
+    \State \textbf{return} $Fsv$
+  \EndProcedure
+\end{algorithmic}
+
+if n is the number of pixels, then computational complexity
+of this funciton is $O(n\ log(n))$.
+
+\subsection{Cluster funciton}
+
+Computation of cluster function consists of three steps
+\begin{enumerate}
+  \item label different clusters with distinct integers
+  \item compute $S_2$ map for every cluster
+  \item add up all maps
+\end{enumerate}
+
+For labeling we use `label\_components' function from
+Images.jl package \textcolor{red}{[add link]}.
+
+\begin{algorithmic}[1]
+  \Procedure{cluster\_map}{$a, phase, periodic$}
+    \State $a_1 \gets a = phase$
+    \State $labeled\_a \gets label\_components(a_1, periodic)$
+    \State $number\_of\_labels = maximum(labeled\_a)$
+    \ForAll{$label \in range(1, number\_of\_labels)$}
+      \State $b \gets labeled\_a = label$
+      \If{label = 1}
+        \State $c2 \gets S2\_MAP(b, periodic)$
+      \Else
+        \State $c2 \gets c2 + S2\_MAP(b, periodic)$
+      \EndIf
+    \EndFor
+    \State \textbf{return} $c2$
+  \EndProcedure
+\end{algorithmic}
+
+if n is the number of pixels and N is the number of clusters, then computational complexity
+of this funciton is $O(N\ n\ log(n))$.
 
@@
 
+\onecolumngrid
 \begin{figure*}[t]
   \centering
-  \subfigure[Lineal-path correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/l2-2d.png}
-    \label{fig:l2-2d}}
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/l2-2d.png}
+    \caption[]{{\small Lineal-path correlation function}}
+    \label{fig:l2-2d}
+  \end{subfigure}
   \hfill
-  \subfigure[Two-point correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/s2-2d.png}
-    \label{fig:s2-2d}}
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/s2-2d.png}
+    \caption[]{{\small Two-point correlation function}}
+    \label{fig:s2-2d}
+  \end{subfigure}
   \vskip\baselineskip
-  \subfigure[Surface-surface correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/ss-2d.png}
-    \label{fig:ss-2d}}
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/ss-2d.png}
+    \caption[]{{\small Surface-surface correlation function}}
+    \label{fig:ss-2d}
+  \end{subfigure}
   \hfill
-  \subfigure[Surface-void correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/sv-2d.png}
-    \label{fig:sv-2d}}
-  \caption[]{A comparison of calculated values of $L_2(r)$, $S_2(r)$,
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/sv-2d.png}
+    \caption[]{{\small Surface-void correlation function}}
+    \label{fig:sv-2d}
+  \end{subfigure}
+  \caption[]{\small A comparison of calculated values of $L_2(r)$, $S_2(r)$,
     $F_{ss}(r)$ and $F_{sv}(r)$ with theoretical values for overlapping disks.}
@@
   \centering
-  \subfigure[Lineal-path correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/l2-3d.png}
-    \label{fig:l2-3d}}
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/l2-3d.png}
+    \caption[]{{\small Lineal-path correlation function}}
+    \label{fig:l2-3d}
+  \end{subfigure}
   \hfill
-  \subfigure[Two-point correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/s2-3d.png}
-    \label{fig:s3-3d}}
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/s2-3d.png}
+    \caption[]{{\small Two-point correlation function}}
+    \label{fig:s3-3d}
+  \end{subfigure}
   \vskip\baselineskip
-  \subfigure[Surface-surface correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/ss-3d.png}
-    \label{fig:ss-3d}}
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/ss-3d.png}
+    \caption[]{{\small Surface-surface correlation function}}
+    \label{fig:ss-3d}
+  \end{subfigure}
   \hfill
-  \subfigure[Surface-void correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/sv-3d.png}
-    \label{fig:sv-3d}}
-  \caption[]{A comparison of calculated values of $L_2(r)$, $S_2(r)$,
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/sv-3d.png}
+    \caption[]{{\small Surface-void correlation function}}
+    \label{fig:sv-3d}
+  \end{subfigure}
+  \caption[]{\small A comparison of calculated values of $L_2(r)$, $S_2(r)$,
     $F_{ss}(r)$ and $F_{sv}(r)$ with theoretical values for overlapping balls.}
@@
   \centering
-  \subfigure[Pore size correlation function (2D)]{
-    \includegraphics[width=0.475\linewidth]{images/ps-2d.png}
-    \label{fig:ps-2d}}
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/ps-2d.png}
+    \caption[]{{\small Pore size correlation function (2D)}}
+    \label{fig:ps-2d}
+  \end{subfigure}
   \hfill
-  \subfigure[Chord length correlation function (2D)]{
-    \includegraphics[width=0.475\linewidth]{images/cl-2d.png}
-    \label{fig:cl-2d}}
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/cl-2d.png}
+    \caption[]{{\small Chord length correlation function (2D)}}
+    \label{fig:cl-2d}
+  \end{subfigure}
   \vskip\baselineskip
-  \subfigure[Pore size correlation function (3D)]{
-    \includegraphics[width=0.475\linewidth]{images/ps-3d.png}
-    \label{fig:ps-3d}}
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/ps-3d.png}
+    \caption[]{{\small Pore size correlation function (3D)}}
+    \label{fig:ps-3d}
+  \end{subfigure}
   \hfill
-  \subfigure[Chord length correlation function (3D)]{
-    \includegraphics[width=0.475\linewidth]{images/cl-3d.png}
-    \label{fig:cl-3d}}
-  \caption[]{A comparison of calculated values of $P(r)$ and $p(r)$
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/cl-3d.png}
+    \caption[]{{\small Chord length correlation function (3D)}}
+    \label{fig:cl-3d}
+  \end{subfigure}
+  \caption[]{\small A comparison of calculated values of $P(r)$ and $p(r)$
     with theoretical values for overlapping disks (\cref{fig:ps-2d} and
@@
 \end{figure*}
+\twocolumngrid
 
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{images/timing-image.png}
-  \caption[]{An example of 2D image used in timing measurements.}
+  \includegraphics[width=.3\textwidth]{images/timing-image.png}
+  \caption[]{{\small An example of 2D image used in timing measurements}}
   \label{fig:valuenoise}
@@
 
+\onecolumngrid
 \begin{figure*}[t]
   \centering
-  \subfigure[Two-dimensional case, module \code{Directional}]{
-    \includegraphics[width=0.475\linewidth]{images/time-2d.png}
-    \label{fig:timings-2d}}
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/time-2d.png}
+    \caption[]{{\small Two-dimensional case, module \code{Directional}}}
+    \label{fig:timings-2d}
+  \end{subfigure}
   \hfill
-  \subfigure[Three-dimensional case, module \code{Directional}]{
-    \includegraphics[width=0.475\linewidth]{images/time-3d.png}
-    \label{fig:timings-3d}}
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/time-3d.png}
+    \caption[]{{\small Three-dimensional case, module \code{Directional}}}
+    \label{fig:timings-3d}
+  \end{subfigure}
   \vskip\baselineskip
-  \subfigure[Two-dimensional case, module \code{Map}, CPU]{
-    \includegraphics[width=0.475\linewidth]{images/time-2d-map.png}
-    \label{fig:timings-2d-map}}
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/time-2d-map.png}
+    \caption[]{{\small Two-dimensional case, module \code{Map}, CPU}}
+    \label{fig:timings-2d-map}
+  \end{subfigure}
   \hfill
-  \subfigure[Three-dimensional case, module \code{Map}, CPU]{
-    \includegraphics[width=0.475\linewidth]{images/time-3d-map.png}
-    \label{fig:timings-3d-map}}
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/time-3d-map.png}
+    \caption[]{{\small Three-dimensional case, module \code{Map}, CPU}}
+    \label{fig:timings-3d-map}
+  \end{subfigure}
   \vskip\baselineskip
-  \subfigure[Two-dimensional case, module \code{Map}, GPU]{
-    \includegraphics[width=0.475\linewidth]{images/time-2d-gpu.png}
-    \label{fig:timings-2d-gpu}}
+    \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/time-2d-gpu.png}
+    \caption[]{{\small Two-dimensional case, module \code{Map}, GPU}}
+    \label{fig:timings-2d-gpu}
+  \end{subfigure}
   \hfill
-  \subfigure[Three-dimensional case, module \code{Map}, GPU]{
-    \includegraphics[width=0.475\linewidth]{images/time-3d-gpu.png}
-    \label{fig:timings-3d-gpu}}
-  \caption[]{Execution times for different correlation functions.}
+  \begin{subfigure}[b]{0.475\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/time-3d-gpu.png}
+    \caption[]{{\small Three-dimensional case, module \code{Map}, GPU}}
+    \label{fig:timings-3d-gpu}
+  \end{subfigure}
+  \caption[]{\small Execution times for different correlation functions.}
   \label{fig:timings}
 \end{figure*}
+\twocolumngrid
 
@@
 correlation lengths from $0$ to $maxlen-1$. If $periodic$ is true (resp. false)
-then periodic (resp. zero padding) boundary conditions are used. The entry point of the
+then periodic (resp. CW) boundary conditions are used. The entry point of the
 algorithm is the function L2. The efficiency of the proposed algorithm is $O(n)$

### 2022-06-07 paper-correlations.tex
l2

--- 2022-05-31 paper-correlations.tex
@@
 
-High-level algorithm:
-\begin{enumerate}
-  \item Chose a set of directions
-  \item for a direction in the set
-    \begin{enumerate}
-      \item align the image along the direction
-      \item scan the aligned image
-    \end{enumerate}
-\end{enumerate}
-
-Align and rotate - simple operations with linear computational complexity.
+Since the method for calculating $l_2$ using the FFT is unknown,
+we use the direct approach:
+scan the image in each selected direction.
+\textcolor{red}{[czech paper]} uses this method,
+but our approach saves porosity when rotating the image.
+The top-level algorithm is described below, 
+and the details are placed in the appendix.
+
+\begin{algorithmic}[1]
+  \Procedure{l2\_map}{$a, periodic, directions$}
+    \ForAll{$direction \in directions$}
+      \State $rotated \gets rotate(a, direction, periodic)$
+      \State $l2[direction] \gets scan\_l2(aligned, periodic)$
+    \EndFor
+    \State \textbf{return} $l2$
+  \EndProcedure
+\end{algorithmic}
+
+Align and rotate --- simple operations with linear computational complexity.
 Therefore, the complexity of the entire algorithm depends linearly 
@@
 
+\section{Algorithm for image rotation}
+\label{rotating}
+
+\begin{algorithmic}[1]
+  \Procedure{rotate}{$a, direction, periodic$}
+    \ForAll{$slice \in eachslice(a)$}
+      \State $shift \gets get\_shift(slice, direction)$
+      \State $rotated\_slice \gets circshift(slice, shift)$
+      \If{$! periodic$}
+        \State $rotated\_slice[end - shift:end] \gets -1$
+      \EndIf
+    \EndFor
+  \State \textbf{return} $rotated$
+  \EndProcedure
+\end{algorithmic}
+
 \onecolumngrid

### 2022-09-05 paper-correlations.tex
Replace bibliography file

@@
-\documentclass[reprint,amsmath,amssymb,aps,pre,nofootinbib]{revtex4-1}
+\documentclass[reprint,amsmath,amssymb,aps,pre,showkeys,showpacs,nofootinbib]{revtex4-1}
 % Latex
@@
 \begin{document}
-%*Corresponding author: Kirill M. Gerke, Tel.: +79661877715, E-mail: kg@ifz.ru,
-%Address: Schmidt Institute of Physics of the Earth of Russian Academy of
-%Sciences, Bolshaya Gruzinskaya str. 10/1, Moscow, 123242, Russia
-\author{Vasily Postnicov}
-\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of
-  Sciences, Moscow, 123242, Russia}
-\author{Alexey I. Samarin}
-\altaffiliation{Computational Mathematics and Cybernetics, Lomonosov Moscow
-  State University, Moscow, 119991, Russia}
-\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of
-  Sciences, Moscow, 123242, Russia}
-\author{Efim V. Lavrukhin}
-\altaffiliation{Computational Mathematics and Cybernetics, Lomonosov Moscow
-  State University, Moscow, 119991, Russia}
-\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of
-  Sciences, Moscow, 123242, Russia}
-\author{Marina V. Karsanina}
-\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of
-  Sciences, Moscow, 123242, Russia}
-\author{Mathieu Gravey}
-\altaffiliation{University of Lausanne, Faculty of Geosciences and Environment,
-  Institute of Earth Surface Dynamics, Lausanne, Switzerland}
-\author{Kirill M. Gerke}
-\email[E-mail:]{kg@ifz.ru}
-\affiliation{Schmidt Institute of Physics of the Earth of Russian Academy of
-  Sciences, Moscow, 123242, Russia}
+\preprint{APS/123-QED}
+
+\author{Aleksei Samarin\textsuperscript{1,2}}
+\author{Vasily Postnicov\textsuperscript{1}}
+\author{Marina Karsanina\textsuperscript{1}}
+\author{Efim Lavrukhin\textsuperscript{1,2}}
+\author{Dina Gafurova\textsuperscript{3}}
+\author{Aleksey Khlyupin\textsuperscript{1}}
+\author{Kirill Gerke\textsuperscript{1}}
+\email{kg@ifz.ru}
+
+\affiliation{\textsuperscript{1}Schmidt Institute of Physics of the Earth of
+  Russian Academy of Sciences, Moscow, 107031, Russia}
+\affiliation{\textsuperscript{2}Computational Mathematics and Cybernetics,
+  Lomonosov Moscow State University, Moscow, 119991, Russia}
+\affiliation{\textsuperscript{3}Oil and Gas Research Institute Russian Academy
+  of Sciences (OGRI RAS) 3, Gubkina st., Moscow, 119333, Russian Federation}
 
@@
 their physical properties are interconnected to
-structure\cite{Torq_book}\cite{Sahimi_book}\cite{Adler_book}. The information
+structure\cite{Torquato_book}\cite{Sahimi_book}\cite{Adler_recon}. The information
 about the structure usually comes in the way of 2D and 3D images obtained by
@@
 points that are utilized to evaluate such a probability. While so-called
-$n$-point probability function\cite{Torq_book} will totally describe any
+$n$-point probability function\cite{Torquato_book} will totally describe any
 structure in the limit of $n \rightarrow$ number of voxels/pixels on the image,
@@
 \cref{fig:functions}. All major details and numerous analytical cases can be
-found in seminal work of Torquato \cite{Torq_book}. To all CFs described in this
+found in seminal work of Torquato \cite{Torquato_book}. To all CFs described in this
 book and applicable to digital images we shall refer as to classical correlation
@@
 
-\onecolumngrid
-\bibliography{habib}
-\bibliographystyle{plain}
-\twocolumngrid
-
+\bibliography{apssamp}
 \end{document}

### 2022-10-04 timings/timings.jl
Script which calculates timings

@@ -1,35 +1,56 @@
+module Timings
+
 using ValueNoise
 using CorrelationFunctions
 using Statistics
 using DelimitedFiles
 
 getdata(side, :: Val{2}) =
-    [value_noise(5x/side, 5y/side, 0.0, 5, 34365) < 0.5 for x in 1:side, y in 1:side]
+    [value_noise(3x/side, 3y/side, 0.0, 4, 34365) < 0.5 for x in 1:side, y in 1:side]
 
 getdata(side, :: Val{3}) =
-    [value_noise(5x/side, 5y/side, 5z/side, 5, 34365) < 0.5 for x in 1:side, y in 1:side, z in 1:side]
+    [value_noise(3x/side, 3y/side, 3z/side, 4, 34365) < 0.5 for x in 1:side, y in 1:side, z in 1:side]
 
-#const data_2d = [getdata(side, Val(2)) for side in 1000:1000:10000]
-const data_3d = [getdata(side, Val(3)) for side in 50:50:500]
+const data_2d = (getdata(side, Val(2)) for side in 1000:1000:6000)
+const data_3d = (getdata(side, Val(3)) for side in 50:50:300)
 
-function calculate_time!(fn, dim)
-    sides = Vector{Int}(undef, 0)
-    times = Vector{Float64}(undef, 0)
+fst((x, _)) = x
+snd((_, y)) = y
+
+function calculate_time!(fn, dim, prefix)
     data_arrays = (dim == 2) ? data_2d : data_3d
 
-    for data in data_arrays
+    timings = map(data_arrays) do data
         side = size(data, 1)
-        push!(sides, side)
         println(side)
-        #time = sum(let time = time_ns(); fn(data, 1); time_ns() - time end for i in 1:5) / 5
-        time = sum(let time = time_ns(); fn(data, 1); time_ns() - time end for i in 1:2) / 2
-        push!(times, time / 10^9)
+        time = let
+            time = time_ns();
+            fn(data, true; periodic = true);
+            (time_ns() - time) / 10^9
+        end
+        (side, time)
     end
 
-    res = hcat(sides, times)
-    open("/home/vasily/timings/$(fn)-$(dim)d.dat", "w") do io
+    res = hcat(fst.(timings), snd.(timings))
+    open("$(fn)-$(prefix)-$(dim)d.dat", "w") do io
         writedlm(io, res)
     end
     
     return res
+end
+
+const fn_dir = [
[…]

### 2022-10-04 paper-correlations.tex
Fix labels

@@
 \section{Background and motivation}
+\label{sec:background}
 Materials are ubiquitous both in nature and in industrial human activities, and
@@
 package allows to compute numerous CFs easily under any operating system. The
-manuscript describing the package is organized as follows: in \cref{scansec} we
+manuscript describing the package is organized as follows: in \cref{sec:scan} we
 provide all algorithmic details for CFs computation in directions (scanning
-method). \cref{mapsec} presents all algorithmic details for computing full CFs
-maps (map method, full 2-point statistics for a given image). In \cref{verisec}
-we verify the all computations based on known analytical
-solutions. \cref{effisec} deals with computational efficiency of our code, we
-compare computational times for 2D and 3D images of different sizes for scanning
-and map methods as evaluated using either CPU or GPU. In \cref{exasec} some
-application examples are provided, including CFs evaluation for multi-phase
-materials. Finally, \cref{sumsec} summarizes all results and outlines possible
-future improvements.
+method). \cref{sec:map} presents all algorithmic details for computing full CFs
+maps (map method, full 2-point statistics for a given image). In
+\cref{sec:verification} we verify the all computations based on known analytical
+solutions. \cref{sec:efficiency} deals with computational efficiency of our
+code, we compare computational times for 2D and 3D images of different sizes for
+scanning and map methods as evaluated using either CPU or GPU. In
+\cref{sec:examples} some application examples are provided, including CFs
+evaluation for multi-phase materials. Finally, \cref{sec:summary} summarizes all
+results and outlines possible future improvements.
 
 \section{Overview of supported functions and modules.}
-\label{oversec}
+\label{sec:overview}
 \verb+CorrelationFunctions.jl+ is capable to compute the following correlation
@@
 function in all directions. The scan and map approaches are described in
-\cref{scansec} and \cref{mapsec} respectively.
+\cref{sec:scan} and \cref{sec:map} respectively.
 
@@
 \section{The scan approach.}
-\label{scansec}
+\label{sec:scan}
 In this approach, the input array is cut in parallel slices (``scanned'') along
@@
 structure. In the following sections we provide the algorithms for computation
-of the functions given in \cref{oversec}.
+of the functions given in \cref{sec:overview}.
 
@@
 \code{total} arrays. These arrays are then accumulated as described in
-\cref{scansec} for final calculation of $L_2^{(i)}(\bm{r})$ function.
+\cref{sec:scan} for final calculation of $L_2^{(i)}(\bm{r})$ function.
 
@@
 \section{The map approach.}
-\label{mapsec}
+\label{sec:map}
 
@@
 \section{Verifying our algorithms}
-\label{verisec}
+\label{sec:verification}
 To verify our package we use random datasets of overlapping disks (the number of
@@
 \section{Efficiency of our algorithms}
-\label{effisec}
+\label{sec:efficiency}
 To measure efficiecy of our algorithms we use a machine with the following
@@
 \section{Examples and applications}
-\label{exasec}
+\label{sec:examples}
 After the verification of our computational approach based on analytical
@@
 \section{Summary}
-\label{sumsec}
+\label{sec:summary}
 Text

### 2022-10-04 paper-correlations.tex
Add mathematical introduction

@@
 \usepackage{subfigure}
+
+\newtheorem{definition}{Definition}
 
@@
   \includegraphics[width=0.9\linewidth]{images/corr.png}
-  \caption[]{WTF?}
+  \caption[]{A schematic depiction of a binary porous media (pores are shown in
+    color) with examples of positive events for surface $F_{ss}$, $F_{sv}$ and
+    two-point probability $S_2$ correlation functions. The zoomed in area
+    represents the difference between the true ``continuous'' interface in
+    between pore and solid phases with pixelized ``digital'' interface emerging
+    due to limited resolution of digital images.}
   \label{fig:functions}
@@
 CPU and GPU power. Our answer in the form of \code{CorrelationFunctions.jl}
-package allows to compute numerous CFs easily under any operating system. The
-manuscript describing the package is organized as follows: in \cref{sec:scan} we
+package allows to compute numerous CFs easily on any operating system. The
+manuscript describing the package is organized as follows: in \cref{sec:math} we
+introduce a reader to the most common and useful correlation functions,
+\cref{sec:map} presents all algorithmic details for computing full CFs maps (map
+method, full 2-point statistics for a given image). In \cref{sec:scan} we
 provide all algorithmic details for CFs computation in directions (scanning
-method). \cref{sec:map} presents all algorithmic details for computing full CFs
-maps (map method, full 2-point statistics for a given image). In
-\cref{sec:verification} we verify the all computations based on known analytical
-solutions. \cref{sec:efficiency} deals with computational efficiency of our
-code, we compare computational times for 2D and 3D images of different sizes for
-scanning and map methods as evaluated using either CPU or GPU. In
-\cref{sec:examples} some application examples are provided, including CFs
-evaluation for multi-phase materials. Finally, \cref{sec:summary} summarizes all
-results and outlines possible future improvements.
-
-\section{Overview of supported functions and modules.}
-\label{sec:overview}
-\verb+CorrelationFunctions.jl+ is capable to compute the following correlation
-functions:
+method). In \cref{sec:verification} we verify the all computations based on
+known analytical solutions. \cref{sec:efficiency} deals with computational
+efficiency of our code, we compare computational times for 2D and 3D images of
+different sizes for scanning and map methods as evaluated using either CPU or
+GPU. In \cref{sec:examples} some application examples are provided, including
+CFs evaluation for multi-phase materials. Finally, \cref{sec:summary} summarizes
+all results and outlines possible future improvements.
+
+\section{Introduction to the correlation functions}
+\label{sec:math}
+In practice porous media are often described with special descriptors called
+``correlation functions''. In this section we provide a brief introduction to
+these functions which can also be found in \cite{Torquato_book}. The functions
+supported by our package are:
 \begin{itemize}
@@
 
+One of basic correlation functions is a lineal path function which is defined as
+follows for homogenous media:
+\begin{definition}
+  Lineal path function $L_2^{(i)}(\mathbf{r})$ equals to probability that a
+  vector $\mathbf{r}$ lies wholly in phase $i$ when randomly thrown into the
+  sample.
+\end{definition}
+If a sample is isotropic a vector $\mathbf{r}$ can be replaced with its length
+$r$ and the definition becomes:
+\begin{definition}
+  Lineal path function (for isotropic media) $L_2^{(i)}(r)$ equals to
+  probability that a line segment of length $r$ lies wholly in phase $i$ when
+  randomly thrown into the sample.
+\end{definition}
+
+Another function of big importance is a two-point correlation function $S_2$. A
+definition for homogenous media is as follows:
+\begin{definition}
+  Two point function $S_2^{(i)}(\mathbf{r})$ equals to probability that both ends
+  of a vector $\mathbf{r}$ lie in phase $i$ when the vector is randomly thrown
+  into the sample.
+\end{definition}
+For isotopic media a vector $\mathbf{r}$ can be again reduced to a scalar value
+$r$ (i.e. a correlation function depends only on length of a vector and not on
+its direction.) Mathematically this definition can be expressed with the
+following equation:
+\begin{equation}
+  S_2^{(i)}(\mathbf{r}) = \langle I^{(i)}(\mathbf{x}) I^{(i)}(\mathbf{x} +
+  \mathbf{r}) \rangle
+  \label{eq:s2-def}
+\end{equation}
+where $I^{(i)}$ is an indicator function for a set of all points belonging to
+the phase $i$ and $\langle \cdots \rangle$ is an average over all xs.
+
+A function closely related to $S_2$ is phase cross-correlation function
+$\rho_{ij}$ which is defined with the following equation:
+\begin{equation}
+  \rho_{ij}(\mathbf{r}) = \langle I^{(i)}(\mathbf{x}) I^{(j)}(\mathbf{x} +
+  \mathbf{r}) \rangle
+  \label{eq:cross-def}
+\end{equation}
+
+The next function is a cluster function $C_2$.
+\begin{definition}
+  Cluster function $C_2^{(i)}(\mathbf{r})$ equals to probability that both
+  ends of a vector $\mathbf{r}$ lie in the same cluster when the vector is
+  randomly thrown into the sample. A cluster is a set of points of the same
+  phase $i$ where any to points can be connected by a path lying entirely in
+  that phase.
+\end{definition}
+
+The next two functions describe surface of a sample. These functions are
+surface-surface and surface-void functions. For homogenous media their
+definitions are:
+\begin{definition}
+  Surface-surface function $F_{ss}^{(i)}(\mathbf{r})$ equals to probability that
+  both ends of a vector $\mathbf{r}$ touch the interface of phase $i$ when the
+  vector is randomly thrown into the sample.
+\end{definition}
+and
+\begin{definition}
+  Surface-void function $F_{sv}^{(i)}(\mathbf{r})$ equals to probability that
+  one end of a vector $\mathbf{r}$ touches the interface of phase $i$ and the
+  other end touches the void phase when the vector is randomly thrown into the
+  sample.
+\end{definition}
+If we introduce an interface indicator function
+\begin{equation*}
+  M^{(i)}(\mathbf{r}) = | \nabla I^{(i)}(\mathbf{r}) |
+\end{equation*}
+we can define these functions mathematically as
+\begin{align}
+  F_{ss}^{(i)}(\mathbf{r}) &= \langle M^{(i)}(\mathbf{x}) M^{(i)}(\mathbf{x} +
+  \mathbf{r}) \rangle \label{eq:fss-def} \\ 
+  F_{sv}^{(i)}(\mathbf{r}) &= \langle M^{(i)}(\mathbf{x}) I^{(void)}(\mathbf{x}
+  + \mathbf{r}) \rangle \label{eq:fsv-def}
+\end{align}
+As always, there are versions of these functions applicable to scalar argument
+for isotropic media.
+
+Pore size function $P(\delta)$ is a probability density function defined as
+follows:
+\begin{definition}
+  $P(\delta)d\delta$ = Probability that a randomly chosen point in a set of points
+  belonging to the void phase lies at a distance between $\delta$ and $\delta + d\delta$
+  from the nearest point on the pore-solid interface.
+\end{definition}
+
+Finally, a chord length function $p^{(i)}(r)$ is defined as follows:
+\begin{definition}
+$p^{(i)}(r)dz$ = Probability of finding a chord of length between $r$ and $r+dr$
+in phase $i$. Chords are all of the line segments between intersections of an
+infinitely long line with the two-phase interface.
+\end{definition}
+
+\section{Overview of supported functions and modules.}
+\label{sec:overview}
+\verb+CorrelationFunctions.jl+ is capable to compute the following correlation
+functions:
+
 These correlation functions are calculated using two different approaches (when
@@
 $0 < k < N_k$.
+
+\section{The map approach.}
+\label{sec:map}
+In this approach we actively use fast Fourier transform (FFT)
+to compute some correlation function ($S_2, F_{ss}, F_{sv}, C_2$)
+in all directions.
+The FFT algorithm let us compute auto and cross-correlation fast,
+especially on GPU.
+
+Lineal-path function doesn't have FFT realization,
+therefore, we use different approach.
+
+\subsection{Lineal-path function}
+
+Since the method for calculating $l_2$ using the FFT is unknown,
+we use the direct approach:
+scan the image in each selected direction.
+\textcolor{red}{[czech paper]} uses this method,
+but our approach saves porosity when rotating the image.
+The top-level algorithm is described below, 
+and the details are placed in the appendix.
+
+\begin{algorithmic}[1]
+  \Procedure{l2\_map}{$a, periodic, directions$}
+    \ForAll{$direction \in directions$}
+      \State $rotated \gets rotate(a, direction, periodic)$
+      \State $l2[direction] \gets scan\_l2(aligned, periodic)$
+    \EndFor
+    \State \textbf{return} $l2$
+  \EndProcedure
+\end{algorithmic}
+
+Align and rotate --- simple operations with linear computational complexity.
+Therefore, the complexity of the entire algorithm depends linearly 
+on the number of directions and on the size of the image.
+
+\subsection{Correlation map}
+
+\subsubsection{Auto- and cross-correlation using FFT}
+
+All subsequent functions are auto- or cross-correlations.
+Therefore, here we describe a method to compute them using FFT.
+
+\begin{algorithmic}[1]
+  \Procedure{cross\_correlation}{$a, b$}
+    \State $A \gets rfft(a)$\Comment{Real fast Fourie transform}
+    \State $B \gets rfft(b)$
+    \ForAll{$i \in CartesianIndices(A)$}
+      \State $C[i] \gets conj(A[i]) \cdot B[i]$
+    \EndFor
+    \State $c = irfft(C)$ 
+    \Comment{inverse rfft}
+    \State \textbf{return} $c$
+  \EndProcedure
+\end{algorithmic}
+
+One can use cross-correlation to compute auto-correlation,
+but special function would permorm better.
+
+\begin{algorithmic}[1]
+  \Procedure{auto\_correlation}{$a$}
+    \State $A \gets rfft(a)$
+    \ForAll{$i \in CartesianIndices(A)$}
+      \State $C[i] \gets |A[i]|^2$
+    \EndFor
+    \State $c = irfft(C)$ 
+    \State \textbf{return} $c$
+  \EndProcedure
+\end{algorithmic}
+
+CartesianIndices --- all indices of multidimensional array,
+therefore, the for loop describe elementwise operations
+and have linear computational complexity $O(n)$.
+For both functions computational complexity is $O(n\ log(n))$.
+
+It is worth noting, that the FFT approach imply
+periodic boundary conditions by design.
+
+\subsubsection{Total number of trials}
+
+$auto\_correlation$ and $cross\_correlation$ return non-negative number
+of success trials \cref{eq:probability}.
+To compute probability we need to count total number of trials.
+This value depends on boundary conditions.
+We realize two types: periodic and non-periodic (flat).
+
+\begin{algorithmic}[1]
+  \Procedure{total}{$a, periodic$}
+    \State $m, n \gets size(a)$
+    \If{periodic}
+      \ForAll{$i \in range(0, m - 1)$}
+        \ForAll{$j \in range(0, n - 1)$}
+          \State $total[i, j] \gets m \cdot n$
+        \EndFor
+      \EndFor
+    \Else
+      \ForAll{$i \in range(-m + 1, m - 1)$}
+        \ForAll{$j \in range(-n + 1, n - 1)$}
+          \State $i' \gets mod(i, 2m - 1)$
+          \State $j' \gets mod(j, 2n - 1)$
+          \State $total[i', j'] \gets |m - i| \cdot |n - j|$
+        \EndFor
+      \EndFor
+    \EndIf
+    \State \textbf{return} $total$
+  \EndProcedure
+\end{algorithmic}
+
+Described function is for 2D images,
+for 1D and 3D images realization is similar.
+
+if n is the number of pixels, then computational complexity
+of this funciton is $O(n)$.
+
+\subsubsection{Two-point funciton}
+
+We realize two boundary conditions: periodic and non-periodic (flat).
+For non-periodic boundary conditions one need to double image size
+by padding new values with zeros.
+Thus, if original image is $(m \times n)$,
+then expanded image will have size $(2m - 1 \times 2n - 1)$.
+
+\begin{algorithmic}[1]
+  \Procedure{s2\_map}{$a, phase, periodic$}
+    \State $a_1 \gets a = phase$
+    \If{periodic}
+      \State $a_2 \gets a_1$
+    \Else
+      \State $a_2 \gets expand(a_1)$\Comment{double image size by padding new values with zeros}
+    \EndIf
+
+    \State $success \gets AUTO\_CORRELATION(a_2)$
+
+    \State $total \gets TOTAL(a, periodic)$
+
+    \ForAll{$i \in CartesianIndices(success)$}
+      \State $s2[i] \gets success[i]\ /\ total[i]$
+    \EndFor
+
+    \State \textbf{return} $s2$
+  \EndProcedure
+\end{algorithmic}
+
+if n is the number of pixels, then computational complexity
+of this funciton is $O(n\ log(n))$.
+
+\subsubsection{Phase cross-correlation funciton}
+
+\begin{algorithmic}[1]
+  \Procedure{cc\_map}{$a, b, periodic$}
+    \If{periodic}
+      \State $a_1 \gets a$
+      \State $b_1 \gets b$
+    \Else
+      \State $a_1 \gets expand(a)$
+      \State $b_1 \gets expand(b)$
+    \EndIf
+
+    \State $success \gets CROSS\_CORRELATION(a_1, b_1)$
+
+    \State $total \gets TOTAL(a, periodic)$
+
+    \ForAll{$i \in CartesianIndices(success)$}
+      \State $cc[i] \gets success[i]\ /\ total[i]$
+    \EndFor
+
+    \State \textbf{return} $cc$
+  \EndProcedure
+\end{algorithmic}
+
+if n is the number of pixels, then computational complexity
+of this funciton is $O(n\ log(n))$.
+
+\subsection{Surface-surface function}
+
+Computation of surface-surface function consists of two steps 
+\textcolor{red}{[link to surface paper]}:
+\begin{enumerate}
+  \item extracting surface $M = \nabla I(a)$
+  \item computing $F_{ss} = S_2(M)$
+\end{enumerate}
+
+For surface extraction we use `imgradient' function
+and Sobel kernel as default kernel, 
+both defined in ImageFiltering.jl package \textcolor{red}{[add link]}.
+
+\begin{algorithmic}[1]
+  \Procedure{surf\_surf}{$a, phase, periodic, kernel$}
+    \State $a_1 \gets a = phase$
+    \State $M \gets imgradient(a_1, kernel)$
+    \State $Fss = S2\_MAP(M, periodic)$
+    \State \textbf{return} $Fss$
+  \EndProcedure
+\end{algorithmic}
+
+if n is the number of pixels, then computational complexity
+of this funciton is $O(n\ log(n))$.
+
+\subsection{Surface-void function}
+Computation of surface-void function consists of three steps 
+\textcolor{red}{[link to surface paper]}:
+\begin{enumerate}
+  \item extracting surface $M = \nabla I(a)$
+  \item extracting void phase $V = I_v(a)$
+  \item computing $F_{sv} = cross\_correlation(M, V)$
+\end{enumerate}
+
+\begin{algorithmic}[1]
+  \Procedure{surf\_void}{$a, phase, periodic, kernel$}
+    \State $a_1 \gets a = phase$
+    \State $M \gets imgradient(a_1, kernel)$
+    \State $V \gets a = 0$
+    \State $Fsv = CC\_MAP(M, V, periodic)$
+    \State \textbf{return} $Fsv$
+  \EndProcedure
+\end{algorithmic}
+
+if n is the number of pixels, then computational complexity
+of this funciton is $O(n\ log(n))$.
+
+\subsection{Cluster funciton}
+
+Computation of cluster function consists of three steps
+\begin{enumerate}
+  \item label different clusters with distinct integers
+  \item compute $S_2$ map for every cluster
+  \item add up all maps
+\end{enumerate}
+
+For labeling we use `label\_components' function from
+Images.jl package \textcolor{red}{[add link]}.
+
+\begin{algorithmic}[1]
+  \Procedure{cluster\_map}{$a, phase, periodic$}
+    \State $a_1 \gets a = phase$
+    \State $labeled\_a \gets label\_components(a_1, periodic)$
+    \State $number\_of\_labels = maximum(labeled\_a)$
+    \ForAll{$label \in range(1, number\_of\_labels)$}
+      \State $b \gets labeled\_a = label$
+      \If{label = 1}
+        \State $c2 \gets S2\_MAP(b, periodic)$
+      \Else
+        \State $c2 \gets c2 + S2\_MAP(b, periodic)$
+      \EndIf
+    \EndFor
+    \State \textbf{return} $c2$
+  \EndProcedure
+\end{algorithmic}
+
+if n is the number of pixels and N is the number of clusters, then computational complexity
+of this funciton is $O(N\ n\ log(n))$.
 
@@
 described in \cref{sec:s2}.
-
-\section{The map approach.}
-\label{sec:map}
-
-In this approach we actively use fast Fourier transform (FFT)
-to compute some correlation function ($S_2, F_{ss}, F_{sv}, C_2$)
-in all directions.
-The FFT algorithm let us compute auto and cross-correlation fast,
-especially on GPU.
-
-Lineal-path function doesn't have FFT realization,
-therefore, we use different approach.
-
-\subsection{Lineal-path function}
-
-Since the method for calculating $l_2$ using the FFT is unknown,
-we use the direct approach:
-scan the image in each selected direction.
-\textcolor{red}{[czech paper]} uses this method,
-but our approach saves porosity when rotating the image.
-The top-level algorithm is described below, 
-and the details are placed in the appendix.
-
-\begin{algorithmic}[1]
-  \Procedure{l2\_map}{$a, periodic, directions$}
-    \ForAll{$direction \in directions$}
-      \State $rotated \gets rotate(a, direction, periodic)$
-      \State $l2[direction] \gets scan\_l2(aligned, periodic)$
-    \EndFor
-    \State \textbf{return} $l2$
-  \EndProcedure
-\end{algorithmic}
-
-Align and rotate --- simple operations with linear computational complexity.
-Therefore, the complexity of the entire algorithm depends linearly 
-on the number of directions and on the size of the image.
-
-\subsection{Correlation map}
-
-\subsubsection{Auto- and cross-correlation using FFT}
-
-All subsequent functions are auto- or cross-correlations.
-Therefore, here we describe a method to compute them using FFT.
-
-\begin{algorithmic}[1]
-  \Procedure{cross\_correlation}{$a, b$}
-    \State $A \gets rfft(a)$\Comment{Real fast Fourie transform}
-    \State $B \gets rfft(b)$
-    \ForAll{$i \in CartesianIndices(A)$}
-      \State $C[i] \gets conj(A[i]) \cdot B[i]$
-    \EndFor
-    \State $c = irfft(C)$ 
-    \Comment{inverse rfft}
-    \State \textbf{return} $c$
-  \EndProcedure
-\end{algorithmic}
-
-One can use cross-correlation to compute auto-correlation,
-but special function would permorm better.
-
-\begin{algorithmic}[1]
-  \Procedure{auto\_correlation}{$a$}
-    \State $A \gets rfft(a)$
-    \ForAll{$i \in CartesianIndices(A)$}
-      \State $C[i] \gets |A[i]|^2$
-    \EndFor
-    \State $c = irfft(C)$ 
-    \State \textbf{return} $c$
-  \EndProcedure
-\end{algorithmic}
-
-CartesianIndices --- all indices of multidimensional array,
-therefore, the for loop describe elementwise operations
-and have linear computational complexity $O(n)$.
-For both functions computational complexity is $O(n\ log(n))$.
-
-It is worth noting, that the FFT approach imply
-periodic boundary conditions by design.
-
-\subsubsection{Total number of trials}
-
-$auto\_correlation$ and $cross\_correlation$ return non-negative number
-of success trials \cref{eq:probability}.
-To compute probability we need to count total number of trials.
-This value depends on boundary conditions.
-We realize two types: periodic and non-periodic (flat).
-
-\begin{algorithmic}[1]
-  \Procedure{total}{$a, periodic$}
-    \State $m, n \gets size(a)$
-    \If{periodic}
-      \ForAll{$i \in range(0, m - 1)$}
-        \ForAll{$j \in range(0, n - 1)$}
-          \State $total[i, j] \gets m \cdot n$
-        \EndFor
-      \EndFor
-    \Else
-      \ForAll{$i \in range(-m + 1, m - 1)$}
-        \ForAll{$j \in range(-n + 1, n - 1)$}
-          \State $i' \gets mod(i, 2m - 1)$
-          \State $j' \gets mod(j, 2n - 1)$
-          \State $total[i', j'] \gets |m - i| \cdot |n - j|$
-        \EndFor
-      \EndFor
-    \EndIf
-    \State \textbf{return} $total$
-  \EndProcedure
-\end{algorithmic}
-
-Described function is for 2D images,
-for 1D and 3D images realization is similar.
-
-if n is the number of pixels, then computational complexity
-of this funciton is $O(n)$.
-
-\subsubsection{Two-point funciton}
-
-We realize two boundary conditions: periodic and non-periodic (flat).
-For non-periodic boundary conditions one need to double image size
-by padding new values with zeros.
-Thus, if original image is $(m \times n)$,
-then expanded image will have size $(2m - 1 \times 2n - 1)$.
-
-\begin{algorithmic}[1]
-  \Procedure{s2\_map}{$a, phase, periodic$}
-    \State $a_1 \gets a = phase$
-    \If{periodic}
-      \State $a_2 \gets a_1$
-    \Else
-      \State $a_2 \gets expand(a_1)$\Comment{double image size by padding new values with zeros}
-    \EndIf
-
-    \State $success \gets AUTO\_CORRELATION(a_2)$
-
-    \State $total \gets TOTAL(a, periodic)$
-
-    \ForAll{$i \in CartesianIndices(success)$}
-      \State $s2[i] \gets success[i]\ /\ total[i]$
-    \EndFor
-
-    \State \textbf{return} $s2$
-  \EndProcedure
-\end{algorithmic}
-
-if n is the number of pixels, then computational complexity
-of this funciton is $O(n\ log(n))$.
-
-\subsubsection{Phase cross-correlation funciton}
-
-\begin{algorithmic}[1]
-  \Procedure{cc\_map}{$a, b, periodic$}
-    \If{periodic}
-      \State $a_1 \gets a$
-      \State $b_1 \gets b$
-    \Else
-      \State $a_1 \gets expand(a)$
-      \State $b_1 \gets expand(b)$
-    \EndIf
-
-    \State $success \gets CROSS\_CORRELATION(a_1, b_1)$
-
-    \State $total \gets TOTAL(a, periodic)$
-
-    \ForAll{$i \in CartesianIndices(success)$}
-      \State $cc[i] \gets success[i]\ /\ total[i]$
-    \EndFor
-
-    \State \textbf{return} $cc$
-  \EndProcedure
-\end{algorithmic}
-
-if n is the number of pixels, then computational complexity
-of this funciton is $O(n\ log(n))$.
-
-\subsection{Surface-surface function}
-
-Computation of surface-surface function consists of two steps 
-\textcolor{red}{[link to surface paper]}:
-\begin{enumerate}
-  \item extracting surface $M = \nabla I(a)$
-  \item computing $F_{ss} = S_2(M)$
-\end{enumerate}
-
-For surface extraction we use `imgradient' function
-and Sobel kernel as default kernel, 
-both defined in ImageFiltering.jl package \textcolor{red}{[add link]}.
-
-\begin{algorithmic}[1]
-  \Procedure{surf\_surf}{$a, phase, periodic, kernel$}
-    \State $a_1 \gets a = phase$
-    \State $M \gets imgradient(a_1, kernel)$
-    \State $Fss = S2\_MAP(M, periodic)$
-    \State \textbf{return} $Fss$
-  \EndProcedure
-\end{algorithmic}
-
-if n is the number of pixels, then computational complexity
-of this funciton is $O(n\ log(n))$.
-
-\subsection{Surface-void function}
-
-Computation of surface-void function consists of three steps 
-\textcolor{red}{[link to surface paper]}:
-\begin{enumerate}
-  \item extracting surface $M = \nabla I(a)$
-  \item extracting void phase $V = I_v(a)$
-  \item computing $F_{sv} = cross\_correlation(M, V)$
-\end{enumerate}
-
-\begin{algorithmic}[1]
-  \Procedure{surf\_void}{$a, phase, periodic, kernel$}
-    \State $a_1 \gets a = phase$
-    \State $M \gets imgradient(a_1, kernel)$
-    \State $V \gets a = 0$
-    \State $Fsv = CC\_MAP(M, V, periodic)$
-    \State \textbf{return} $Fsv$
-  \EndProcedure
-\end{algorithmic}
-
-if n is the number of pixels, then computational complexity
-of this funciton is $O(n\ log(n))$.
-
-\subsection{Cluster funciton}
-
-Computation of cluster function consists of three steps
-\begin{enumerate}
-  \item label different clusters with distinct integers
-  \item compute $S_2$ map for every cluster
-  \item add up all maps
-\end{enumerate}
-
-For labeling we use `label\_components' function from
-Images.jl package \textcolor{red}{[add link]}.
-
-\begin{algorithmic}[1]
-  \Procedure{cluster\_map}{$a, phase, periodic$}
-    \State $a_1 \gets a = phase$
-    \State $labeled\_a \gets label\_components(a_1, periodic)$
-    \State $number\_of\_labels = maximum(labeled\_a)$
-    \ForAll{$label \in range(1, number\_of\_labels)$}
-      \State $b \gets labeled\_a = label$
-      \If{label = 1}
-        \State $c2 \gets S2\_MAP(b, periodic)$
-      \Else
-        \State $c2 \gets c2 + S2\_MAP(b, periodic)$
-      \EndIf
-    \EndFor
-    \State \textbf{return} $c2$
-  \EndProcedure
-\end{algorithmic}
-
-if n is the number of pixels and N is the number of clusters, then computational complexity
-of this funciton is $O(N\ n\ log(n))$.
 

### 2022-10-04 paper-correlations.tex
Suddenly I must do another job

@@
 
-\section{Overview of supported functions and modules.}
-\label{sec:overview}
-\verb+CorrelationFunctions.jl+ is capable to compute the following correlation
-functions:
-
-These correlation functions are calculated using two different approaches (when
-applicable). The first approach is implemented in the module \code{Directional}
-and the second approach is in the module \code{Map}. The former approach (called
-the scan approach) calculates correlation functions along specified directions
-which can include axial and diagonal directions. The results of computations can
-be provided to the user separately for each requested direction or averaged
-across multiple directions. The latter approach (called the map approach)
-calculates a ``correlation map'' which holds the values of a correlation
-function in all directions. The scan and map approaches are described in
-\cref{sec:scan} and \cref{sec:map} respectively.
-
-Our package takes one-, two- or three-dimensional arrays of any element type
-(usually we restrict ourselves to integer numbers of type \code{Int} or
-\code{Int8}) and treats them as homogeneous anisotropic media. The package can
-understand two-phase as well as multiphase systems. Indeed, a multiphase system
-$A$ can be easily converted to a two-phase system $B$ by applying an indicator
-function $\chi(x)$ to each element of $A$ which can be written as $B = \chi(A)$.
-
-Correlation functions can be computed using periodic and zero-padding boundary
-conditions. With periodic boundary conditions a correlation function is
-calculated as if the input array were periodically extended to infinity,
-i.e. $A_k = A_{k+N_k}$ where $N_k$ is the k-th array dimension. With
-zero-padding the input is extended with zeros, i.e. $A_k = 0$ when
-$0 < k < N_k$.
+\verb+CorrelationFunctions.jl+ is capable to compute all these
+functions. Usually there are two implementations for a function. The first
+implementation computes a correlation function in specific predefined directions
+(i.e. orientation of test vectors thrown into a sample is fixed). There are one
+predefined direction in 1D case, four directions in 2D case and thirteen
+directions in 3D case. This implementation is somewhat slow but requires much
+less memory than the second one. The second implementation computes a
+correlation function in all directions and is faster but requires much memory.
+These implementations are contained in \code{Directional} and \code{Map} modules
+of the package correspondingly.
+
+These functions can work in periodic and non-periodic modes. Periodic mode
+assumes that an input sample is periodically continued to the whole Euclidean
+space. Non-periodic mode assumes zero-padded input.
 
@@
 \label{sec:map}
+Definition \cref{eq:s2-def} can be rewritten as follows:
+\begin{equation}
+  S_2^{(i)}(r) = \frac{F^{-1} [|F [A^{(i)}](z)|] (r)}{N(r)} \label{eq:s2-ft}
+\end{equation}
+where $A^{(i)} \xleftarrow{I^{(i)}} A$ is a binary array obtained by element-wise
+application of interface indicator $I^{(i)}$ to an input $A$, $F$ is a discrete
+Fourier transform operator and $N(r)$ is a total number of trials (vectors
+thrown into sample).
+
 In this approach we actively use fast Fourier transform (FFT)
@@
 structure. In the following sections we provide the algorithms for computation
-of the functions given in \cref{sec:overview}.
+of the functions given in \cref{sec:math}.
 

### 2022-10-06 paper-correlations.tex
Map approach (1/2)

@@
 application of interface indicator $I^{(i)}$ to an input $A$, $F$ is a discrete
-Fourier transform operator and $N(r)$ is a total number of trials (vectors
-thrown into sample).
-
-In this approach we actively use fast Fourier transform (FFT)
-to compute some correlation function ($S_2, F_{ss}, F_{sv}, C_2$)
-in all directions.
-The FFT algorithm let us compute auto and cross-correlation fast,
-especially on GPU.
-
-Lineal-path function doesn't have FFT realization,
-therefore, we use different approach.
+Fourier transform (DFT) operator and $N(r)$ is a total number of trials (vectors
+thrown into sample). If we want to calculate $S_2$ function in periodic mode we
+need only to apply \cref{eq:s2-ft} to an input to obtain the result because DFT
+implicitly continues a signal to infinity \textcolor{red}{Does this need a
+clarification?}. In non-periodic mode we need to pad an input with zeros to at
+least twice the size minus one for each dimension. In periodic mode a total
+number of trials is independent of $r$ and equals to the number of elements in
+an input array, or otherwise is calculated as described
+\textcolor{red}{Here}. The following algorithm summarizes all said above:
+\begin{algorithmic}[1]
+  \Procedure{$S_2$}{$A, phase, periodic$}
+  \If{$\neg periodic$}
+    \State $A \gets zeropad(A)$
+  \EndIf
+  \State $A^{(phase)} \gets I^{(phase)} (A)$
+  \State $\hat{A}^{(phase)} \gets F[A^{(phase)}]$
+  \State $\hat{S}_2 \gets |\hat{A}^{(phase)}| / N$
+  \State \textbf{return} $F^{-1} [\hat{S}_2]$
+  \EndProcedure
+\end{algorithmic}
+Algorithmic complexity of this implementation if $O(M \log M)$ where $M$ is the
+number of elements in the input.
+
+This function is a special case of a cross-correlation function $\rho_{ij}$
+which computes a correlation between phases $i$ and $j$ using a formula
+\begin{equation}
+  \rho_{ij}(r) = \frac{F^{-1} [F[A^{(i)}](z) \overline{F[A^{(j)}](z)}] (r)}{N(r)} \label{eq:cross-ft}
+\end{equation}
+or an equivalent algorithm
+\begin{algorithmic}[1]
+  \Procedure{$\rho_{ij}$}{$A, i, j, periodic$}
+  \If{$\neg periodic$}
+    \State $A \gets zeropad(A)$
+  \EndIf
+  \State $A^{(i)} \gets I^{(i)} (A)$
+  \State $A^{(j)} \gets I^{(j)} (A)$
+  \State $\hat{A}^{(i)} \gets F[A^{(i)}]$
+  \State $\hat{A}^{(j)} \gets F[A^{(j)}]$
+  \State $\hat{\rho} \gets \hat{A}^{(i)} \overline{\hat{A}^{(j)}} / N$
+  \State \textbf{return} $F^{-1} [\hat{\rho}]$
+  \EndProcedure
+\end{algorithmic}
+
+Cluster function can be calculated in the similar manner. Firstly, we apply an
+indicator function to an input $A$: $A^{(i)} \xleftarrow{I^{(i)}} A$. When we
+label connected components in $A^{(i)}$ using one of many popular algorithms for
+this purpose \textcolor{red}{cite something}. This algorithm must take into
+account if the function is calculated in periodic mode or not. Then $C_2$
+function is a sum of $S_2$ functions calculated for all clusters
+separately. Algorithmic complexity of this implementation is $O(MC \log M)$
+where $M$ is the number of elements in the input and $C$ is the number of
+clusters. The algorithm is as follows:
+\begin{algorithmic}[1]
+  \Procedure{$C_2$}{$A, phase, periodic$}
+  \State $A^{(phase)} \gets I^{(phase)} (A)$
+  \State $CC \gets label\_components(A^{(phase)}, periodic)$
+  \State $N \gets maximum(CC)$ \Comment Number of connected components
+  \State \textbf{return} $\sum_{n=1}^N S_2(CC, n, periodic)$
+  \EndProcedure
+\end{algorithmic}
+
+For surface-surface and surface-void functions we use an edge detection filter
+and then calculate either autocorrelation of the edge or cross-correlation of
+the edge and the void phase. The edge is extracted by convolving an input with a
+short signal $E$ (\cref{eq:filter-1d} for 1D case, \cref{eq:filter-2d} for 2D case or
+\cref{eq:filter-3d-1}-\cref{eq:filter-3d-3} for 3D case).
+\begin{align}
+  E^{1D} &= \frac{\sqrt{2}}{3} \left[
+    \begin{array}{ccc}
+        1 & -2 & 1
+      \end{array}
+    \right] \label{eq:filter-1d} \\
+  E^{2D} &= \frac{\sqrt{2}}{9} \left[
+    \begin{array}{ccc}
+        1 & 1 & 1 \\
+        1 & -8 & 1 \\
+        1 & 1 & 1
+      \end{array}
+    \right] \label{eq:filter-2d} \\
+  E^{3D}_{ij0} &= \frac{\sqrt{2}}{27} \left[
+    \begin{array}{ccc}
+        1 & 1 & 1 \\
+        1 & 1 & 1 \\
+        1 & 1 & 1
+    \end{array}
+    \right] \label{eq:filter-3d-1} \\
+  E^{3D}_{ij1} &= \frac{\sqrt{2}}{27} \left[
+    \begin{array}{ccc}
+      1 & 1 & 1 \\
+      1 & -26 & 1 \\
+      1 & 1 & 1
+    \end{array}
+    \right] \label{eq:filter-3d-2} \\
+  E^{3D}_{ij2} &= F^{3D}_{ij0} \label{eq:filter-3d-3}
+\end{align}
+
+An algorithm for $F_{ss}$ function is the following:
+\begin{algorithmic}[1]
+  \Procedure{$F_{ss}$}{$A, phase, periodic$}
+  \If{$\neg periodic$}
+    \State $A \gets zeropad(A)$
+  \EndIf
+  \State $A^{(phase)} \gets I^{(phase)} (A)$
+  \State $E_A \gets E * A^{(phase)}$
+  \State $\hat{E}_A \gets F[E_A]$
+  \State $\hat{F}_{ss} \gets |\hat{E}_A| / N$
+  \State \textbf{return} $F^{-1} [\hat{F}_{ss}]$
+  \EndProcedure
+\end{algorithmic}
 
@@
 
-Align and rotate --- simple operations with linear computational complexity.
+Align and rotate are simple operations with linear computational complexity.
 Therefore, the complexity of the entire algorithm depends linearly 
@@
 
-\subsection{Correlation map}
-
-\subsubsection{Auto- and cross-correlation using FFT}
-
-All subsequent functions are auto- or cross-correlations.
-Therefore, here we describe a method to compute them using FFT.
-
-\begin{algorithmic}[1]
-  \Procedure{cross\_correlation}{$a, b$}
-    \State $A \gets rfft(a)$\Comment{Real fast Fourie transform}
-    \State $B \gets rfft(b)$
-    \ForAll{$i \in CartesianIndices(A)$}
-      \State $C[i] \gets conj(A[i]) \cdot B[i]$
-    \EndFor
-    \State $c = irfft(C)$ 
-    \Comment{inverse rfft}
-    \State \textbf{return} $c$
-  \EndProcedure
-\end{algorithmic}
-
-One can use cross-correlation to compute auto-correlation,
-but special function would permorm better.
-
-\begin{algorithmic}[1]
-  \Procedure{auto\_correlation}{$a$}
-    \State $A \gets rfft(a)$
-    \ForAll{$i \in CartesianIndices(A)$}
-      \State $C[i] \gets |A[i]|^2$
-    \EndFor
-    \State $c = irfft(C)$ 
-    \State \textbf{return} $c$
-  \EndProcedure
-\end{algorithmic}
-
-CartesianIndices --- all indices of multidimensional array,
-therefore, the for loop describe elementwise operations
-and have linear computational complexity $O(n)$.
-For both functions computational complexity is $O(n\ log(n))$.
-
-It is worth noting, that the FFT approach imply
-periodic boundary conditions by design.
-
 \subsubsection{Total number of trials}
-
 $auto\_correlation$ and $cross\_correlation$ return non-negative number
@@
 of this funciton is $O(n)$.
-
-\subsubsection{Two-point funciton}
-
-We realize two boundary conditions: periodic and non-periodic (flat).
-For non-periodic boundary conditions one need to double image size
-by padding new values with zeros.
-Thus, if original image is $(m \times n)$,
-then expanded image will have size $(2m - 1 \times 2n - 1)$.
-
-\begin{algorithmic}[1]
-  \Procedure{s2\_map}{$a, phase, periodic$}
-    \State $a_1 \gets a = phase$
-    \If{periodic}
-      \State $a_2 \gets a_1$
-    \Else
-      \State $a_2 \gets expand(a_1)$\Comment{double image size by padding new values with zeros}
-    \EndIf
-
-    \State $success \gets AUTO\_CORRELATION(a_2)$
-
-    \State $total \gets TOTAL(a, periodic)$
-
-    \ForAll{$i \in CartesianIndices(success)$}
-      \State $s2[i] \gets success[i]\ /\ total[i]$
-    \EndFor
-
-    \State \textbf{return} $s2$
-  \EndProcedure
-\end{algorithmic}
-
-if n is the number of pixels, then computational complexity
-of this funciton is $O(n\ log(n))$.
-
-\subsubsection{Phase cross-correlation funciton}
-
-\begin{algorithmic}[1]
-  \Procedure{cc\_map}{$a, b, periodic$}
-    \If{periodic}
-      \State $a_1 \gets a$
-      \State $b_1 \gets b$
-    \Else
-      \State $a_1 \gets expand(a)$
-      \State $b_1 \gets expand(b)$
-    \EndIf
-
-    \State $success \gets CROSS\_CORRELATION(a_1, b_1)$
-
-    \State $total \gets TOTAL(a, periodic)$
-
-    \ForAll{$i \in CartesianIndices(success)$}
-      \State $cc[i] \gets success[i]\ /\ total[i]$
-    \EndFor
-
-    \State \textbf{return} $cc$
-  \EndProcedure
-\end{algorithmic}
-
-if n is the number of pixels, then computational complexity
-of this funciton is $O(n\ log(n))$.
-
-\subsection{Surface-surface function}
-
-Computation of surface-surface function consists of two steps 
-\textcolor{red}{[link to surface paper]}:
-\begin{enumerate}
-  \item extracting surface $M = \nabla I(a)$
-  \item computing $F_{ss} = S_2(M)$
-\end{enumerate}
-
-For surface extraction we use `imgradient' function
-and Sobel kernel as default kernel, 
-both defined in ImageFiltering.jl package \textcolor{red}{[add link]}.
-
-\begin{algorithmic}[1]
-  \Procedure{surf\_surf}{$a, phase, periodic, kernel$}
-    \State $a_1 \gets a = phase$
-    \State $M \gets imgradient(a_1, kernel)$
-    \State $Fss = S2\_MAP(M, periodic)$
-    \State \textbf{return} $Fss$
-  \EndProcedure
-\end{algorithmic}
-
-if n is the number of pixels, then computational complexity
-of this funciton is $O(n\ log(n))$.
-
-\subsection{Surface-void function}
-Computation of surface-void function consists of three steps 
-\textcolor{red}{[link to surface paper]}:
-\begin{enumerate}
-  \item extracting surface $M = \nabla I(a)$
-  \item extracting void phase $V = I_v(a)$
-  \item computing $F_{sv} = cross\_correlation(M, V)$
-\end{enumerate}
-
-\begin{algorithmic}[1]
-  \Procedure{surf\_void}{$a, phase, periodic, kernel$}
-    \State $a_1 \gets a = phase$
-    \State $M \gets imgradient(a_1, kernel)$
-    \State $V \gets a = 0$
-    \State $Fsv = CC\_MAP(M, V, periodic)$
-    \State \textbf{return} $Fsv$
-  \EndProcedure
-\end{algorithmic}
-
-if n is the number of pixels, then computational complexity
-of this funciton is $O(n\ log(n))$.
-
-\subsection{Cluster funciton}
-
-Computation of cluster function consists of three steps
-\begin{enumerate}
-  \item label different clusters with distinct integers
-  \item compute $S_2$ map for every cluster
-  \item add up all maps
-\end{enumerate}
-
-For labeling we use `label\_components' function from
-Images.jl package \textcolor{red}{[add link]}.
-
-\begin{algorithmic}[1]
-  \Procedure{cluster\_map}{$a, phase, periodic$}
-    \State $a_1 \gets a = phase$
-    \State $labeled\_a \gets label\_components(a_1, periodic)$
-    \State $number\_of\_labels = maximum(labeled\_a)$
-    \ForAll{$label \in range(1, number\_of\_labels)$}
-      \State $b \gets labeled\_a = label$
-      \If{label = 1}
-        \State $c2 \gets S2\_MAP(b, periodic)$
-      \Else
-        \State $c2 \gets c2 + S2\_MAP(b, periodic)$
-      \EndIf
-    \EndFor
-    \State \textbf{return} $c2$
-  \EndProcedure
-\end{algorithmic}
-
-if n is the number of pixels and N is the number of clusters, then computational complexity
-of this funciton is $O(N\ n\ log(n))$.
 

### 2022-10-06 paper-correlations.tex
Map approach (2/2)

@@
 
-\subsection{Lineal-path function}
-
-Since the method for calculating $l_2$ using the FFT is unknown,
-we use the direct approach:
-scan the image in each selected direction.
-\textcolor{red}{[czech paper]} uses this method,
-but our approach saves porosity when rotating the image.
-The top-level algorithm is described below, 
-and the details are placed in the appendix.
-
-\begin{algorithmic}[1]
-  \Procedure{l2\_map}{$a, periodic, directions$}
-    \ForAll{$direction \in directions$}
-      \State $rotated \gets rotate(a, direction, periodic)$
-      \State $l2[direction] \gets scan\_l2(aligned, periodic)$
-    \EndFor
-    \State \textbf{return} $l2$
-  \EndProcedure
-\end{algorithmic}
-
-Align and rotate are simple operations with linear computational complexity.
-Therefore, the complexity of the entire algorithm depends linearly 
-on the number of directions and on the size of the image.
-
-\subsubsection{Total number of trials}
-$auto\_correlation$ and $cross\_correlation$ return non-negative number
-of success trials \cref{eq:probability}.
-To compute probability we need to count total number of trials.
-This value depends on boundary conditions.
-We realize two types: periodic and non-periodic (flat).
-
-\begin{algorithmic}[1]
-  \Procedure{total}{$a, periodic$}
-    \State $m, n \gets size(a)$
-    \If{periodic}
-      \ForAll{$i \in range(0, m - 1)$}
-        \ForAll{$j \in range(0, n - 1)$}
-          \State $total[i, j] \gets m \cdot n$
-        \EndFor
-      \EndFor
-    \Else
-      \ForAll{$i \in range(-m + 1, m - 1)$}
-        \ForAll{$j \in range(-n + 1, n - 1)$}
-          \State $i' \gets mod(i, 2m - 1)$
-          \State $j' \gets mod(j, 2n - 1)$
-          \State $total[i', j'] \gets |m - i| \cdot |n - j|$
-        \EndFor
-      \EndFor
-    \EndIf
-    \State \textbf{return} $total$
-  \EndProcedure
-\end{algorithmic}
-
-Described function is for 2D images,
-for 1D and 3D images realization is similar.
-
-if n is the number of pixels, then computational complexity
-of this funciton is $O(n)$.
+Using \cref{eq:cross-ft} we obtain an algorithm for surface-void function:
+\begin{algorithmic}[1]
+  \Procedure{$F_{sv}$}{$A, phase, periodic$}
+  \If{$\neg periodic$}
+    \State $A \gets zeropad(A)$
+  \EndIf
+  \State $A^{(phase)} \gets I^{(phase)} (A)$
+  \State $A^{(void)} \gets I^{(void)} (A)$
+  \State $E_A \gets E * A^{(phase)}$
+  \State $\hat{E}_A \gets F[E_A]$
+  \State $\hat{A}^{(void)} \gets F[A^{(void)}]$
+  \State $\hat{F}_{sv} \gets \hat{E}_A \overline{\hat{A}^{(void)}} / N$
+  \State \textbf{return} $F^{-1} [\hat{F}_{sv}]$
+  \EndProcedure
+\end{algorithmic}
+
+\textcolor{red}{Lineal path function?}
 

### 2022-10-07 paper-correlations.tex
Scan approach (1/N)

@@
 method, full 2-point statistics for a given image). In \cref{sec:scan} we
-provide all algorithmic details for CFs computation in directions (scanning
-method). In \cref{sec:verification} we verify the all computations based on
+discuss the second method to calculate correlation functions which is called the
+scan approach. In \cref{sec:verification} we verify the all computations based on
 known analytical solutions. \cref{sec:efficiency} deals with computational
@@
 \begin{definition}
-  Lineal path function $L_2^{(i)}(\mathbf{r})$ equals to probability that a
-  vector $\mathbf{r}$ lies wholly in phase $i$ when randomly thrown into the
+  Lineal path function $L_2^{(i)}(\bm{r})$ equals to probability that a
+  vector $\bm{r}$ lies wholly in phase $i$ when randomly thrown into the
   sample.
 \end{definition}
-If a sample is isotropic a vector $\mathbf{r}$ can be replaced with its length
+If a sample is isotropic a vector $\bm{r}$ can be replaced with its length
 $r$ and the definition becomes:
@@
 \begin{definition}
-  Two point function $S_2^{(i)}(\mathbf{r})$ equals to probability that both ends
-  of a vector $\mathbf{r}$ lie in phase $i$ when the vector is randomly thrown
+  Two point function $S_2^{(i)}(\bm{r})$ equals to probability that both ends
+  of a vector $\bm{r}$ lie in phase $i$ when the vector is randomly thrown
   into the sample.
 \end{definition}
-For isotopic media a vector $\mathbf{r}$ can be again reduced to a scalar value
+For isotopic media a vector $\bm{r}$ can be again reduced to a scalar value
 $r$ (i.e. a correlation function depends only on length of a vector and not on
@@
 \begin{equation}
-  S_2^{(i)}(\mathbf{r}) = \langle I^{(i)}(\mathbf{x}) I^{(i)}(\mathbf{x} +
-  \mathbf{r}) \rangle
+  S_2^{(i)}(\bm{r}) = \langle I^{(i)}(\bm{x}) I^{(i)}(\bm{x} +
+  \bm{r}) \rangle
   \label{eq:s2-def}
@@
 \begin{equation}
-  \rho_{ij}(\mathbf{r}) = \langle I^{(i)}(\mathbf{x}) I^{(j)}(\mathbf{x} +
-  \mathbf{r}) \rangle
+  \rho_{ij}(\bm{r}) = \langle I^{(i)}(\bm{x}) I^{(j)}(\bm{x} +
+  \bm{r}) \rangle
   \label{eq:cross-def}
@@
 \begin{definition}
-  Cluster function $C_2^{(i)}(\mathbf{r})$ equals to probability that both
-  ends of a vector $\mathbf{r}$ lie in the same cluster when the vector is
+  Cluster function $C_2^{(i)}(\bm{r})$ equals to probability that both
+  ends of a vector $\bm{r}$ lie in the same cluster when the vector is
   randomly thrown into the sample. A cluster is a set of points of the same
@@
 \begin{definition}
-  Surface-surface function $F_{ss}^{(i)}(\mathbf{r})$ equals to probability that
-  both ends of a vector $\mathbf{r}$ touch the interface of phase $i$ when the
+  Surface-surface function $F_{ss}^{(i)}(\bm{r})$ equals to probability that
+  both ends of a vector $\bm{r}$ touch the interface of phase $i$ when the
   vector is randomly thrown into the sample.
@@
 \begin{definition}
-  Surface-void function $F_{sv}^{(i)}(\mathbf{r})$ equals to probability that
-  one end of a vector $\mathbf{r}$ touches the interface of phase $i$ and the
+  Surface-void function $F_{sv}^{(i)}(\bm{r})$ equals to probability that
+  one end of a vector $\bm{r}$ touches the interface of phase $i$ and the
   other end touches the void phase when the vector is randomly thrown into the
@@
 \begin{equation*}
-  M^{(i)}(\mathbf{r}) = | \nabla I^{(i)}(\mathbf{r}) |
+  M^{(i)}(\bm{r}) = | \nabla I^{(i)}(\bm{r}) |
 \end{equation*}
@@
 \begin{align}
-  F_{ss}^{(i)}(\mathbf{r}) &= \langle M^{(i)}(\mathbf{x}) M^{(i)}(\mathbf{x} +
-  \mathbf{r}) \rangle \label{eq:fss-def} \\ 
-  F_{sv}^{(i)}(\mathbf{r}) &= \langle M^{(i)}(\mathbf{x}) I^{(void)}(\mathbf{x}
-  + \mathbf{r}) \rangle \label{eq:fsv-def}
+  F_{ss}^{(i)}(\bm{r}) &= \langle M^{(i)}(\bm{x}) M^{(i)}(\bm{x} +
+  \bm{r}) \rangle \label{eq:fss-def} \\
+  F_{sv}^{(i)}(\bm{r}) &= \langle M^{(i)}(\bm{x}) I^{(void)}(\bm{x}
+  + \bm{r}) \rangle \label{eq:fsv-def}
 \end{align}
@@
   \State $N \gets maximum(CC)$ \Comment Number of connected components
-  \State \textbf{return} $\sum_{n=1}^N S_2(CC, n, periodic)$
+  \State \textbf{return} $\sum\limits_{n=1}^N S_2(CC, n, periodic)$
   \EndProcedure
@@
 
+All these algorithms contain parallelizable operations such as fast Fourier
+transform, connected components labeling and image filtering, hence they are
+perfectly suited for execution on GPUs.
+
 \section{The scan approach.}
 \label{sec:scan}
-In this approach, the input array is cut in parallel slices (``scanned'') along
-each requested direction. Each slice is then analyzed independently as
-one-dimensional system and the result is accumulated into \code{CorrelationData}
-structure. In the following sections we provide the algorithms for computation
-of the functions given in \cref{sec:math}.
+All algorithms described above are executed on the whole input and hence require
+a lot of memory. The scan approach deals with memory limitations at the cost of
+higher execution time. In this approach we select a list of predefined
+directions and cut all one dimensional slices from the input along those
+directions. Then for each direction we use an appropriate algorithm in
+\cref{sec:map} to calculate a correlation function just for that slice. When all
+slices are processed we calculate the result using the formula:
+\begin{equation*}
+  F^{\bm{d}}(r) = \frac{\sum\limits_i F^{\bm{d}}_i(r) N_i(r)}{\sum\limits_i N_i(r)}
+\end{equation*}
+Here $F^{\bm{d}}(r)$ is a correlation function computed with respect to a
+direction $\bm{d}$, $F^{\bm{d}}_i(r)$ is a ``partial'' correlation
+function calculated for a $i$-th slice and $N_i(r)$ is a total number of trials
+for a correlation length $r$ and slice $i$.
 
-Generally a correlation function $F(\bm{r})$ is defined as a probability
-$p(\bm{r})$ of event $A$ which can occur when a line segment of length
-$|\bm{r}|$ and parallel to $\bm{r}$ is randomly dropped into the input
-array. Examples of $A$ include an event that the whole segment lies in some
-phase $i$ or that it touches an interface between phases with both of its ends
-and so on.
+\textcolor{red}{Lineal path function and chord length function}
 
-The probability $p(\bm{r})$ can be expressed as
-\begin{equation}\label{eq:probability}
-  p(\bm{r}) = \frac{\text{Number of successful trials $S(\bm{r})$}}
-  {\text{Total number of trials $N(\bm{r})$}}
-\end{equation}
-
-In the scan approach we fix one direction $\bm{e}$ and accumulate the values of
-$S(\bm{r})$ and $N(\bm{r})$ so that $\bm{r} \parallel \bm{e}$ into two arrays
-\code{success} and \code{total} respectively. We then calculate \code{success}
-and \code{total} for all directions and construct a \code{CorrelationData}
-structure which holds two dictionaries with key-value pairs
-\code{(direction, success)} and \code{(direction, total)}. With this information
-it's easy to calculate a correlation function for each combination of
-correlation length and direction.
-
-\subsection{Lineal-path function}
-Lineal-path function $L_2^{(i)}(\bm{r})$ is defined as the probability that a
-line segment with the length $|\bm{r}|$ and paralel to $\bm{r}$ lies wholly in
-the phase $i$ when randomly thrown into the input array. This function for a
-one-dimensional array is computed using the algorithm described in
-\apref{linpathalg}. A multidimensional arrays is firstly cut in slices and
-\code{l2} function is calculated for each slice returning \code{success} and
-\code{total} arrays. These arrays are then accumulated as described in
-\cref{sec:scan} for final calculation of $L_2^{(i)}(\bm{r})$ function.
-
-\subsection{Two-point function}
-\label{sec:s2}
-Two-point correlation function $S_2^{(i)}(\bm{r})$ is defined as the probability
-that both ends of a line segment with the length $|\bm{r}|$ and paralel to
-$\bm{r}$ lie in the phase $i$ when the segment is randomly thrown into the input
-array. This can be expressed using the following formula:
-\begin{equation*}
-  S_2^{(i)}(\bm{r}) = \langle I^{(i)}(\bm{x}) I^{(i)}(\bm{x} + \bm{r}) \rangle
-\end{equation*}
-where $I^{(i)}(\bm{x})$ is an indicator function for the phase $i$:
-\begin{equation*}
-I^{(i)}(\bm{x}) = \left\{
-\begin{array}{ll}
-  1 & \quad \bm{x} \in \text{phase $i$} \\
-  0 & \quad \text{otherwise}
-\end{array}
-\right.
-\end{equation*}
-
-Two-point function is so heaviliy used internally in the package so we propose a
-bit more general definition for it:
-\begin{equation}
-  S_2^{\chi}(\bm{r}) = \langle \chi(\bm{x}, \bm{x} + \bm{r}) \rangle
-  \label{eq:s2gen}
-\end{equation}
-where $\chi(\bm{x_1}, \bm{x_2})$ can be understood as some arbitrary indicator
-(or membership) function on $\mathbb{R}^{2n}$ where $n$ is dimensionality of the
-input array. Vectors $\bm{x_1}$ and $\bm{x_2}$ are the coordinates of the both
-ends of a line segment thrown into the input array.
-
-If $\chi(\bm{x_1}, \bm{x_2})$ can be expressed as
-$\chi(\bm{x_1}, \bm{x_2}) = \chi_1(\bm{x_1})\chi_2(\bm{x_2})$ (what we call
-\code{SeparableIndicator} in our package) we use the following algorithm to
-calculate the array \code{success} for one-dimensional slice $a$: \footnote{From
-here on $\odot$ denotes concatenation and $:$ denotes consing (joining an
-element in front of a list).}
-\begin{algorithmic}[1]
-  \Procedure{s2sep}{$a, \chi_1, \chi_2, periodic$}
-  \If{$!periodic$}
-    \State $a \gets a \odot [0 \dots 0]$ \Comment{Pad with zeros to twice the
-      length of $a$.}
-  \EndIf
-  \State $a_1 \gets \chi_1(a)$ \Comment{apply $\chi_1$ element-wise to $a$}
-  \State $a_2 \gets \chi_2(a)$ \Comment{apply $\chi_2$ element-wise to $a$}
-  \State $f_1 \gets rfft(a_1)$ \Comment{$rfft$ is fast Fourier transform for
-    real-valued data}
-  \State $f_2 \gets rfft(a_2)$
-  \State $f_{S_2} \gets f_1 \cdot \overline{f_2}$ \Comment{multiply element-wise}
-  \State $success \gets irfft(f_{S_2})$ \Comment{$irfft$ is inverse of $rfft$}
-  \State \textbf{return} $success$
-  \EndProcedure
-\end{algorithmic}
-
-If $\chi(\bm{x})$ cannot be expressed in this way (what we call
-\code{InseparableIndicator}) the algorithm is slightly different:
-\begin{algorithmic}[1]
-  \Procedure{s2insep}{$a, \chi, periodic$}
-    \State $len \gets length(a)$
-    \If{$periodic$}
-      \State $a \gets a \odot a$
-    \EndIf
-    \State $success \gets zeros(len)$
-    \For{$shift \gets 0,len-1$}
-      \State $a_2 \gets a[shift \dots]$
-      \Comment{Take elements with index bigger than $shift$.}
-      \State $success[shift] \gets sum(\chi(a, a_2))$
-      \Comment{Apply $\chi$ element-wise and take a sum.}
-    \EndFor
-    \State \textbf{return} $success$
-  \EndProcedure
-\end{algorithmic}
-
-The array \code{total} is obtained in the same way as in $L_2$ function because
-it depends only on correlation lengths and the length of the input array.
-
-The efficiency of \code{s2sep} is $O(n\log n)$ and efficiency of
-\code{s2insep} is $O(n^2)$ where $n$ is the length of the array.
-
-\subsection{Cluster function}
-The cluster correlation function $C_2^{(i)}(\bm{r})$ is defined as the
-probability that both ends of a line segment with the length $|\bm{r}|$ and
-paralel to $\bm{r}$ lie in the same cluster of the phase $i$ when the segment is
-randomly thrown into the input array.
-
-For computation of cluster function we use \code{label\_components} function
-from \code{Image.jl} package which extracts connected comonents (clusters) from the
-binary array. Each cluster gets its own unique integer identificator. The
-identificator $0$ is reserved for the void phase.
-
-The algorithm for calculation of the array \code{success} for
-$C_2^{(i)}(\bm{r})$ for one-dimensional slice $a$ is straightforward:
-\begin{algorithmic}[1]
-  \Procedure{c2}{$a, phase, periodic$}
-  \State $a_1 \gets x = phase$ \Comment{$a$ is compared with $phase$
-    element-wise}
-  \State $c \gets label\_components(a_1)$
-  \State $\chi(x,y) \gets (x = y \ne 0)$
-  \State \textbf{return} $s2insep(c, \chi, periodic)$
-  \EndProcedure
-\end{algorithmic}
-
-\subsection{Surface-surface and surface-void functions}
-The surface-surface correlation function $F_{ss}^{(i)}(\bm{r})$ is defined as
-the probability that both ends of a line segment with the length $|\bm{r}|$ and
-paralel to $\bm{r}$ touch the interface of the phase $i$ when the segment is
-randomly thrown into the input array. This can be expressed using the following
-formula:
-\begin{equation*}
-  F_{ss}^{(i)}(\bm{r}) = \langle |\nabla I^{(i)}(\bm{x})| |\nabla I^{(i)}(\bm{x}
-  + \bm{r})| \rangle
-\end{equation*}
-where $I^{(i)}(\bm{x})$ is an indicator function for the phase $i$.
-
-The algorithm for calculation of the array \code{success} for
-$F_{ss}^{(i)}(\bm{r})$ for one-dimensional slice $a$is also straightforward:
-\begin{algorithmic}[1]
-  \Procedure{surfsurf}{$a, phase, periodic$}
-    \State $a_1 \gets a = phase$
-    \State $edge \gets \text{Detect edges in $a_1$}$
-    \State \textbf{return} $s2sep(edge, E, E, periodic)$
-    \Comment{$E(x) = x$}
-  \EndProcedure
-\end{algorithmic}
-
-The surface-void correlation function $F_{sv}^{(i)}(\bm{r})$is defined as
-follows:
-\begin{equation*}
-  F_{sv}^{(i)}(\bm{r}) = \langle |\nabla I^{(i)}(\bm{x})| I^{(void)}(\bm{x}
-  + \bm{r}) \rangle
-\end{equation*}
-
-The algorithm for calculation of the array \code{success} for
-$F_{sv}^{(i)}(\bm{r})$ for one-dimensional slice $a$ is very similar to the
-previous one:
-\begin{algorithmic}[1]
-  \Procedure{surfvoid}{$a, phase, periodic$}
-    \State $a_1 \gets a = phase$
-    \State $edge \gets \text{Detect edges in $a_1$}$
-    \State $indices \gets \text{Array of all indices in $a$}$
-    \State $\chi_1(x) \gets edge[x]$
-    \State $\chi_2(x) \gets a[x] = 0$ \Comment{$0$ is a value reserved for the
-      void phase}
-    \State \textbf{return} $s2sep(indices, \chi_1, \chi_2, periodic)$
-  \EndProcedure
-\end{algorithmic}
-
-The edges are extracted by calculating $|S(a)|$ where $S$ is the Sobel
-operator. \textbf{TODO: Cite our first paper}. Algorithmic efficiency of these
-algorithms are $O(n\log n)$ because it's implemented using \code{s2sep} and
-filtering to extract edges is $O(n)$.
-
-\subsection{Pore size function}
-The pore size correlation function $P(r)dr$ is defined as the probability that a
-randomly chosen point in the input array lies at a distance between
-$r$ and $r + dr$ from the nearest point on the pore-solid interface.
-
-As you can see this function cannot be obtained from one-dimensional slices. We
-calculate it using distance transform. For each point $\bm{x}$ distance
+Another function which does not use this approach but is in the
+\code{Directional} module for historical reasons is the pore size function
+$P(r)$. Remember that pore size function is a probability distribution
+function. In practice it is better represented as a histogram of pore size
+fractions, so all bars of the histogram sum to 1. In our approach we calculate
+this histogram using distance transform. For each point $\bm{x}$ distance
 transform $\mathcal{D}(\bm{x})$ is defined as
@@
 \end{equation*}
-
-Our algorithm for calculating $P(r)$ for a two-phase system $a$ is the
-following:
+Distance transform has many implementations \textcolor{red}{cite something}. Our
+algorithm for calculating $P(r)$ is then:
 \begin{algorithmic}[1]
-  \Procedure{poresize}{$a, nbins$}
-    \State $d \gets dist(a)$ \Comment{$dist(a)$ calculates
-      $\mathcal{D}(\bm{x})$ for each element of $a$}
-    \State $f(x) \gets x \ne 0$
-    \State $d' \gets filter(f, d)$
-    \State Bin values in $d'$ to $nbins$ bins to compute a histogram $H$
+  \Procedure{$P$}{$A, nbins$}
+    \State $D \gets \mathcal{D}(A)$ \Comment{Apply $\mathcal{D}$ to each element of $A$}
+    \State $D' = \{\forall x \in D: x \ne 0\}$
+    \State Bin values in $D'$ to $nbins$ bins to compute a histogram $H$
     \State \textbf{return} $H$
@@
 \end{algorithmic}
-
-\subsection{Phase cross-corellation function}
-
-Phase cross-correlation function $\rho_{ij}(\bm{r})$ can be defined as
-\begin{equation*}
-  \rho_{ij}(\bm{r}) = \langle I^{(i)}(\bm{x}) I^{(j)}(\bm{x} + \bm{r}) \rangle
-\end{equation*}
-which can be rewritten as \cref{eq:s2gen} with $\chi(\bm{x_1}, \bm{x_2})$
-defined as follows:
-\begin{equation*}
-  \chi(\bm{x_1}, \bm{x_2}) = I^{(i)}(\bm{x}) I^{(j)}(\bm{x})
-\end{equation*}
-Now to calculate cross-correlation function we can use \code{s2sep} function
-described in \cref{sec:s2}.
 

### 2022-10-07 paper-correlations.tex
Scan approach (2/N): Remove chord length by now

@@
 
-\subsection{Chord length function}
-The chord length function $p^{(i)}(\bm{r})d\bm{r}$ is defined as the probability of
-finding a chord of length between $|\bm{r}|$ and $|\bm{r} + d\bm{r}|$ and
-paralled to $\bm{r}$ in phase $i$. A chord is a line segment between
-intersections of an infinitely long line with the interface of the phase
-$i$. This function, again, can be calculated by cutting slices from a
-multidimensional array. The algorithm which works in $O(n)$ time where $n$ is
-the number of elements in the input is as follows:
-\begin{algorithmic}[1]
-  \Procedure{chordlength}{$a, phase, nbins$}
-    \State $lengths \gets [\quad]$
-    \State $a_1 \gets a = phase$
-    \State $p' \gets maximum(a) + 1$ \Comment{``bogus'' phase for the
-      interface of the phase $phase$}
-    \State $edge \gets p' \cdot [\text{Detect edges in $a_1$}]$ \Comment{We
-      use distance transform here}
-    \State $a_2 = min(edge + a, p')$ \Comment{Combine the original
-      array and the interface for the phase $phase$}
-    \ForAll{$dir \in \{\text{Requested directions}\}$}
-      \ForAll{$s \in \{\text{Slices of $a_2$ parallel to $dir$}\}$}
-        \State $len \gets 0$
-        \State $startonedge \gets false$
-        \ForAll{$x \in s$}
-          \If{$x = p'$}
-            \Comment{Edge found}
-            \If{$len > 1 \land startonedge$}
-              \State $lengths \gets (len-1):lengths$
-            \EndIf
-            \State $len \gets 0$
-            \State $startonedge \gets true$
-          \ElsIf{$x \ne phase$}
-            \State $startonedge \gets false$
-          \EndIf
-          \State $len \gets len + 1$
-        \EndFor
-      \EndFor
-    \EndFor
-    \State Bin elements in $lengths$ to $nbins$ bins to compute a histogram $H$
-    \State \textbf{return} $H$
-  \EndProcedure
-\end{algorithmic}
-
 \section{Verifying our algorithms}

### 2022-10-07 paper-correlations.tex
Add many formulas to look like a smart guy

@@
 \label{sec:verification}
-To verify our package we use random datasets of overlapping disks (the number of
-dimensions $n = 2$) or balls ($n = 3$) with radii $R$ and centers placed in
-points generated by Poisson point process with a parameter $\lambda$. For these
-datasets correlation functions can be given in closed-form expressions for one-,
-two- and three-dimensional cases. For the sake of testing we obtain a collection
-of disks (resp. balls) in a square (resp. cube) with the side $s$ using the
-following algorithm:
-\begin{algorithmic}[1]
-  \label{testdata}
-  \Procedure{testdata}{$s, n, R, \lambda$}
-    \State $nballs \gets poisson(\lambda s^n)$ \Comment{$poisson(\lambda)$
-      generates random numbers with Poisson distribution with parameter
-      $\lambda$.}
-    \State Generate $nballs$ random points which are uniformly distributes in
-    a cube ($n = 3$) or square ($n = 2$) with a side $s$
-    \State Draw balls (disks) of radius $R$ in those points. Store the result in
-    an array $output$.
-    \State \textbf{return} $output$
-  \EndProcedure
-\end{algorithmic}
+Our algorithms are verified by comparing their results with known closed-form
+expressions for correlation functions for some sort of input data. One kind of
+well-studied data is overlapping n-balls with fixed radius and centers generated
+by Poisson point process. Here we consider two-dimensional and three-dimensional
+cases.
 
-In two-dimensional case we test functions $L_2(r)$, $S_2(r)$, $F_{ss}(r)$ and
-$F_{sv}(r)$ using parameters $R = 100$, $\lambda = 4\cdot10^{-5}$ and
-$s = 5000$. The correlation functions are calculated in two axial directions
-with periodic boundary conditions and the result is averaged across the
-directions. Instead of taking one realization of Poisson process we take 15
-realizations and average results over them. The result can be seen on
-\cref{fig:2d}.
+\subsection{Two-dimensional case}
+Consider an infinite set of disks with radii $R$ and centers generated by
+Poisson point process with parameter $\lambda$. \textcolor{red}{Insert picture}.
 
-For pore size function $P(r)$ and chord length function $p(\bm{r})$ a slightly
-different approach is required. We take a single realization of Poisson point
-process with the same parameters $R$ and $\lambda$ in a square with the side
-$s = 20000$ (resp. $s = 12000$) and calculate histograms for Pore size
-(resp. Chord length) function. Chord length function is calculated in two axial
-directions. The theoretical values are integrated over bin ranges and compared
-with the number of elements in those bins. The results are presented on
-\cref{fig:pscl}.
+Two-point function in this case is: \cite{Torquato_book}
+\begin{equation*}
+  S_2(r) = e^{-2\lambda \left\{
+  \begin{array}{ll}
+    \pi R^2 & \quad r > 2R \\
+    \pi R^2 + r\sqrt{A}/4 - BR^2 & \quad \text{otherwise}
+  \end{array}
+  \right.}
+\end{equation*}
+Here and later $A = 4R^2 - r^2$ and $B = \arccos \frac{r}{2R}$.
 
-In three-dimensional case the approach for testing is still the same but with
-different parameters to speed up calculations. We choose $R = 20$,
-$\lambda = 3\cdot10^{-5}$ and $s = 500$. The correlation functions are
-calculated in three axial directions with periodic boundary conditions and the
-result is also averaged across the directions as in two-dimensional
-case. We take six realizations of Poisson process for averaging the results
-which are presented on \cref{fig:3d}.
+An expression for $F_{ss}$ is
+\begin{equation*}
+  F_{ss}(r) = 4S_2(r) \left\{
+  \begin{array}{ll}
+    (\pi\lambda R)^2 & \quad r > 2R \\
+    \frac{AR^2\lambda^2 r(B^2 - 2\pi B + \pi^2) + \sqrt{A}R^2\lambda}{Ar} & \quad \text{otherwise}
+  \end{array}
+  \right.
+\end{equation*}
 
-Pore size and chord length functions are calculated using the side of a cube
-$s = 700$. The results are presented on \cref{fig:pscl}.
+Surface-void function $F_{sv}$ becomes
+\begin{equation*}
+  F_{sv}(r) = 2R\lambda S_2(r) \left\{
+  \begin{array}{ll}
+    \pi & \quad r > 2R \\
+    \pi-B & \quad \text{otherwise}
+  \end{array}
+  \right.
+\end{equation*}
 
-The results for three-dimensional case are seemingly worse than for
-two-dimensional case. This can be explained by a reduced number of realizations
-of Poisson process and smaller value of $s$.
+Two-point function $L_2$:
+\begin{equation*}
+  L_2(r) = e^{-\lambda(\pi R^2 + 2rR)}
+\end{equation*}
+
+Chord length function $p$:
+\begin{equation*}
+  p(r) = 2\lambda R e^{-2\lambda rR}
+\end{equation*}
+
+And finally pore size function $P$:
+\begin{equation*}
+  P(r) = 2\lambda\pi (r+R) e^{-\lambda\pi(r^2 + 2rR)}
+\end{equation*}
+
+\textcolor{red}{Add results}
+
+\subsection{Three-dimensional case}
+Like in the previous case, consider an infinite set of balls with radii $R$ and
+centers generated by Poisson point process with parameter $\lambda$. Closed-form
+expressions for correlations functions are also known for this case.
+
+Two-point function in this case is:
+\begin{equation*}
+  S_2(r) = e^{-\lambda\pi \left\{
+  \begin{array}{ll}
+    \frac{8}{3} R^3 & \quad r > 2R \\
+    \frac{4}{3} R^3 + rR^2 - \frac{1}{12}r^3 & \quad \text{otherwise}
+  \end{array}
+  \right.}
+\end{equation*}
+
+Let $\eta = \frac{4}{3}\lambda \pi R^3$. Then an expression for $F_{ss}$ is
+\begin{equation*}
+  F_{ss}(r) = S_2(r) \left\{
+  \begin{array}{ll}
+    \frac{9\eta^2}{R^2} & \quad r > 2R \\
+    \frac{9\eta^2}{R^2}(\frac{1}{2}+\frac{r}{4R})^2 + \frac{3\eta}{2rR} & \quad \text{otherwise}
+  \end{array}
+  \right.
+\end{equation*}
+
+Surface-void function $F_{sv}$ is:
+\begin{equation*}
+  F_{sv}(r) = \frac{3\eta}{R} S_2(r) \left\{
+  \begin{array}{ll}
+    1 & \quad r > 2R \\
+    \frac{1}{2} + \frac{r}{4R} & \quad \text{otherwise}
+  \end{array}
+  \right.
+\end{equation*}
+
+Two-point function $L_2$:
+\begin{equation*}
+  L_2(r) = e^{-\lambda\pi (\frac{4}{3}R^3 + rR^2)}
+\end{equation*}
+
+Chord length function $p$:
+\begin{equation*}
+  p(r) = \pi\lambda R^2 e^{-\pi\lambda rR^2}
+\end{equation*}
+
+And finally pore size function $P$:
+\begin{equation*}
+  P(r) = 4\pi\lambda(r+R)^2 e^{-\frac{4}{3}\pi\lambda (r^3 + 3r^2R + 3rR^2)}
+\end{equation*}
+
+\textcolor{red}{Add results}
 

### 2022-10-07 verification/calc-cf-3d.jl
Verification plots (1/N)

@@ -1,0 +1,120 @@
+module Shit
+using Distributions
+using Statistics
+using CorrelationFunctions
+using DelimitedFiles
+import Random
+
+function gencenters(side, λ)
+    n = (λ * side^3) |> Poisson |> rand
+    return reduce(hcat, (rand(1:side, 3) for i in 1:n))
+end
+
+function genballs(side, R, λ)
+    sphere_side = 2R + 1
+    padded_side = side + sphere_side
+    spheres = zeros(Int8, (padded_side, padded_side, padded_side))
+    sphere = zeros(Int8, (sphere_side, sphere_side, sphere_side))
+    centers = gencenters(side, λ)
+    for i in -R:R
+        for j in -R:R
+            for k in -R:R
+                dist = i^2 + j^2 + k^2
+                if dist < R^2
+                    sphere[k+R+1, j+R+1, i+R+1] = 1
+                end
+            end
+        end
+    end
+
+    for center in (centers[:,i] for i in 1:size(centers,2))
+        x = center[1]
+        y = center[2]
+        z = center[3]
+        spheres[x:x + 2R, y:y + 2R, z:z + 2R] .|= sphere
+    end
+    return spheres[R+1:end-R-1, R+1:end-R-1, R+1:end-R-1]
+end
+
+s2_theory(r, R, λ) =
+    let a = (r > 2R) ? 8/3*R^3 : (4/3*R^3 + r*R^2 - r^3/12);
+        exp(-λ*π*a)
+    end
+
+ss_theory(r, R, λ) =
+    let η = 4/3*λ*π*R^3;
+        a = (r > 2R) ? 9η^2/R^2 : (9η^2/R^2*(1/2 + r/(4R))^2 + 3η/(2r*R))
+        a*s2_theory(r, R, λ)
+    end
+
+sv_theory(r, R, λ) =
+    let η = 4/3*λ*π*R^3;
+        a = (r > 2R) ? 1 : (1/2 + r/(4R))
+        3η/R*a*s2_theory(r, R, λ)
+    end
+
+l2_theory(r, R, λ) =
+    exp(-λ*π * (4/3*R^3 + r*R^2))
+
+cl_theory(r, R, λ) = π*λ*R^2*exp(-π*λ*r*R^2)
+function ps_theory(r, R, λ)
+    s(x) = 4π * x^2
+    v(x) = 4/3 * π * x^3
+    η  = v(R) * λ
[…]

### 2022-10-21 paper-correlations.tex
Insert plots in the paper

@@
 Consider an infinite set of disks with radii $R$ and centers generated by
-Poisson point process with parameter $\lambda$. \textcolor{red}{Insert picture}.
+Poisson point process with parameter $\lambda$.
 
@@
 
-\textcolor{red}{Add results}
+To test out package we generate a realization of random overlapping disks
+(\cref{fig:overlapping-disks}) with dimensions $10000 \times 10000$ and
+parameters $R = 40$ and $\lambda = 10^{-4}$ and compare calculated correlation
+functions with their theoretical values. The results are present on
+\cref{fig:verification}.
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=0.9\linewidth]{images/disks-fragment.png}
+  \caption[]{A fragment of overlapping disks used in testing of our library.}
+  \label{fig:overlapping-disks}
+\end{figure}
 
@@
 
-\textcolor{red}{Add results}
+To test out package we generate a realization of random overlapping disks
+(\cref{fig:overlapping-disks}) with dimensions $500 \times 500 \times 500$ and
+parameters $R = 10$ and $\lambda = 10^{-4}$ and compare calculated correlation
+functions with their theoretical values. The results are present on
+\cref{fig:verification}.
 
-\begin{figure*}[t]
+\begin{figure*}[tp]
   \centering
   \subfigure[Lineal-path correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/l2-2d.png}
-    \label{fig:l2-2d}}
+    \includegraphics[width=0.3\linewidth]{images/l2.png}
+    \label{fig:l2}}
   \hfill
   \subfigure[Two-point correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/s2-2d.png}
-    \label{fig:s2-2d}}
+    \includegraphics[width=0.3\linewidth]{images/s2.png}
+    \label{fig:s2}}
+  \hfill
+  \subfigure[Surface-surface correlation function]{
+    \includegraphics[width=0.3\linewidth]{images/ss.png}
+    \label{fig:ss}}
   \vskip\baselineskip
-  \subfigure[Surface-surface correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/ss-2d.png}
-    \label{fig:ss-2d}}
+  \subfigure[Surface-void correlation function]{
+    \includegraphics[width=0.3\linewidth]{images/sv.png}
+    \label{fig:sv}}
   \hfill
-  \subfigure[Surface-void correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/sv-2d.png}
-    \label{fig:sv-2d}}
-  \caption[]{A comparison of calculated values of $L_2(r)$, $S_2(r)$,
-    $F_{ss}(r)$ and $F_{sv}(r)$ with theoretical values for overlapping disks.}
-  \label{fig:2d}
-\end{figure*}
-
-\begin{figure*}[t]
-  \centering
-  \subfigure[Lineal-path correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/l2-3d.png}
-    \label{fig:l2-3d}}
+  \subfigure[Pore size correlation function]{
+    \includegraphics[width=0.3\linewidth]{images/ps.png}
+    \label{fig:ps}}
   \hfill
-  \subfigure[Two-point correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/s2-3d.png}
-    \label{fig:s3-3d}}
-  \vskip\baselineskip
-  \subfigure[Surface-surface correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/ss-3d.png}
-    \label{fig:ss-3d}}
-  \hfill
-  \subfigure[Surface-void correlation function]{
-    \includegraphics[width=0.475\linewidth]{images/sv-3d.png}
-    \label{fig:sv-3d}}
-  \caption[]{A comparison of calculated values of $L_2(r)$, $S_2(r)$,
-    $F_{ss}(r)$ and $F_{sv}(r)$ with theoretical values for overlapping balls.}
-  \label{fig:3d}
-\end{figure*}
-
-\begin{figure*}[t]
-  \centering
-  \subfigure[Pore size correlation function (2D)]{
-    \includegraphics[width=0.475\linewidth]{images/ps-2d.png}
-    \label{fig:ps-2d}}
-  \hfill
-  \subfigure[Chord length correlation function (2D)]{
-    \includegraphics[width=0.475\linewidth]{images/cl-2d.png}
-    \label{fig:cl-2d}}
-  \vskip\baselineskip
-  \subfigure[Pore size correlation function (3D)]{
-    \includegraphics[width=0.475\linewidth]{images/ps-3d.png}
-    \label{fig:ps-3d}}
-  \hfill
-  \subfigure[Chord length correlation function (3D)]{
-    \includegraphics[width=0.475\linewidth]{images/cl-3d.png}
-    \label{fig:cl-3d}}
-  \caption[]{A comparison of calculated values of $P(r)$ and $p(r)$
-    with theoretical values for overlapping disks (\cref{fig:ps-2d} and
-    \cref{fig:cl-2d}) and balls(\cref{fig:ps-3d} and \cref{fig:cl-3d}).}
-  \label{fig:pscl}
+  \subfigure[Chord length correlation function]{
+    \includegraphics[width=0.3\linewidth]{images/cl.png}
+    \label{fig:cl}}
+  \caption[]{A comparison of calculated and theoretical values of correlation
+    functions for overlapping disks and balls.}
+  \label{fig:verification}
 \end{figure*}

### 2022-10-21 verification/calc-cf-2d.jl

@@ -3,6 +3,8 @@ using Distributions
 using Statistics
 using CorrelationFunctions
 using DelimitedFiles
+using Images
+using FileIO
 import Random
 
 function gencenters(side, λ)
@@ -84,6 +86,7 @@ function main!()
 
     Random.seed!(13435)
     data = gendisks(side, R, λ)
+    save("disks.png", Gray.(data))
     println(sum(data)/length(data))
     for (name, theory, impl) in fns
         calc = data |> impl |> mean

### 2022-10-21 verification/plot.py

@@ -7,11 +7,12 @@ s2_2d = np.loadtxt('s2-2d.dat')
 s2_3d = np.loadtxt('s2-3d.dat')
 
 plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 18)
+plt.rc('font', size = 25)
 plt.plot(s2_2d[:, 0], 'r-', linewidth = 2.0)
 plt.plot(s2_2d[:, 1], 'b-', linewidth = 2.0)
 plt.plot(s2_3d[:, 0], 'r--', linewidth = 2.0)
 plt.plot(s2_3d[:, 1], 'b--', linewidth = 2.0)
+plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
 plt.xlim([0, 130])
 plt.xlabel('Correlation length $r$')
 plt.ylabel('Two point function $S_2(r)$')
@@ -23,11 +24,12 @@ l2_2d = np.loadtxt('l2-2d.dat')
 l2_3d = np.loadtxt('l2-3d.dat')
 
 plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 18)
+plt.rc('font', size = 25)
 plt.plot(l2_2d[:, 0], 'r-', linewidth = 2.0)
 plt.plot(l2_2d[:, 1], 'b-', linewidth = 2.0)
 plt.plot(l2_3d[:, 0], 'r--', linewidth = 2.0)
 plt.plot(l2_3d[:, 1], 'b--', linewidth = 2.0)
+plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
 plt.xlim([0, 150])
 plt.xlabel('Correlation length $r$')
 plt.ylabel('Lineal-path function $L_2(r)$')
@@ -39,11 +41,12 @@ ss_2d = np.loadtxt('ss-2d.dat')
 ss_3d = np.loadtxt('ss-3d.dat')
 
 plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 18)
+plt.rc('font', size = 25)
 plt.plot(ss_2d[:, 0], 'r-', linewidth = 2.0)
 plt.plot(ss_2d[:, 1], 'b-', linewidth = 2.0)
 plt.plot(ss_3d[:, 0], 'r--', linewidth = 2.0)
 plt.plot(ss_3d[:, 1], 'b--', linewidth = 2.0)
[…]

### 2022-10-21 verification/plot.py
Make bars semitransparent

@@ -78,8 +78,8 @@ ps_prob_3d = np.loadtxt('pore_size-3d-prob.dat')
 
 plt.figure(figsize = (10, 8), dpi = 300)
 plt.rc('font', size = 25)
-plt.hist(ps_hist_2d, density = True, bins = 20)
-plt.hist(ps_hist_3d, density = True, bins = 20)
+plt.hist(ps_hist_2d, density = True, bins = 20, alpha = 0.5)
+plt.hist(ps_hist_3d, density = True, bins = 20, alpha = 0.5)
 plt.plot(ps_prob_2d[:,0], ps_prob_2d[:,1])
 plt.plot(ps_prob_3d[:,0], ps_prob_3d[:,1])
 plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
@@ -97,8 +97,8 @@ cl_prob_3d = np.loadtxt('chord_length-3d-prob.dat')
 
 plt.figure(figsize = (10, 8), dpi = 300)
 plt.rc('font', size = 25)
-plt.hist(cl_hist_2d, density = True, bins = 20)
-plt.hist(cl_hist_3d, density = True, bins = 20)
+plt.hist(cl_hist_2d, density = True, bins = 20, alpha = 0.5)
+plt.hist(cl_hist_3d, density = True, bins = 20, alpha = 0.5)
 plt.plot(cl_prob_2d[:,0], cl_prob_2d[:,1])
 plt.plot(cl_prob_3d[:,0], cl_prob_3d[:,1])
 plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)

### 2022-10-24 paper-correlations.tex
Fix a typo
New data for real samples

@@
     \right] \label{eq:filter-3d-2} \\
-  E^{3D}_{ij2} &= F^{3D}_{ij0} \label{eq:filter-3d-3}
+  E^{3D}_{ij2} &= E^{3D}_{ij0} \label{eq:filter-3d-3}
 \end{align}
@@
 
+\section{Examples and applications}
+\label{sec:examples}
+After the verification of our computational approach based on analytical
+solution we can apply our algorithms to evaluate correlation functions for
+different porous media images, including real XCT and SEM images. A summary
+which contains information about type of the images, dimensions and resolution
+can be found in \cref{tab:samples}. XCT images of sandstones are provided by
+Digital Rocks Portal\cite{DigitalRocks}. Correlation functions of these samples
+can be seen on \cref{fig:real-data}.
+
+\begin{table*}[!pt]
+  \centering
+  \begin{ruledtabular}
+    \begin{tabular}{|c|c|c|c|}
+      Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) \\
+      \hline
+      Bandera Brown sandstone & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
+      Bentheimer sandstone    & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
+      Kirby sandstone         & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
+      Sandstone 1 & SEM &  $1280 \times 869$ & 0.10 \\
+      Sandstone 2 & SEM &  $1280 \times 869$ & 0.05 \\
+      Carbonate 1 & SEM &  $1024 \times 691$ & 0.06
+    \end{tabular}
+  \end{ruledtabular}
+  \caption{Summary of samples used for calculation of correlation functions.}
+  \label{tab:samples}
+\end{table*}
+
+\begin{figure*}[pt]
+  \centering
+  \subfigure[Bandera Brown sandstone]{
+    \includegraphics[width=0.3\linewidth]{real-data/BanderaBrown_2d25um_binary.png}
+    \label{fig:bandera}}
+  \hfill
+  \subfigure[Bentheimer sandstone]{
+    \includegraphics[width=0.3\linewidth]{real-data/Bentheimer_2d25um_binary.png}
+    \label{fig:bentheimer}}
+  \hfill
+  \subfigure[Kirby sandstone]{
+    \includegraphics[width=0.3\linewidth]{real-data/Kirby_2d25um_binary.png}
+    \label{fig:kirby}}
+  \vskip\baselineskip
+  \subfigure[Sandstone 1]{
+    \includegraphics[width=0.3\linewidth]{real-data/sandstone1.png}
+    \label{fig:real-sandstone-1}}
+  \hfill
+  \subfigure[Sandstone 2]{
+    \includegraphics[width=0.3\linewidth]{real-data/sandstone2.png}
+    \label{fig:real-sandstone-2}}
+  \hfill
+  \subfigure[Carbonate 1]{
+    \includegraphics[width=0.3\linewidth]{real-data/carbonate1.png}
+    \label{fig:real-carbonate-1}}
+  \caption[]{Plots of correlation functions for real samples.}
+  \label{fig:real-data}
+\end{figure*}
+
 \section{Efficiency of our algorithms}
@@
 
-\section{Examples and applications}
-\label{sec:examples}
-After the verification of our computational approach based on analytical
-solution we can apply our algorithms to evaluate correlation functions for
-different porous media images, including real XCT and SEM images.
-
-For demonstration purposes, we computed correlation functions for images of
-sandstone found on Digital Rocks Portal \cite{DigitalRocks} all of which have
-dimensions $1000 \times 1000 \times 1000$. The result can be seen on
-\cref{fig:real-data}.
-
-\begin{figure*}[t]
-  \centering
-  \subfigure[$S_2^{(void)}$ correlation function.]{
-    \includegraphics[width=0.3\linewidth]{real-data-plots/real-s2void.png}
-    \label{fig:real-s2}}
-  \hfill
-  \subfigure[$L_2^{(void)}$ correlation function.]{
-    \includegraphics[width=0.3\linewidth]{real-data-plots/real-l2void.png}
-    \label{fig:real-l2}}
-  \subfigure[$C_2^{(void)}$ correlation function.]{
-    \includegraphics[width=0.3\linewidth]{real-data-plots/real-c2void.png}
-    \label{fig:real-c2}}
-  \vskip\baselineskip
-  \subfigure[$F_{ss}$ correlation function.]{
-    \includegraphics[width=0.3\linewidth]{real-data-plots/real-ss.png}
-    \label{fig:real-ss}}
-  \subfigure[$F_{sv}$ correlation function.]{
-    \includegraphics[width=0.3\linewidth]{real-data-plots/real-sv.png}
-    \label{fig:real-sv}}
-  \caption[]{Plots of correlation functions for images of sandstones.}
-  \label{fig:real-data}
-\end{figure*}
-
 \section{Summary}

### 2022-10-24 real-data/plot-c2.py

@@ -1,28 +1,0 @@
-#!/usr/bin/env python
-
-import numpy as np
-import matplotlib.pyplot as plt
-
-names = [
-    "BanderaBrown",
-    "Bentheimer",
-    "Berea",
-    "BSG",
-    "CastleGate",
-    "Kirby"
-]
-
-plt.figure(figsize = (10, 9), dpi = 300)
-plt.rc('font', size = 20)
-
-for name in names:
-    path = name + '_2d25um_binary.pbm-c2void.dat'
-    data = np.loadtxt(path)
-    plt.plot(data)
-
-plt.xlabel('Correlation length $r$')
-plt.ylabel('$C_2^{(void)}(r)$')
-#plt.yscale('log')
-plt.legend(names)
-plt.savefig('../real-data-plots/real-c2void.png')
-#plt.show()

### 2022-10-24 real-data/plot-l2.py

@@ -1,28 +1,0 @@
-#!/usr/bin/env python
-
-import numpy as np
-import matplotlib.pyplot as plt
-
-names = [
-    "BanderaBrown",
-    "Bentheimer",
-    "Berea",
-    "BSG",
-    "CastleGate",
-    "Kirby"
-]
-
-plt.figure(figsize = (10, 9), dpi = 300)
-plt.rc('font', size = 20)
-
-for name in names:
-    path = name + '_2d25um_binary.pbm-l2void.dat'
-    data = np.loadtxt(path)
-    plt.plot(data)
-
-plt.xlabel('Correlation length $r$')
-plt.ylabel('$L_2^{(void)}(r)$')
-plt.yscale('log')
-plt.legend(names)
-plt.savefig('../real-data-plots/real-l2void.png')
-#plt.show()

### 2022-10-24 real-data/plot-s2.py

@@ -1,26 +1,0 @@
-#!/usr/bin/env python
-
-import numpy as np
-import matplotlib.pyplot as plt
-
-names = [
-    "BanderaBrown",
-    "Bentheimer",
-    "Berea",
-    "BSG",
-    "CastleGate",
-    "Kirby"
-]
-
-plt.figure(figsize = (10, 9), dpi = 300)
-plt.rc('font', size = 20)
-
-for name in names:
-    path = name + '_2d25um_binary.pbm-s2void.dat'
-    data = np.loadtxt(path)
-    plt.plot(data)
-
-plt.xlabel('Correlation length $r$')
-plt.ylabel('$S_2^{(void)}(r)$')
-plt.legend(names)
-plt.savefig('../real-data-plots/real-s2void.png')

### 2022-10-24 real-data/plot-ss.py

@@ -1,28 +1,0 @@
-#!/usr/bin/env python
-
-import numpy as np
-import matplotlib.pyplot as plt
-
-names = [
-    "BanderaBrown",
-    "Bentheimer",
-    "Berea",
-    "BSG",
-    "CastleGate",
-    "Kirby"
-]
-
-plt.figure(figsize = (10, 9), dpi = 300)
-plt.rc('font', size = 20)
-
-for name in names:
-    path = name + '_2d25um_binary.pbm-surfsurf.dat'
-    data = np.loadtxt(path)
-    plt.plot(np.arange(10, 500), data[10:])
-
-plt.ticklabel_format(scilimits = (0, 0), axis = 'y')
-plt.xlabel('Correlation length $r$')
-plt.ylabel('$F_{ss}(r)$')
-plt.legend(names)
-plt.savefig('../real-data-plots/real-ss.png')
-#plt.show()

### 2022-10-24 real-data/plot-sv.py

@@ -1,28 +1,0 @@
-#!/usr/bin/env python
-
-import numpy as np
-import matplotlib.pyplot as plt
-
-names = [
-    "BanderaBrown",
-    "Bentheimer",
-    "Berea",
-    "BSG",
-    "CastleGate",
-    "Kirby"
-]
-
-plt.figure(figsize = (10, 9), dpi = 300)
-plt.rc('font', size = 20)
-
-for name in names:
-    path = name + '_2d25um_binary.pbm-surfvoid.dat'
-    data = np.loadtxt(path)
-    plt.plot(data)
-
-plt.ticklabel_format(scilimits = (0, 0), axis = 'y')
-plt.xlabel('Correlation length $r$')
-plt.ylabel('$F_{sv}(r)$')
-plt.legend(names)
-plt.savefig('../real-data-plots/real-sv.png')
-#plt.show()

### 2022-10-24 paper-correlations.tex
Example of calculations

@@
   \vskip\baselineskip
+  \subfigure[Bandera Brown sandstone (correlation functions)]{
+    \includegraphics[width=0.3\linewidth]{real-data/BanderaBrown_2d25um_binary-plot.png}
+    \label{fig:bandera-plt}}
+  \hfill
+  \subfigure[Bentheimer sandstone (correlation functions)]{
+    \includegraphics[width=0.3\linewidth]{real-data/Bentheimer_2d25um_binary-plot.png}
+    \label{fig:bentheimer-plt}}
+  \hfill
+  \subfigure[Kirby sandstone (correlation functions)]{
+    \includegraphics[width=0.3\linewidth]{real-data/Kirby_2d25um_binary-plot.png}
+    \label{fig:kirby-plt}}
+  \vskip\baselineskip
   \subfigure[Sandstone 1]{
@@
     \includegraphics[width=0.3\linewidth]{real-data/carbonate1.png}
+    \label{fig:real-carbonate-1-plt}}
+  \vskip\baselineskip
+  \subfigure[Sandstone 1 (correlation functions)]{
+    \includegraphics[width=0.3\linewidth]{real-data/sandstone1-plot.png}
+    \label{fig:real-sandstone-1-plt}}
+  \hfill
+  \subfigure[Sandstone 2 (correlation functions)]{
+    \includegraphics[width=0.3\linewidth]{real-data/sandstone2-plot.png}
+    \label{fig:real-sandstone-2-plt}}
+  \hfill
+  \subfigure[Carbonate 1 (correlation functions)]{
+    \includegraphics[width=0.3\linewidth]{real-data/carbonate1-plot.png}
     \label{fig:real-carbonate-1}}

### 2022-10-24 real-data/plot.py

@@ -1,0 +1,30 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+import sys
+
+data = sys.argv[1]
+s2 = np.loadtxt(data + '-s2.dat')
+l2 = np.loadtxt(data + '-l2.dat')
+c2 = np.loadtxt(data + '-c2.dat')
+ss = np.loadtxt(data + '-surfsurf.dat')
+sv = np.loadtxt(data + '-surfvoid.dat')
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 25)
+plt.plot(s2, linewidth = 2.0)
+plt.plot(l2, linewidth = 2.0)
+plt.plot(c2, linewidth = 2.0)
+plt.plot(ss, linewidth = 2.0)
+plt.plot(sv, linewidth = 2.0)
+plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
+plt.xlim([0, 150])
+plt.xlabel('Correlation length $r$')
+plt.ylabel('Correlation function')
+plt.legend(['Two point function $S_2(r)$',
+            'Lineal-path function $L_2(r)$',
+            'Cluster function $C_2(r)$',
+            'Surface-surface function $F_{ss}(r)$',
+            'Surface-void function $F_{sv}(r)$'])
+plt.savefig(data + '-plot.png')

### 2023-04-26 paper-correlations.tex
Fix a typo
Rework map section

@@
   randomly thrown into the sample. A cluster is a set of points of the same
-  phase $i$ where any to points can be connected by a path lying entirely in
+  phase $i$ where any two points can be connected by a path lying entirely in
   that phase.
@@
 
-The next two functions describe surface of a sample. These functions are
-surface-surface and surface-void functions. For homogenous media their
-definitions are:
-\begin{definition}
-  Surface-surface function $F_{ss}^{(i)}(\bm{r})$ equals to probability that
-  both ends of a vector $\bm{r}$ touch the interface of phase $i$ when the
-  vector is randomly thrown into the sample.
-\end{definition}
-and
-\begin{definition}
-  Surface-void function $F_{sv}^{(i)}(\bm{r})$ equals to probability that
-  one end of a vector $\bm{r}$ touches the interface of phase $i$ and the
-  other end touches the void phase when the vector is randomly thrown into the
-  sample.
-\end{definition}
-If we introduce an interface indicator function
+The next two functions are called surface-surface ($F_{ss}$) and surface-void
+($F_{sv}$) functions and describe surface of a sample. We skip strict verbal
+definitions and introduce an interface indicator function instead:
 \begin{equation*}
@@
 \end{equation*}
-we can define these functions mathematically as
+Here differentiation is understood in the sense of generalized functions,
+because an ordinary differential of $I$ is either zero or undefined. For
+homogenous media definitions of these functions are:
 \begin{align}
@@
 \end{align}
-As always, there are versions of these functions applicable to scalar argument
-for isotropic media.
+These functions are defined for media with dimensionality of 2 and
+higher. $F_{sv}$ is a physical quantity inversely proportional to length and
+$F_{ss}$ is inversionaly proportional to surface area, therefore we can use
+$\mu m^{-1}$ to measure surface-void and $\mu m^{-2}$ to measure surface-surface
+functions. Putting it simply, surface-void function measures length (2D case) or
+surface (3D case) of a part of the interface which lies in the void phase of
+porous medium shifted by vector $\bm{r}$. Surface-surface function characterizes
+intersections of interfaces of porous medium and its shifted version. As always,
+there are versions of these functions applicable to scalar argument for
+isotropic media.
 
@@
 $p^{(i)}(r)dz$ = Probability of finding a chord of length between $r$ and $r+dr$
-in phase $i$. Chords are all of the line segments between intersections of an
-infinitely long line with the two-phase interface.
+in phase $i$. Chord is a line segment which lies entirely in the same phase and
+touches the interface with its ends.
 \end{definition}
@@
 less memory than the second one. The second implementation computes a
-correlation function in all directions and is faster but requires much memory.
-These implementations are contained in \code{Directional} and \code{Map} modules
-of the package correspondingly.
+correlation function in all possible directions and is faster but requires much
+memory. These implementations are contained in \code{Directional} and \code{Map}
+modules of the package correspondingly.
 
@@
 Fourier transform (DFT) operator and $N(r)$ is a total number of trials (vectors
-thrown into sample). If we want to calculate $S_2$ function in periodic mode we
-need only to apply \cref{eq:s2-ft} to an input to obtain the result because DFT
-implicitly continues a signal to infinity \textcolor{red}{Does this need a
-clarification?}. In non-periodic mode we need to pad an input with zeros to at
-least twice the size minus one for each dimension. In periodic mode a total
-number of trials is independent of $r$ and equals to the number of elements in
-an input array, or otherwise is calculated as described
-\textcolor{red}{Here}. The following algorithm summarizes all said above:
+thrown into the sample). If we want to calculate $S_2$ function in periodic mode
+we need only to apply \cref{eq:s2-ft} to an input to obtain the result. In
+non-periodic mode we need to pad an input with zeros to at least twice the size
+minus one for each dimension. In periodic mode a total number of trials is
+independent of $r$ and equals to the number of elements in an input array. In
+non-periodic mode $N(r)$ is calculated as described \textcolor{red}{Here}. The
+following algorithm summarizes all said above:
 \begin{algorithmic}[1]
@@
   \State $A \gets zeropad(A)$
+  \Comment Pad with at least $2\cdot size(A, i) - 1$ zeros for each dimension $i$.
   \EndIf
@@
   \State $\hat{S}_2 \gets |\hat{A}^{(phase)}| / N$
+  \Comment $N$ is an array with numbers of trials
   \State \textbf{return} $F^{-1} [\hat{S}_2]$
@@
 the edge and the void phase. The edge is extracted by convolving an input with a
-short signal $E$ (\cref{eq:filter-1d} for 1D case, \cref{eq:filter-2d} for 2D case or
-\cref{eq:filter-3d-1}-\cref{eq:filter-3d-3} for 3D case).
-\begin{align}
-  E^{1D} &= \frac{\sqrt{2}}{3} \left[
-    \begin{array}{ccc}
-        1 & -2 & 1
+short low-pass filter $H$. It has a width $7$ and all its coefficients with
+exception of the central coefficient are inversely proportional to distance
+from the center:
+\begin{equation}
+  \begin{aligned}
+    H_{ij} &= S \left\{
+    \begin{array}{cc}
+      \frac{1}{\sqrt{(i-3)^2 + (j-3)^2}} & \quad i \ne 3, j \ne 3 \\
+      C & \quad \text{otherwise}
     \end{array}
-    \right] \label{eq:filter-1d} \\
-  E^{2D} &= \frac{\sqrt{2}}{9} \left[
-    \begin{array}{ccc}
-        1 & 1 & 1 \\
-        1 & -8 & 1 \\
-        1 & 1 & 1
+    \right. \\
+    H_{ijk} &= S \left\{
+    \begin{array}{cc}
+      \frac{1}{\sqrt{(i-3)^2 + (j-3)^2 + (k-3)^3}} & \quad i \ne 3, j \ne 3, k
+      \ne 3 \\
+      C & \quad \text{otherwise}
     \end{array}
-    \right] \label{eq:filter-2d} \\
-  E^{3D}_{ij0} &= \frac{\sqrt{2}}{27} \left[
-    \begin{array}{ccc}
-        1 & 1 & 1 \\
-        1 & 1 & 1 \\
-        1 & 1 & 1
-    \end{array}
-    \right] \label{eq:filter-3d-1} \\
-  E^{3D}_{ij1} &= \frac{\sqrt{2}}{27} \left[
-    \begin{array}{ccc}
-      1 & 1 & 1 \\
-      1 & -26 & 1 \\
-      1 & 1 & 1
-    \end{array}
-    \right] \label{eq:filter-3d-2} \\
-  E^{3D}_{ij2} &= E^{3D}_{ij0} \label{eq:filter-3d-3}
-\end{align}
+    \right.
+  \end{aligned}
+  \label{eq:filter-7x7}
+\end{equation}
+where $C$ is such that all coefficients of $H'$ sum to zero, and $S$ equals to
+$30.45849$ in 2D and $172.96232$ in 3D case.
 
@@
   \State $A^{(phase)} \gets I^{(phase)} (A)$
-  \State $E_A \gets E * A^{(phase)}$
-  \State $\hat{E}_A \gets F[E_A]$
-  \State $\hat{F}_{ss} \gets |\hat{E}_A| / N$
+  \State $A_H \gets H * A^{(phase)}$
+  \State $\hat{A}_H \gets F[A_H]$
+  \State $\hat{F}_{ss} \gets |\hat{A}_H| / N$
   \State \textbf{return} $F^{-1} [\hat{F}_{ss}]$
@@
   \State $A^{(void)} \gets I^{(void)} (A)$
-  \State $E_A \gets E * A^{(phase)}$
-  \State $\hat{E}_A \gets F[E_A]$
+  \State $A_H \gets H * A^{(phase)}$
+  \State $\hat{A}_H \gets F[A_H]$
   \State $\hat{A}^{(void)} \gets F[A^{(void)}]$
-  \State $\hat{F}_{sv} \gets \hat{E}_A \overline{\hat{A}^{(void)}} / N$
+  \State $\hat{F}_{sv} \gets \hat{A}_H \overline{\hat{A}^{(void)}} / N$
   \State \textbf{return} $F^{-1} [\hat{F}_{sv}]$
@@
 
-\textcolor{red}{Lineal path function?}
+Our library does not have an implementation for lineal-path maps, although we
+know that such implementations exist.
 

### 2023-04-26 paper-correlations.tex
Style and typos fixes

@@
 higher execution time. In this approach we select a list of predefined
-directions and cut all one dimensional slices from the input along those
+directions and cut all one-dimensional slices from the input along those
 directions. Then for each direction we use an appropriate algorithm in
@@
 $P(r)$. Remember that pore size function is a probability distribution
-function. In practice it is better represented as a histogram of pore size
-fractions, so all bars of the histogram sum to 1. In our approach we calculate
-this histogram using distance transform. For each point $\bm{x}$ distance
-transform $\mathcal{D}(\bm{x})$ is defined as
+function. In practice it is better represented as a histogram of pore sizes
+found in the input. In our approach we calculate this histogram using distance
+transform. For each point $\bm{x}$ distance transform $\mathcal{D}(\bm{x})$ is
+defined as
 \begin{equation*}
@@
     \State $D \gets \mathcal{D}(A)$ \Comment{Apply $\mathcal{D}$ to each element of $A$}
-    \State $D' = \{\forall x \in D: x \ne 0\}$
+    \State $D' = \{ x \in D: x \ne 0\}$
+    \Comment Remove zeros
     \State Bin values in $D'$ to $nbins$ bins to compute a histogram $H$
@@
 
-\section{Verifying our algorithms}
+\section{Verification of our algorithms}
 \label{sec:verification}
@@
 \appendix
-\section{Algorithm of computation of lineal-phase function}
+\section{Algorithm of computation of lineal-path function}
 \label{linpathalg}

### 2023-04-27 paper-correlations.tex
Write about number of trials

@@
 independent of $r$ and equals to the number of elements in an input array. In
-non-periodic mode $N(r)$ is calculated as described \textcolor{red}{Here}. The
-following algorithm summarizes all said above:
+non-periodic mode $N(r)$ is calculated as described in
+\cref{sec:number-of-trials}. The following algorithm summarizes all said above:
 \begin{algorithmic}[1]
@@
 \appendix
+\section{Computation of number of trials for non-periodic mode}
+\label{sec:number-of-trials}
+Here we assume that an input is padded with zeros to the length $2s_i - 1$
+across each dimension $i$ where $s_i$ is the size of the unpadded input in that
+dimension. For each dimension we calculate a sequence
+\begin{equation*}
+  N^i_j = \left\{
+  \begin{array}{cc}
+    s_i - j & \quad j \in \overline{0, s_i-1} \\
+    j - s_i + 1 & \quad j \in \overline{s_i, 2s_i-2}
+  \end{array}
+  \right.
+\end{equation*}
+
+When a number of trials is calculated as follows:
+\begin{equation*}
+  N_{i_1, i_2, \dots, i_n} = \prod_{k=1}^n N^k_{i_k}
+\end{equation*}
+Here $n$ is a number of dimensions and $i_k$ is an index into the output array
+for $k$-th dimension.
+
 \section{Algorithm of computation of lineal-path function}

### 2023-04-28 paper-correlations.tex
Remove unused appendix
Update an algorithm for L₂

@@
 
+An algorithm for computation of linear-path function for one-dimensional slice
+is present below. Here $a$ is a one-dimensional input array, $phase$ can be
+void, solid or some other phase, and $periodic$ is a boolean value which equals
+to true if we compute $L_2$ in periodic mode and false otherwise. The efficiency
+of the proposed algorithm is $O(n)$ where $n$ is the length of the array.
+\begin{algorithmic}[1]
+  \Procedure{l2}{$a, phase, periodic$}
+    \State $len \gets length(a)$
+    \State $result \gets zeros(len)$
+    \State $runs \gets countruns(a, phase)$
+    \ForAll{$run \in runs$}
+      \State $updateruns(result, run)$
+    \EndFor
+    \If{$periodic$}
+      \State $first \gets first(a)$
+      \State $last \gets last(a)$
+      \If{$first = last$}
+        \State $updateperiodic(result, first, last)$
+      \EndIf
+    \EndIf
+    \State \textbf{return} $success$ divided by number of trials
+    (see \cref{sec:number-of-trials})
+  \EndProcedure
+  \\
+  \Procedure{countruns}{$a, phase$}
+    \State $runslist \gets [\ ]$
+    \State $runs \gets 0$
+    \ForAll{$x \in a$}
+      \If{$x = phase$}
+        \State $runs \gets runs + 1$
+      \ElsIf{$runs \ne 0$}
+        \Comment Add $runs$ to the accumulator
+        \State $runslist \gets runs:runslist$
+        \State $runs \gets 0$
+      \EndIf
+    \EndFor
+    \If{$runs \ne 0$}
+      \State $runslist \gets runs:runslist$
+    \EndIf
+    \State \textbf{return} $runslist$
+  \EndProcedure
+  \\
+  \Procedure{updateruns}{$array, runs$}
+    \State $r \gets runs$
+    \For{$idx = 0,\ idx < runs$}
+      \State $array[idx] \gets array[idx] + r$
+      \State $r \gets r - 1$
+    \EndFor
+  \EndProcedure
+  \\
+  \Procedure{updateperiodic}{$a, first, last$}
+    \State $sum \gets first + last$
+    \For{$idx = 0,\ idx < sum$}
+      \State $up \gets \min(idx, first, last, sum - idx)$
+      \State $a[idx] \gets a[idx] + up$
+    \EndFor
+  \EndProcedure
+\end{algorithmic}
+
 \textcolor{red}{Lineal path function and chord length function}
@@
 
-\begin{algorithmic}[1]
-  \Procedure{countruns}{$a, len, phase$}
-    \State $runslist \gets [\quad]$
-    \State $runs \gets 0$
-    \ForAll{$x \in a$}
-      \If{$x = phase$}
-        \State $runs \gets runs + 1$
-      \ElsIf{$runs \ne 0$}
-        \State $runslist \gets runs:runslist$
-        \State $runs \gets 0$
-      \EndIf
-    \EndFor
-    \If{$runs \ne 0$}
-      \State $runslist \gets runs:runslist$
-    \EndIf
-    \State \textbf{return} $runslist$
-  \EndProcedure
-  \\
-  \Procedure{updateruns}{$a, runs, n$}
-    \For{$idx = 1,n$}
-      \State $a[idx] \gets a[idx] + runs$
-      \State $runs \gets runs - 1$
-    \EndFor
-  \EndProcedure
-  \\
-  \Procedure{updateperiodic}{$a, first, last, n$}
-    \State $sum \gets first + last$
-    \State $n \gets \min(n, sum)$
-    \For{$idx = 1,n$}
-      \State $a \gets \min(idx - 1, first, last, sum - (idx - 1))$
-      \State $a[idx] \gets a[idx] + a$
-    \EndFor
-  \EndProcedure
-  \\
-  \Procedure{l2}{$a, phase, maxlen, periodic$}
-    \State $success \gets zeros(maxlen)$
-    \State $total \gets zeros(maxlen)$
-    \State $len \gets length(a)$
-    \State $nupdates \gets \min(len, maxlen)$
-    \State $runs \gets countruns(a, maxlen, phase)$
-    \ForAll{$run \in runs$}
-      \State $updateruns(success, run, \min(run, maxlen))$
-    \EndFor
-    \If{$periodic$}
-      \State $first \gets first(a)$
-      \State $last \gets last(a)$
-      \If{$first = last$}
-        \State $updateperiodic(success, first, last, nupdates)$
-      \EndIf
-      \State Increment $total[\text{from} \, 1 \, \text{to} \, nupdates]$ by
-      $len$
-    \Else
-      \State $updateruns(total, len, nupdates)$
-    \EndIf
-    \State \textbf{return} $success$ divided by $total$ element-wise.  
-  \EndProcedure
-\end{algorithmic}
-
-\section{Algorithm for image rotation}
-\label{rotating}
-
-\begin{algorithmic}[1]
-  \Procedure{rotate}{$a, direction, periodic$}
-    \ForAll{$slice \in eachslice(a)$}
-      \State $shift \gets get\_shift(slice, direction)$
-      \State $rotated\_slice \gets circshift(slice, shift)$
-      \If{$! periodic$}
-        \State $rotated\_slice[end - shift:end] \gets -1$
-      \EndIf
-    \EndFor
-  \State \textbf{return} $rotated$
-  \EndProcedure
-\end{algorithmic}
-
 \bibliography{apssamp}

### 2023-04-28 paper-correlations.tex
Add an algorithm for chord_length function

@@
 \begin{algorithmic}[1]
-  \Procedure{l2}{$a, phase, periodic$}
-    \State $len \gets length(a)$
+  \Procedure{l2}{$A, phase, periodic$}
+    \State $len \gets length(A)$
     \State $result \gets zeros(len)$
-    \State $runs \gets countruns(a, phase)$
+    \State $runs \gets countruns(A, phase)$
     \ForAll{$run \in runs$}
@@
     \If{$periodic$}
-      \State $first \gets first(a)$
-      \State $last \gets last(a)$
+      \State $first \gets first(A)$
+      \State $last \gets last(A)$
       \If{$first = last$}
@@
   \\
-  \Procedure{countruns}{$a, phase$}
+  \Procedure{countruns}{$A, phase$}
     \State $runslist \gets [\ ]$
     \State $runs \gets 0$
-    \ForAll{$x \in a$}
+    \ForAll{$x \in A$}
       \If{$x = phase$}
@@
   \\
-  \Procedure{updateruns}{$array, runs$}
+  \Procedure{updateruns}{$A, runs$}
     \State $r \gets runs$
     \For{$idx = 0,\ idx < runs$}
-      \State $array[idx] \gets array[idx] + r$
+      \State $A[idx] \gets A[idx] + r$
       \State $r \gets r - 1$
@@
   \\
-  \Procedure{updateperiodic}{$a, first, last$}
+  \Procedure{updateperiodic}{$A, first, last$}
     \State $sum \gets first + last$
@@
       \State $up \gets \min(idx, first, last, sum - idx)$
-      \State $a[idx] \gets a[idx] + up$
+      \State $A[idx] \gets A[idx] + up$
     \EndFor
@@
 
-\textcolor{red}{Lineal path function and chord length function}
+Before computation of chord length function an input array must be pre-processed
+to label an interface for the phase of interest. For this purpose we use
+distance transform function defined as follows:
+\begin{equation}
+  \mathcal{D}(\bm{x})= \left\{
+  \begin{array}{ll}
+    0 & \quad \bm{x} \in \text{solid phase} \\
+    \min\limits_{y \in \text{solid phase}} \rho(\bm{x},\bm{y}) & \quad \text{otherwise}
+  \end{array}
+\right. \label{eq:distance-transform}
+\end{equation}
+Distance transform has many implementations \textcolor{red}{cite something},
+many of them can be parralelized on GPU. Array pre-processing is performed in
+\code{cl\_preprocess} function and per-slice chord lengths accumulation is
+performed in \code{cl\_slice} function. After all cord lengths are accumulated
+they can be binned in a histogram. In the following algorithm we suppose that
+phases in the input are labeled with non-negative integers.
+\begin{algorithmic}[1]
+  \Procedure{chord\_length}{$A, phase$}
+    \State $A' \gets cl\_preprocess(A, phase)$
+    \State $chordlist \gets [\ ]$
+    \ForAll{$slice \in slices(A')$}
+      \State Append $cl\_slice(A', phase)$ to $chordlist$
+    \EndFor
+    \State \textbf{return} $chordlist$ or $histogram(chordlist)$  
+  \EndProcedure
+  \\
+  \Procedure{cl\_preprocess}{$A, phase$}
+    \State $A' \gets I^{(phase)}(A)$
+    \State $edge\_label \gets maximum(A) + 1$
+    \Comment Choose an unused label to mark elements of the interface with
+    \State $A_D = \mathcal{D}(A')$
+    \Comment Perform distance transform for all elements of $A'$
+    \State $E \gets edge\_label \cdot (A_D = 1)$
+    \Comment We consider elements of $A_D$ equal to $1$ to be part of the
+    interface and mark them so
+    \State $R \gets min(A + E, edge\_label)$
+    \Comment Add interface labels to the input
+    \State \textbf{return} $R$
+  \EndProcedure
+  \\
+  \Procedure{cl\_slice}{$A, phase$}
+    \State $chordlist \gets [\ ]$
+    \State $len \gets 0$
+    \State $maybechord \gets false$
+    \State $edge\_label \gets maximum(A)$
+    \ForAll{$x \in A$}
+      \If{$x = edge\_label$}
+        \If{$len > 1\ and\ maybechord$}
+          \State $chordlist \gets (len-1):chordlist$
+          \Comment A chord with length $len-1$ voxels is found
+        \EndIf
+        \State $len \gets 0$
+        \State $maybechord \gets true$
+      \ElsIf{$x \ne phase$}
+        \State $maybechord \gets false$
+      \EndIf
+      \State $len \gets len+1$
+    \EndFor
+    \State \textbf{return} $chordlist$
+    \EndProcedure
+\end{algorithmic}
 

### 2023-04-28 paper-correlations.tex
Update pore size function

@@
 \end{algorithmic}
+This implementation also works in linear time.
 
-Another function which does not use this approach but is in the
-\code{Directional} module for historical reasons is the pore size function
+Another function built on top of distance transform is the pore size function
 $P(r)$. Remember that pore size function is a probability distribution
 function. In practice it is better represented as a histogram of pore sizes
-found in the input. In our approach we calculate this histogram using distance
-transform. For each point $\bm{x}$ distance transform $\mathcal{D}(\bm{x})$ is
-defined as
-\begin{equation*}
-  \mathcal{D}(\bm{x})= \left\{
-  \begin{array}{ll}
-    0 & \quad \bm{x} \in \text{solid phase} \\
-    \min\limits_{y \in \text{solid phase}} \rho(\bm{x},\bm{y}) & \quad \text{otherwise}
-  \end{array}
-\right.
-\end{equation*}
-Distance transform has many implementations \textcolor{red}{cite something}. Our
-algorithm for calculating $P(r)$ is then:
+found in the input. Our algorithm for calculating $P(r)$ is as follows:
 \begin{algorithmic}[1]
-  \Procedure{$P$}{$A, nbins$}
-    \State $D \gets \mathcal{D}(A)$ \Comment{Apply $\mathcal{D}$ to each element of $A$}
+  \Procedure{$P$}{$A$}
+    \State $D \gets \mathcal{D}(A)$
+    \Comment Apply $\mathcal{D}$ (\cref{eq:distance-transform}) to each element of $A$
     \State $D' = \{ x \in D: x \ne 0\}$
     \Comment Remove zeros
-    \State Bin values in $D'$ to $nbins$ bins to compute a histogram $H$
+    \State Bin values in $D'$ to histogram $H$
     \State \textbf{return} $H$
+    \Comment Alternatively just return $D'$
   \EndProcedure

### 2023-05-02 paper-correlations.tex
A note about preprocessing
Add units of measurement

@@
 function calculated for a $i$-th slice and $N_i(r)$ is a total number of trials
-for a correlation length $r$ and slice $i$.
+for a correlation length $r$ and slice $i$. Some algorithms require
+preprocessing stages before cutting the input in slices, e.g. image filtering
+for edge detection or connected components labeling is performed on the whole
+array, not on slices.
 
@@
 (\cref{fig:overlapping-disks}) with dimensions $10000 \times 10000$ and
-parameters $R = 40$ and $\lambda = 10^{-4}$ and compare calculated correlation
-functions with their theoretical values. The results are present on
+parameters $R = 40\ px$ and $\lambda = 10^{-4}\ px^{-2}$ and compare calculated
+correlation functions with their theoretical values. The results are present on
 \cref{fig:verification}.
@@
 (\cref{fig:overlapping-disks}) with dimensions $500 \times 500 \times 500$ and
-parameters $R = 10$ and $\lambda = 10^{-4}$ and compare calculated correlation
-functions with their theoretical values. The results are present on
+parameters $R = 10\ px$ and $\lambda = 10^{-4}\ px^{-3}$ and compare calculated
+correlation functions with their theoretical values. The results are present on
 \cref{fig:verification}.

### 2023-05-02 paper-correlations.tex
Remove junk

@@
 
-\section{Algorithm of computation of lineal-path function}
-\label{linpathalg}
-The algorithm below calculates $L_2^{(phase)}$ correlation function for
-one-dimensional array $a$. The result is an array of $L_2$ values for
-correlation lengths from $0$ to $maxlen-1$. If $periodic$ is true (resp. false)
-then periodic (resp. zero padding) boundary conditions are used. The entry point of the
-algorithm is the function L2. The efficiency of the proposed algorithm is $O(n)$
-where $n$ is the length of the array.
-
 \bibliography{apssamp}

### 2023-05-02 paper-correlations.tex
Do not mention value noise

@@
 
-\section{Efficiency of our algorithms}
+\section{Execution times of our algorithms}
 \label{sec:efficiency}
-To measure efficiecy of our algorithms we use a machine with the following
-configuration:
+To measure execution times of our algorithms we use a machine with the following
+configuration:\textcolor{red}{Must be configuration of Asus notebook}
 \begin{itemize}
@@
 We generate two (resp. three) dimensional square (resp. cubic) binary arrays
-with different number of elements. Each element $a_{ij}$ (resp. $a_{ijk}$) of a
-two-dimensional (resp. three-dimensional) array is calculated as follows:
-\begin{align*}
-  a_{ij} & = \left\{
-  \begin{array}{ll}
-    0 & \quad vn(5i/s, 5j/s, 0, 5, 34365) < 0.5 \\
-    1 & \quad \text{otherwise}
-  \end{array}
-  \right. \\
-  a_{ijk} & = \left\{
-  \begin{array}{ll}
-    0 & \quad vn(5i/s, 5j/s, 5k/s, 5, 34365) < 0.5 \\
-    1 & \quad \text{otherwise}
-  \end{array}
-  \right.
-\end{align*}
-Here $vn(x,y,z,o,s)$ is a value noise function. We fix a number of
-octaves $o = 5$ and a random seed $s = 34365$. The particular implementation of
-value noise for our measurements was taken from \code{ValueNoise.jl} package. An
-example of a two-dimensional image generated in this way is on
-\cref{fig:valuenoise}.
+with different sides. An array used for measurements contains two solid disks
+(resp. balls) surrounded by void phase, therefore it is excected for $C_2$
+function to perform two times slower than $S_2$.
 
@@
 three-dimensional case and calculate execution time for each function. All
-functions are calculated with default values of optional arguments (that is:
-closed walls boundary conditions and computation along axial directions).
+functions are calculated along axial directions using periodic boundary
+conditions.
 
@@
 array. If it's \code{CuArray} rather than generic \code{AbstractArray} then CUDA
-implementation is chosen. Please note, that CPU versions are much slower, so we
-choose a different sides of squares ($s = 700, 1350, \dots, 7000$) and cubes
-($s = 10, 45, \dots, 350$) for evaluation of the performance.
+implementation is chosen. \textcolor{red}{Please note, that CPU versions are
+  much slower, so we choose a different sides of squares
+  ($s = 700, 1350, \dots, 7000$) and cubes ($s = 10, 45, \dots, 350$)
+  for evaluation of the performance.}
 
@@
 versions (when available) are faster than CPU versions and limited only by
-amount of video memory. Functions in \code{Directional} are slower (with
-exception of the lineal-path function) but are also useful in medium
-reconstruction algorithms which utilize simulated annealing.
+amount of video memory. Functions in \code{Directional} are the slowest among
+other implementations, but require less memory.
 
+% Replace by two disks?
 \begin{figure}[ht]
   \centering
-  \includegraphics[width=0.9\linewidth]{images/timing-image.png}
-  \caption[]{An example of 2D image used in timing measurements.}
+  \includegraphics[width=0.6\linewidth]{images/timing-image.png}
+  \caption[]{One of 2D image used in timing measurements.}
   \label{fig:valuenoise}

### 2023-05-02 timings/plot-timings.py
Update scripts used for measurement of execution speed

@@ -4,40 +4,50 @@ import numpy as np
 import matplotlib.pyplot as plt
 
 names2d = [
-    'gpu/s2-2d.dat',
-    'gpu/surfsurf-2d.dat',
-    'gpu/surfvoid-2d.dat',
-    'gpu/c2-2d.dat',
+    'chord_length-directional-2d.dat',
+    'pore_size-directional-2d.dat',
+    's2-directional-2d.dat',
+    'l2-directional-2d.dat',
+    'c2-directional-2d.dat',
+    'surf2-directional-2d.dat',
+    'surfvoid-directional-2d.dat',
 ]
 
 names3d = [
-    'gpu/s2-3d.dat',
-    'gpu/surfsurf-3d.dat',
-    'gpu/surfvoid-3d.dat',
-    'gpu/c2-3d.dat',
+    'chord_length-directional-3d.dat',
+    'pore_size-directional-3d.dat',
+    's2-directional-3d.dat',
+    'l2-directional-3d.dat',
+    'c2-directional-3d.dat',
+    'surf2-directional-3d.dat',
+    'surfvoid-directional-3d.dat',
 ]
 
 markers = [
-    '.', 'o', 's', 'p'
+    '.', 'o', 's', 'p', '.', 'o', 's'
 ]
 
 data2d = [np.loadtxt(name) for name in names2d]
 data3d = [np.loadtxt(name) for name in names3d]
 
 labels = [
-    'Two-point function',
+    'Chord length function',
+    'Pore size function',
+    'Two point function',
+    'Lineal-path function',
+    'Cluster function',
     'Surface-surface function',
     'Surface-void function',
-    'Cluster function'
 ]
 
-plt.figure(dpi = 300)
+#plt.figure(dpi = 300)
 
 for data, marker in zip(data3d, markers):
-    data[:, 0] = data[:, 0] ** 3
-    plt.plot(data[:, 0], data[:, 1], marker = marker)
+    #plt.plot(data[:, 0], data[:, 1], marker = marker)
+    plt.errorbar(data[:, 0], data[:, 1], marker = marker, yerr = data[:, 2])
 
 plt.legend(labels)
-plt.xlabel('Number of voxels')
+plt.xlabel('Side of an image, pixels')
 plt.ylabel('Time of execution, seconds')
-plt.savefig('time-3d.png')
+#plt.savefig('time-3d.png')
+plt.show()

### 2023-05-02 timings/timings.jl

@@ -1,38 +1,97 @@
 module Timings
 
-using ValueNoise
-using CorrelationFunctions
-using Statistics
+import CorrelationFunctions.Map as M
+import CorrelationFunctions.Directional as D
+import Statistics as S
+import Distributions as Dist
 using DelimitedFiles
+using NPZ
 
-getdata(side, :: Val{2}) =
-    [value_noise(3x/side, 3y/side, 0.0, 4, 34365) < 0.5 for x in 1:side, y in 1:side]
+function draw_balls(s)
+    array = falses(s...)
+    center1 = Iterators.repeated(0.3, length(s))
+    center2 = Iterators.repeated(0.7, length(s))
+    r = 0.2
 
-getdata(side, :: Val{3}) =
-    [value_noise(3x/side, 3y/side, 3z/side, 4, 34365) < 0.5 for x in 1:side, y in 1:side, z in 1:side]
+    for idx in CartesianIndices(array)
+        dist1 = sum((Tuple(idx) ./s .- center1) .^ 2)
+        dist2 = sum((Tuple(idx) ./s .- center2) .^ 2)
+        if dist1 <= r^2 || dist2 <= r^2
+            array[idx] = true
+        end
+    end
 
-const data_2d = (getdata(side, Val(2)) for side in 1000:1000:6000)
-const data_3d = (getdata(side, Val(3)) for side in 50:50:300)
+    return array
+end
+
+function prepare!()
+    for side in 1000:1000:6000
+        println(side)
+        balls = draw_balls((side, side))
+        npzwrite("disks-$(side).npy", balls)
+    end
+
+    for side in 50:50:300
+        println(side)
+        balls = draw_balls((side, side, side))
+        npzwrite("balls-$(side).npy", balls)
+    end
+end
 
 fst((x, _)) = x
 snd((_, y)) = y
 
-function calculate_time!(fn, dim, prefix)
-    data_arrays = (dim == 2) ? data_2d : data_3d
+struct FnSpec
+    fn   :: Function
+    name :: String
+end
 
-    timings = map(data_arrays) do data
+struct ExecResult
+    side  :: Int
+    mean  :: Float64
+    range :: Float64
+end
+
+s(res :: ExecResult) = res.side
+μ(res :: ExecResult) = res.mean
+r(res :: ExecResult) = res.range
+
+(fn :: FnSpec)(data) = fn.fn(data)
+
+function estimate_range(array :: AbstractArray, prob)
+    len = length(array)
+    t = Dist.TDist(len - 1)
[…]

### 2023-05-03 paper-correlations.tex
Rewrite chord_length again

@@
     \State $r \gets runs$
-    \For{$idx = 0,\ idx < runs$}
+    \For{$idx \gets 0, runs - 1$}
       \State $A[idx] \gets A[idx] + r$
@@
     \State $sum \gets first + last$
-    \For{$idx = 0,\ idx < sum$}
+    \For{$idx \gets 0, sum - 1$}
       \State $up \gets \min(idx, first, last, sum - idx)$
@@
 Before computation of chord length function an input array must be pre-processed
-to label an interface for the phase of interest. For this purpose we use
+to find an interface for the phase of interest. For this purpose we use
 distance transform function defined as follows:
@@
 Distance transform has many implementations \textcolor{red}{cite something},
-many of them can be parralelized on GPU. Array pre-processing is performed in
-\code{cl\_preprocess} function and per-slice chord lengths accumulation is
-performed in \code{cl\_slice} function. After all cord lengths are accumulated
-they can be binned in a histogram. In the following algorithm we suppose that
-phases in the input are labeled with non-negative integers.
+many of them can be parralelized on GPU. In \code{chord\_length} function we
+firstly apply distance transform to an input to find the interface and then
+accumulate chord length in per-slice manner. Finally, cord lengths can be binned
+in a histogram.
 \begin{algorithmic}[1]
   \Procedure{chord\_length}{$A, phase$}
-    \State $A' \gets cl\_preprocess(A, phase)$
-    \State $chordlist \gets [\ ]$
-    \ForAll{$slice \in slices(A')$}
-      \State Append $cl\_slice(A', phase)$ to $chordlist$
+    \State $A' \gets I^{(phase)}(A)$
+    \State $A_E \gets \mathcal{D}(A') = 1$
+    \Comment We consider elements for which the distance transform equals to $1$
+    to be part of the interface
+    \State $chord\_list \gets [\ ]$
+    \ForAll{$(S', S_E) \in zip(slices(A'), slices(A_E))$}
+      \Comment iterate through all one-dimensional slices in $A'$ and
+      corresponding slices in $A_E$
+      \State $l \gets 0$
+      \State $maybe\_chord \gets False$
+      \For{$idx \gets 0, length(S')-1$}
+        \If{$S_E[idx]$}
+          \Comment Interface found
+          \If{$l > 1\ and\ maybe\_chord$}
+            \Comment Chord found
+            \State $chord\_list \gets l:chord\_list$
+          \EndIf
+          \State $l \gets 0$
+          \State $maybe\_chord \gets True$
+        \ElsIf{$\neg S'[idx]$}
+          \Comment We are not in the phase of interest
+          \State $maybe\_chord \gets False$
+        \EndIf
       \EndFor
-    \State \textbf{return} $chordlist$ or $histogram(chordlist)$  
-  \EndProcedure
-  \\
-  \Procedure{cl\_preprocess}{$A, phase$}
-    \State $A' \gets I^{(phase)}(A)$
-    \State $edge\_label \gets maximum(A) + 1$
-    \Comment Choose an unused label to mark elements of the interface with
-    \State $A_D = \mathcal{D}(A')$
-    \Comment Perform distance transform for all elements of $A'$
-    \State $E \gets edge\_label \cdot (A_D = 1)$
-    \Comment We consider elements of $A_D$ equal to $1$ to be part of the
-    interface and mark them so
-    \State $R \gets min(A + E, edge\_label)$
-    \Comment Add interface labels to the input
-    \State \textbf{return} $R$
-  \EndProcedure
-  \\
-  \Procedure{cl\_slice}{$A, phase$}
-    \State $chordlist \gets [\ ]$
-    \State $len \gets 0$
-    \State $maybechord \gets false$
-    \State $edge\_label \gets maximum(A)$
-    \ForAll{$x \in A$}
-      \If{$x = edge\_label$}
-        \If{$len > 1\ and\ maybechord$}
-          \State $chordlist \gets (len-1):chordlist$
-          \Comment A chord with length $len-1$ voxels is found
-        \EndIf
-        \State $len \gets 0$
-        \State $maybechord \gets true$
-      \ElsIf{$x \ne phase$}
-        \State $maybechord \gets false$
-      \EndIf
-      \State $len \gets len+1$
     \EndFor
-    \State \textbf{return} $chordlist$
+    \State \textbf{return} $chord\_list$ or $histogram(chord\_list)$
   \EndProcedure

### 2023-05-03 timings/plot-timings.py
exec times plots: Number of voxels on X axis

@@ -43,11 +43,10 @@ labels = [
 #plt.figure(dpi = 300)
 
 for data, marker in zip(data3d, markers):
-    #plt.plot(data[:, 0], data[:, 1], marker = marker)
-    plt.errorbar(data[:, 0], data[:, 1], marker = marker, yerr = data[:, 2])
+    plt.errorbar(data[:, 0] ** 3, data[:, 1], marker = marker, yerr = data[:, 2])
 
 plt.legend(labels)
-plt.xlabel('Side of an image, pixels')
+plt.xlabel('Number of voxels')
 plt.ylabel('Time of execution, seconds')
 #plt.savefig('time-3d.png')
 plt.show()

### 2023-05-04 timings/timings.jl
Update timings.jl

@@ -4,6 +4,7 @@ import CorrelationFunctions.Map as M
 import CorrelationFunctions.Directional as D
 import Statistics as S
 import Distributions as Dist
+import CUDA
 using DelimitedFiles
 using NPZ
 
@@ -38,9 +39,6 @@ function prepare!()
     end
 end
 
-fst((x, _)) = x
-snd((_, y)) = y
-
 struct FnSpec
     fn   :: Function
     name :: String
@@ -51,6 +49,14 @@ struct ExecResult
     mean  :: Float64
     range :: Float64
 end
+
+abstract type AbstractCU end
+
+struct CPU <: AbstractCU end
+struct GPU <: AbstractCU end
+
+upload_to_cu(array, :: CPU) = array
+upload_to_cu(array, :: GPU) = CUDA.CuArray(array)
 
 s(res :: ExecResult) = res.side
 μ(res :: ExecResult) = res.mean
@@ -67,21 +73,22 @@ function estimate_range(array :: AbstractArray, prob)
     return Dist.quantile(t, 1 - α/2) * S.std(array) / sqrt(len)
 end
 
-function calculate_time!(fn :: FnSpec, dim, prefix)
+function calculate_time!(fn :: FnSpec, dim, prefix, cu :: AbstractCU = CPU())
     println(fn.name)
     data_arrays = (dim == 2) ?
         ("disks-$(side).npy" for side in 1000:1000:6000) :
         ("balls-$(side).npy" for side in 50:50:300)
+    upload(array) = upload_to_cu(array, cu)
 
     # Make sure JIT is done
-    data_arrays |> first |> npzread |> fn
+    data_arrays |> first |> npzread |> upload |> fn
 
     timings = map(data_arrays) do datapath
-        data = npzread(datapath)
+        data = datapath |> npzread |> upload
         side = size(data, 1)
         println(side)
         times = Float64[]
-        while sum(times) < 10 || length(times) < 3
+        while sum(times) < 10 || length(times) < 4
             atime = time_ns()
             fn(data)
             atime = (time_ns() - atime) / 10^9
@@ -108,9 +115,20 @@ const fn_dir = [
     FnSpec(data -> D.surfvoid(data, true; periodic = true), "surfvoid")
 ]
 
+const fn_map = [
+    FnSpec(data -> M.s2(data, true; periodic = true), "s2"),
[…]

### 2023-05-05 paper-correlations.tex
Fix a typo
Update execution plots

@@
 the edge and the void phase. The edge is extracted by convolving an input with a
-short low-pass filter $H$. It has a width $7$ and all its coefficients with
+short high-pass filter $H$. It has a width $7$ and all its coefficients with
 exception of the central coefficient are inversely proportional to distance
@@
 To measure execution times of our algorithms we use a machine with the following
-configuration:\textcolor{red}{Must be configuration of Asus notebook}
+configuration:
 \begin{itemize}
-\item \textbf{CPU}: AMD Ryzen 5 1600X
-\item \textbf{Memory}: 32~Gb DDR4-2400 memory
+\item \textbf{CPU}: AMD Ryzen 7 5800X
+\item \textbf{Memory}: 32~Gb DDR4 memory
 \item \textbf{GPU}: Nvidia Tesla V100 with 32~Gb video memory
@@
 with different sides. An array used for measurements contains two solid disks
-(resp. balls) surrounded by void phase, therefore it is excected for $C_2$
-function to perform two times slower than $S_2$.
+(resp. balls) surrounded by void phase.
 
-To measure efficiency of \code{Directional} module we generate ten arrays with
-a side of a square $s = 1000, 2000, \dots, 10000$ pixels for two-dimensional
-case and ten arrays with a side of a cube $s = 50, 100, \dots, 500$ voxels for
-three-dimensional case and calculate execution time for each function. All
-functions are calculated along axial directions using periodic boundary
-conditions.
+To measure efficiency of our code we generate six arrays with a side of a square
+$s = 1000, 2000, \dots, 6000$ pixels for two-dimensional case and six arrays
+with a side of a cube $s = 50, 100, \dots, 300$ voxels for three-dimensional
+case and calculate execution time for each function. All functions are
+calculated using periodic boundary conditions. Functions which use per-slice
+directional approach are calculated along axial directions.
 
-With the \code{Map} module we follow the same procedure. Many functions in
-\code{Map} can utilize Nvidia's GPUs using the CUDA library. For example,
-two-point correlation function uses FFT transform optimized for Nvidia GPUs and
-provided in \code{CUDA.FFT} package. We provide execution times for both CPU and
-GPU. The choice between CPU or GPU version is made depending on type of input
-array. If it's \code{CuArray} rather than generic \code{AbstractArray} then CUDA
-implementation is chosen. \textcolor{red}{Please note, that CPU versions are
-  much slower, so we choose a different sides of squares
-  ($s = 700, 1350, \dots, 7000$) and cubes ($s = 10, 45, \dots, 350$)
-  for evaluation of the performance.}
+Functions which calculate full correlation maps are suitable for running on CPU
+and GPU, so we provide execution times for both. The cluster function still uses
+an algorithm for closest component labeling which works only on CPU, so there is
+a potentional for improvement for this function.
 
@@
 versions (when available) are faster than CPU versions and limited only by
-amount of video memory. Functions in \code{Directional} are the slowest among
-other implementations, but require less memory.
+amount of video memory. Functions in module \code{Directional} (which utilize
+per-slice directional approach) are the slowest among other implementations, but
+require less memory.
 

### 2023-05-05 timings/plot-timings-directional.py

@@ -1,0 +1,61 @@
+#!/usr/local/bin/python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+names2d = [
+    'chord_length-dir-2d.dat',
+    'pore_size-dir-2d.dat',
+    's2-dir-2d.dat',
+    'l2-dir-2d.dat',
+    'c2-dir-2d.dat',
+    'surf2-dir-2d.dat',
+    'surfvoid-dir-2d.dat',
+]
+
+names3d = [
+    'chord_length-dir-3d.dat',
+    'pore_size-dir-3d.dat',
+    's2-dir-3d.dat',
+    'l2-dir-3d.dat',
+    'c2-dir-3d.dat',
+    'surf2-dir-3d.dat',
+    'surfvoid-dir-3d.dat',
+]
+
+markers = [
+    '.', 'o', 's', 'p', '.', 'o', 's'
+]
+
+data2d = [np.loadtxt(name) for name in names2d]
+data3d = [np.loadtxt(name) for name in names3d]
+
+labels = [
+    'Chord length function',
+    'Pore size function',
+    'Two point function',
+    'Lineal-path function',
+    'Cluster function',
+    'Surface-surface function',
+    'Surface-void function',
+]
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 18)
+for data, marker in zip(data3d, markers):
+    plt.errorbar(data[:, 0] ** 3, data[:, 1], marker = marker, yerr = data[:, 2])
+plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
+plt.legend(labels)
+plt.xlabel('Number of voxels')
+plt.ylabel('Time of execution, seconds')
+plt.savefig('time-3d.png', bbox_inches = 'tight')
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 18)
+for data, marker in zip(data2d, markers):
+    plt.errorbar(data[:, 0] ** 2, data[:, 1], marker = marker, yerr = data[:, 2])
+plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
+plt.legend(labels)
+plt.xlabel('Number of pixels')
+plt.ylabel('Time of execution, seconds')
+plt.savefig('time-2d.png', bbox_inches = 'tight')

### 2023-05-05 timings/plot-timings-gpu.py

@@ -1,0 +1,52 @@
+#!/usr/local/bin/python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+names2d = [
+    's2-gpu-2d.dat',
+    'c2-gpu-2d.dat',
+    'surf2-gpu-2d.dat',
+    'surfvoid-gpu-2d.dat',
+]
+
+names3d = [
+    's2-gpu-3d.dat',
+    'c2-gpu-3d.dat',
+    'surf2-gpu-3d.dat',
+    'surfvoid-gpu-3d.dat',
+]
+
+markers = [
+    '.', 'o', 's', 'p'
+]
+
+data2d = [np.loadtxt(name) for name in names2d]
+data3d = [np.loadtxt(name) for name in names3d]
+
+labels = [
+    'Two point function',
+    'Cluster function',
+    'Surface-surface function',
+    'Surface-void function',
+]
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 18)
+for data, marker in zip(data3d, markers):
+    plt.errorbar(data[:, 0] ** 3, data[:, 1], marker = marker, yerr = data[:, 2])
+plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
+plt.legend(labels)
+plt.xlabel('Number of voxels')
+plt.ylabel('Time of execution, seconds')
+plt.savefig('time-3d-gpu.png', bbox_inches = 'tight')
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 18)
+for data, marker in zip(data2d, markers):
+    plt.errorbar(data[:, 0] ** 2, data[:, 1], marker = marker, yerr = data[:, 2])
+plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
+plt.legend(labels)
+plt.xlabel('Number of pixels')
+plt.ylabel('Time of execution, seconds')
+plt.savefig('time-2d-gpu.png', bbox_inches = 'tight')

### 2023-05-05 timings/plot-timings-map.py

@@ -1,0 +1,52 @@
+#!/usr/local/bin/python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+names2d = [
+    's2-map-2d.dat',
+    'c2-map-2d.dat',
+    'surf2-map-2d.dat',
+    'surfvoid-map-2d.dat',
+]
+
+names3d = [
+    's2-map-3d.dat',
+    'c2-map-3d.dat',
+    'surf2-map-3d.dat',
+    'surfvoid-map-3d.dat',
+]
+
+markers = [
+    '.', 'o', 's', 'p'
+]
+
+data2d = [np.loadtxt(name) for name in names2d]
+data3d = [np.loadtxt(name) for name in names3d]
+
+labels = [
+    'Two point function',
+    'Cluster function',
+    'Surface-surface function',
+    'Surface-void function',
+]
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 18)
+for data, marker in zip(data3d, markers):
+    plt.errorbar(data[:, 0] ** 3, data[:, 1], marker = marker, yerr = data[:, 2])
+plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
+plt.legend(labels)
+plt.xlabel('Number of voxels')
+plt.ylabel('Time of execution, seconds')
+plt.savefig('time-3d-map.png', bbox_inches = 'tight')
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 18)
+for data, marker in zip(data2d, markers):
+    plt.errorbar(data[:, 0] ** 2, data[:, 1], marker = marker, yerr = data[:, 2])
+plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
+plt.legend(labels)
+plt.xlabel('Number of pixels')
+plt.ylabel('Time of execution, seconds')
+plt.savefig('time-2d-map.png', bbox_inches = 'tight')

### 2023-05-05 timings/plot-timings.py

@@ -1,52 +1,0 @@
-#!/usr/local/bin/python
-
-import numpy as np
-import matplotlib.pyplot as plt
-
-names2d = [
-    'chord_length-directional-2d.dat',
-    'pore_size-directional-2d.dat',
-    's2-directional-2d.dat',
-    'l2-directional-2d.dat',
-    'c2-directional-2d.dat',
-    'surf2-directional-2d.dat',
-    'surfvoid-directional-2d.dat',
-]
-
-names3d = [
-    'chord_length-directional-3d.dat',
-    'pore_size-directional-3d.dat',
-    's2-directional-3d.dat',
-    'l2-directional-3d.dat',
-    'c2-directional-3d.dat',
-    'surf2-directional-3d.dat',
-    'surfvoid-directional-3d.dat',
-]
-
-markers = [
-    '.', 'o', 's', 'p', '.', 'o', 's'
-]
-
-data2d = [np.loadtxt(name) for name in names2d]
-data3d = [np.loadtxt(name) for name in names3d]
-
-labels = [
-    'Chord length function',
-    'Pore size function',
-    'Two point function',
-    'Lineal-path function',
-    'Cluster function',
-    'Surface-surface function',
-    'Surface-void function',
-]
-
-#plt.figure(dpi = 300)
-
-for data, marker in zip(data3d, markers):
-    plt.errorbar(data[:, 0] ** 3, data[:, 1], marker = marker, yerr = data[:, 2])
-
-plt.legend(labels)
-plt.xlabel('Number of voxels')
-plt.ylabel('Time of execution, seconds')
-#plt.savefig('time-3d.png')
-plt.show()

### 2023-05-12 paper-correlations.tex
Describe another algorithm for C₂

@@
 
+Cluster function can be calculated using the same technique as in map approach,
+but if the number of clusters is high, a naïve $O(n^2)$ algorithm may be more
+preferred than $O(MC \log M)$ algorithm. This algorithm is present below:
+\begin{algorithmic}[1]
+  \Procedure{c2}{$A, phase, periodic$}
+    \State $A' \gets I^{(phase)}(A)$
+    \State $CC \gets label\_components(A', periodic)$
+    \State $len \gets length(A)$
+    \State $result \gets zeros(len)$
+    \ForAll{$slice \in slices(CC)$}
+      \For{$i = 0,len-1$}
+        \State $end \gets len-1$
+        \If{$periodic$}
+          \State $end \gets end + i$
+        \EndIf
+        \For{$j = i, end$}
+          \If{$slice[i] = slice[j \mod len] \ne 0$}
+            \Comment $0$ is a label for background (phase not equal to $phase$).
+            \State $dst \gets |(j \mod len) - i|$
+            \State $result[dst] \gets result[dst] + 1$
+          \EndIf
+        \EndFor
+      \EndFor
+    \EndFor
+    \State \textbf{return} $result$ divided by number of trials
+  \EndProcedure
+\end{algorithmic}
+
 Before computation of chord length function an input array must be pre-processed

### 2023-05-16 real-data/plot.py
Replace real data

@@ -1,30 +1,0 @@
-#!/usr/bin/env python
-
-import numpy as np
-import matplotlib.pyplot as plt
-import sys
-
-data = sys.argv[1]
-s2 = np.loadtxt(data + '-s2.dat')
-l2 = np.loadtxt(data + '-l2.dat')
-c2 = np.loadtxt(data + '-c2.dat')
-ss = np.loadtxt(data + '-surfsurf.dat')
-sv = np.loadtxt(data + '-surfvoid.dat')
-
-plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 25)
-plt.plot(s2, linewidth = 2.0)
-plt.plot(l2, linewidth = 2.0)
-plt.plot(c2, linewidth = 2.0)
-plt.plot(ss, linewidth = 2.0)
-plt.plot(sv, linewidth = 2.0)
-plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
-plt.xlim([0, 150])
-plt.xlabel('Correlation length $r$')
-plt.ylabel('Correlation function')
-plt.legend(['Two point function $S_2(r)$',
-            'Lineal-path function $L_2(r)$',
-            'Cluster function $C_2(r)$',
-            'Surface-surface function $F_{ss}(r)$',
-            'Surface-void function $F_{sv}(r)$'])
-plt.savefig(data + '-plot.png')

### 2023-05-16 samples/calc.jl

@@ -1,0 +1,47 @@
+module SomeShit
+
+import CorrelationFunctions.Directional as D
+import CorrelationFunctions.Utilities as U
+using Statistics
+using NPZ
+using FileIO
+using Images
+
+const fns = [:s2, :l2, :c2, :surf2, :surfvoid]
+
+#=
+function read_files()
+    rawfiles = filter(readdir(".")) do name
+        splitext(name)[2] == ".raw"
+    end
+
+    return Iterators.map(rawfiles) do name
+        (splitext(name)[1], U.read_cuboid(name, 1000, 3) |> BitArray)
+    end
+end
+=#
+
+function read_files()
+    rawfiles = filter(readdir(".")) do name
+        splitext(name)[2] == ".png"
+    end
+
+    return Iterators.map(rawfiles) do name
+        (splitext(name)[1], name |> load .|> Gray |> BitArray)
+    end
+end
+
+function do_it!()
+    data = read_files()
+
+    for (name, sample) in data
+        println(name)
+        for sym in fns
+            fn = D.eval(sym)
+            a = fn(sample, true; periodic = true) |> mean
+            npzwrite("$(name)-$(sym).npy", a)
+        end
+    end
+end
+
+end

### 2023-05-16 samples/plot.py

@@ -1,0 +1,34 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+data = [
+    "Bentheimer_2d25um_binary",
+    "CastleGate_2d25um_binary",
+    "Kirby_2d25um_binary"
+]
+
+def load_data(name, fn):
+    return np.load("%s-%s.npy" % (name, fn))
+
+def plot_fn(fn, ylabel, power):
+    plt.figure(figsize = (10, 8), dpi = 300)
+    plt.rc('font', size = 18)
+
+    for n in data:
+        d = load_data(n, fn) * (1/2.25)**power
+        xs = np.arange(0, d.size) * 2.25
+        plt.plot(xs, d)
+
+    plt.legend(list(map(lambda name: name.split('_')[0], data)))
+    plt.xlabel('Correlation length, μm')
+    plt.ylabel(ylabel)
+    plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
+    plt.savefig("%s-xct.png" % fn, bbox_inches = 'tight')
+
+plot_fn('s2', '$S_2$', 0)
+plot_fn('l2', '$L_2$', 0)
+plot_fn('c2', '$C_2$', 0)
+plot_fn('surf2', '$F_{ss}, \mu m^{-2}$', 2)
+plot_fn('surfvoid', '$F_{sv}, \mu m^{-1}$', 1)

### 2023-05-16 paper-correlations.tex
Redraw plots for real XCT samples

@@
 can be found in \cref{tab:samples}. XCT images of sandstones are provided by
-Digital Rocks Portal\cite{DigitalRocks}. Correlation functions of these samples
-can be seen on \cref{fig:real-data}.
+Digital Rocks Portal\cite{DigitalRocks}. Correlation functions of XCT images
+can be seen on \cref{fig:real-xct}.
 
@@
       \hline
-      Bandera Brown sandstone & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
+      Castlegate sandstone & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
       Bentheimer sandstone & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
@@
   \centering
-  \subfigure[Bandera Brown sandstone]{
-    \includegraphics[width=0.3\linewidth]{real-data/BanderaBrown_2d25um_binary.png}
-    \label{fig:bandera}}
+  \subfigure[Castlegate sandstone]{
+    \includegraphics[width=0.3\linewidth]{samples/CastleGate_2d25um_binary.png}
+    \label{fig:castlegate}}
   \hfill
   \subfigure[Bentheimer sandstone]{
-    \includegraphics[width=0.3\linewidth]{real-data/Bentheimer_2d25um_binary.png}
+    \includegraphics[width=0.3\linewidth]{samples/Bentheimer_2d25um_binary.png}
     \label{fig:bentheimer}}
@@
   \subfigure[Kirby sandstone]{
-    \includegraphics[width=0.3\linewidth]{real-data/Kirby_2d25um_binary.png}
+    \includegraphics[width=0.3\linewidth]{samples/Kirby_2d25um_binary.png}
     \label{fig:kirby}}
   \vskip\baselineskip
-  \subfigure[Bandera Brown sandstone (correlation functions)]{
-    \includegraphics[width=0.3\linewidth]{real-data/BanderaBrown_2d25um_binary-plot.png}
-    \label{fig:bandera-plt}}
-  \hfill
-  \subfigure[Bentheimer sandstone (correlation functions)]{
-    \includegraphics[width=0.3\linewidth]{real-data/Bentheimer_2d25um_binary-plot.png}
-    \label{fig:bentheimer-plt}}
-  \hfill
-  \subfigure[Kirby sandstone (correlation functions)]{
-    \includegraphics[width=0.3\linewidth]{real-data/Kirby_2d25um_binary-plot.png}
-    \label{fig:kirby-plt}}
+  \includegraphics[width=0.3\linewidth]{samples/s2-xct.png}
+  \includegraphics[width=0.3\linewidth]{samples/c2-xct.png}
+  \includegraphics[width=0.3\linewidth]{samples/l2-xct.png}
   \vskip\baselineskip
-  \subfigure[Sandstone 1]{
-    \includegraphics[width=0.3\linewidth]{real-data/sandstone1.png}
-    \label{fig:real-sandstone-1}}
-  \hfill
-  \subfigure[Sandstone 2]{
-    \includegraphics[width=0.3\linewidth]{real-data/sandstone2.png}
-    \label{fig:real-sandstone-2}}
-  \hfill
-  \subfigure[Carbonate 1]{
-    \includegraphics[width=0.3\linewidth]{real-data/carbonate1.png}
-    \label{fig:real-carbonate-1-plt}}
-  \vskip\baselineskip
-  \subfigure[Sandstone 1 (correlation functions)]{
-    \includegraphics[width=0.3\linewidth]{real-data/sandstone1-plot.png}
-    \label{fig:real-sandstone-1-plt}}
-  \hfill
-  \subfigure[Sandstone 2 (correlation functions)]{
-    \includegraphics[width=0.3\linewidth]{real-data/sandstone2-plot.png}
-    \label{fig:real-sandstone-2-plt}}
-  \hfill
-  \subfigure[Carbonate 1 (correlation functions)]{
-    \includegraphics[width=0.3\linewidth]{real-data/carbonate1-plot.png}
-    \label{fig:real-carbonate-1}}
-  \caption[]{Plots of correlation functions for real samples.}
-  \label{fig:real-data}
+  \includegraphics[width=0.3\linewidth]{samples/surf2-xct.png}
+  \includegraphics[width=0.3\linewidth]{samples/surfvoid-xct.png}
+  \caption[]{Visualization of XCT images and plots of correlation functions for
+    these images.}
+  \label{fig:real-xct}
 \end{figure*}

### 2023-05-16 samples/plot.py

@@ -14,7 +14,7 @@ def load_data(name, fn):
 
 def plot_fn(fn, ylabel, power):
     plt.figure(figsize = (10, 8), dpi = 300)
-    plt.rc('font', size = 18)
+    plt.rc('font', size = 25)
 
     for n in data:
         d = load_data(n, fn) * (1/2.25)**power

### 2023-07-22 paper-correlations.tex
some additional changes from kg

@@
 
+\author{Vasily Postnicov\textsuperscript{1}}
 \author{Aleksei Samarin\textsuperscript{1,2}}
-\author{Vasily Postnicov\textsuperscript{1}}
 \author{Marina Karsanina\textsuperscript{1}}
-\author{Efim Lavrukhin\textsuperscript{1,2}}
-\author{Dina Gafurova\textsuperscript{3}}
 \author{Aleksey Khlyupin\textsuperscript{1}}
@@
   Lomonosov Moscow State University, Moscow, 119991, Russia}
-\affiliation{\textsuperscript{3}Oil and Gas Research Institute Russian Academy
-  of Sciences (OGRI RAS) 3, Gubkina st., Moscow, 119333, Russian Federation}
 
@@
 their physical properties are interconnected to
-structure\cite{Torquato_book}\cite{Sahimi_book}\cite{Adler_recon}. The information
+structure \cite{Torquato_book,Sahimi_book}. The information
 about the structure usually comes in the way of 2D and 3D images obtained by
-microscopy, tomography and other related methodologies. This structural
-information can be used for numerous types of analysis, including simulations of
+microscopy \cite{moussaoui2018,neumann2019,FIB-SEMpaper}, tomography \cite{xctmat_book} and other related methodologies.
+This structural information can be used for numerous types of analysis, including simulations of
 different processes within studied materials or evaluation of their properties
-using so-called pore-scale modelling. Unlike computational modelling techniques
+based on 3D structural data \cite{youssef2005,Miao2017,FDMSS}. Unlike computational modelling techniques
 a whole class of approximate methods exists including (rigorous) bounds that
-allows very fast estimations of physical properties albeit the bounds themselves
-are too wide to be applicable in majority of practical problems. Nonetheless, it
-is noteworthy that such bounds are originally based on structural descriptors in
-the form of correlation functions.
+allows very fast estimations of physical properties \cite{eshelby1957,berryman1986use,rozanski2023} albeit the bounds themselves
+are too wide to be applicable in the majority of practical problems. Nonetheless, it
+is noteworthy that many of such bounds are originally based on structural descriptors in
+the form of correlation functions (CFs).
 
 Two ways exist to obtain correlation functions for a given structure at hand:
-measure them either experimentally with the help of scattering intensity or
-from digital images. None is perfect, as the first approach suffers from the
+measure them either experimentally with the help of scattering intensity \cite{debye1957scattering,li2018direct} or
+from digital images \cite{berryman1985measurement,ma2018SS}. None is perfect, as the first approach suffers from the
 limitation of CFs that can be obtained this way, while the second one provides
-information with limited resolution or/and resolution to field-of-view ratio. In
+information with limited resolution or/and resolution to field-of-view ratio \cite{gerke2015universal}. In
 addition to the resolution conundrum, the most useful imaging methods such as
@@
 distributions) due to their underlying physical principles and require labeling
-of constituent phases (this is called segmentation) before computation of
-CFs. If properly segmented, high-resolution digital images do provide a
+of constituent phases (or segmentation) before computation of
+CFs \cite{samarin2023robust}. If properly segmented \cite{NNseg}, high-resolution digital images do provide a
 possibility to compute any correlation function and, thus, possibility to
@@
 
-Correlation functions (CFs) as invaluable universal descriptors of structure are
-utilized in a multitude of scientific disciplines: material sciences, rock
-physics, soil physics and hydrology, cosmology and food engineering, biology and
+Correlation functions as invaluable universal descriptors of structure are
+utilized in a multitude of scientific disciplines: material sciences \cite{hasanabadi20163d,Havelka,feng2018reconstruction,chen2022quantifying}, rock
+physics \cite{ledesma2018effect}, soil physics and hydrology \cite{PLoS_ONE,KarsaninaEJSS}, cosmology and food engineering \cite{TakadaJain,Derossi2019}, biology \cite{veatch2012correlation} and
 many others. Computed from 2D and 3D images, CFs can be applied to:
@@
   \item to characterize the morphology and representativeness via correlation
-    lengths;
+    lengths \cite{vcapek2009stochastic,thovert2011grain,tensorPRE};
   \item to perform stochastic reconstructions from experimentally measured CFs
     or 2D to 3D reconstructions based on CFs that can be extracted from less
-    dimensions or through penetrable sphere model;
+    dimensions or through penetrable sphere model \cite{Adler_recon,Y-T,tahmasebiPRL,hasanabadi20163d,karsaninaPRL};
   \item compare different structures to each other, including verification of
-    stochastic reconstructions;
+    stochastic reconstructions \cite{vcapek2009stochastic,tahmasebiPRL,EPL2};
   \item compress structural information in the form of raw or parameterized CFs
     with the possibility to recover the structure using stochastic
-    reconstruction
-  \item describe structural dynamics under different boundary conditions;
-  \item extract structural features for deep learning;
+    reconstruction \cite{SciRep1,Havelka,KarsaninaEJSS};
+  \item describe structural dynamics under different boundary conditions \cite{chen2015dynamic,xu2022correlation,fomin2023soil};
+  \item extract structural features for deep learning \cite{pilania2017multi,kamrava2020linking,roding2020predicting,KarsaninaEJSS};
   \item fuse multi-scale images and structural information as obtained by
-    different methods into a single digital model;
-  \item quantify spatial heterogeneity.
+    different methods into a single digital model \cite{Geoderma2018};
+  \item quantify spatial heterogeneity \cite{zhang2000pore,REVpaper}.
 \end{enumerate}
@@
 solve an inverse problem and recover structure from known set of correlation
-functions. This ability for recovery serves as the basis for majority of usages
+functions \cite{Adler_recon,Y-T,vcapek2009stochastic,hasanabadi20163d,Havelka,feng2018reconstruction,tahmasebiPRL,EPL2,thovert2011grain,tensorPRE}.
+This ability for recovery serves as the basis for majority of usages
 in the list above. While it is necessary to compute CFs from digital images as a
@@
 recomputations or optimizations, e.g., re-evaluation during simulated
-annealing. Such optimizations are not the part of the computational package and
+annealing. Such optimizations are not the part of the computational package described here and
 are not considered in this work.
@@
 points that are utilized to evaluate such a probability. While so-called
-$n$-point probability function\cite{Torquato_book} will totally describe any
+$n$-point probability function \cite{Torquato_book} will completely describe any
 structure in the limit of $n \rightarrow$ number of voxels/pixels on the image,
@@
 marginally improves the quality of the structure quantification and these
-improvements decay with increasing $n$. For stochastic reconstruction purposes
+improvements decay with increasing $n$ \cite{yao1993high,Gommes2}. For stochastic reconstruction purposes
 computation of higher-order statistics will, arguably, not be balanced by
@@
 probability of a whole line segment to fall into the phase ($L_2$ function) or
-to lie on the interface between phases ($F_{ss}$ function), and mainly originate
+to lie on the interface between phases ($F_{ss}$ function), and mainly originated
 from aforementioned bounds on physical properties such as permeability and
@@
 found in seminal work of Torquato \cite{Torquato_book}. To all CFs described in this
-book and applicable to digital images we shall refer as to classical correlation
+book and applicable to digital images we shall refer to as classical correlation
 functions.
@@
 
-\section{Introduction to the correlation functions}
+\section{A brief introduction to correlation functions}
 \label{sec:math}
-In practice porous media are often described with special descriptors called
-``correlation functions''. In this section we provide a brief introduction to
-these functions which can also be found in \cite{Torquato_book}. The functions
-supported by our package are:
+In this section we shall provide major properties of correlation functions
+supported by our package; the full list of functions is 
+(see \cref{fig:functions} for graphical explanation in addition to definitions below):
 \begin{itemize}
-\item Lineal-path function $L_2$.
-\item Two-point function $S_2$.
-\item Cluster function $C_2$.
-\item Surface-surface function $F_{ss}$.
-\item Surface-void function $F_{sv}$.
-\item Pore size function $P$.
-\item Chord length function $p$.
-\item Phase cross-correlation function $\rho_{ij}$
+\item Two-point probability function $S_2$,
+\item Lineal-path function $L_2$,
+\item Cluster function $C_2$,
+\item Surface-surface function $F_{ss}$,
+\item Surface-void function $F_{sv}$,
+\item Pore size function $P$,
+\item Chord length function $p$,
+\item Phase cross-correlation function $\rho_{ij}$.
 \end{itemize}
+Note that cross-correlation $\rho_{ij}$ is actually not a classical CF, but technically is a variety of $S_2$
+for the case when the end of line segment lie in different phases. This function is useful for multi-phase
+structures only, as for binary media two-point probability CFs are interdependent.
 
-One of basic correlation functions is a lineal path function which is defined as
-follows for homogenous media:
+The most widely used is a two-point probability correlation function $S_2$, or autocorrelation. A
+definition for homogenous media is as follows:
+\begin{definition}
+  Two point function $S_2^{(i)}(\bm{r})$ equals to probability that both ends
+  of a vector $\bm{r}$ lie in phase $i$ when the vector is randomly thrown
+  into the sample.
+\end{definition}
+For isotopic media a vector $\bm{r}$ can be reduced to a scalar value
+$r$ (i.e., a correlation function depends only on length of a vector and not on
+its direction). Mathematically this definition can be expressed with the
+following equation:
+\begin{equation}
+  S_2^{(i)}(\bm{r}) = \langle I^{(i)}(\bm{x}) I^{(i)}(\bm{x} +
+  \bm{r}) \rangle
+  \label{eq:s2-def}
+\end{equation}
+where $I^{(i)}$ is an indicator function for a set of all points belonging to
+the phase $i$ and $\langle \cdots \rangle$ is ensemble average.
+
+A function closely related to $S_2$ is phase cross-correlation function
+$\rho_{ij}$ which is defined as follows:
+\begin{equation}
+  \rho_{ij}(\bm{r}) = \langle I^{(i)}(\bm{x}) I^{(j)}(\bm{x} +
+  \bm{r}) \rangle
+  \label{eq:cross-def}
+\end{equation}
+
+Another basic correlation function is a lineal path function. It provides some non-trivial
+information (albeit usually not complete \cite{vcapek2011transport}) about the connectedness
+of the phase and is defined for homogenous media as:
 \begin{definition}
@@
 
-Another function of big importance is a two-point correlation function $S_2$. A
-definition for homogenous media is as follows:
-\begin{definition}
-  Two point function $S_2^{(i)}(\bm{r})$ equals to probability that both ends
-  of a vector $\bm{r}$ lie in phase $i$ when the vector is randomly thrown
-  into the sample.
-\end{definition}
-For isotopic media a vector $\bm{r}$ can be again reduced to a scalar value
-$r$ (i.e. a correlation function depends only on length of a vector and not on
-its direction.) Mathematically this definition can be expressed with the
-following equation:
-\begin{equation}
-  S_2^{(i)}(\bm{r}) = \langle I^{(i)}(\bm{x}) I^{(i)}(\bm{x} +
-  \bm{r}) \rangle
-  \label{eq:s2-def}
-\end{equation}
-where $I^{(i)}$ is an indicator function for a set of all points belonging to
-the phase $i$ and $\langle \cdots \rangle$ is an average over all xs.
-
-A function closely related to $S_2$ is phase cross-correlation function
-$\rho_{ij}$ which is defined with the following equation:
-\begin{equation}
-  \rho_{ij}(\bm{r}) = \langle I^{(i)}(\bm{x}) I^{(j)}(\bm{x} +
-  \bm{r}) \rangle
-  \label{eq:cross-def}
-\end{equation}
-
-The next function is a cluster function $C_2$.
+The function that contain a lot of structural connectivity information \cite{JiaoPNAS}
+is cluster function $C_2$.
 \begin{definition}
@@
 \end{definition}
+Note that for a fully connected phase $C_2$ will be equal to $S_2$, something
+we shall utilize later for computations.
 
 The next two functions are called surface-surface ($F_{ss}$) and surface-void
-($F_{sv}$) functions and describe surface of a sample. We skip strict verbal
-definitions and introduce an interface indicator function instead:
+($F_{sv}$) functions and describe an interphase between phases. We skip strict verbal
+definitions and first introduce an interface indicator function instead:
 \begin{equation*}
@@
 because an ordinary differential of $I$ is either zero or undefined. For
-homogenous media definitions of these functions are:
+homogenous media the definitions of surface functions then are:
 \begin{align}
@@
 higher. $F_{sv}$ is a physical quantity inversely proportional to length and
-$F_{ss}$ is inversionaly proportional to surface area, therefore we can use
-$\mu m^{-1}$ to measure surface-void and $\mu m^{-2}$ to measure surface-surface
-functions. Putting it simply, surface-void function measures length (2D case) or
-surface (3D case) of a part of the interface which lies in the void phase of
-porous medium shifted by vector $\bm{r}$. Surface-surface function characterizes
-intersections of interfaces of porous medium and its shifted version. As always,
-there are versions of these functions applicable to scalar argument for
+$F_{ss}$ is inversionaly proportional to surface area. Putting it simply, 
+surface-void function measures length (2D case) or surface (3D case) of a part of the
+interface which lies in the void phase of porous medium shifted by vector $\bm{r}$. 
+Surface-surface function characterizes intersections of interfaces of porous medium and its shifted version.
+As always, there are versions of these functions applicable to scalar argument for
 isotropic media.
@@
 
-Finally, a chord length function $p^{(i)}(r)$ is defined as follows:
+Finally, a chord length function $p^{(i)}(r)$ is defined as:
 \begin{definition}
@@
 
-\verb+CorrelationFunctions.jl+ is capable to compute all these
-functions. Usually there are two implementations for a function. The first
+More detailed information on all classical CFs can be found in \cite{Torquato_book}.
+
+\section{Computational methodology}
+
+\verb+CorrelationFunctions.jl+ is capable to compute all aforementioned correlation
+functions. Where possible we provide two implementations for each CF. The first
 implementation computes a correlation function in specific predefined directions
-(i.e. orientation of test vectors thrown into a sample is fixed). There are one
-predefined direction in 1D case, four directions in 2D case and thirteen
-directions in 3D case. This implementation is somewhat slow but requires much
-less memory than the second one. The second implementation computes a
-correlation function in all possible directions and is faster but requires much
-memory. These implementations are contained in \code{Directional} and \code{Map}
-modules of the package correspondingly.
+(i.e., orientation of test vectors thrown into a sample is fixed) \cite{jiao2014chawla,EPL1}.
+There are one predefined direction in 1D case, four directions in 2D case 
+(two orthogonal and two diagonal) and thirteen directions in 3D case (three orthogonal, 
+six diagonal within each orthogonal plane and four diagonal). The line segment scanning
+approach is slower for some CFs but requires much less memory resources. The full map approach
+establishes correlations between all points on the image is usually faster. 
+Both implementations are contained in \code{Directional} and \code{Map}
+modules of the package, correspondingly.
 
-These functions can work in periodic and non-periodic modes. Periodic mode
-assumes that an input sample is periodically continued to the whole Euclidean
+With the help of the package one can compute CFs in periodic and non-periodic modes. 
+Periodic mode assumes that an input sample is periodically continued to the whole Euclidean
 space. Non-periodic mode assumes zero-padded input.
 
-\section{The map approach.}
+\subsection{Full correlation map}
 \label{sec:map}
@@
 non-periodic mode $N(r)$ is calculated as described in
-\cref{sec:number-of-trials}. The following algorithm summarizes all said above:
+\cref{sec:number-of-trials}. The following algorithm summarizes all the above:
 \begin{algorithmic}[1]
@@
 \end{algorithmic}
-Algorithmic complexity of this implementation if $O(M \log M)$ where $M$ is the
-number of elements in the input.
+Algorithmic complexity of this implementation is $O(M \log M)$, where $M$ is the
+number of elements in the input image.
 
-This function is a special case of a cross-correlation function $\rho_{ij}$
-which computes a correlation between phases $i$ and $j$ using a formula
+Computation of $S_2$ is a special case of a cross-correlation function $\rho_{ij}$
+which computes a correlation between phases $i$ and $j$ using a formula:
 \begin{equation}
@@
 \end{equation}
-or an equivalent algorithm
+that algorithmically operates as follows:
 \begin{algorithmic}[1]
@@
 
-Cluster function can be calculated in the similar manner. Firstly, we apply an
-indicator function to an input $A$: $A^{(i)} \xleftarrow{I^{(i)}} A$. When we
-label connected components in $A^{(i)}$ using one of many popular algorithms for
-this purpose \textcolor{red}{cite something}. This algorithm must take into
-account if the function is calculated in periodic mode or not. Then $C_2$
+Cluster function can be calculated with the help of previuously described procedures. 
+Firstly, we apply an indicator function to an input $A$: $A^{(i)} \xleftarrow{I^{(i)}} A$. When we
+label connected components in $A^{(i)}$ using a function that is a part of Julia \code{ImageMorphology.jl} library. 
+Labeling algorithm must take into account if the function is calculated with periodic boundary 
+conditions \cite{evstigneev2023}. For periodic boundary conditions we implemented our own solution 
+as part of the package, as it is absent in the public domain. Then $C_2$
 function is a sum of $S_2$ functions calculated for all clusters
@@
 where $M$ is the number of elements in the input and $C$ is the number of
-clusters. The algorithm is as follows:
+clusters. The algorithm is then written as:
 \begin{algorithmic}[1]
@@
 
-For surface-surface and surface-void functions we use an edge detection filter
+For surface-surface and surface-void functions we use an edge detection filter \cite{samarin2023robust}
 and then calculate either autocorrelation of the edge or cross-correlation of
@@
 where $C$ is such that all coefficients of $H'$ sum to zero, and $S$ equals to
-$30.45849$ in 2D and $172.96232$ in 3D case.
+$30.45849$ in 2D and $172.96232$ in 3D case. The parameters of the filter were adjusted
+based on comparison against exact computations of surface functions on smooth-boundary
+sets \cite{Postnicov2023}.
 
@@
 Our library does not have an implementation for lineal-path maps, although we
-know that such implementations exist.
+know that such implementations exist \cite{Paper}. The reason is a very slow
+computation even on GPUs, plus the resulting map is not for all points on the image,
+but within a spherical volume (due to rotation of the 3D image during lineal-path
+evaluation). Moreover, linear scan approach is orders of magnitude faster for $L_2$.
 
-All these algorithms contain parallelizable operations such as fast Fourier
+All described algorithms contain parallelizable operations such as fast Fourier
 transform, connected components labeling and image filtering, hence they are
-perfectly suited for execution on GPUs.
+perfectly suited for execution on GPUs and provide very fast computations (see wall times below).
 
-\section{The scan approach.}
+\subsection{Directional scanning with line segment}
 \label{sec:scan}
-All algorithms described above are executed on the whole input and hence require
-a lot of memory. The scan approach deals with memory limitations at the cost of
-higher execution time. In this approach we select a list of predefined
+All algorithms described above (full correlation maps) are executed on the whole input and hence require
+a lot of RAM memory. The scan approach deals with memory limitations at the cost of
+higher execution time (except for $L_2$). With line-segment scanning we select a list of predefined
 directions and cut all one-dimensional slices from the input along those
 directions. Then for each direction we use an appropriate algorithm in
-\cref{sec:map} to calculate a correlation function just for that slice. When all
-slices are processed we calculate the result using the formula:
+\cref{sec:map} to calculate a correlation function just for that single slice. When all
+slices are processed we calculate the resulting directional or averaged CF using the formula:
 \begin{equation*}
@@
 for a correlation length $r$ and slice $i$. Some algorithms require
-preprocessing stages before cutting the input in slices, e.g. image filtering
-for edge detection or connected components labeling is performed on the whole
+preprocessing stages before cutting the input in slices, e.g., image filtering
+for edge detection or connected components labeling performed on the whole
 array, not on slices.
@@
 An algorithm for computation of linear-path function for one-dimensional slice
-is present below. Here $a$ is a one-dimensional input array, $phase$ can be
+is presented below. Here $a$ is a one-dimensional input array, $phase$ can be
 void, solid or some other phase, and $periodic$ is a boolean value which equals
@@
 but if the number of clusters is high, a naïve $O(n^2)$ algorithm may be more
-preferred than $O(MC \log M)$ algorithm. This algorithm is present below:
+preferred than $O(MC \log M)$ algorithm. Such an algorithm is present below:
 \begin{algorithmic}[1]
@@
 \end{equation}
-Distance transform has many implementations \textcolor{red}{cite something},
-many of them can be parralelized on GPU. In \code{chord\_length} function we
+For distance transform has many implementations \textcolor{red}{cite something}. In \code{chord\_length} function we
 firstly apply distance transform to an input to find the interface and then
-accumulate chord length in per-slice manner. Finally, cord lengths can be binned
+accumulate chord length in per-slice manner. Finally, chord lengths can be binned
 in a histogram.
@@
 Another function built on top of distance transform is the pore size function
-$P(r)$. Remember that pore size function is a probability distribution
-function. In practice it is better represented as a histogram of pore sizes
-found in the input. Our algorithm for calculating $P(r)$ is as follows:
+$P(r)$. Reckon that pore size function is a probability distribution
+function. In practice, it is better represented as a histogram of pore sizes
+found in the input image. Our algorithm for calculating $P(r)$ is as follows:
 \begin{algorithmic}[1]
@@
 
-\section{Verification of our algorithms}
+\section{Verification of CFs compuations}
 \label{sec:verification}
-Our algorithms are verified by comparing their results with known closed-form
-expressions for correlation functions for some sort of input data. One kind of
-well-studied data is overlapping n-balls with fixed radius and centers generated
-by Poisson point process. Here we consider two-dimensional and three-dimensional
+To verify all algorithms we compare their results against known closed-form
+expressions for correlation functions for some particular type of input data. One such type 
+with analytical solution is overlapping n-balls with fixed radius and centers generated
+by Poisson point process. Here we consider both two-dimensional and three-dimensional
 cases.
 
-\subsection{Two-dimensional case}
+\subsection{Two-dimensional analytical solutions}
 Consider an infinite set of disks with radii $R$ and centers generated by
@@
 
-Two-point function in this case is: \cite{Torquato_book}
+Two-point probability function in this case is \cite{Torquato_book}:
 \begin{equation*}
@@
 
-An expression for $F_{ss}$ is
+An expression for $F_{ss}$ is \cite{samarin2023robust}:
 \begin{equation*}
@@
 
-Surface-void function $F_{sv}$ becomes
+Surface-void function $F_{sv}$ becomes \cite{samarin2023robust}:
 \begin{equation*}
@@
 
-Two-point function $L_2$:
+Two-point function $L_2$ \cite{Torquato_book}:
 \begin{equation*}
@@
 
-Chord length function $p$:
+Chord length function $p$ \cite{Torquato_book}:
 \begin{equation*}
@@
 
-And finally pore size function $P$:
+And finally pore size function $P$ \cite{Torquato_book}:
 \begin{equation*}
@@
 
-To test out package we generate a realization of random overlapping disks
-(\cref{fig:overlapping-disks}) with dimensions $10000 \times 10000$ and
-parameters $R = 40\ px$ and $\lambda = 10^{-4}\ px^{-2}$ and compare calculated
-correlation functions with their theoretical values. The results are present on
-\cref{fig:verification}.
-\begin{figure}[ht]
-  \centering
-  \includegraphics[width=0.9\linewidth]{images/disks-fragment.png}
-  \caption[]{A fragment of overlapping disks used in testing of our library.}
-  \label{fig:overlapping-disks}
-\end{figure}
+\subsection{Three-dimensional analytical solutions}
+As in the previous case, consider an infinite set of balls with radii $R$ and
+centers generated by Poisson point process with parameter $\lambda$. Closed-form
+expressions for correlations functions are also known for this case for all CFs \cite{Torquato_book}.
 
-\subsection{Three-dimensional case}
-Like in the previous case, consider an infinite set of balls with radii $R$ and
-centers generated by Poisson point process with parameter $\lambda$. Closed-form
-expressions for correlations functions are also known for this case.
-
-Two-point function in this case is:
+Two-point probability function in this case is:
 \begin{equation*}
@@
 
-Let $\eta = \frac{4}{3}\lambda \pi R^3$. Then an expression for $F_{ss}$ is
+Let $\eta = \frac{4}{3}\lambda \pi R^3$. Then an expression for $F_{ss}$ is:
 \begin{equation*}
@@
 
+\subsection{Comparison against analytical solutions}
 To test out package we generate a realization of random overlapping disks
+(\cref{fig:overlapping-disks}) with dimensions $10000 \times 10000$ and
+parameters $R = 40\ px$ and $\lambda = 10^{-4}\ px^{-2}$ and compare calculated
+correlation functions with their theoretical values.
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=0.9\linewidth]{images/disks-fragment.png}
+  \caption[]{A fragment of overlapping disks used in testing of our library.}
+  \label{fig:overlapping-disks}
+\end{figure}
+
+For a 3D test, we generate a realization of random overlapping spheres
 (\cref{fig:overlapping-disks}) with dimensions $500 \times 500 \times 500$ and
 parameters $R = 10\ px$ and $\lambda = 10^{-4}\ px^{-3}$ and compare calculated
-correlation functions with their theoretical values. The results are present on
-\cref{fig:verification}.
+correlation functions with their theoretical values.
+
+The results of comparison of computational results against analytical solutions 
+are present on \cref{fig:verification}. It is clear from the test shown that CFs 
+are computed with high accuracy; minor deviations are due to finite size of our
+Poisson realizations (i.e., larger images reduce deviations \cite{samarin2023robust}).
 
@@
 
-\section{Examples and applications}
+\section{Applications and benchmarks}
+After the verification of our computational approach based on analytical
+solution, in this section we apply \code{CorrelationFUnctions.jl} to compute CFs
+for a variety of real 2D (SEM) and 3D (XCT) images. We also report benchmark on execution time and
+compare GPU and CPU implementations.
+
+\subsection{Examples of application to experimental images}
 \label{sec:examples}
-After the verification of our computational approach based on analytical
-solution we can apply our algorithms to evaluate correlation functions for
-different porous media images, including real XCT and SEM images. A summary
-which contains information about type of the images, dimensions and resolution
+A summary which contains information about type of the images, dimensions and resolution
 can be found in \cref{tab:samples}. XCT images of sandstones are provided by
@@
 
-\section{Execution times of our algorithms}
+\subsection{Execution times for our algorithms}
 \label{sec:efficiency}
@@
 
+\section{Discussion and outlook}
+When to use map and when to use linear scan
+  memory
+  how fast
+  optimization during reconstruction
+  +directional CFs for anisotropic media
+Reconstructions based on maps - from Cherkasov to SA?
+Why we need more functions? Information content
+3-point in future - do we need more points?
+Or may be we need more CFs? Add topology (Zubov)?
+GPU computations are limited by RAM - if we are interested in correlation length of width of cube that can be
+put into GPU card memory - we can ensemble by computation in subcubes (possible future upodates)
+
 \section{Summary}

### 2023-07-24 paper-correlations.tex
Fix formatting

@@
 Materials are ubiquitous both in nature and in industrial human activities, and
-their physical properties are interconnected to
-structure \cite{Torquato_book,Sahimi_book}. The information
-about the structure usually comes in the way of 2D and 3D images obtained by
-microscopy \cite{moussaoui2018,neumann2019,FIB-SEMpaper}, tomography \cite{xctmat_book} and other related methodologies.
-This structural information can be used for numerous types of analysis, including simulations of
-different processes within studied materials or evaluation of their properties
-based on 3D structural data \cite{youssef2005,Miao2017,FDMSS}. Unlike computational modelling techniques
-a whole class of approximate methods exists including (rigorous) bounds that
-allows very fast estimations of physical properties \cite{eshelby1957,berryman1986use,rozanski2023} albeit the bounds themselves
-are too wide to be applicable in the majority of practical problems. Nonetheless, it
-is noteworthy that many of such bounds are originally based on structural descriptors in
-the form of correlation functions (CFs).
+their physical properties are interconnected to structure
+\cite{Torquato_book,Sahimi_book}. The information about the structure usually
+comes in the way of 2D and 3D images obtained by microscopy
+\cite{moussaoui2018,neumann2019,FIB-SEMpaper}, tomography \cite{xctmat_book} and
+other related methodologies.  This structural information can be used for
+numerous types of analysis, including simulations of different processes within
+studied materials or evaluation of their properties based on 3D structural data
+\cite{youssef2005,Miao2017,FDMSS}. Unlike computational modelling techniques a
+whole class of approximate methods exists including (rigorous) bounds that
+allows very fast estimations of physical properties
+\cite{eshelby1957,berryman1986use,rozanski2023} albeit the bounds themselves are
+too wide to be applicable in the majority of practical problems. Nonetheless, it
+is noteworthy that many of such bounds are originally based on structural
+descriptors in the form of correlation functions (CFs).
 
 Two ways exist to obtain correlation functions for a given structure at hand:
-measure them either experimentally with the help of scattering intensity \cite{debye1957scattering,li2018direct} or
-from digital images \cite{berryman1985measurement,ma2018SS}. None is perfect, as the first approach suffers from the
-limitation of CFs that can be obtained this way, while the second one provides
-information with limited resolution or/and resolution to field-of-view ratio \cite{gerke2015universal}. In
-addition to the resolution conundrum, the most useful imaging methods such as
-X-ray computed tomography (XCT) and scanning electron microscopy (SEM) provide
-gray-scale images (e.g., X-ray attenuation or electron back-scattering
-distributions) due to their underlying physical principles and require labeling
-of constituent phases (or segmentation) before computation of
-CFs \cite{samarin2023robust}. If properly segmented \cite{NNseg}, high-resolution digital images do provide a
-possibility to compute any correlation function and, thus, possibility to
-address numerous fundamental and practical research problems.
+measure them either experimentally with the help of scattering intensity
+\cite{debye1957scattering,li2018direct} or from digital images
+\cite{berryman1985measurement,ma2018SS}. None is perfect, as the first approach
+suffers from the limitation of CFs that can be obtained this way, while the
+second one provides information with limited resolution or/and resolution to
+field-of-view ratio \cite{gerke2015universal}. In addition to the resolution
+conundrum, the most useful imaging methods such as X-ray computed tomography
+(XCT) and scanning electron microscopy (SEM) provide gray-scale images (e.g.,
+X-ray attenuation or electron back-scattering distributions) due to their
+underlying physical principles and require labeling of constituent phases (or
+segmentation) before computation of CFs \cite{samarin2023robust}. If properly
+segmented \cite{NNseg}, high-resolution digital images do provide a possibility
+to compute any correlation function and, thus, possibility to address numerous
+fundamental and practical research problems.
 
 Correlation functions as invaluable universal descriptors of structure are
-utilized in a multitude of scientific disciplines: material sciences \cite{hasanabadi20163d,Havelka,feng2018reconstruction,chen2022quantifying}, rock
-physics \cite{ledesma2018effect}, soil physics and hydrology \cite{PLoS_ONE,KarsaninaEJSS}, cosmology and food engineering \cite{TakadaJain,Derossi2019}, biology \cite{veatch2012correlation} and
-many others. Computed from 2D and 3D images, CFs can be applied to:
+utilized in a multitude of scientific disciplines: material sciences
+\cite{hasanabadi20163d,Havelka,feng2018reconstruction,chen2022quantifying}, rock
+physics \cite{ledesma2018effect}, soil physics and hydrology
+\cite{PLoS_ONE,KarsaninaEJSS}, cosmology and food engineering
+\cite{TakadaJain,Derossi2019}, biology \cite{veatch2012correlation} and many
+others. Computed from 2D and 3D images, CFs can be applied to:
 \begin{enumerate}
@@
     or 2D to 3D reconstructions based on CFs that can be extracted from less
-    dimensions or through penetrable sphere model \cite{Adler_recon,Y-T,tahmasebiPRL,hasanabadi20163d,karsaninaPRL};
+    dimensions or through penetrable sphere model
+    \cite{Adler_recon,Y-T,tahmasebiPRL,hasanabadi20163d,karsaninaPRL};
   \item compare different structures to each other, including verification of
@@
     reconstruction \cite{SciRep1,Havelka,KarsaninaEJSS};
-  \item describe structural dynamics under different boundary conditions \cite{chen2015dynamic,xu2022correlation,fomin2023soil};
-  \item extract structural features for deep learning \cite{pilania2017multi,kamrava2020linking,roding2020predicting,KarsaninaEJSS};
+  \item describe structural dynamics under different boundary conditions
+    \cite{chen2015dynamic,xu2022correlation,fomin2023soil};
+  \item extract structural features for deep learning
+    \cite{pilania2017multi,kamrava2020linking,roding2020predicting,KarsaninaEJSS};
   \item fuse multi-scale images and structural information as obtained by
@@
 solve an inverse problem and recover structure from known set of correlation
-functions \cite{Adler_recon,Y-T,vcapek2009stochastic,hasanabadi20163d,Havelka,feng2018reconstruction,tahmasebiPRL,EPL2,thovert2011grain,tensorPRE}.
-This ability for recovery serves as the basis for majority of usages
-in the list above. While it is necessary to compute CFs from digital images as a
-target set for stochastic reconstructions, they rely more on efficient
-recomputations or optimizations, e.g., re-evaluation during simulated
-annealing. Such optimizations are not the part of the computational package described here and
+functions
+\cite{Adler_recon,Y-T,vcapek2009stochastic,hasanabadi20163d,Havelka,feng2018reconstruction,tahmasebiPRL,EPL2,thovert2011grain,tensorPRE}. This
+ability for recovery serves as the basis for majority of usages in the list
+above. While it is necessary to compute CFs from digital images as a target set
+for stochastic reconstructions, they rely more on efficient recomputations or
+optimizations, e.g., re-evaluation during simulated annealing. Such
+optimizations are not the part of the computational package described here and
 are not considered in this work.
@@
 \end{itemize}
-Note that cross-correlation $\rho_{ij}$ is actually not a classical CF, but technically is a variety of $S_2$
-for the case when the end of line segment lie in different phases. This function is useful for multi-phase
-structures only, as for binary media two-point probability CFs are interdependent.
+Note that cross-correlation $\rho_{ij}$ is actually not a classical CF, but
+technically is a variety of $S_2$ for the case when the end of line segment lie
+in different phases. This function is useful for multi-phase structures only, as
+for binary media two-point probability CFs are interdependent.
 
-The most widely used is a two-point probability correlation function $S_2$, or autocorrelation. A
-definition for homogenous media is as follows:
+The most widely used is a two-point probability correlation function $S_2$, or
+autocorrelation. A definition for homogenous media is as follows:
 \begin{definition}
@@
 
-Another basic correlation function is a lineal path function. It provides some non-trivial
-information (albeit usually not complete \cite{vcapek2011transport}) about the connectedness
-of the phase and is defined for homogenous media as:
+Another basic correlation function is a lineal path function. It provides some
+non-trivial information (albeit usually not complete \cite{vcapek2011transport})
+about the connectedness of the phase and is defined for homogenous media as:
 \begin{definition}
@@
 $F_{ss}$ is inversionaly proportional to surface area. Putting it simply,
-surface-void function measures length (2D case) or surface (3D case) of a part of the
-interface which lies in the void phase of porous medium shifted by vector $\bm{r}$. 
-Surface-surface function characterizes intersections of interfaces of porous medium and its shifted version.
-As always, there are versions of these functions applicable to scalar argument for
-isotropic media.
+surface-void function measures length (2D case) or surface (3D case) of a part
+of the interface which lies in the void phase of porous medium shifted by vector
+$\bm{r}$.  Surface-surface function characterizes intersections of interfaces of
+porous medium and its shifted version.  As always, there are versions of these
+functions applicable to scalar argument for isotropic media.
 
@@
 
-\verb+CorrelationFunctions.jl+ is capable to compute all aforementioned correlation
-functions. Where possible we provide two implementations for each CF. The first
-implementation computes a correlation function in specific predefined directions
-(i.e., orientation of test vectors thrown into a sample is fixed) \cite{jiao2014chawla,EPL1}.
-There are one predefined direction in 1D case, four directions in 2D case 
-(two orthogonal and two diagonal) and thirteen directions in 3D case (three orthogonal, 
-six diagonal within each orthogonal plane and four diagonal). The line segment scanning
-approach is slower for some CFs but requires much less memory resources. The full map approach
-establishes correlations between all points on the image is usually faster. 
-Both implementations are contained in \code{Directional} and \code{Map}
-modules of the package, correspondingly.
+\code{CorrelationFunctions.jl} is capable to compute all aforementioned
+correlation functions. Where possible we provide two implementations for each
+CF. The first implementation computes a correlation function in specific
+predefined directions (i.e., orientation of test vectors thrown into a sample is
+fixed) \cite{jiao2014chawla,EPL1}.  There are one predefined direction in 1D
+case, four directions in 2D case (two orthogonal and two diagonal) and thirteen
+directions in 3D case (three orthogonal, six diagonal within each orthogonal
+plane and four diagonal). The line segment scanning approach is slower for some
+CFs but requires much less memory resources. The full map approach establishes
+correlations between all points on the image is usually faster.  Both
+implementations are contained in \code{Directional} and \code{Map} modules of
+the package, correspondingly.
 
-With the help of the package one can compute CFs in periodic and non-periodic modes. 
-Periodic mode assumes that an input sample is periodically continued to the whole Euclidean
-space. Non-periodic mode assumes zero-padded input.
+With the help of the package one can compute CFs in periodic and non-periodic
+modes.  Periodic mode assumes that an input sample is periodically continued to
+the whole Euclidean space. Non-periodic mode assumes zero-padded input.
 
@@
 
-Cluster function can be calculated with the help of previuously described procedures. 
-Firstly, we apply an indicator function to an input $A$: $A^{(i)} \xleftarrow{I^{(i)}} A$. When we
-label connected components in $A^{(i)}$ using a function that is a part of Julia \code{ImageMorphology.jl} library. 
-Labeling algorithm must take into account if the function is calculated with periodic boundary 
-conditions \cite{evstigneev2023}. For periodic boundary conditions we implemented our own solution 
-as part of the package, as it is absent in the public domain. Then $C_2$
-function is a sum of $S_2$ functions calculated for all clusters
-separately. Algorithmic complexity of this implementation is $O(MC \log M)$
-where $M$ is the number of elements in the input and $C$ is the number of
-clusters. The algorithm is then written as:
+Cluster function can be calculated with the help of previuously described
+procedures.  Firstly, we apply an indicator function to an input $A$: $A^{(i)}
+\xleftarrow{I^{(i)}} A$. When we label connected components in $A^{(i)}$ using a
+function that is a part of Julia \code{ImageMorphology.jl} library.  Labeling
+algorithm must take into account if the function is calculated with periodic
+boundary conditions \cite{evstigneev2023}. For periodic boundary conditions we
+implemented our own solution as part of the package, as it is absent in the
+public domain. Then $C_2$ function is a sum of $S_2$ functions calculated for
+all clusters separately. Algorithmic complexity of this implementation is
+$O(MC\log M)$ where $M$ is the number of elements in the input and $C$ is the
+number of clusters. The algorithm is then written as:
 \begin{algorithmic}[1]
@@
 
-For surface-surface and surface-void functions we use an edge detection filter \cite{samarin2023robust}
-and then calculate either autocorrelation of the edge or cross-correlation of
-the edge and the void phase. The edge is extracted by convolving an input with a
-short high-pass filter $H$. It has a width $7$ and all its coefficients with
-exception of the central coefficient are inversely proportional to distance
-from the center:
+For surface-surface and surface-void functions we use an edge detection filter
+\cite{samarin2023robust} and then calculate either autocorrelation of the edge
+or cross-correlation of the edge and the void phase. The edge is extracted by
+convolving an input with a short high-pass filter $H$. It has a width $7$ and
+all its coefficients with exception of the central coefficient are inversely
+proportional to distance from the center:
 \begin{equation}
@@
 know that such implementations exist \cite{Paper}. The reason is a very slow
-computation even on GPUs, plus the resulting map is not for all points on the image,
-but within a spherical volume (due to rotation of the 3D image during lineal-path
-evaluation). Moreover, linear scan approach is orders of magnitude faster for $L_2$.
+computation even on GPUs, plus the resulting map is not for all points on the
+image, but within a spherical volume (due to rotation of the 3D image during
+lineal-path evaluation). Moreover, linear scan approach is orders of magnitude
+faster for $L_2$.
 
@@
 transform, connected components labeling and image filtering, hence they are
-perfectly suited for execution on GPUs and provide very fast computations (see wall times below).
+perfectly suited for execution on GPUs and provide very fast computations (see
+wall times below).
 
@@
 \label{sec:scan}
-All algorithms described above (full correlation maps) are executed on the whole input and hence require
-a lot of RAM memory. The scan approach deals with memory limitations at the cost of
-higher execution time (except for $L_2$). With line-segment scanning we select a list of predefined
-directions and cut all one-dimensional slices from the input along those
-directions. Then for each direction we use an appropriate algorithm in
-\cref{sec:map} to calculate a correlation function just for that single slice. When all
-slices are processed we calculate the resulting directional or averaged CF using the formula:
+All algorithms described above (full correlation maps) are executed on the whole
+input and hence require a lot of RAM memory. The scan approach deals with memory
+limitations at the cost of higher execution time (except for $L_2$). With
+line-segment scanning we select a list of predefined directions and cut all
+one-dimensional slices from the input along those directions. Then for each
+direction we use an appropriate algorithm in \cref{sec:map} to calculate a
+correlation function just for that single slice. When all slices are processed
+we calculate the resulting directional or averaged CF using the formula:
 \begin{equation*}
@@
 \end{equation}
-For distance transform has many implementations \textcolor{red}{cite something}. In \code{chord\_length} function we
-firstly apply distance transform to an input to find the interface and then
-accumulate chord length in per-slice manner. Finally, chord lengths can be binned
-in a histogram.
+For distance transform has many implementations \textcolor{red}{cite
+  something}. In \code{chord\_length} function we firstly apply distance
+transform to an input to find the interface and then accumulate chord length in
+per-slice manner. Finally, chord lengths can be binned in a histogram.
 \begin{algorithmic}[1]
@@
 To verify all algorithms we compare their results against known closed-form
-expressions for correlation functions for some particular type of input data. One such type 
-with analytical solution is overlapping n-balls with fixed radius and centers generated
-by Poisson point process. Here we consider both two-dimensional and three-dimensional
-cases.
+expressions for correlation functions for some particular type of input
+data. One such type with analytical solution is overlapping n-balls with fixed
+radius and centers generated by Poisson point process. Here we consider both
+two-dimensional and three-dimensional cases.
 
@@
 centers generated by Poisson point process with parameter $\lambda$. Closed-form
-expressions for correlations functions are also known for this case for all CFs \cite{Torquato_book}.
+expressions for correlations functions are also known for this case for all CFs
+\cite{Torquato_book}.
 
@@
 solution, in this section we apply \code{CorrelationFUnctions.jl} to compute CFs
-for a variety of real 2D (SEM) and 3D (XCT) images. We also report benchmark on execution time and
-compare GPU and CPU implementations.
+for a variety of real 2D (SEM) and 3D (XCT) images. We also report benchmark on
+execution time and compare GPU and CPU implementations.
 

### 2023-07-24 paper-correlations.tex
Add missing citation

@@
 \end{equation}
-For distance transform has many implementations \textcolor{red}{cite
-  something}. In \code{chord\_length} function we firstly apply distance
-transform to an input to find the interface and then accumulate chord length in
-per-slice manner. Finally, chord lengths can be binned in a histogram.
+There are many algorithms for distance transform, including algorithms performed
+in linear time \cite{DT}.In \code{chord\_length} function we firstly apply
+distance transform to an input to find the interface and then accumulate chord
+length in per-slice manner. Finally, chord lengths can be binned in a histogram.
 \begin{algorithmic}[1]

### 2023-07-24 paper-correlations.tex
Insert an image of balls
Add SEM images and more

@@
 \usepackage{subfigure}
+\usepackage[export]{adjustbox}
 
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{images/disks-fragment.png}
-  \caption[]{A fragment of overlapping disks used in testing of our library.}
+  \includegraphics[width=0.45\linewidth]{images/disks.png}
+  \includegraphics[width=0.45\linewidth]{images/balls.png}
+  \caption[]{Images of overlapping disks and balls used in testing of our library.}
   \label{fig:overlapping-disks}
@@
 A summary which contains information about type of the images, dimensions and resolution
-can be found in \cref{tab:samples}. XCT images of sandstones are provided by
-Digital Rocks Portal\cite{DigitalRocks}. Correlation functions of XCT images
-can be seen on \cref{fig:real-xct}.
+can be found in \cref{tab:samples}. Correlation functions of XCT images can be
+seen on \cref{fig:real-xct} and correlation functions of SEM images are on
+\cref{fig:real-sem}.
 
@@
   \begin{ruledtabular}
-    \begin{tabular}{|c|c|c|c|}
-      Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) \\
+    \begin{tabular}{|c|c|c|c|c|}
+      Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
       \hline
-      Castlegate sandstone & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
-      Bentheimer sandstone & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
-      Kirby sandstone      & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
-      Sandstone 1 & SEM &  $1280 \times 869$ & 0.10 \\
-      Sandstone 2 & SEM &  $1280 \times 869$ & 0.05 \\
-      Carbonate 1 & SEM &  $1024 \times 691$ & 0.06
+      Ceramic 1   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9823 \\
+      Ceramic 2   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9890 \\
+      Ceramic 3   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9712 \\
+      Sandstone 1 & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
+      Sandstone 2 & SEM &  $1280 \times 869$ & 0.05 & 0.9897 \\
+      Carbonate 1 & SEM &  $1024 \times 691$ & 0.06 & 0.9721
     \end{tabular}
@@
   \centering
-  \subfigure[Castlegate sandstone]{
-    \includegraphics[width=0.3\linewidth]{samples/CastleGate_2d25um_binary.png}
-    \label{fig:castlegate}}
+  \subfigure[Ceramic 1]{
+    \includegraphics[width=0.3\linewidth]{samples/Ceramic1.png}}
   \hfill
-  \subfigure[Bentheimer sandstone]{
-    \includegraphics[width=0.3\linewidth]{samples/Bentheimer_2d25um_binary.png}
-    \label{fig:bentheimer}}
+  \subfigure[Ceramic 2]{
+    \includegraphics[width=0.3\linewidth]{samples/Ceramic2.png}}
   \hfill
-  \subfigure[Kirby sandstone]{
-    \includegraphics[width=0.3\linewidth]{samples/Kirby_2d25um_binary.png}
-    \label{fig:kirby}}
+  \subfigure[Ceramic 3]{
+    \includegraphics[width=0.3\linewidth]{samples/Ceramic3.png}}
   \vskip\baselineskip
@@
   \label{fig:real-xct}
+\end{figure*}
+
+\begin{figure*}[pt]
+  \centering
+  \subfigure[Sandstone 1]{
+    \includegraphics[width=0.3\linewidth, frame]{samples/sandstone1.png}}
+  \hfill
+  \subfigure[Sandstone 2]{
+    \includegraphics[width=0.3\linewidth, frame]{samples/sandstone2.png}}
+  \hfill
+  \subfigure[Carbonate 1]{
+    \includegraphics[width=0.3\linewidth, frame]{samples/carbonate1.png}}
+  \vskip\baselineskip
+  \includegraphics[width=0.3\linewidth]{samples/s2-sem.png}
+  \includegraphics[width=0.3\linewidth]{samples/c2-sem.png}
+  \includegraphics[width=0.3\linewidth]{samples/l2-sem.png}
+  \vskip\baselineskip
+  \includegraphics[width=0.3\linewidth]{samples/surf2-sem.png}
+  \includegraphics[width=0.3\linewidth]{samples/surfvoid-sem.png}
+  \caption[]{SEM images and plots of correlation functions for these images.}
+  \label{fig:real-sem}
 \end{figure*}
@@
 
-% Replace by two disks?
 \begin{figure}[ht]

### 2023-07-24 paper-correlations.tex
On C0.5 criterion

@@
 \end{algorithmic}
+
+The interface between phases must not change very rapidly for the edge filter to
+work correctly. Therefore, the algorithms for surface functions require input
+images to be in good resolution. A criterion for goodness can be expressed with
+$C_{\alpha}$ parameter. Let $\alpha \in [0, 1]$ and $f(x)$ be your
+(band-limited) input image ($x \in \mathbb{R}^2$ or $\mathbb{R}^3$). We define
+$C_\alpha$ as follows:
+\begin{align*}
+  f_0(x) &= f(x) - \langle f(x) \rangle \\
+  C_\alpha &= \frac{\int_{-\alpha\omega}^{\alpha\omega} |\hat{f_0}(z)|^2
+    dz}{\int_{-\omega}^{\omega} |\hat{f_0}(z)|^2 dz}
+\end{align*}
+where $\hat{f_0}$ is a Fourier transform of $f_0$ and $\omega$ is a folding
+frequency which depends only on resolution of the image. Our criterion is that
+if $C_{0.5} > 0.97$ then the image is suitable for our algorithms which compute
+$F_{ss}$ and $F_{sv}$.
 

### 2023-07-25 paper-correlations.tex
Add missing citation
Change document class

@@
-\documentclass[reprint,amsmath,amssymb,aps,pre,showkeys,showpacs,nofootinbib]{revtex4-1}
+\documentclass[1p]{elsarticle}
 % Latex
@@
 %\setmonofont{DejaVu Sans Mono}
+\usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{bm}
+\usepackage{hyperref}
 \usepackage{cleveref}
@@
 
+\bibliographystyle{elsarticle-num}
+\journal{Physica A: Statistical Mechanics and its Applications}
+
 \begin{document}
-\preprint{APS/123-QED}
-
-\author{Vasily Postnicov\textsuperscript{1}}
-\author{Aleksei Samarin\textsuperscript{1,2}}
-\author{Marina Karsanina\textsuperscript{1}}
-\author{Aleksey Khlyupin\textsuperscript{1}}
-\author{Kirill Gerke\textsuperscript{1}}
-\email{kg@ifz.ru}
-
-\affiliation{\textsuperscript{1}Schmidt Institute of Physics of the Earth of
-  Russian Academy of Sciences, Moscow, 107031, Russia}
-\affiliation{\textsuperscript{2}Computational Mathematics and Cybernetics,
-  Lomonosov Moscow State University, Moscow, 119991, Russia}
+
+\author[Smith]{Vasily~Postnicov}
+\author[Smith,MIT]{Aleksei~Samarin}
+\author[Smith]{Marina~Karsanina}
+\author[Smith]{Aleksey~Khlyupin}
+\author[Smith]{Kirill~Gerke}
+\ead{kg@ifz.ru}
+
+\address[Smith]{Schmidt Institute of Physics of the Earth of Russian Academy of
+  Sciences, Moscow, 107031, Russia}
+\address[MIT]{Computational Mathematics and Cybernetics, Lomonosov Moscow State
+  University, Moscow, 119991, Russia}
 
@@
 Our library does not have an implementation for lineal-path maps, although we
-know that such implementations exist \cite{Paper}. The reason is a very slow
-computation even on GPUs, plus the resulting map is not for all points on the
-image, but within a spherical volume (due to rotation of the 3D image during
+know that such implementations exist \cite{havelkafast}. The reason is a very
+slow computation even on GPUs, plus the resulting map is not for all points on
+the image, but within a spherical volume (due to rotation of the 3D image during
 lineal-path evaluation). Moreover, linear scan approach is orders of magnitude
@@
 
-\begin{table*}[!pt]
+\begin{table}[!pt]
   \centering
-  \begin{ruledtabular}
   \begin{tabular}{|c|c|c|c|c|}
+    \hline
     Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
@@
     Sandstone 2 & SEM &  $1280 \times 869$ & 0.05 & 0.9897 \\
-      Carbonate 1 & SEM &  $1024 \times 691$ & 0.06 & 0.9721
+    Carbonate 1 & SEM &  $1024 \times 691$ & 0.06 & 0.9721 \\
+    \hline
   \end{tabular}
-  \end{ruledtabular}
   \caption{Summary of samples used for calculation of correlation functions.}
   \label{tab:samples}
-\end{table*}
+\end{table}
 
@@
   \centering
-  \includegraphics[width=0.6\linewidth]{images/timing-image.png}
+  \includegraphics[width=0.45\linewidth]{images/timing-image.png}
   \caption[]{One of 2D image used in timing measurements.}

### 2023-07-27 samples/multiphase.jl
Add multiphase sample

@@ -1,0 +1,16 @@
+module WTF
+import CorrelationFunctions.Utilities as U
+import CorrelationFunctions.Directional as D
+using NPZ
+using Statistics
+
+function do_it!()
+    data = U.read_cuboid("image3d_multi_4phases.raw", 304, 3)
+
+    for (p1, p2) in [(0, 1), (0, 2), (0, 3), (1, 3), (2, 3), (3, 3), (1, 2)]
+        cc = D.cross_correlation(data, p1, p2; periodic = true)
+        npzwrite("multiphase-$(p1)-$(p2).npy", mean(cc))
+    end
+end
+
+end

### 2023-07-27 samples/multiphase.py

@@ -1,0 +1,22 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+pairs = [(1, 2), (1, 3), (2, 3)]
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 25)
+
+for pair in pairs:
+    p1, p2 = pair
+    data = np.load('multiphase-%i-%i.npy' % (p1 - 1, p2 - 1))
+    xs = np.arange(0, data.size) * 2.25
+    plt.plot(xs, data)
+
+plt.legend(list(map(lambda x: r'$\rho_{%i%i}$' % x, pairs)), loc = 1)
+plt.xlabel('Correlation length, μm')
+plt.ylabel('Cross-correlation')
+plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
+#plt.show()
+plt.savefig("multiphase-cc.png", bbox_inches = 'tight')

### 2023-08-04 samples/multiphase.py
Normalize cross-correlations

@@ -3,7 +3,7 @@
 import numpy as np
 import matplotlib.pyplot as plt
 
-pairs = [(1, 2), (1, 3), (2, 3)]
+pairs = [(1, 2), (1, 3), (1, 4), (2, 3), (2, 4), (3, 4)]
 
 plt.figure(figsize = (10, 8), dpi = 300)
 plt.rc('font', size = 25)
@@ -14,7 +14,7 @@ for pair in pairs:
     xs = np.arange(0, data.size) * 2.25
     plt.plot(xs, data)
 
-plt.legend(list(map(lambda x: r'$\rho_{%i%i}$' % x, pairs)), loc = 1)
+plt.legend(list(map(lambda x: r'$\rho_{%i%i}$' % x, pairs)))
 plt.xlabel('Correlation length, μm')
 plt.ylabel('Cross-correlation')
 plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)

### 2023-08-04 paper-correlations.tex
Add multiphase sample
Normalize cross-correlations
Histograms of pore-size and chord-length functions

@@
 seen on \cref{fig:real-xct} and correlation functions of SEM images are on
-\cref{fig:real-sem}.
+\cref{fig:real-sem}. Cross-correlation funcions for a multiphase XCT image is on
+\cref{fig:real-multiphase}.
 
@@
     Carbonate 1 & SEM &  $1024 \times 691$ & 0.06 & 0.9721 \\
+    \hline
+    Soil (multiphase sample) & XCT & $304 \times 304 \times 304$ &
+    \textcolor{red}{2.25} & \\
     \hline
@@
   \includegraphics[width=0.3\linewidth]{samples/surfvoid-xct.png}
+  \vskip\baselineskip
+  \includegraphics[width=0.3\linewidth]{samples/pore-size-xct.png}
+  \includegraphics[width=0.3\linewidth]{samples/chord-length-xct.png}
   \caption[]{Visualization of XCT images and plots of correlation functions for
@@
   \includegraphics[width=0.3\linewidth]{samples/surfvoid-sem.png}
+  \vskip\baselineskip
+  \includegraphics[width=0.3\linewidth]{samples/pore-size-sem.png}
+  \includegraphics[width=0.3\linewidth]{samples/pore-size-sem.png}
   \caption[]{SEM images and plots of correlation functions for these images.}
@@
 \end{figure*}
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=0.45\linewidth]{samples/multiphase.png}
+  \includegraphics[width=0.45\linewidth]{samples/multiphase-cc.png}
+  \caption[]{Cross-correlation functions for multiphase sample (soil) which has
+    4 distinct phases, labeled as 1-4. Each function $\rho_{ij}$ is normalized
+    by division by $\rho_{ii}(0) \rho_{jj}(0)$.}
+  \label{fig:real-multiphase}
+\end{figure}
 

### 2023-08-04 paper-correlations.tex
half of discussion i hope

--- 2023-07-25 paper-correlations.tex
@@
 \bibliographystyle{elsarticle-num}
-\journal{Physica A: Statistical Mechanics and its Applications}
+\journal{Computational Material Science}
 
@@
 \author[Smith,MIT]{Aleksei~Samarin}
-\author[Smith]{Marina~Karsanina}
+\author[Smith]{Marina ~V. Karsanina}
+\author[Aus]{Martieu ~Gravey}
 \author[Smith]{Aleksey~Khlyupin}
-\author[Smith]{Kirill~Gerke}
+\author[Smith]{Kirill ~M. Gerke}
 \ead{kg@ifz.ru}
@@
   University, Moscow, 119991, Russia}
+\address[Aus]{Institute for Interdisciplinary Mountain Research, Austrian Academy of Sciences, Innsbruck, 6020, Austria}
 
@@
 computation of higher-order statistics will, arguably, not be balanced by
-increased number of points, but this is the topic of active research. For
+increased number of points, but this is the topic of active research \cite{skolnick2021,cherkasovIC}. For
 aforementioned reasons, we mainly focus on 2-point statistics, leaving the
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{images/corr.png}
+  \includegraphics[width=0.9\linewidth]{images/figa1.jpg}
   \caption[]{A schematic depiction of a binary porous media (pores are shown in
@@
 directions in 3D case (three orthogonal, six diagonal within each orthogonal
-plane and four diagonal). The line segment scanning approach is slower for some
+plane and four diagonal). All directions available are schematically represented in \cref{fig:directions}. The line segment scanning approach is slower for some
 CFs but requires much less memory resources. The full map approach establishes
@@
 modes.  Periodic mode assumes that an input sample is periodically continued to
-the whole Euclidean space. Non-periodic mode assumes zero-padded input.
+the whole Euclidean space. Non-periodic mode treats the input as zero-padded image.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=0.9\linewidth]{images/figa_direction.jpg}
+  \caption[]{Available directions to compute directional correlation functions in 2D and 3D cases with line scanning approach.}
+  \label{fig:directions}
+\end{figure}
 
@@
 based on comparison against exact computations of surface functions on smooth-boundary
-sets \cite{Postnicov2023}.
+sets \cite{postcov23}.
 
@@
 
-The interface between phases must not change very rapidly for the edge filter to
+The interface between phases must not change rapidly for the edge filter to
 work correctly. Therefore, the algorithms for surface functions require input
-images to be in good resolution. A criterion for goodness can be expressed with
-$C_{\alpha}$ parameter. Let $\alpha \in [0, 1]$ and $f(x)$ be your
+images to be with an apropriate resolution. A criterion for goodness can be expressed with
+$C_{\alpha}$ parameter. Let $\alpha \in [0, 1]$ and $f(x)$ be
 (band-limited) input image ($x \in \mathbb{R}^2$ or $\mathbb{R}^3$). We define
@@
 where $\hat{f_0}$ is a Fourier transform of $f_0$ and $\omega$ is a folding
-frequency which depends only on resolution of the image. Our criterion is that
-if $C_{0.5} > 0.97$ then the image is suitable for our algorithms which compute
-$F_{ss}$ and $F_{sv}$.
-
-Our library does not have an implementation for lineal-path maps, although we
-know that such implementations exist \cite{havelkafast}. The reason is a very
+frequency which depends only on resolution of the image. We have previously shown that criterion 
+$C_{0.5} > 0.97$ holds then the image is suitable for robust $F_{ss}$ and $F_{sv}$ evaluation \cite{samarin2023robust}.
+Note that function \code{lowfreq\_energy\_ratio} that computes $C_{0.5}$ criterion for any input binary image is the part of \code{CorrelationFunctions.jl} package.
+
+Our library does not have an implementation for lineal-path and chord-length maps, although we
+know that such implementations exist \cite{turner2016efficient,Havelka}. The reason is a very
 slow computation even on GPUs, plus the resulting map is not for all points on
@@
 
-All described algorithms contain parallelizable operations such as fast Fourier
+Majority of described algorithms contain parallelizable operations such as fast Fourier
 transform, connected components labeling and image filtering, hence they are
@@
 All algorithms described above (full correlation maps) are executed on the whole
-input and hence require a lot of RAM memory. The scan approach deals with memory
+input image and hence require a lot of RAM memory. The scan approach deals with memory
 limitations at the cost of higher execution time (except for $L_2$). With
@@
 one-dimensional slices from the input along those directions. Then for each
-direction we use an appropriate algorithm in \cref{sec:map} to calculate a
-correlation function just for that single slice. When all slices are processed
-we calculate the resulting directional or averaged CF using the formula:
+direction, as shown in  \cref{fig:directions}, we use an appropriate algorithm in \cref{sec:map} to calculate a
+correlation function just for that single slice. For this reason we do not repeat algorithms for $S_2$, $\rho_{ij}$, $F_{ss}$ and $F_{sv}$.
+When all slices are processed we calculate the resulting directional or averaged CF using the formula:
 \begin{equation*}
@@
 An algorithm for computation of linear-path function for one-dimensional slice
-is presented below. Here $a$ is a one-dimensional input array, $phase$ can be
+is presented below. Here $A$ is a one-dimensional input array, $phase$ can be
 void, solid or some other phase, and $periodic$ is a boolean value which equals
@@
 Cluster function can be calculated using the same technique as in map approach,
-but if the number of clusters is high, a naïve $O(n^2)$ algorithm may be more
-preferred than $O(MC \log M)$ algorithm. Such an algorithm is present below:
+but if the number of clusters is high, a naïve $O(n^2)$ algorithm may be
+preferred to $O(MC \log M)$ full map algorithm. Such an approach is present below:
 \begin{algorithmic}[1]
@@
 distance transform to an input to find the interface and then accumulate chord
-length in per-slice manner. Finally, chord lengths can be binned in a histogram.
+length in per-slice manner. Finally, chord lengths can be binned to a histogram.
 \begin{algorithmic}[1]
@@
 (\cref{fig:overlapping-disks}) with dimensions $10000 \times 10000$ and
-parameters $R = 40\ px$ and $\lambda = 10^{-4}\ px^{-2}$ and compare calculated
+parameters of radii $R = 40\ pixels$ and $\lambda = 10^{-4}\ pixels^{-2}$ and then compare calculated
 correlation functions with their theoretical values.
@@
 (\cref{fig:overlapping-disks}) with dimensions $500 \times 500 \times 500$ and
-parameters $R = 10\ px$ and $\lambda = 10^{-4}\ px^{-3}$ and compare calculated
-correlation functions with their theoretical values.
+$R = 10\ voxels$ and $\lambda = 10^{-4}\ voxels^{-3}$ and then compare calculated
+correlation functions with analytical solutions.
 
@@
 Poisson realizations (i.e., larger images reduce deviations \cite{samarin2023robust}).
+The package contains automatic tests based on these comparisons.
 
@@
 solution, in this section we apply \code{CorrelationFUnctions.jl} to compute CFs
-for a variety of real 2D (SEM) and 3D (XCT) images. We also report benchmark on
-execution time and compare GPU and CPU implementations.
+for a variety of real 2D (SEM) and 3D (XCT) images. We also report benchmarks on
+execution time and compare the efficiency of GPU and CPU implementations.
 
@@
 \label{sec:examples}
-A summary which contains information about type of the images, dimensions and resolution
-can be found in \cref{tab:samples}. Correlation functions of XCT images can be
-seen on \cref{fig:real-xct} and correlation functions of SEM images are on
-\cref{fig:real-sem}.
+For testing purposes we have gathered an assortment of different porous materials including XCT images of
+artificial ceramics \cite{ceramics} and natural soil composite \cite{Geoderma2018}, segmented into numerous phases,
+and SEM images of oil-bearing rocks such as sandstones and carbonate \cite{samarin2023robust}.
+A summary of this library of 2D and 3D images, including dimensions and resolutions,
+can be found in \cref{tab:samples}.
+
+Correlation functions of XCT images can be seen on \cref{fig:real-xct} and correlation functions of SEM images are on
+\cref{fig:real-sem}. Cross-correlation functions for a multiphase XCT image is on \cref{fig:real-multiphase}.
 
@@
 
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=0.45\linewidth]{samples/multiphase.png}
+  \includegraphics[width=0.45\linewidth]{samples/multiphase-cc.png}
+  \caption[]{Cross-correlation functions for multiphase sample (soil) which has
+    4 distinct phases, labeled as 1-4.}
+  \label{fig:real-multiphase}
+\end{figure}
+
 \subsection{Execution times for our algorithms}
 \label{sec:efficiency}
-To measure execution times of our algorithms we use a machine with the following
+To measure execution times for developed computational algorithms we use a machine with the following
 configuration:
@@
 \item \textbf{CPU}: AMD Ryzen 7 5800X
-\item \textbf{Memory}: 32~Gb DDR4 memory
-\item \textbf{GPU}: Nvidia Tesla V100 with 32~Gb video memory
+\item \textbf{Memory}: 32~GB DDR4 memory
+\item \textbf{GPU}: Nvidia Tesla V100 with 32~GB video memory
 \end{itemize}
 
-We generate two (resp. three) dimensional square (resp. cubic) binary arrays
-with different sides. An array used for measurements contains two solid disks
-(resp. balls) surrounded by void phase.
-
-To measure efficiency of our code we generate six arrays with a side of a square
+We generate 2 and 3-dimensional square/cubical binary arrays
+with different width (see insets on \cref{fig:timings}). An array used for measurements contains two solid disks
+or balls surrounded by void phase. This configuration is a compromise between ease of
+image scaling and complexity of the structure (e.g., full map $C_2$ computational time
+is not compromised by too many clusters).
+
+We generated six arrays with dimensions of
 $s = 1000, 2000, \dots, 6000$ pixels for two-dimensional case and six arrays
 with a side of a cube $s = 50, 100, \dots, 300$ voxels for three-dimensional
-case and calculate execution time for each function. All functions are
+case and calculated execution time for each correlation function. All functions are
 calculated using periodic boundary conditions. Functions which use per-slice
-directional approach are calculated along axial directions.
-
-Functions which calculate full correlation maps are suitable for running on CPU
-and GPU, so we provide execution times for both. The cluster function still uses
-an algorithm for closest component labeling which works only on CPU, so there is
-a potentional for improvement for this function.
-
-The measurements of execution time is on \cref{fig:timings}. As you can see, GPU
-versions (when available) are faster than CPU versions and limited only by
+directional approach were calculated along major axial directions only.
+
+Functions which calculate full correlation maps are suitable for running on both CPU
+and GPU, so we provide execution times for both. The cluster function uses
+an algorithm for closest component labeling which has CPU-only implementation (thus,
+leaving a room for future improvements). Directional computations are performed exclusively
+on CPUs.
+
+All measurements of execution time are presented on \cref{fig:timings}. It is immediately apparent that GPU
+versions (where available) are much faster than CPU versions and limited only by
 amount of video memory. Functions in module \code{Directional} (which utilize
 per-slice directional approach) are the slowest among other implementations, but
-require less memory.
-
-\begin{figure}[ht]
-  \centering
-  \includegraphics[width=0.45\linewidth]{images/timing-image.png}
-  \caption[]{One of 2D image used in timing measurements.}
-  \label{fig:valuenoise}
-\end{figure}
+require less memory. Depending on CF, our video card with 24 GBs of memory could handle a cube of
+~$300^3$ voxels, whilst the workstation with 512-1024 GBs of RAM can handle virtually any XCT-obtained
+image volume with any correlation length.
 
@@
 \section{Discussion and outlook}
+In the light of the end of the previous section it is important to clarify that available
+(video) RAM or speed of computations are not the only considerations behind choosing between full correlation map
+and directional linear scan. Directional CFs are extremely useful in describing or reconstructing
+anisotropic structures \cite{jiao2014chawla,EPL1,tensorPRE}. At the same time, they also much easier to
+work with and good candidates for data compression and feature extraction \cite{KarsaninaEJSS}. On the other hand,
+full map for $S_2$ allows computing ensemble averaged two-point probability - in the similar fashion it is
+measured with scattering experiments. The usefulness of full correlation maps for other CFs is questionable,
+as they are either non-measurable experimentally, e.g., \cite{Gommes_notchord}, or non-applicable for stochastic reconstructions.
+The latter refers to our ability to reconstruct almost any structure from its $S_2$ map \cite{fullwood2008}. And while we
+have fast and efficient techniques such as phase-recovery to reconstruct the structure from its $S_2$ correlation map, the utilization
+of other CFs is complicated \cite{cherkasov2021,cherkasovIC}. Simulated-annealing based methods that operate on the full map are, 
+to the best of our knowledge, were not developed to date. This is the reason we did not invest into improvement on existing approaches to compute maps for $L_2$.
+
+The trade-off in using full map or directional CFs is closely related to the information content of correlation
+functions \cite{Gommes1,Gommes2,skolnick2021}. Any reduction of the full map into ensemble averaged or
+directionally computed CFs significantly decreases the information available. On the other hand, full correlation map is
+larger than the image itself and, thus, storing such huge amount of data for already voluminous datasets is not practical.
+Vectorization of directional correlation functions is, thus, seems like a natural feature reduction approach while
+working with correlation maps. As applied to stochastic reconstructions, similar logic applies -
+it seems to be beneficial to increase the number of functions rather than their "volume". Full correlation maps
+are usually not available unless the structure is already known; but they may be useful in the form of 2D maps
+available from images for 3D reconstructions \cite{cherkasov2021}. Wether reconstructions of, say, full 3D maps
+based on 2D maps is a better approach than using directional CFs computed from images for stochastic reconstructions
+is an open question. Simulated annealing based methods were developed in the first place due to absence of
+methods like phase-recovery for correlation functions other than autocorrelation $S_2$. We believe that our fast and robust
+computational framework in the form of \code{CorrelationFunctions.jl} package will facilitate research in these areas.
+
 When to use map and when to use linear scan
@@
 put into GPU card memory - we can ensemble by computation in subcubes (possible future upodates)
+clusterization on GPUs
+Numerous directions or solid angle
 
@@
 Here we assume that an input is padded with zeros to the length $2s_i - 1$
-across each dimension $i$ where $s_i$ is the size of the unpadded input in that
-dimension. For each dimension we calculate a sequence
+across each dimension $i$ where $s_i$ is the size of the non-padded input in that respective
+dimension. For each dimension we calculate a sequence:
 \begin{equation*}

### 2023-08-04 paper-correlations.tex

@@
   \caption[]{Cross-correlation functions for multiphase sample (soil) which has
-    4 distinct phases, labeled as 1-4.}
+    4 distinct phases, labeled as 1-4. Each function $\rho_{ij}$ is normalized
+    by division by $\rho_{ii}(0) \rho_{jj}(0)$.}
   \label{fig:real-multiphase}

### 2023-08-31 paper-correlations.tex
Fix images

@@
   \vskip\baselineskip
-  \includegraphics[width=0.3\linewidth]{samples/s2-xct.png}
-  \includegraphics[width=0.3\linewidth]{samples/c2-xct.png}
-  \includegraphics[width=0.3\linewidth]{samples/l2-xct.png}
+  \includegraphics[width=0.32\linewidth]{samples/s2-xct.png}
+  \includegraphics[width=0.32\linewidth]{samples/c2-xct.png}
+  \includegraphics[width=0.32\linewidth]{samples/l2-xct.png}
   \vskip\baselineskip
-  \includegraphics[width=0.3\linewidth]{samples/surf2-xct.png}
-  \includegraphics[width=0.3\linewidth]{samples/surfvoid-xct.png}
+  \includegraphics[width=0.32\linewidth]{samples/surf2-xct.png}
+  \includegraphics[width=0.32\linewidth]{samples/surfvoid-xct.png}
   \vskip\baselineskip
-  \includegraphics[width=0.3\linewidth]{samples/pore-size-xct.png}
-  \includegraphics[width=0.3\linewidth]{samples/chord-length-xct.png}
+  \includegraphics[width=0.32\linewidth]{samples/pore-size-xct.png}
+  \includegraphics[width=0.32\linewidth]{samples/chord-length-xct.png}
   \caption[]{Visualization of XCT images and plots of correlation functions for
@@
   \vskip\baselineskip
-  \includegraphics[width=0.3\linewidth]{samples/s2-sem.png}
-  \includegraphics[width=0.3\linewidth]{samples/c2-sem.png}
-  \includegraphics[width=0.3\linewidth]{samples/l2-sem.png}
+  \includegraphics[width=0.32\linewidth]{samples/s2-sem.png}
+  \includegraphics[width=0.32\linewidth]{samples/c2-sem.png}
+  \includegraphics[width=0.32\linewidth]{samples/l2-sem.png}
   \vskip\baselineskip
-  \includegraphics[width=0.3\linewidth]{samples/surf2-sem.png}
-  \includegraphics[width=0.3\linewidth]{samples/surfvoid-sem.png}
+  \includegraphics[width=0.32\linewidth]{samples/surf2-sem.png}
+  \includegraphics[width=0.32\linewidth]{samples/surfvoid-sem.png}
   \vskip\baselineskip
-  \includegraphics[width=0.3\linewidth]{samples/pore-size-sem.png}
-  \includegraphics[width=0.3\linewidth]{samples/pore-size-sem.png}
+  \includegraphics[width=0.32\linewidth]{samples/pore-size-sem.png}
+  \includegraphics[width=0.32\linewidth]{samples/chord-length-sem.png}
   \caption[]{SEM images and plots of correlation functions for these images.}

### 2023-09-04 paper-correlations.tex
Add correlation map examples

@@
 \label{sec:examples}
-For testing purposes we have gathered an assortment of different porous materials including XCT images of
-artificial ceramics \cite{ceramics} and natural soil composite \cite{Geoderma2018}, segmented into numerous phases,
-and SEM images of oil-bearing rocks such as sandstones and carbonate \cite{samarin2023robust}.
-A summary of this library of 2D and 3D images, including dimensions and resolutions,
-can be found in \cref{tab:samples}.
-
-Correlation functions of XCT images can be seen on \cref{fig:real-xct} and correlation functions of SEM images are on
-\cref{fig:real-sem}. Cross-correlation functions for a multiphase XCT image is on \cref{fig:real-multiphase}.
+For testing purposes we have gathered an assortment of different porous
+materials including XCT images of artificial ceramics \cite{ceramics} and
+natural soil composite \cite{Geoderma2018}, segmented into numerous phases, and
+SEM images of oil-bearing rocks such as sandstones and carbonate
+\cite{samarin2023robust}.  A summary of this library of 2D and 3D images,
+including dimensions and resolutions, can be found in \cref{tab:samples}.
+
+Correlation functions of XCT images can be seen on \cref{fig:real-xct} and
+correlation functions of SEM images are on
+\cref{fig:real-sem}. Cross-correlation functions for a multiphase XCT image is
+on \cref{fig:real-multiphase}. Correlation maps for one of SEM samples are of
+\cref{fig:real-sem-map}.
 
@@
 
+\begin{figure*}[pt]
+  \centering
+  \subfigure[$S_2$]{
+    \includegraphics[width=0.45\linewidth]{samples/map-s2.png}}
+  \hfill
+  \subfigure[$C_2$]{
+    \includegraphics[width=0.45\linewidth]{samples/map-c2.png}}
+  \vskip\baselineskip
+  \subfigure[$F_{ss}$]{
+    \includegraphics[width=0.45\linewidth]{samples/map-surf2.png}}
+  \hfill
+  \subfigure[$F_{sv}$]{
+    \includegraphics[width=0.45\linewidth]{samples/map-surfvoid.png}}
+  \caption[]{Correlation maps for Sandstone 1.}
+  \label{fig:real-sem-map}
+\end{figure*}
+
 \begin{figure}[ht]

### 2023-09-04 paper-correlations.tex
Color different clusters on SEM images
almost done

--- 2023-08-04 paper-correlations.tex
@@
 \begin{abstract}
-  What have we done?
+Correlation functions are becoming one of the major tools for quantification of structural information that is usually represented as material's 2D or 3D image.
+In this paper we introduce \code{CorrelationFunctions.jl} open-source package developed in Julia and capable of computing all classical
+correlation functions based on imaging input data. Images include both binary and multi-phase representations.
+Our code is capable of evaluating two-point probability $S_2$, cluster $C_2$, lineal-path $L_2$, surface-surface $F_ss$,
+surface-void $F_sv$, pore-size $P$ and chord-length $p$ functions on both CPU and GPU architectures.
+There possible, we presented two types of computations: full correlation map (correlations of each point with other pints on the image, that also allows obtaining ensemble averaged CF) and directional correlation functions (currently in major orthogonal and diagonal directions).
+Such an implementation allowed for the first time to assemble a completely free solution to evaluate correlation functions under any operating system with well documented API.
+Our package includes automatic tests against analytical solutions that are described in this paper.
+We measured wall times for all CPU and GPU implementations and as a rule of thumb full correlation maps on GPU are faster than directional scans using CPU due to the usage of fast Fourier transform.
+However, full maps require more RAM and, thus, are limited to available GPU RAM resources.
+On the other hand, directional CFs are memory efficient and can be evaluated for huge datasets - this way they are the first candidates for
+structural data compression of feature extraction. The package itself is available through Julia package ecosystem and on GitHub 
+(https://github.com/fatimp/CorrelationFunctions.jl), the latter source also contains documentation and additional helpful resources such as tutorials.
+We believe that a single powerful computational tool such as \code{CorrelationFunctions.jl} will significantly facilitate the usage of correlation
+functions in numerous areas of structural description and research, as well as in machine learning applications. We also present some example as applied to
+ceramic, soil composite and oil-bearing rock samples based on their 3D X-ray tomography and 2D scanning electron microscope images. Finally, we conclude our paper with
+discussion of possible ways to further improve presented computational framework.
 \end{abstract}
@@
 Two ways exist to obtain correlation functions for a given structure at hand:
-measure them either experimentally with the help of scattering intensity
+measure them either experimentally with the help of, for example, scattering intensity
 \cite{debye1957scattering,li2018direct} or from digital images
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{images/figa1.jpg}
-  \caption[]{A schematic depiction of a binary porous media (pores are shown in
-    color) with examples of positive events for surface $F_{ss}$, $F_{sv}$ and
-    two-point probability $S_2$ correlation functions. The zoomed in area
-    represents the difference between the true ``continuous'' interface in
-    between pore and solid phases with pixelized ``digital'' interface emerging
-    due to limited resolution of digital images.}
+  \includegraphics[width=0.9\linewidth]{images/cf_1.png}
+  \caption[]{A schematic representation of a binary porous media (pores are shaded) 
+  with examples of CFs computations (all classical correlation functions are presented
+  according to the legend on the right side). Computations are results of individual
+  events (producing either 0 or 1) ensemble averaged over the image, direction or represented as full correlation map.}
   \label{fig:functions}
@@
 
-\section{A brief introduction to correlation functions}
+\section{A brief primer on correlation functions}
 \label{sec:math}
@@
 CFs but requires much less memory resources. The full map approach establishes
-correlations between all points on the image is usually faster.  Both
+correlations between all points on the image is usually faster, as it leverages on Fast Fourier Transform computational speed.  Both
 implementations are contained in \code{Directional} and \code{Map} modules of
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{images/figa_direction.jpg}
+  \includegraphics[width=0.9\linewidth]{images/cf_diag.png}
   \caption[]{Available directions to compute directional correlation functions in 2D and 3D cases with line scanning approach.}
@@
 \end{equation}
-where $C$ is such that all coefficients of $H'$ sum to zero, and $S$ equals to
+where $C$ is such that all coefficients of $H$ sum to zero, and $S$ equals to
 $30.45849$ in 2D and $172.96232$ in 3D case. The parameters of the filter were adjusted
@@
 know that such implementations exist \cite{turner2016efficient,Havelka}. The reason is a very
-slow computation even on GPUs, plus the resulting map is not for all points on
+slow computation even on GPUs or the resulting map is not for all points on
 the image, but within a spherical volume (due to rotation of the 3D image during
@@
 $P(r)$. Reckon that pore size function is a probability distribution
-function. In practice, it is better represented as a histogram of pore sizes
+function. In practice, it is conveniently represented as a histogram of pore sizes
 found in the input image. Our algorithm for calculating $P(r)$ is as follows:
@@
   \includegraphics[width=0.45\linewidth]{images/balls.png}
-  \caption[]{Images of overlapping disks and balls used in testing of our library.}
+  \caption[]{Images of overlapping disks and balls used for testing of our package.}
   \label{fig:overlapping-disks}
@@
 
-Correlation functions of XCT images can be seen on \cref{fig:real-xct} and correlation functions of SEM images are on
-\cref{fig:real-sem}. Cross-correlation functions for a multiphase XCT image is on \cref{fig:real-multiphase}.
-
 \begin{table}[!pt]
@@
     Soil (multiphase sample) & XCT & $304 \times 304 \times 304$ &
-    \textcolor{red}{2.25} & \\
+    15.0 & - \\
     \hline
@@
 \end{table}
+
+At first, we compare the three ceramic images which have somewhat different genesis depending on the mixture
+ratio of powder and binder used for firing the material \cite{ceramics}. As observed from \cref{fig:real-xct}, the structure of
+all three samples is visually very similar. The lineal path function supports this observation. The $S_2$ functions are
+also quite similar except for Sample 2 having higher porosity that results in elevated curve (the tail for two-point probability
+as expected fluctuates around porosity squared). Notably, $S_2$ and $C_2$ are almost identical - this indicates that
+pore phase represents a single large cluster. Recall that for $S_2$, $C_2$ and $L_2$ functions the value at correlation length
+of 0 is the porosity value. Surface functions, on the other hand, feel significant difference between samples in
+how pore-solid interface is organized. This is further evidenced on pore-size and chord-length graphs, with Ceramic 2
+sample with the highest porosity having larger amount of large pores. Both $P$ and $p$ show very similar behavior,
+but for different correlation lengths; such behavior is attributed to quite regular pores shapes in all ceramics samples -
+this is evident from much larger differences between pore-size and chord-length for SEM images considered next.
 
@@
 
+The \cref{fig:real-sem} presents three 2D images of sandstones and carbonate with computed correlation functions. In this example,
+unlike for quite isotropic ceramics, we evaluated CFs in the directional manner. The $S_2$ graph immediately provides us
+with porosity values. It also highlights severe anisotropy in sandstone SEM images. For 2D images numerous patches of pores are
+not connected to each other and, thus, $S_2$ and $C_2$ are very different. Cluster functions show how connectivity decays with
+length, also we can easily observe if given pore structure percolates in a given direction - none of the images percolates
+(we highlighted the clusters to make this statement easily verifiable with the naked eye). Note that $C_2$ and $L_2$ were computed
+with correlations lengths equal to image dimensions explore connectivity - for other CFs this leads to noised curves due to smaller number of sampled points (for example, see correlation functions' graphs in \cite{Euras2012}).
+Lineal paths are close for sandstones (with lower $L_2$ values for Sandstone 1 where large pores are occluded with clays or grain fragments),
+but for carbonate with much smaller apertures of pores it is way below $L_2$ for sandstones. Also, $L_2$ suggests that computations
+with correlations lengths beyond where lineal path goes to zero are not very informative. For very irregular pores on 2D SEM images,
+$P$ and $p$ functions look much less similar compared to the ceramics case on \cref{fig:real-xct}. For 2D images it is also visually
+easy to analyze full CF maps, as presented on \cref{fig:real-sem_maps} for Sandstone 1 sample. Full correlation maps show expanded version of directional functions -
+asymmetry is immediately evidenced from $S_2$, $F_ss$ and $F_sv$ maps. Moreover, the map for $C_2$ shows higher connectivity in y-direction
+as compared to x-axis. The interpretation of full correlation maps is less straightforward, but anisotropy patterns in directions different from
+those presented in \cref{fig:directions} can be spotted.
+
 \begin{figure*}[pt]
@@
   \includegraphics[width=0.3\linewidth]{samples/pore-size-sem.png}
-  \includegraphics[width=0.3\linewidth]{samples/pore-size-sem.png}
+  \includegraphics[width=0.3\linewidth]{samples/chord-length-sem.png}
   \caption[]{SEM images and plots of correlation functions for these images.}
@@
 \end{figure*}
+
+Finally, we conclude this section with the example of multi-phase soil composite for which we computed cross-correlation functions \cref{fig:real-multiphase}.
+The graph on the right side of the figure shows cross-correlations between different pairs of phases (normalized by each phase's ratio). One can easily conclude
+that organo-mineral complex (phase 2) is mainly located on pore (phase 1) walls. Heavy minerals (phase 4) do not cross-correlate with pores, as
+they are mainly lie within the mineral solid phase (phase 3) - they do show high cross-correlations. Other CFs can be easily computed for each separate phase,
+while $F_sv$ can potentially be extended beyond void (or pores) and be represented by any other phase or their superposition.
 
@@
 \end{figure}
+
+This section clearly demonstrated, that \code{CorrelationFunctions.jl} can be utilized in analysis of any 2D and 3D images, including structures
+consisting of numerous phases.
 
@@
 (video) RAM or speed of computations are not the only considerations behind choosing between full correlation map
-and directional linear scan. Directional CFs are extremely useful in describing or reconstructing
+and directional linear scans. Directional CFs are extremely useful in describing or reconstructing
 anisotropic structures \cite{jiao2014chawla,EPL1,tensorPRE}. At the same time, they also much easier to
@@
 methods like phase-recovery for correlation functions other than autocorrelation $S_2$. We believe that our fast and robust
-computational framework in the form of \code{CorrelationFunctions.jl} package will facilitate research in these areas.
-
-When to use map and when to use linear scan
-  memory
-  how fast
-  optimization during reconstruction
-  +directional CFs for anisotropic media
-Reconstructions based on maps - from Cherkasov to SA?
-Why we need more functions? Information content
-3-point in future - do we need more points?
-Or may be we need more CFs? Add topology (Zubov)?
-GPU computations are limited by RAM - if we are interested in correlation length of width of cube that can be
-put into GPU card memory - we can ensemble by computation in subcubes (possible future upodates)
-clusterization on GPUs
-Numerous directions or solid angle
+computational framework in the form of \code{CorrelationFunctions.jl} package will facilitate research in these directions.
+
+While the toolbox of presented package and its API are solid, based on additional research numerous areas for future improvements of \code{CorrelationFunctions.jl}
+are possible:
+\begin{enumerate}
+  \item include novel non-classical correlation functions, e.g., describing topology of phases;
+  \item implementing sub-cube based computations of CFs with a given correlation functions with later averaging for larger volume - 
+  with such domain decomposition one could compute CFs for larger samples with limited GPU resources;
+  \item implementing GPU-based clustering (cluster labeling) and distance-map transform to further speed up computations for $C_2$, chord-length and pore-size functions;
+  \item implementing higher order functions, such as 3-point probabilities or even 3-point cluster and other more involved CFs;
+  \item increase number of directions for scan approach or implementing calculations within a given solid angle.
+\end{enumerate}
+We perform steps forward in some directions, whilst others still require additional research to be made to facilitate their implementation
+within the package.
 
@@
 \label{sec:summary}
-Text
+In this paper we introduced \code{CorrelationFunctions.jl} open-source package developed in Julia and capable of computing all classical
+correlation functions based on 2D and 3D input images. Our code is capable of evaluating two-point probability, cluster, lineal-path, surface-surface,
+surface-void, pore-size and chord-length functions on both CPU and GPU architectures. There possible, we presented two types of computations: full correlation map
+(correlations of each point with other pints on the image, that also allows obtaining ensemble averaged CF) and directional correlation functions
+(currently in major orthogonal and diagonal directions). Such an implementation allowed for the first time to assemble a completely free solution to
+evaluate correlation functions under any operating system with well documented API. Our package includes automatic tests against analytical solutions
+that are described in this paper. We measured wall times for all CPU and GPU implementations and as a rule of thumb full correlation maps on GPU are faster
+than directional scans using CPU due to the usage of fast Fourier transform. However, full maps require more RAM and, thus, are limited to available GPU RAM
+resources. On the other hand, directional CFs are memory efficient and can be evaluated for huge datasets - this way they are the first candidates for
+structural data compression of feature extraction. The package itself is available through Julia package ecosystem and on GitHub 
+(https://github.com/fatimp/CorrelationFunctions.jl), the latter source also contains documentation and additional helpful resources such as tutorials.
+We believe that a single powerful computational tool such as \code{CorrelationFunctions.jl} will significantly facilitate the usage of correlation
+functions in numerous areas of structural description and research, as well as in machine learning applications.
+
+\section{Acknowledgments}
+This research was supported by the Russian Science Foundation grant
+19-72-10082.
+
+Collaborative effort of the authors within the FaT iMP (Flow and Transport in
+Media with Pores) research group (www.porenetwork.com) and used some of its
+software.
 

### 2023-09-05 paper-correlations.tex
almost done paper

@@
 correlation functions based on imaging input data. Images include both binary and multi-phase representations.
-Our code is capable of evaluating two-point probability $S_2$, cluster $C_2$, lineal-path $L_2$, surface-surface $F_ss$,
-surface-void $F_sv$, pore-size $P$ and chord-length $p$ functions on both CPU and GPU architectures.
+Our code is capable of evaluating two-point probability $S_2$, cluster $C_2$, lineal-path $L_2$, surface-surface $F_{ss}$,
+surface-void $F_{sv}$, pore-size $P$ and chord-length $p$ functions on both CPU and GPU architectures.
 There possible, we presented two types of computations: full correlation map (correlations of each point with other pints on the image, that also allows obtaining ensemble averaged CF) and directional correlation functions (currently in major orthogonal and diagonal directions).
-Such an implementation allowed for the first time to assemble a completely free solution to evaluate correlation functions under any operating system with well documented API.
-Our package includes automatic tests against analytical solutions that are described in this paper.
+Such an implementation allowed for the first time to assemble a completely free solution to evaluate correlation functions under any operating system with well documented application programming interface (API).
+Our package includes automatic tests against analytical solutions that are described in the paper.
 We measured wall times for all CPU and GPU implementations and as a rule of thumb full correlation maps on GPU are faster than directional scans using CPU due to the usage of fast Fourier transform.

### 2023-09-05 paper-correlations.tex

@@
 \label{sec:examples}
-For testing purposes we have gathered an assortment of different porous materials including XCT images of
-artificial ceramics \cite{ceramics} and natural soil composite \cite{Geoderma2018}, segmented into numerous phases,
-and SEM images of oil-bearing rocks such as sandstones and carbonate \cite{samarin2023robust}.
-A summary of this library of 2D and 3D images, including dimensions and resolutions,
-can be found in \cref{tab:samples}.
+For testing purposes we have gathered an assortment of different porous
+materials including XCT images of artificial ceramics \cite{ceramics} and
+natural soil composite \cite{Geoderma2018}, segmented into numerous phases, and
+SEM images of oil-bearing rocks such as sandstones and carbonate
+\cite{samarin2023robust}.  A summary of this library of 2D and 3D images,
+including dimensions and resolutions, can be found in \cref{tab:samples}.
 
@@
 $P$ and $p$ functions look much less similar compared to the ceramics case on \cref{fig:real-xct}. For 2D images it is also visually
-easy to analyze full CF maps, as presented on \cref{fig:real-sem_maps} for Sandstone 1 sample. Full correlation maps show expanded version of directional functions -
-asymmetry is immediately evidenced from $S_2$, $F_ss$ and $F_sv$ maps. Moreover, the map for $C_2$ shows higher connectivity in y-direction
+easy to analyze full CF maps, as presented on \cref{fig:real-sem-map} for Sandstone 1 sample. Full correlation maps show expanded version of directional functions -
+asymmetry is immediately evidenced from $S_2$, $F_{ss}$ and $F_{sv}$ maps. Moreover, the map for $C_2$ shows higher connectivity in y-direction
 as compared to x-axis. The interpretation of full correlation maps is less straightforward, but anisotropy patterns in directions different from
@@
   \vskip\baselineskip
-  \includegraphics[width=0.3\linewidth]{samples/s2-sem.png}
-  \includegraphics[width=0.3\linewidth]{samples/c2-sem.png}
-  \includegraphics[width=0.3\linewidth]{samples/l2-sem.png}
+  \includegraphics[width=0.32\linewidth]{samples/s2-sem.png}
+  \includegraphics[width=0.32\linewidth]{samples/c2-sem.png}
+  \includegraphics[width=0.32\linewidth]{samples/l2-sem.png}
   \vskip\baselineskip
-  \includegraphics[width=0.3\linewidth]{samples/surf2-sem.png}
-  \includegraphics[width=0.3\linewidth]{samples/surfvoid-sem.png}
+  \includegraphics[width=0.32\linewidth]{samples/surf2-sem.png}
+  \includegraphics[width=0.32\linewidth]{samples/surfvoid-sem.png}
   \vskip\baselineskip
-  \includegraphics[width=0.3\linewidth]{samples/pore-size-sem.png}
-  \includegraphics[width=0.3\linewidth]{samples/chord-length-sem.png}
-  \caption[]{SEM images and plots of correlation functions for these images.}
+  \includegraphics[width=0.32\linewidth]{samples/pore-size-sem.png}
+  \includegraphics[width=0.32\linewidth]{samples/chord-length-sem.png}
+  \caption[]{SEM images and plots of correlation functions for these
+    images. Different clusters of the void phase are shown in color.}
   \label{fig:real-sem}
@@
 
-Finally, we conclude this section with the example of multi-phase soil composite for which we computed cross-correlation functions \cref{fig:real-multiphase}.
-The graph on the right side of the figure shows cross-correlations between different pairs of phases (normalized by each phase's ratio). One can easily conclude
-that organo-mineral complex (phase 2) is mainly located on pore (phase 1) walls. Heavy minerals (phase 4) do not cross-correlate with pores, as
-they are mainly lie within the mineral solid phase (phase 3) - they do show high cross-correlations. Other CFs can be easily computed for each separate phase,
-while $F_sv$ can potentially be extended beyond void (or pores) and be represented by any other phase or their superposition.
+\begin{figure*}[pt]
+  \centering
+  \subfigure[$S_2$]{
+    \includegraphics[width=0.45\linewidth]{samples/map-s2.png}}
+  \hfill
+  \subfigure[$C_2$]{
+    \includegraphics[width=0.45\linewidth]{samples/map-c2.png}}
+  \vskip\baselineskip
+  \subfigure[$F_{ss}$]{
+    \includegraphics[width=0.45\linewidth]{samples/map-surf2.png}}
+  \hfill
+  \subfigure[$F_{sv}$]{
+    \includegraphics[width=0.45\linewidth]{samples/map-surfvoid.png}}
+  \caption[]{Correlation maps for Sandstone 1.}
+  \label{fig:real-sem-map}
+\end{figure*}
+
+Finally, we conclude this section with the example of multi-phase soil composite
+for which we computed cross-correlation functions \cref{fig:real-multiphase}.
+The graph on the right side of the figure shows cross-correlations between
+different pairs of phases (normalized by each phase's ratio). One can easily
+conclude that organo-mineral complex (phase 2) is mainly located on pore (phase
+1) walls. Heavy minerals (phase 4) do not cross-correlate with pores, as they
+are mainly lie within the mineral solid phase (phase 3) -- they do show high
+cross-correlations. Other CFs can be easily computed for each separate phase,
+while $F_{sv}$ can potentially be extended beyond void (or pores) and be
+represented by any other phase or their superposition.
 
@@
 work with and good candidates for data compression and feature extraction \cite{KarsaninaEJSS}. On the other hand,
-full map for $S_2$ allows computing ensemble averaged two-point probability - in the similar fashion it is
+full map for $S_2$ allows computing ensemble averaged two-point probability -- in the similar fashion it is
 measured with scattering experiments. The usefulness of full correlation maps for other CFs is questionable,

### 2023-09-05 paper-correlations.tex
Fix a typo
Fix formatting + run fill-region

@@
 \author[Smith]{Marina ~V. Karsanina}
-\author[Aus]{Martieu ~Gravey}
+\author[Aus]{Mathieu ~Gravey}
 \author[Smith]{Aleksey~Khlyupin}
@@
 \begin{abstract}
-Correlation functions are becoming one of the major tools for quantification of structural information that is usually represented as material's 2D or 3D image.
-In this paper we introduce \code{CorrelationFunctions.jl} open-source package developed in Julia and capable of computing all classical
-correlation functions based on imaging input data. Images include both binary and multi-phase representations.
-Our code is capable of evaluating two-point probability $S_2$, cluster $C_2$, lineal-path $L_2$, surface-surface $F_{ss}$,
-surface-void $F_{sv}$, pore-size $P$ and chord-length $p$ functions on both CPU and GPU architectures.
-There possible, we presented two types of computations: full correlation map (correlations of each point with other pints on the image, that also allows obtaining ensemble averaged CF) and directional correlation functions (currently in major orthogonal and diagonal directions).
-Such an implementation allowed for the first time to assemble a completely free solution to evaluate correlation functions under any operating system with well documented application programming interface (API).
-Our package includes automatic tests against analytical solutions that are described in the paper.
-We measured wall times for all CPU and GPU implementations and as a rule of thumb full correlation maps on GPU are faster than directional scans using CPU due to the usage of fast Fourier transform.
-However, full maps require more RAM and, thus, are limited to available GPU RAM resources.
-On the other hand, directional CFs are memory efficient and can be evaluated for huge datasets - this way they are the first candidates for
-structural data compression of feature extraction. The package itself is available through Julia package ecosystem and on GitHub 
-(https://github.com/fatimp/CorrelationFunctions.jl), the latter source also contains documentation and additional helpful resources such as tutorials.
-We believe that a single powerful computational tool such as \code{CorrelationFunctions.jl} will significantly facilitate the usage of correlation
-functions in numerous areas of structural description and research, as well as in machine learning applications. We also present some example as applied to
-ceramic, soil composite and oil-bearing rock samples based on their 3D X-ray tomography and 2D scanning electron microscope images. Finally, we conclude our paper with
-discussion of possible ways to further improve presented computational framework.
+Correlation functions are becoming one of the major tools for quantification of
+structural information that is usually represented as material's 2D or 3D image.
+In this paper we introduce \code{CorrelationFunctions.jl} open-source package
+developed in Julia and capable of computing all classical correlation functions
+based on imaging input data. Images include both binary and multi-phase
+representations.  Our code is capable of evaluating two-point probability $S_2$,
+cluster $C_2$, lineal-path $L_2$, surface-surface $F_{ss}$, surface-void
+$F_{sv}$, pore-size $P$ and chord-length $p$ functions on both CPU and GPU
+architectures.  There possible, we presented two types of computations: full
+correlation map (correlations of each point with other pints on the image, that
+also allows obtaining ensemble averaged CF) and directional correlation
+functions (currently in major orthogonal and diagonal directions).  Such an
+implementation allowed for the first time to assemble a completely free solution
+to evaluate correlation functions under any operating system with well
+documented application programming interface (API). Our package includes
+automatic tests against analytical solutions that are described in the paper. We
+measured wall times for all CPU and GPU implementations and as a rule of thumb
+full correlation maps on GPU are faster than directional scans using CPU due to
+the usage of fast Fourier transform. However, full maps require more RAM and,
+thus, are limited to available GPU RAM resources. On the other hand, directional
+CFs are memory efficient and can be evaluated for huge datasets - this way they
+are the first candidates for structural data compression of feature
+extraction. The package itself is available through Julia package ecosystem and
+on GitHub (https://github.com/fatimp/CorrelationFunctions.jl), the latter source
+also contains documentation and additional helpful resources such as tutorials.
+We believe that a single powerful computational tool such as
+\code{CorrelationFunctions.jl} will significantly facilitate the usage of
+correlation functions in numerous areas of structural description and research,
+as well as in machine learning applications. We also present some example as
+applied to ceramic, soil composite and oil-bearing rock samples based on their
+3D X-ray tomography and 2D scanning electron microscope images. Finally, we
+conclude our paper with discussion of possible ways to further improve presented
+computational framework.
 \end{abstract}
@@
 Two ways exist to obtain correlation functions for a given structure at hand:
-measure them either experimentally with the help of, for example, scattering intensity
-\cite{debye1957scattering,li2018direct} or from digital images
+measure them either experimentally with the help of, for example, scattering
+intensity \cite{debye1957scattering,li2018direct} or from digital images
 \cite{berryman1985measurement,ma2018SS}. None is perfect, as the first approach
@@
 marginally improves the quality of the structure quantification and these
-improvements decay with increasing $n$ \cite{yao1993high,Gommes2}. For stochastic reconstruction purposes
-computation of higher-order statistics will, arguably, not be balanced by
-increased number of points, but this is the topic of active research \cite{skolnick2021,cherkasovIC}. For
-aforementioned reasons, we mainly focus on 2-point statistics, leaving the
-possibility to include higher order CFs in the future work. The simplest 2-point
-probability function ($S_2$ or autocorrelation) actually arise from small angle
-scattering experiments and measures the probability that both ends of line
-segment with a given length fall into the same phase. Other types include the
-probability of a whole line segment to fall into the phase ($L_2$ function) or
-to lie on the interface between phases ($F_{ss}$ function), and mainly originated
-from aforementioned bounds on physical properties such as permeability and
-elasticity. The general idea of computation of different 2-point CFs is shown in
-\cref{fig:functions}. All major details and numerous analytical cases can be
-found in seminal work of Torquato \cite{Torquato_book}. To all CFs described in this
-book and applicable to digital images we shall refer to as classical correlation
-functions.
+improvements decay with increasing $n$ \cite{yao1993high,Gommes2}. For
+stochastic reconstruction purposes computation of higher-order statistics will,
+arguably, not be balanced by increased number of points, but this is the topic
+of active research \cite{skolnick2021,cherkasovIC}. For aforementioned reasons,
+we mainly focus on 2-point statistics, leaving the possibility to include higher
+order CFs in the future work. The simplest 2-point probability function ($S_2$
+or autocorrelation) actually arise from small angle scattering experiments and
+measures the probability that both ends of line segment with a given length fall
+into the same phase. Other types include the probability of a whole line segment
+to fall into the phase ($L_2$ function) or to lie on the interface between
+phases ($F_{ss}$ function), and mainly originated from aforementioned bounds on
+physical properties such as permeability and elasticity. The general idea of
+computation of different 2-point CFs is shown in \cref{fig:functions}. All major
+details and numerous analytical cases can be found in seminal work of Torquato
+\cite{Torquato_book}. To all CFs described in this book and applicable to
+digital images we shall refer to as classical correlation functions.
 
@@
   \includegraphics[width=0.9\linewidth]{images/cf_1.png}
-  \caption[]{A schematic representation of a binary porous media (pores are shaded) 
-  with examples of CFs computations (all classical correlation functions are presented
-  according to the legend on the right side). Computations are results of individual
-  events (producing either 0 or 1) ensemble averaged over the image, direction or represented as full correlation map.}
+  \caption[]{A schematic representation of a binary porous media (pores are
+    shaded) with examples of CFs computations (all classical correlation
+    functions are presented according to the legend on the right
+    side). Computations are results of individual events (producing either 0 or
+    1) ensemble averaged over the image, direction or represented as full
+    correlation map.}
   \label{fig:functions}
@@
 \section{Computational methodology}
-
 \code{CorrelationFunctions.jl} is capable to compute all aforementioned
@@
 directions in 3D case (three orthogonal, six diagonal within each orthogonal
-plane and four diagonal). All directions available are schematically represented in \cref{fig:directions}. The line segment scanning approach is slower for some
+plane and four diagonal). All directions available are schematically represented
+in \cref{fig:directions}. The line segment scanning approach is slower for some
 CFs but requires much less memory resources. The full map approach establishes
-correlations between all points on the image is usually faster, as it leverages on Fast Fourier Transform computational speed.  Both
-implementations are contained in \code{Directional} and \code{Map} modules of
-the package, correspondingly.
+correlations between all points on the image is usually faster, as it leverages
+on Fast Fourier Transform computational speed.  Both implementations are
+contained in \code{Directional} and \code{Map} modules of the package,
+correspondingly.
 
@@
   \includegraphics[width=0.9\linewidth]{images/cf_diag.png}
-  \caption[]{Available directions to compute directional correlation functions in 2D and 3D cases with line scanning approach.}
+  \caption[]{Available directions to compute directional correlation functions
+    in 2D and 3D cases with line scanning approach.}
   \label{fig:directions}
@@
 where $\hat{f_0}$ is a Fourier transform of $f_0$ and $\omega$ is a folding
-frequency which depends only on resolution of the image. We have previously shown that criterion 
-$C_{0.5} > 0.97$ holds then the image is suitable for robust $F_{ss}$ and $F_{sv}$ evaluation \cite{samarin2023robust}.
-Note that function \code{lowfreq\_energy\_ratio} that computes $C_{0.5}$ criterion for any input binary image is the part of \code{CorrelationFunctions.jl} package.
-
-Our library does not have an implementation for lineal-path and chord-length maps, although we
-know that such implementations exist \cite{turner2016efficient,Havelka}. The reason is a very
-slow computation even on GPUs or the resulting map is not for all points on
-the image, but within a spherical volume (due to rotation of the 3D image during
-lineal-path evaluation). Moreover, linear scan approach is orders of magnitude
-faster for $L_2$.
-
-Majority of described algorithms contain parallelizable operations such as fast Fourier
-transform, connected components labeling and image filtering, hence they are
-perfectly suited for execution on GPUs and provide very fast computations (see
-wall times below).
+frequency which depends only on resolution of the image. We have previously
+shown that criterion $C_{0.5} > 0.97$ holds then the image is suitable for
+robust $F_{ss}$ and $F_{sv}$ evaluation \cite{samarin2023robust}.  Note that
+function \code{lowfreq\_energy\_ratio} that computes $C_{0.5}$ criterion for any
+input binary image is the part of \code{CorrelationFunctions.jl} package.
+
+Our library does not have an implementation for lineal-path and chord-length
+maps, although we know that such implementations exist
+\cite{turner2016efficient,Havelka}. The reason is a very slow computation even
+on GPUs or the resulting map is not for all points on the image, but within a
+spherical volume (due to rotation of the 3D image during lineal-path
+evaluation). Moreover, linear scan approach is orders of magnitude faster for
+$L_2$.
+
+Majority of described algorithms contain parallelizable operations such as fast
+Fourier transform, connected components labeling and image filtering, hence they
+are perfectly suited for execution on GPUs and provide very fast computations
+(see wall times below).
 
@@
 All algorithms described above (full correlation maps) are executed on the whole
-input image and hence require a lot of RAM memory. The scan approach deals with memory
-limitations at the cost of higher execution time (except for $L_2$). With
+input image and hence require a lot of RAM memory. The scan approach deals with
+memory limitations at the cost of higher execution time (except for $L_2$). With
 line-segment scanning we select a list of predefined directions and cut all
 one-dimensional slices from the input along those directions. Then for each
-direction, as shown in  \cref{fig:directions}, we use an appropriate algorithm in \cref{sec:map} to calculate a
-correlation function just for that single slice. For this reason we do not repeat algorithms for $S_2$, $\rho_{ij}$, $F_{ss}$ and $F_{sv}$.
-When all slices are processed we calculate the resulting directional or averaged CF using the formula:
+direction, as shown in \cref{fig:directions}, we use an appropriate algorithm in
+\cref{sec:map} to calculate a correlation function just for that single
+slice. For this reason we do not repeat algorithms for $S_2$, $\rho_{ij}$,
+$F_{ss}$ and $F_{sv}$.  When all slices are processed we calculate the resulting
+directional or averaged CF using the formula:
 \begin{equation*}
@@
 (\cref{fig:overlapping-disks}) with dimensions $10000 \times 10000$ and
-parameters of radii $R = 40\ pixels$ and $\lambda = 10^{-4}\ pixels^{-2}$ and then compare calculated
-correlation functions with their theoretical values.
+parameters of radii $R = 40\ pixels$ and $\lambda = 10^{-4}\ pixels^{-2}$ and
+then compare calculated correlation functions with their theoretical values.
 \begin{figure}[ht]
@@
 
-At first, we compare the three ceramic images which have somewhat different genesis depending on the mixture
-ratio of powder and binder used for firing the material \cite{ceramics}. As observed from \cref{fig:real-xct}, the structure of
-all three samples is visually very similar. The lineal path function supports this observation. The $S_2$ functions are
-also quite similar except for Sample 2 having higher porosity that results in elevated curve (the tail for two-point probability
-as expected fluctuates around porosity squared). Notably, $S_2$ and $C_2$ are almost identical - this indicates that
-pore phase represents a single large cluster. Recall that for $S_2$, $C_2$ and $L_2$ functions the value at correlation length
-of 0 is the porosity value. Surface functions, on the other hand, feel significant difference between samples in
-how pore-solid interface is organized. This is further evidenced on pore-size and chord-length graphs, with Ceramic 2
-sample with the highest porosity having larger amount of large pores. Both $P$ and $p$ show very similar behavior,
-but for different correlation lengths; such behavior is attributed to quite regular pores shapes in all ceramics samples -
-this is evident from much larger differences between pore-size and chord-length for SEM images considered next.
+At first, we compare the three ceramic images which have somewhat different
+genesis depending on the mixture ratio of powder and binder used for firing the
+material \cite{ceramics}. As observed from \cref{fig:real-xct}, the structure of
+all three samples is visually very similar. The lineal path function supports
+this observation. The $S_2$ functions are also quite similar except for Sample 2
+having higher porosity that results in elevated curve (the tail for two-point
+probability as expected fluctuates around porosity squared). Notably, $S_2$ and
+$C_2$ are almost identical -- this indicates that pore phase represents a single
+large cluster. Recall that for $S_2$, $C_2$ and $L_2$ functions the value at
+correlation length of 0 is the porosity value. Surface functions, on the other
+hand, feel significant difference between samples in how pore-solid interface is
+organized. This is further evidenced on pore-size and chord-length graphs, with
+Ceramic 2 sample with the highest porosity having larger amount of large
+pores. Both $P$ and $p$ show very similar behavior, but for different
+correlation lengths; such behavior is attributed to quite regular pores shapes
+in all ceramics samples -- this is evident from much larger differences between
+pore-size and chord-length for SEM images considered next.
 
@@
 
-The \cref{fig:real-sem} presents three 2D images of sandstones and carbonate with computed correlation functions. In this example,
-unlike for quite isotropic ceramics, we evaluated CFs in the directional manner. The $S_2$ graph immediately provides us
-with porosity values. It also highlights severe anisotropy in sandstone SEM images. For 2D images numerous patches of pores are
-not connected to each other and, thus, $S_2$ and $C_2$ are very different. Cluster functions show how connectivity decays with
-length, also we can easily observe if given pore structure percolates in a given direction - none of the images percolates
-(we highlighted the clusters to make this statement easily verifiable with the naked eye). Note that $C_2$ and $L_2$ were computed
-with correlations lengths equal to image dimensions explore connectivity - for other CFs this leads to noised curves due to smaller number of sampled points (for example, see correlation functions' graphs in \cite{Euras2012}).
-Lineal paths are close for sandstones (with lower $L_2$ values for Sandstone 1 where large pores are occluded with clays or grain fragments),
-but for carbonate with much smaller apertures of pores it is way below $L_2$ for sandstones. Also, $L_2$ suggests that computations
-with correlations lengths beyond where lineal path goes to zero are not very informative. For very irregular pores on 2D SEM images,
-$P$ and $p$ functions look much less similar compared to the ceramics case on \cref{fig:real-xct}. For 2D images it is also visually
-easy to analyze full CF maps, as presented on \cref{fig:real-sem-map} for Sandstone 1 sample. Full correlation maps show expanded version of directional functions -
-asymmetry is immediately evidenced from $S_2$, $F_{ss}$ and $F_{sv}$ maps. Moreover, the map for $C_2$ shows higher connectivity in y-direction
-as compared to x-axis. The interpretation of full correlation maps is less straightforward, but anisotropy patterns in directions different from
-those presented in \cref{fig:directions} can be spotted.
+The \cref{fig:real-sem} presents three 2D images of sandstones and carbonate
+with computed correlation functions. In this example, unlike for quite isotropic
+ceramics, we evaluated CFs in the directional manner. The $S_2$ graph
+immediately provides us with porosity values. It also highlights severe
+anisotropy in sandstone SEM images. For 2D images numerous patches of pores are
+not connected to each other and, thus, $S_2$ and $C_2$ are very
+different. Cluster functions show how connectivity decays with length, also we
+can easily observe if given pore structure percolates in a given direction -
+none of the images percolates (we highlighted the clusters to make this
+statement easily verifiable with the naked eye). Note that $C_2$ and $L_2$ were
+computed with correlations lengths equal to image dimensions explore
+connectivity -- for other CFs this leads to noised curves due to smaller number
+of sampled points (for example, see correlation functions' graphs in
+\cite{Euras2012}).  Lineal paths are close for sandstones (with lower $L_2$
+values for Sandstone 1 where large pores are occluded with clays or grain
+fragments), but for carbonate with much smaller apertures of pores it is way
+below $L_2$ for sandstones. Also, $L_2$ suggests that computations with
+correlations lengths beyond where lineal path goes to zero are not very
+informative. For very irregular pores on 2D SEM images, $P$ and $p$ functions
+look much less similar compared to the ceramics case on \cref{fig:real-xct}. For
+2D images it is also visually easy to analyze full CF maps, as presented on
+\cref{fig:real-sem-map} for Sandstone 1 sample. Full correlation maps show
+expanded version of directional functions -- asymmetry is immediately evidenced
+from $S_2$, $F_{ss}$ and $F_{sv}$ maps. Moreover, the map for $C_2$ shows higher
+connectivity in y-direction as compared to x-axis. The interpretation of full
+correlation maps is less straightforward, but anisotropy patterns in directions
+different from those presented in \cref{fig:directions} can be spotted.
 
@@
 
-This section clearly demonstrated, that \code{CorrelationFunctions.jl} can be utilized in analysis of any 2D and 3D images, including structures
-consisting of numerous phases.
+This section clearly demonstrated, that \code{CorrelationFunctions.jl} can be
+utilized in analysis of any 2D and 3D images, including structures consisting of
+numerous phases.
 
@@
 \label{sec:efficiency}
-To measure execution times for developed computational algorithms we use a machine with the following
-configuration:
+To measure execution times for developed computational algorithms we use a
+machine with the following configuration:
 \begin{itemize}
@@
 
-We generate 2 and 3-dimensional square/cubical binary arrays
-with different width (see insets on \cref{fig:timings}). An array used for measurements contains two solid disks
-or balls surrounded by void phase. This configuration is a compromise between ease of
-image scaling and complexity of the structure (e.g., full map $C_2$ computational time
-is not compromised by too many clusters).
-
-We generated six arrays with dimensions of
-$s = 1000, 2000, \dots, 6000$ pixels for two-dimensional case and six arrays
-with a side of a cube $s = 50, 100, \dots, 300$ voxels for three-dimensional
-case and calculated execution time for each correlation function. All functions are
-calculated using periodic boundary conditions. Functions which use per-slice
-directional approach were calculated along major axial directions only.
-
-Functions which calculate full correlation maps are suitable for running on both CPU
-and GPU, so we provide execution times for both. The cluster function uses
-an algorithm for closest component labeling which has CPU-only implementation (thus,
-leaving a room for future improvements). Directional computations are performed exclusively
-on CPUs.
-
-All measurements of execution time are presented on \cref{fig:timings}. It is immediately apparent that GPU
-versions (where available) are much faster than CPU versions and limited only by
-amount of video memory. Functions in module \code{Directional} (which utilize
-per-slice directional approach) are the slowest among other implementations, but
-require less memory. Depending on CF, our video card with 24 GBs of memory could handle a cube of
-~$300^3$ voxels, whilst the workstation with 512-1024 GBs of RAM can handle virtually any XCT-obtained
-image volume with any correlation length.
+We generate 2 and 3-dimensional square/cubical binary arrays with different
+width (see insets on \cref{fig:timings}). An array used for measurements
+contains two solid disks or balls surrounded by void phase. This configuration
+is a compromise between ease of image scaling and complexity of the structure
+(e.g., full map $C_2$ computational time is not compromised by too many
+clusters).
+
+We generated six arrays with dimensions of $s = 1000, 2000, \dots, 6000$ pixels
+for two-dimensional case and six arrays with a side of a cube $s = 50, 100,
+\dots, 300$ voxels for three-dimensional case and calculated execution time for
+each correlation function. All functions are calculated using periodic boundary
+conditions. Functions which use per-slice directional approach were calculated
+along major axial directions only.
+
+Functions which calculate full correlation maps are suitable for running on both
+CPU and GPU, so we provide execution times for both. The cluster function uses
+an algorithm for closest component labeling which has CPU-only implementation
+(thus, leaving a room for future improvements). Directional computations are
+performed exclusively on CPUs.
+
+All measurements of execution time are presented on \cref{fig:timings}. It is
+immediately apparent that GPU versions (where available) are much faster than
+CPU versions and limited only by amount of video memory. Functions in module
+\code{Directional} (which utilize per-slice directional approach) are the
+slowest among other implementations, but require less memory. Depending on CF,
+our video card with 24 GBs of memory could handle a cube of $\sim 300^3$
+voxels, whilst the workstation with 512-1024 GBs of RAM can handle virtually any
+XCT-obtained image volume with any correlation length.
 
@@
 \section{Discussion and outlook}
-In the light of the end of the previous section it is important to clarify that available
-(video) RAM or speed of computations are not the only considerations behind choosing between full correlation map
-and directional linear scans. Directional CFs are extremely useful in describing or reconstructing
-anisotropic structures \cite{jiao2014chawla,EPL1,tensorPRE}. At the same time, they also much easier to
-work with and good candidates for data compression and feature extraction \cite{KarsaninaEJSS}. On the other hand,
-full map for $S_2$ allows computing ensemble averaged two-point probability -- in the similar fashion it is
-measured with scattering experiments. The usefulness of full correlation maps for other CFs is questionable,
-as they are either non-measurable experimentally, e.g., \cite{Gommes_notchord}, or non-applicable for stochastic reconstructions.
-The latter refers to our ability to reconstruct almost any structure from its $S_2$ map \cite{fullwood2008}. And while we
-have fast and efficient techniques such as phase-recovery to reconstruct the structure from its $S_2$ correlation map, the utilization
-of other CFs is complicated \cite{cherkasov2021,cherkasovIC}. Simulated-annealing based methods that operate on the full map are, 
-to the best of our knowledge, were not developed to date. This is the reason we did not invest into improvement on existing approaches to compute maps for $L_2$.
-
-The trade-off in using full map or directional CFs is closely related to the information content of correlation
-functions \cite{Gommes1,Gommes2,skolnick2021}. Any reduction of the full map into ensemble averaged or
-directionally computed CFs significantly decreases the information available. On the other hand, full correlation map is
-larger than the image itself and, thus, storing such huge amount of data for already voluminous datasets is not practical.
-Vectorization of directional correlation functions is, thus, seems like a natural feature reduction approach while
-working with correlation maps. As applied to stochastic reconstructions, similar logic applies -
-it seems to be beneficial to increase the number of functions rather than their "volume". Full correlation maps
-are usually not available unless the structure is already known; but they may be useful in the form of 2D maps
-available from images for 3D reconstructions \cite{cherkasov2021}. Wether reconstructions of, say, full 3D maps
-based on 2D maps is a better approach than using directional CFs computed from images for stochastic reconstructions
-is an open question. Simulated annealing based methods were developed in the first place due to absence of
-methods like phase-recovery for correlation functions other than autocorrelation $S_2$. We believe that our fast and robust
-computational framework in the form of \code{CorrelationFunctions.jl} package will facilitate research in these directions.
-
-While the toolbox of presented package and its API are solid, based on additional research numerous areas for future improvements of \code{CorrelationFunctions.jl}
-are possible:
+In the light of the end of the previous section it is important to clarify that
+available (video) RAM or speed of computations are not the only considerations
+behind choosing between full correlation map and directional linear
+scans. Directional CFs are extremely useful in describing or reconstructing
+anisotropic structures \cite{jiao2014chawla,EPL1,tensorPRE}. At the same time,
+they also much easier to work with and good candidates for data compression and
+feature extraction \cite{KarsaninaEJSS}. On the other hand, full map for $S_2$
+allows computing ensemble averaged two-point probability -- in the similar
+fashion it is measured with scattering experiments. The usefulness of full
+correlation maps for other CFs is questionable, as they are either
+non-measurable experimentally, e.g., \cite{Gommes_notchord}, or non-applicable
+for stochastic reconstructions.  The latter refers to our ability to reconstruct
+almost any structure from its $S_2$ map \cite{fullwood2008}. And while we have
+fast and efficient techniques such as phase-recovery to reconstruct the
+structure from its $S_2$ correlation map, the utilization of other CFs is
+complicated \cite{cherkasov2021,cherkasovIC}. Simulated-annealing based methods
+that operate on the full map are, to the best of our knowledge, were not
+developed to date. This is the reason we did not invest into improvement on
+existing approaches to compute maps for $L_2$.
+
+The trade-off in using full map or directional CFs is closely related to the
+information content of correlation functions
+\cite{Gommes1,Gommes2,skolnick2021}. Any reduction of the full map into ensemble
+averaged or directionally computed CFs significantly decreases the information
+available. On the other hand, full correlation map is larger than the image
+itself and, thus, storing such huge amount of data for already voluminous
+datasets is not practical.  Vectorization of directional correlation functions
+is, thus, seems like a natural feature reduction approach while working with
+correlation maps. As applied to stochastic reconstructions, similar logic
+applies - it seems to be beneficial to increase the number of functions rather
+than their "volume". Full correlation maps are usually not available unless the
+structure is already known; but they may be useful in the form of 2D maps
+available from images for 3D reconstructions \cite{cherkasov2021}. Wether
+reconstructions of, say, full 3D maps based on 2D maps is a better approach than
+using directional CFs computed from images for stochastic reconstructions is an
+open question. Simulated annealing based methods were developed in the first
+place due to absence of methods like phase-recovery for correlation functions
+other than autocorrelation $S_2$. We believe that our fast and robust
+computational framework in the form of \code{CorrelationFunctions.jl} package
+will facilitate research in these directions.
+
+While the toolbox of presented package and its API are solid, based on
+additional research numerous areas for future improvements of
+\code{CorrelationFunctions.jl} are possible:
 \begin{enumerate}
-  \item include novel non-classical correlation functions, e.g., describing topology of phases;
-  \item implementing sub-cube based computations of CFs with a given correlation functions with later averaging for larger volume - 
-  with such domain decomposition one could compute CFs for larger samples with limited GPU resources;
-  \item implementing GPU-based clustering (cluster labeling) and distance-map transform to further speed up computations for $C_2$, chord-length and pore-size functions;
-  \item implementing higher order functions, such as 3-point probabilities or even 3-point cluster and other more involved CFs;
-  \item increase number of directions for scan approach or implementing calculations within a given solid angle.
+\item include novel non-classical correlation functions, e.g., describing
+  topology of phases;
+\item implementing sub-cube based computations of CFs with a given correlation
+  functions with later averaging for larger volume - with such domain
+  decomposition one could compute CFs for larger samples with limited GPU
+  resources;
+\item implementing GPU-based clustering (cluster labeling) and distance-map
+  transform to further speed up computations for $C_2$, chord-length and
+  pore-size functions;
+\item implementing higher order functions, such as 3-point probabilities or even
+  3-point cluster and other more involved CFs;
+\item increase number of directions for scan approach or implementing
+  calculations within a given solid angle.
 \end{enumerate}
-We perform steps forward in some directions, whilst others still require additional research to be made to facilitate their implementation
-within the package.
+We perform steps forward in some directions, whilst others still require
+additional research to be made to facilitate their implementation within the
+package.
 
@@
 \label{sec:summary}
-In this paper we introduced \code{CorrelationFunctions.jl} open-source package developed in Julia and capable of computing all classical
-correlation functions based on 2D and 3D input images. Our code is capable of evaluating two-point probability, cluster, lineal-path, surface-surface,
-surface-void, pore-size and chord-length functions on both CPU and GPU architectures. There possible, we presented two types of computations: full correlation map
-(correlations of each point with other pints on the image, that also allows obtaining ensemble averaged CF) and directional correlation functions
-(currently in major orthogonal and diagonal directions). Such an implementation allowed for the first time to assemble a completely free solution to
-evaluate correlation functions under any operating system with well documented API. Our package includes automatic tests against analytical solutions
-that are described in this paper. We measured wall times for all CPU and GPU implementations and as a rule of thumb full correlation maps on GPU are faster
-than directional scans using CPU due to the usage of fast Fourier transform. However, full maps require more RAM and, thus, are limited to available GPU RAM
-resources. On the other hand, directional CFs are memory efficient and can be evaluated for huge datasets - this way they are the first candidates for
-structural data compression of feature extraction. The package itself is available through Julia package ecosystem and on GitHub 
-(https://github.com/fatimp/CorrelationFunctions.jl), the latter source also contains documentation and additional helpful resources such as tutorials.
-We believe that a single powerful computational tool such as \code{CorrelationFunctions.jl} will significantly facilitate the usage of correlation
-functions in numerous areas of structural description and research, as well as in machine learning applications.
+In this paper we introduced \code{CorrelationFunctions.jl} open-source package
+developed in Julia and capable of computing all classical correlation functions
+based on 2D and 3D input images. Our code is capable of evaluating two-point
+probability, cluster, lineal-path, surface-surface, surface-void, pore-size and
+chord-length functions on both CPU and GPU architectures. There possible, we
+presented two types of computations: full correlation map (correlations of each
+point with other pints on the image, that also allows obtaining ensemble
+averaged CF) and directional correlation functions (currently in major
+orthogonal and diagonal directions). Such an implementation allowed for the
+first time to assemble a completely free solution to evaluate correlation
+functions under any operating system with well documented API. Our package
+includes automatic tests against analytical solutions that are described in this
+paper. We measured wall times for all CPU and GPU implementations and as a rule
+of thumb full correlation maps on GPU are faster than directional scans using
+CPU due to the usage of fast Fourier transform. However, full maps require more
+RAM and, thus, are limited to available GPU RAM resources. On the other hand,
+directional CFs are memory efficient and can be evaluated for huge datasets -
+this way they are the first candidates for structural data compression of
+feature extraction. The package itself is available through Julia package
+ecosystem and on GitHub (https://github.com/fatimp/CorrelationFunctions.jl), the
+latter source also contains documentation and additional helpful resources such
+as tutorials.  We believe that a single powerful computational tool such as
+\code{CorrelationFunctions.jl} will significantly facilitate the usage of
+correlation functions in numerous areas of structural description and research,
+as well as in machine learning applications.
 
 \section{Acknowledgments}
-This research was supported by the Russian Science Foundation grant
-19-72-10082.
+This research was supported by the Russian Science Foundation grant 19-72-10082.
 
@@
 Here we assume that an input is padded with zeros to the length $2s_i - 1$
-across each dimension $i$ where $s_i$ is the size of the non-padded input in that respective
-dimension. For each dimension we calculate a sequence:
+across each dimension $i$ where $s_i$ is the size of the non-padded input in
+that respective dimension. For each dimension we calculate a sequence:
 \begin{equation*}

### 2023-09-06 paper-correlations.tex
Replace affiliation
Fix a typo

@@
 \author[Aus]{Mathieu ~Gravey}
-\author[Smith]{Aleksey~Khlyupin}
+\author[MIPT]{Aleksey~Khlyupin}
 \author[Smith]{Kirill ~M. Gerke}
@@
   University, Moscow, 119991, Russia}
-\address[Aus]{Institute for Interdisciplinary Mountain Research, Austrian Academy of Sciences, Innsbruck, 6020, Austria}
+\address[Aus]{Institute for Interdisciplinary Mountain Research, Austrian
+  Academy of Sciences, Innsbruck, 6020, Austria}
+\address[MIPT]{Moscow Institute of Physics and Technology, Institutskiy Pereulok 9,
+Dolgoprudny, Moscow, Russia 141700}
 
@@
 \end{definition}
-For isotopic media a vector $\bm{r}$ can be reduced to a scalar value
+For isotropic media a vector $\bm{r}$ can be reduced to a scalar value
 $r$ (i.e., a correlation function depends only on length of a vector and not on

### 2023-09-06 paper-correlations.tex
Наш ответ на критику

@@
 CFs but requires much less memory resources. The full map approach establishes
-correlations between all points on the image is usually faster, as it leverages
-on Fast Fourier Transform computational speed.  Both implementations are
-contained in \code{Directional} and \code{Map} modules of the package,
+correlations between all points on the image and is faster. Both implementations
+are contained in \code{Directional} and \code{Map} modules of the package,
 correspondingly.
@@
 Cluster function can be calculated with the help of previuously described
-procedures.  Firstly, we apply an indicator function to an input $A$: $A^{(i)}
-\xleftarrow{I^{(i)}} A$. When we label connected components in $A^{(i)}$ using a
-function that is a part of Julia \code{ImageMorphology.jl} library.  Labeling
-algorithm must take into account if the function is calculated with periodic
-boundary conditions \cite{evstigneev2023}. For periodic boundary conditions we
-implemented our own solution as part of the package, as it is absent in the
-public domain. Then $C_2$ function is a sum of $S_2$ functions calculated for
-all clusters separately. Algorithmic complexity of this implementation is
-$O(MC\log M)$ where $M$ is the number of elements in the input and $C$ is the
-number of clusters. The algorithm is then written as:
+procedures.  Firstly, we apply an indicator function to an input $A$:
+$A^{(i)} \xleftarrow{I^{(i)}} A$. When we label connected components in
+$A^{(i)}$ using a function that is a part of Julia \code{ImageMorphology.jl}
+library.  Labeling algorithm must take into account if the function is
+calculated with periodic boundary conditions \cite{evstigneev2023}. For periodic
+boundary conditions we implemented our own solution as part of the package, as
+it is absent in the public domain. Then $C_2$ function is a sum of $S_2$
+functions calculated for all clusters separately. Algorithmic complexity of this
+implementation is $O(MC\log M)$ where $M$ is the number of elements in the input
+and $C$ is the number of clusters. The algorithm is then written as:
 \begin{algorithmic}[1]
@@
   \begin{aligned}
-    H_{ij} &= S \left\{
-    \begin{array}{cc}
-      \frac{1}{\sqrt{(i-3)^2 + (j-3)^2}} & \quad i \ne 3, j \ne 3 \\
-      C & \quad \text{otherwise}
+    H_k &= S \left\{
+    \begin{array}{ll}
+      -\sum\limits_{\substack{l \\ l \ne 0}} E_l & \quad k = 0 \\
+      1 / \rho(k, 0) & \quad \text{otherwise}
     \end{array}
     \right. \\
-    H_{ijk} &= S \left\{
-    \begin{array}{cc}
-      \frac{1}{\sqrt{(i-3)^2 + (j-3)^2 + (k-3)^3}} & \quad i \ne 3, j \ne 3, k
-      \ne 3 \\
-      C & \quad \text{otherwise}
-    \end{array}
-    \right.
+    k &\in \{-3, -2, \dots, 3\}^D
   \end{aligned}
@@
 \end{equation}
-where $C$ is such that all coefficients of $H$ sum to zero, and $S$ equals to
-$30.45849$ in 2D and $172.96232$ in 3D case. The parameters of the filter were adjusted
-based on comparison against exact computations of surface functions on smooth-boundary
-sets \cite{postcov23}.
+where $S$ equals to $30.45849$ in 2D and $172.96232$ in 3D case. The parameters
+of the filter were adjusted based on comparison against exact computations of
+surface functions on smooth-boundary sets \cite{postcov23}.
 
@@
 paper. We measured wall times for all CPU and GPU implementations and as a rule
-of thumb full correlation maps on GPU are faster than directional scans using
-CPU due to the usage of fast Fourier transform. However, full maps require more
-RAM and, thus, are limited to available GPU RAM resources. On the other hand,
-directional CFs are memory efficient and can be evaluated for huge datasets -
-this way they are the first candidates for structural data compression of
-feature extraction. The package itself is available through Julia package
-ecosystem and on GitHub (https://github.com/fatimp/CorrelationFunctions.jl), the
-latter source also contains documentation and additional helpful resources such
-as tutorials.  We believe that a single powerful computational tool such as
+of thumb full correlation maps are faster than directional scans because
+calculation of correlation maps applies fast Fourier transform to the whole
+input array while, when calculating scans, FFT needs to be applied to each scan
+separately. Calculation on GPU shows performance increase when compared to CPU,
+as expected.  However, full maps require more RAM and, thus, are limited to
+available RAM resources. On the other hand, directional CFs are memory efficient
+and can be evaluated for huge datasets - this way they are the first candidates
+for structural data compression of feature extraction. The package itself is
+available through Julia package ecosystem and on GitHub
+(https://github.com/fatimp/CorrelationFunctions.jl), the latter source also
+contains documentation and additional helpful resources such as tutorials.  We
+believe that a single powerful computational tool such as
 \code{CorrelationFunctions.jl} will significantly facilitate the usage of

### 2023-09-06 paper-correlations.tex
Remove self-repeating passages.

@@
 measured wall times for all CPU and GPU implementations and as a rule of thumb
-full correlation maps on GPU are faster than directional scans using CPU due to
-the usage of fast Fourier transform. However, full maps require more RAM and,
-thus, are limited to available GPU RAM resources. On the other hand, directional
-CFs are memory efficient and can be evaluated for huge datasets - this way they
-are the first candidates for structural data compression of feature
-extraction. The package itself is available through Julia package ecosystem and
-on GitHub (https://github.com/fatimp/CorrelationFunctions.jl), the latter source
-also contains documentation and additional helpful resources such as tutorials.
-We believe that a single powerful computational tool such as
+full correlation maps on GPU are faster than other methods. However, full maps
+require more RAM and, thus, are limited to available RAM resources. On the other
+hand, directional CFs are memory efficient and can be evaluated for huge
+datasets -- this way they are the first candidates for structural data
+compression of feature extraction. The package itself is available through Julia
+package ecosystem and on GitHub
+(https://github.com/fatimp/CorrelationFunctions.jl), the latter source also
+contains documentation and additional helpful resources such as tutorials.  We
+believe that a single powerful computational tool such as
 \code{CorrelationFunctions.jl} will significantly facilitate the usage of
@@
 available RAM resources. On the other hand, directional CFs are memory efficient
-and can be evaluated for huge datasets - this way they are the first candidates
+and can be evaluated for huge datasets -- this way they are the first candidates
 for structural data compression of feature extraction. The package itself is

### 2023-09-07 paper-correlations.tex
ААААА

@@
 $F_{sv}$, pore-size $P$ and chord-length $p$ functions on both CPU and GPU
-architectures.  There possible, we presented two types of computations: full
-correlation map (correlations of each point with other pints on the image, that
+architectures.  Where possible, we presented two types of computations: full
+correlation map (correlations of each point with other points on the image, that
 also allows obtaining ensemble averaged CF) and directional correlation
@@
 \begin{enumerate}
-  \item to characterize the morphology and representativeness via correlation
+\item characterize the morphology and representativeness via correlation
   lengths \cite{vcapek2009stochastic,thovert2011grain,tensorPRE};
-  \item to perform stochastic reconstructions from experimentally measured CFs
+\item perform stochastic reconstructions from experimentally measured CFs
   or 2D to 3D reconstructions based on CFs that can be extracted from less
@@
     \begin{array}{ll}
-      -\sum\limits_{\substack{l \\ l \ne 0}} E_l & \quad k = 0 \\
+      -\sum\limits_{\substack{l \\ l \ne 0}} H_l & \quad k = 0 \\
       1 / \rho(k, 0) & \quad \text{otherwise}
@@
 robust $F_{ss}$ and $F_{sv}$ evaluation \cite{samarin2023robust}.  Note that
-function \code{lowfreq\_energy\_ratio} that computes $C_{0.5}$ criterion for any
+function \code{lowfreq\_energy\_ratio} that computes $C_{0.5}$ parameter for any
 input binary image is the part of \code{CorrelationFunctions.jl} package.
@@
 \code{Directional} (which utilize per-slice directional approach) are the
-slowest among other implementations, but require less memory. Depending on CF,
-our video card with 24 GBs of memory could handle a cube of $\sim 300^3$
-voxels, whilst the workstation with 512-1024 GBs of RAM can handle virtually any
-XCT-obtained image volume with any correlation length.
+slowest among other implementations, but require less memory.
 
@@
 presented two types of computations: full correlation map (correlations of each
-point with other pints on the image, that also allows obtaining ensemble
+point with other points on the image, that also allows obtaining ensemble
 averaged CF) and directional correlation functions (currently in major
@@
 available through Julia package ecosystem and on GitHub
-(https://github.com/fatimp/CorrelationFunctions.jl), the latter source also
+(\url{https://github.com/fatimp/CorrelationFunctions.jl}), the latter source also
 contains documentation and additional helpful resources such as tutorials.  We

### 2023-09-07 paper-correlations.tex
Remove stupid sentences
Forgot squares
Transform URL to a link

@@
 package ecosystem and on GitHub
-(https://github.com/fatimp/CorrelationFunctions.jl), the latter source also
-contains documentation and additional helpful resources such as tutorials.  We
-believe that a single powerful computational tool such as
+(\url{https://github.com/fatimp/CorrelationFunctions.jl}), the latter source
+also contains documentation and additional helpful resources such as tutorials.
+We believe that a single powerful computational tool such as
 \code{CorrelationFunctions.jl} will significantly facilitate the usage of
@@
 higher. $F_{sv}$ is a physical quantity inversely proportional to length and
-$F_{ss}$ is inversionaly proportional to surface area. Putting it simply,
-surface-void function measures length (2D case) or surface (3D case) of a part
-of the interface which lies in the void phase of porous medium shifted by vector
-$\bm{r}$.  Surface-surface function characterizes intersections of interfaces of
-porous medium and its shifted version.  As always, there are versions of these
-functions applicable to scalar argument for isotropic media.
+$F_{ss}$ is inversionaly proportional to surface area. As always, there are
+versions of these functions applicable to scalar argument for isotropic media.
 
@@
 \begin{equation}
-  S_2^{(i)}(r) = \frac{F^{-1} [|F [A^{(i)}](z)|] (r)}{N(r)} \label{eq:s2-ft}
+  S_2^{(i)}(r) = \frac{F^{-1} [|F [A^{(i)}](z)|^2] (r)}{N(r)} \label{eq:s2-ft}
 \end{equation}
@@
   \State $\hat{A}^{(phase)} \gets F[A^{(phase)}]$
-  \State $\hat{S}_2 \gets |\hat{A}^{(phase)}| / N$
+  \State $\hat{S}_2 \gets |\hat{A}^{(phase)}|^2 / N$
   \Comment $N$ is an array with numbers of trials
@@
   \State $\hat{A}_H \gets F[A_H]$
-  \State $\hat{F}_{ss} \gets |\hat{A}_H| / N$
+  \State $\hat{F}_{ss} \gets |\hat{A}_H|^2 / N$
   \State \textbf{return} $F^{-1} [\hat{F}_{ss}]$

### 2023-09-07 paper-correlations.tex
Fix a typo

@@
 After the verification of our computational approach based on analytical
-solution, in this section we apply \code{CorrelationFUnctions.jl} to compute CFs
+solution, in this section we apply \code{CorrelationFunctions.jl} to compute CFs
 for a variety of real 2D (SEM) and 3D (XCT) images. We also report benchmarks on

### 2023-09-07 paper-correlations.tex
Forgot to increment l
Fix a typo

@@
 work correctly. Therefore, the algorithms for surface functions require input
-images to be with an apropriate resolution. A criterion for goodness can be expressed with
+images to have apropriate resolution. A criterion for goodness can be expressed with
 $C_{\alpha}$ parameter. Let $\alpha \in [0, 1]$ and $f(x)$ be
@@
           \If{$slice[i] = slice[j \mod len] \ne 0$}
-            \Comment $0$ is a label for background (phase not equal to $phase$).
+            \Comment $0$ is a label for background.
             \State $dst \gets |(j \mod len) - i|$
@@
         \EndIf
+        \State $l \gets l+1$
       \EndFor
@@
 Another function built on top of distance transform is the pore size function
-$P(r)$. Reckon that pore size function is a probability distribution
+$P(r)$. Recall that pore size function is a probability distribution
 function. In practice, it is conveniently represented as a histogram of pore sizes

### 2023-09-07 paper-correlations.tex
F_{ss} is NOT a probability

@@
 into the same phase. Other types include the probability of a whole line segment
-to fall into the phase ($L_2$ function) or to lie on the interface between
-phases ($F_{ss}$ function), and mainly originated from aforementioned bounds on
+to fall into the phase ($L_2$ function) or ``pointing'' with its ends to the
+same cluster ($C_2$ function) and mainly originate from aforementioned bounds on
 physical properties such as permeability and elasticity. The general idea of

### 2023-09-07 paper-correlations.tex
More minor fixes

--- 2023-09-07 paper-correlations.tex
@@
 $F_{sv}$, pore-size $P$ and chord-length $p$ functions on both CPU and GPU
-architectures.  Where possible, we presented two types of computations: full
-correlation map (correlations of each point with other points on the image, that
+architectures.  W\here possible, we presented two types of computations: full
+correlation map (correlations of each point with other pints on the image, that
 also allows obtaining ensemble averaged CF) and directional correlation
@@
 package ecosystem and on GitHub
-(\url{https://github.com/fatimp/CorrelationFunctions.jl}), the latter source
-also contains documentation and additional helpful resources such as tutorials.
-We believe that a single powerful computational tool such as
+(https://github.com/fatimp/CorrelationFunctions.jl), the latter source also
+contains documentation and additional helpful resources such as tutorials.  We
+believe that a single powerful computational tool such as
 \code{CorrelationFunctions.jl} will significantly facilitate the usage of
@@
 \begin{enumerate}
-\item characterize the morphology and representativeness via correlation
+  \item to characterize the morphology and representativeness via correlation
     lengths \cite{vcapek2009stochastic,thovert2011grain,tensorPRE};
-\item perform stochastic reconstructions from experimentally measured CFs
+  \item to perform stochastic reconstructions from experimentally measured CFs
     or 2D to 3D reconstructions based on CFs that can be extracted from less
@@
 higher. $F_{sv}$ is a physical quantity inversely proportional to length and
-$F_{ss}$ is inversionaly proportional to surface area. As always, there are
-versions of these functions applicable to scalar argument for isotropic media.
+$F_{ss}$ is inversionaly proportional to surface area. Putting it simply,
+surface-void function measures length (2D case) or surface (3D case) of a part
+of the interface which lies in the void phase of porous medium shifted by vector
+$\bm{r}$.  Surface-surface function characterizes intersections of interfaces of
+porous medium and its shifted version.  As always, there are versions of these
+functions applicable to scalar argument for isotropic media.
 
@@
 \begin{equation}
-  S_2^{(i)}(r) = \frac{F^{-1} [|F [A^{(i)}](z)|^2] (r)}{N(r)} \label{eq:s2-ft}
+  S_2^{(i)}(r) = \frac{F^{-1} [|F [A^{(i)}](z)|] (r)}{N(r)} \label{eq:s2-ft}
 \end{equation}
@@
   \State $\hat{A}^{(phase)} \gets F[A^{(phase)}]$
-  \State $\hat{S}_2 \gets |\hat{A}^{(phase)}|^2 / N$
+  \State $\hat{S}_2 \gets |\hat{A}^{(phase)}| / N$
   \Comment $N$ is an array with numbers of trials
@@
   \State $\hat{A}_H \gets F[A_H]$
-  \State $\hat{F}_{ss} \gets |\hat{A}_H|^2 / N$
+  \State $\hat{F}_{ss} \gets |\hat{A}_H| / N$
   \State \textbf{return} $F^{-1} [\hat{F}_{ss}]$
@@
 After the verification of our computational approach based on analytical
-solution, in this section we apply \code{CorrelationFunctions.jl} to compute CFs
+solution, in this section we apply \code{CorrelationFUnctions.jl} to compute CFs
 for a variety of real 2D (SEM) and 3D (XCT) images. We also report benchmarks on
@@
 \code{Directional} (which utilize per-slice directional approach) are the
-slowest among other implementations, but require less memory.
+slowest among other implementations, but require less memory. Depending on CF,
+our video card with 24 GBs of memory could handle a cube of $\sim 300^3$
+voxels, whilst the workstation with 512-1024 GBs of RAM can handle virtually any
+XCT-obtained image volume with any correlation length.
 

### 2023-09-07 paper-correlations.tex
Remove dubious sentences
Change caption to the figure with line segments

--- 2023-09-07 paper-correlations.tex
@@
     functions are presented according to the legend on the right
-    side). Computations are results of individual events (producing either 0 or
-    1) ensemble averaged over the image, direction or represented as full
-    correlation map.}
+    side). Computations take into account all possible configurations of a line
+    segment (or a N-dimensional ball for pore size function) which either make a
+    contribution to the CF (conventionally shown as ``CF = 1'') or do not make a
+    contribution (``CF = 0'').}
   \label{fig:functions}

### 2023-09-15 paper-correlations.tex
Improvements from Alexey

@@
 \newcommand{\code}[1]{\colorbox{light-gray}{\texttt{#1}}}
-% When cleveref fails to do its job
-\newcommand{\apref}[1]{Appendix \ref{#1}}
 
@@
 Correlation functions are becoming one of the major tools for quantification of
-structural information that is usually represented as material's 2D or 3D image.
-In this paper we introduce \code{CorrelationFunctions.jl} open-source package
-developed in Julia and capable of computing all classical correlation functions
-based on imaging input data. Images include both binary and multi-phase
-representations.  Our code is capable of evaluating two-point probability $S_2$,
-cluster $C_2$, lineal-path $L_2$, surface-surface $F_{ss}$, surface-void
-$F_{sv}$, pore-size $P$ and chord-length $p$ functions on both CPU and GPU
+structural information that is usually represented as 2D or 3D image of porous
+material.  In this paper we introduce \code{CorrelationFunctions.jl} open-source
+package developed in Julia and capable of computing all classical correlation
+functions based on imaging input data. Images include both binary and
+multi-phase representations.  Our code is capable of evaluating two-point
+probability $S_2$, phase cross-correlation $\rho_{ij}$, cluster $C_2$,
+lineal-path $L_2$, surface-surface $F_{ss}$, surface-void $F_{sv}$, pore-size
+$P$ and chord-length $p$ distribution functions on both CPU and GPU
 architectures.  Where possible, we presented two types of computations: full
@@
 automatic tests against analytical solutions that are described in the paper. We
-measured wall times for all CPU and GPU implementations and as a rule of thumb
-full correlation maps on GPU are faster than other methods. However, full maps
-require more RAM and, thus, are limited to available RAM resources. On the other
-hand, directional CFs are memory efficient and can be evaluated for huge
+measured execution times for all CPU and GPU implementations and as a rule of
+thumb full correlation maps on GPU are faster than other methods. However, full
+maps require more RAM and, thus, are limited to available RAM resources. On the
+other hand, directional CFs are memory efficient and can be evaluated for huge
 datasets -- this way they are the first candidates for structural data
@@
 We believe that a single powerful computational tool such as
-\code{CorrelationFunctions.jl} will significantly facilitate the usage of
-correlation functions in numerous areas of structural description and research,
-as well as in machine learning applications. We also present some example as
-applied to ceramic, soil composite and oil-bearing rock samples based on their
-3D X-ray tomography and 2D scanning electron microscope images. Finally, we
-conclude our paper with discussion of possible ways to further improve presented
-computational framework.
+\code{CorrelationFunctions.jl} presented in this paper will significantly
+facilitate the usage of correlation functions in numerous areas of structural
+description and research of porous materials, as well as in machine learning
+applications. We also present some example as applied to ceramic, soil composite
+and oil-bearing rock samples based on their 3D X-ray tomography and 2D scanning
+electron microscope images. Finally, we conclude our paper with discussion of
+possible ways to further improve presented computational framework.
 \end{abstract}
@@
 \label{sec:background}
-Materials are ubiquitous both in nature and in industrial human activities, and
-their physical properties are interconnected to structure
+Heterogeneous materials are ubiquitous both in nature and in industrial human
+activities, and their physical properties are interconnected to structure
 \cite{Torquato_book,Sahimi_book}. The information about the structure usually
@@
 are available for some functions, but they lack general API and are usually
-implemented in proprietary interpreted languages such as Matlab. Due to a recent
+implemented in proprietary interpreted languages (e.g. Matlab). Due to a recent
 leap forward in GPU-based computations, some papers describe computations on
@@
 discuss the second method to calculate correlation functions which is called the
-scan approach. In \cref{sec:verification} we verify the all computations based on
-known analytical solutions. \cref{sec:efficiency} deals with computational
-efficiency of our code, we compare computational times for 2D and 3D images of
-different sizes for scanning and map methods as evaluated using either CPU or
-GPU. In \cref{sec:examples} some application examples are provided, including
-CFs evaluation for multi-phase materials. Finally, \cref{sec:summary} summarizes
-all results and outlines possible future improvements.
+scan approach. In \cref{sec:verification} we verify our algorithms based on
+known analytical solutions. In \cref{sec:examples} some application examples are
+provided, including CFs evaluation for multi-phase materials. Section
+\ref{sec:efficiency} deals with computational efficiency of our code, we compare
+computational times for 2D and 3D images of different sizes for scanning and map
+methods as evaluated using either CPU or GPU.  Finally, sections
+\ref{sec:outlook} and \ref{sec:summary} summarize all results and outline
+possible future improvements.
 
@@
 \label{sec:math}
-In this section we shall provide major properties of correlation functions
-supported by our package; the full list of functions is 
-(see \cref{fig:functions} for graphical explanation in addition to definitions below):
+In this section we shall provide major properties and definitions of correlation
+functions supported by our package; the full list of functions is (see
+\cref{fig:functions} for graphical explanation in addition to definitions
+below):
 \begin{itemize}
@@
 
-Another basic correlation function is a lineal path function. It provides some
-non-trivial information (albeit usually not complete \cite{vcapek2011transport})
-about the connectedness of the phase and is defined for homogenous media as:
+Another basic correlation function is a lineal path function $L_2$. It provides
+some non-trivial information (albeit usually not complete
+\cite{vcapek2011transport}) about the connectedness of the phase and is defined
+for homogenous media as:
 \begin{definition}
@@
 The next two functions are called surface-surface ($F_{ss}$) and surface-void
-($F_{sv}$) functions and describe an interphase between phases. We skip strict verbal
-definitions and first introduce an interface indicator function instead:
+($F_{sv}$) correlation functions and describe an interphase between phases. We
+skip strict verbal definitions and first introduce an interface indicator
+function instead:
 \begin{equation*}
@@
 
-Pore size function $P(\delta)$ is a probability density function defined as
-follows:
+Pore size function $P(r)$ is a probability density function defined as follows:
 \begin{definition}
-  $P(\delta)d\delta$ = Probability that a randomly chosen point in a set of points
-  belonging to the void phase lies at a distance between $\delta$ and $\delta + d\delta$
+  $P(r)dr$ equals to the probability that a randomly chosen point in a set of
+  points belonging to the void phase lies at a distance between $r$ and $r + dr$
   from the nearest point on the pore-solid interface.
@@
 \begin{definition}
-$p^{(i)}(r)dz$ = Probability of finding a chord of length between $r$ and $r+dr$
-in phase $i$. Chord is a line segment which lies entirely in the same phase and
-touches the interface with its ends.
+  $p^{(i)}(r)dr$ equals to the probability of finding a chord of length between
+  $r$ and $r+dr$ in phase $i$. Chord is a line segment which lies entirely in
+  the same phase and touches the interface with its ends.
 \end{definition}
 
-More detailed information on all classical CFs can be found in \cite{Torquato_book}.
+More detailed information on all classical CFs can be found in
+\cite{Torquato_book}.
 
@@
 where $A^{(i)} \xleftarrow{I^{(i)}} A$ is a binary array obtained by element-wise
-application of interface indicator $I^{(i)}$ to an input $A$, $F$ is a discrete
+application of indicator function $I^{(i)}$ to an input $A$, $F$ is a discrete
 Fourier transform (DFT) operator and $N(r)$ is a total number of trials (vectors
@@
 procedures.  Firstly, we apply an indicator function to an input $A$:
-$A^{(i)} \xleftarrow{I^{(i)}} A$. When we label connected components in
-$A^{(i)}$ using a function that is a part of Julia \code{ImageMorphology.jl}
-library.  Labeling algorithm must take into account if the function is
-calculated with periodic boundary conditions \cite{evstigneev2023}. For periodic
-boundary conditions we implemented our own solution as part of the package, as
-it is absent in the public domain. Then $C_2$ function is a sum of $S_2$
-functions calculated for all clusters separately. Algorithmic complexity of this
-implementation is $O(MC\log M)$ where $M$ is the number of elements in the input
-and $C$ is the number of clusters. The algorithm is then written as:
+$A^{(i)} \xleftarrow{I^{(i)}} A$. Then we label clusters in $A^{(i)}$ using a
+function that is a part of Julia \code{ImageMorphology.jl} library.  Labeling
+algorithm must take into account if the function is calculated with periodic
+boundary conditions \cite{evstigneev2023}. For periodic boundary conditions we
+implemented our own solution as part of the package, as it is absent in the
+public domain. Then $C_2$ function is a sum of $S_2$ functions calculated for
+all clusters separately. Algorithmic complexity of this implementation is
+$O(MC\log M)$ where $M$ is the number of elements in the input and $C$ is the
+number of clusters. The algorithm is then written as:
 \begin{algorithmic}[1]
@@
 or cross-correlation of the edge and the void phase. The edge is extracted by
-convolving an input with a short high-pass filter $H$. It has a width $7$ and
-all its coefficients with exception of the central coefficient are inversely
-proportional to distance from the center:
+convolving an input with a short high-pass filter $H$. It has a width of 7
+pixels/voxels and all its coefficients with exception of the central coefficient
+are inversely proportional to distance from the center:
 \begin{equation}
@@
 are perfectly suited for execution on GPUs and provide very fast computations
-(see wall times below).
+(see execution times below).
 
@@
 \begin{algorithmic}[1]
-  \Procedure{l2}{$A, phase, periodic$}
+  \Procedure{$L_2$}{$A, phase, periodic$}
     \State $len \gets length(A)$
@@
 \begin{algorithmic}[1]
-  \Procedure{c2}{$A, phase, periodic$}
+  \Procedure{$C_2$}{$A, phase, periodic$}
     \State $A' \gets I^{(phase)}(A)$
@@
 \end{equation}
-There are many algorithms for distance transform, including algorithms performed
-in linear time \cite{DT}.In \code{chord\_length} function we firstly apply
-distance transform to an input to find the interface and then accumulate chord
-length in per-slice manner. Finally, chord lengths can be binned to a histogram.
+where $\rho$ is the Euclidean distance between two points. There are many
+algorithms for distance transform, including algorithms performed in linear time
+\cite{DT}.In \code{chord\_length} function we firstly apply distance transform
+to an input to find the interface and then accumulate chord length in per-slice
+manner. Finally, chord lengths can be binned to a histogram.
 \begin{algorithmic}[1]
@@
 \section{Discussion and outlook}
+\label{sec:outlook}
 In the light of the end of the previous section it is important to clarify that
@@
 based on 2D and 3D input images. Our code is capable of evaluating two-point
-probability, cluster, lineal-path, surface-surface, surface-void, pore-size and
-chord-length functions on both CPU and GPU architectures. There possible, we
-presented two types of computations: full correlation map (correlations of each
-point with other points on the image, that also allows obtaining ensemble
-averaged CF) and directional correlation functions (currently in major
-orthogonal and diagonal directions). Such an implementation allowed for the
-first time to assemble a completely free solution to evaluate correlation
-functions under any operating system with well documented API. Our package
-includes automatic tests against analytical solutions that are described in this
-paper. We measured wall times for all CPU and GPU implementations and as a rule
-of thumb full correlation maps are faster than directional scans because
-calculation of correlation maps applies fast Fourier transform to the whole
-input array while, when calculating scans, FFT needs to be applied to each scan
-separately. Calculation on GPU shows performance increase when compared to CPU,
-as expected.  However, full maps require more RAM and, thus, are limited to
-available RAM resources. On the other hand, directional CFs are memory efficient
-and can be evaluated for huge datasets -- this way they are the first candidates
-for structural data compression of feature extraction. The package itself is
-available through Julia package ecosystem and on GitHub
-(\url{https://github.com/fatimp/CorrelationFunctions.jl}), the latter source also
-contains documentation and additional helpful resources such as tutorials.  We
-believe that a single powerful computational tool such as
+probability, cross-correlation, cluster, lineal-path, surface-surface,
+surface-void, pore-size and chord-length functions on both CPU and GPU
+architectures. There possible, we presented two types of computations: full
+correlation map (correlations of each point with other points on the image, that
+also allows obtaining ensemble averaged CF) and directional correlation
+functions (currently in major orthogonal and diagonal directions). Such an
+implementation allowed for the first time to assemble a completely free solution
+to evaluate correlation functions under any operating system with well
+documented API. Our package includes automatic tests against analytical
+solutions that are described in this paper. We measured execution times for all
+CPU and GPU implementations and as a rule of thumb full correlation maps are
+faster than directional scans because calculation of correlation maps applies
+fast Fourier transform to the whole input array while, when calculating scans,
+FFT needs to be applied to each scan separately. Calculation on GPU shows
+performance increase when compared to CPU, as expected.  However, full maps
+require more RAM and, thus, are limited to available RAM resources. On the other
+hand, directional CFs are memory efficient and can be evaluated for huge
+datasets -- this way they are the first candidates for structural data
+compression of feature extraction. The package itself is available through Julia
+package ecosystem and on GitHub
+(\url{https://github.com/fatimp/CorrelationFunctions.jl}), the latter source
+also contains documentation and additional helpful resources such as tutorials.
+We believe that a single powerful computational tool such as
 \code{CorrelationFunctions.jl} will significantly facilitate the usage of

### 2023-09-15 paper-correlations.tex
No connected components!

@@
 $A^{(i)} \xleftarrow{I^{(i)}} A$. Then we label clusters in $A^{(i)}$ using a
-function that is a part of Julia \code{ImageMorphology.jl} library.  Labeling
-algorithm must take into account if the function is calculated with periodic
-boundary conditions \cite{evstigneev2023}. For periodic boundary conditions we
-implemented our own solution as part of the package, as it is absent in the
-public domain. Then $C_2$ function is a sum of $S_2$ functions calculated for
-all clusters separately. Algorithmic complexity of this implementation is
-$O(MC\log M)$ where $M$ is the number of elements in the input and $C$ is the
-number of clusters. The algorithm is then written as:
+function \code{label\_components} which is a part of Julia
+\code{ImageMorphology.jl} library.  Labeling algorithm must take into account if
+the function is calculated with periodic boundary conditions
+\cite{evstigneev2023}. For periodic boundary conditions we implemented our own
+solution as part of the package, as it is absent in the public domain. Then
+$C_2$ function is a sum of $S_2$ functions calculated for all clusters
+separately. Algorithmic complexity of this implementation is $O(MC\log M)$ where
+$M$ is the number of elements in the input and $C$ is the number of
+clusters. The algorithm is then written as:
 \begin{algorithmic}[1]
@@
   \State $A^{(phase)} \gets I^{(phase)} (A)$
-  \State $CC \gets label\_components(A^{(phase)}, periodic)$
-  \State $N \gets maximum(CC)$ \Comment Number of connected components
-  \State \textbf{return} $\sum\limits_{n=1}^N S_2(CC, n, periodic)$
+  \State $Labels \gets label\_components(A^{(phase)}, periodic)$
+  \State $N \gets maximum(Labels)$ \Comment Number of clusters
+  \State \textbf{return} $\sum\limits_{n=1}^N S_2(Labels, n, periodic)$
   \EndProcedure
@@
 Majority of described algorithms contain parallelizable operations such as fast
-Fourier transform, connected components labeling and image filtering, hence they
-are perfectly suited for execution on GPUs and provide very fast computations
-(see execution times below).
+Fourier transform, cluster labeling and image filtering, hence they are
+perfectly suited for execution on GPUs and provide very fast computations (see
+execution times below).
 
@@
 preprocessing stages before cutting the input in slices, e.g., image filtering
-for edge detection or connected components labeling performed on the whole
-array, not on slices.
+for edge detection or cluster labeling performed on the whole array, not on
+slices.
 
@@
 CPU and GPU, so we provide execution times for both. The cluster function uses
-an algorithm for closest component labeling which has CPU-only implementation
-(thus, leaving a room for future improvements). Directional computations are
-performed exclusively on CPUs.
+an algorithm for cluster labeling which has CPU-only implementation (thus,
+leaving a room for future improvements). Directional computations are performed
+exclusively on CPUs.
 
@@
   resources;
-\item implementing GPU-based clustering (cluster labeling) and distance-map
+\item implementing GPU-based clustering (cluster labeling) and distance
   transform to further speed up computations for $C_2$, chord-length and

### 2023-09-20 paper-correlations.tex
Cleveref works bad with appendices
Prepare for submission

@@
 
-\bibliographystyle{elsarticle-num}
-\journal{Computational Material Science}
+\journal{Computer Physics Communications}
 
 \begin{document}
+
+\begin{frontmatter}
+  \title{Evaluation of classical correlation functions from 2/3D images on CPU and
+    GPU architectures: introducing CorrelationFunctions.jl}
 
@@
   \author[Smith,MIT]{Aleksei~Samarin}
-\author[Smith]{Marina ~V. Karsanina}
-\author[Aus]{Mathieu ~Gravey}
+  \author[Smith]{Marina~V.~Karsanina}
+  \author[Aus]{Mathieu~Gravey}
   \author[MIPT]{Aleksey~Khlyupin}
-\author[Smith]{Kirill ~M. Gerke}
-\ead{kg@ifz.ru}
+  \author[Smith]{Kirill~M.~Gerke\corref{boss}}
+  \cortext[boss]{Corresponding author.\\\textit{E-mail address:} kg@ifz.ru}
 
@@
 
-\title{Evaluation of classical correlation functions from 2/3D images on CPU and
-  GPU architectures: introducing CorrelationFunctions.jl}
-
   \begin{abstract}
-Correlation functions are becoming one of the major tools for quantification of
-structural information that is usually represented as 2D or 3D image of porous
-material.  In this paper we introduce \code{CorrelationFunctions.jl} open-source
-package developed in Julia and capable of computing all classical correlation
-functions based on imaging input data. Images include both binary and
-multi-phase representations.  Our code is capable of evaluating two-point
-probability $S_2$, phase cross-correlation $\rho_{ij}$, cluster $C_2$,
-lineal-path $L_2$, surface-surface $F_{ss}$, surface-void $F_{sv}$, pore-size
-$P$ and chord-length $p$ distribution functions on both CPU and GPU
-architectures.  Where possible, we presented two types of computations: full
-correlation map (correlations of each point with other points on the image, that
-also allows obtaining ensemble averaged CF) and directional correlation
-functions (currently in major orthogonal and diagonal directions).  Such an
-implementation allowed for the first time to assemble a completely free solution
-to evaluate correlation functions under any operating system with well
-documented application programming interface (API). Our package includes
-automatic tests against analytical solutions that are described in the paper. We
-measured execution times for all CPU and GPU implementations and as a rule of
-thumb full correlation maps on GPU are faster than other methods. However, full
-maps require more RAM and, thus, are limited to available RAM resources. On the
-other hand, directional CFs are memory efficient and can be evaluated for huge
-datasets -- this way they are the first candidates for structural data
-compression of feature extraction. The package itself is available through Julia
-package ecosystem and on GitHub
-(\url{https://github.com/fatimp/CorrelationFunctions.jl}), the latter source
-also contains documentation and additional helpful resources such as tutorials.
-We believe that a single powerful computational tool such as
-\code{CorrelationFunctions.jl} presented in this paper will significantly
-facilitate the usage of correlation functions in numerous areas of structural
-description and research of porous materials, as well as in machine learning
-applications. We also present some example as applied to ceramic, soil composite
-and oil-bearing rock samples based on their 3D X-ray tomography and 2D scanning
-electron microscope images. Finally, we conclude our paper with discussion of
-possible ways to further improve presented computational framework.
+    Correlation functions are becoming one of the major tools for quantification
+    of structural information that is usually represented as 2D or 3D images of
+    porous material.  In this paper we introduce \code{CorrelationFunctions.jl}
+    open-source package developed in Julia and capable of computing all
+    classical correlation functions based on imaging input data. Images include
+    both binary and multi-phase representations.  Our code is capable of
+    evaluating two-point probability $S_2$, phase cross-correlation $\rho_{ij}$,
+    cluster $C_2$, lineal-path $L_2$, surface-surface $F_{ss}$, surface-void
+    $F_{sv}$, pore-size $P$ and chord-length $p$ distribution functions on both
+    CPU and GPU architectures.  Where possible, we presented two types of
+    computations: full correlation map (correlations of each point with other
+    points on the image, that also allows obtaining ensemble averaged CF) and
+    directional correlation functions (currently in major orthogonal and
+    diagonal directions).  Such an implementation allowed for the first time to
+    assemble a completely free solution to evaluate correlation functions under
+    any operating system with well documented application programming interface
+    (API). Our package includes automatic tests against analytical solutions
+    that are described in the paper. We measured execution times for all CPU and
+    GPU implementations and as a rule of thumb full correlation maps on GPU are
+    faster than other methods. However, full maps require more RAM and, thus,
+    are limited to available RAM resources. On the other hand, directional CFs
+    are memory efficient and can be evaluated for huge datasets -- this way they
+    are the first candidates for structural data compression of feature
+    extraction. The package itself is available through Julia package ecosystem
+    and on GitHub, the latter source also contains documentation and additional
+    helpful resources such as tutorials.  We believe that a single powerful
+    computational tool such as \code{CorrelationFunctions.jl} presented in this
+    paper will significantly facilitate the usage of correlation functions in
+    numerous areas of structural description and research of porous materials,
+    as well as in machine learning applications. We also present some example as
+    applied to ceramic, soil composite and oil-bearing rock samples based on
+    their 3D X-ray tomography and 2D scanning electron microscope
+    images. Finally, we conclude our paper with discussion of possible ways to
+    further improve presented computational framework.
 \end{abstract}
 
-\maketitle
+  \begin{keyword}
+    3D images; correlation functions; image analysis
+  \end{keyword}
+\end{frontmatter}
+
+{\bf PROGRAM SUMMARY} \\
+\begin{small}
+\noindent
+{\em Program Title:} CorrelationFunctions.jl \\
+{\em CPC Library link to program files:} (to be added by Technical Editor) \\
+{\em Developer's repository link:}
+\url{https://github.com/fatimp/CorrelationFunctions.jl} \\
+{\em Code Ocean capsule:} (to be added by Technical Editor)\\
+{\em Licensing provisions:} MIT \\
+{\em Programming language:} Julia \\
+{\em Supplementary material:} \\
+{\em Nature of problem:} Correlation functions are invaluable universal
+statistical descriptors of structure of porous media used in many scientific
+field such as astronomy, soil physics, hydrology and biology. We propose an open
+source and cross-platform solution for computation of vast majority of
+correlation functions for both 2D and 3D images of porous material. \\
+{\em Solution method:} Our package computes correlation functions using fast
+Fourier transform using such preprocessing steps as cluster labeling or edge
+detection if needed. Almost all of proposed algorithms can be executed on both
+CPU and GPU which results in high execution speed on modern hardware. Two
+approaches to evaluation of correlation functions are proposed: computation of
+correlation maps and computation along predefined directions. These two
+approaches can be thought of as an execution time - memory trade-off. \\
+\end{small}
 
@@
 non-periodic mode $N(r)$ is calculated as described in
-\cref{sec:number-of-trials}. The following algorithm summarizes all the above:
+\ref{sec:number-of-trials}. The following algorithm summarizes all the above:
 \begin{algorithmic}[1]
@@
     \State \textbf{return} $success$ divided by number of trials
-    (see \cref{sec:number-of-trials})
+    (see \ref{sec:number-of-trials})
   \EndProcedure
@@
 
+\bibliographystyle{elsarticle-num}
 \bibliography{apssamp}

### 2023-09-22 paper-correlations.tex
changes in programm description

@@
 {\em Programming language:} Julia \\
-{\em Supplementary material:} \\
+{\em Supplementary material:} Numerous Jupiter notebooks with examples are available on the GitHub page\\
 {\em Nature of problem:} Correlation functions are invaluable universal
-statistical descriptors of structure of porous media used in many scientific
-field such as astronomy, soil physics, hydrology and biology. We propose an open
-source and cross-platform solution for computation of vast majority of
-correlation functions for both 2D and 3D images of porous material. \\
-{\em Solution method:} Our package computes correlation functions using fast
-Fourier transform using such preprocessing steps as cluster labeling or edge
-detection if needed. Almost all of proposed algorithms can be executed on both
-CPU and GPU which results in high execution speed on modern hardware. Two
-approaches to evaluation of correlation functions are proposed: computation of
+statistical descriptors of structures used in numerous scientific
+fields such as astronomy, material science, rock and soil physics, hydrology and biology, to name just a handful of examples. While computational approaches
+are available in the literature for some functions, they are fragmented and are usually implemented in proprietary
+interpreted languages for CPU architecture alone. \\
+{\em Solution method:} We contribute an open
+source and cross-platform solution with well documented API for computation of all classical
+correlation functions from both 2D and 3D images on CPU and GPU architectures. The package computes correlation functions using two approaches: : computation of
 correlation maps and computation along predefined directions. These two
-approaches can be thought of as an execution time - memory trade-off. \\
+approaches can be thought of as an execution time - memory trade-off, but the choice may also depend on the application.
+The computations are based on fast Fourier transform with preprocessing steps as cluster labeling or edge
+detection, and linear scan approach to evaluate correlation functions along predefined directions. Where justified, the algorithms can be executed on both
+CPU and GPU which results in high execution speed on modern hardware. \\
 \end{small}

### 2023-09-22 paper-correlations.tex
minor novelty

@@
 The aim of this paper is to establish a general open-source solution allowing to
-compute all classical correlation functions. This solution should be well
+compute all classical correlation functions. This solution should incorporate novel methods to compute CFs and be well
 documented with all computational algorithms explained, it should also leverage

### 2024-01-30 verification/calc-cf-2d.jl
Update scripts

@@ -64,11 +64,9 @@ const fns = [
     ("l2", l2_theory,
      img -> Directional.l2(img, false; periodic = true)),
     ("ss", ss_theory,
-     img -> Directional.surfsurf(img, false; periodic = true,
-                                 edgemode = Utilities.EdgesFilterReflect())),
+     img -> Directional.surf2(img, false; periodic = true)),
     ("sv", sv_theory,
-     img -> Directional.surfvoid(img, false; periodic = true,
-                                 edgemode = Utilities.EdgesFilterReflect()))
+     img -> Directional.surfvoid(img, false; periodic = true))
 ]
 
 const hists = [

### 2024-01-30 verification/calc-cf-3d.jl

@@ -66,11 +66,9 @@ const fns = [
     ("l2", l2_theory,
      img -> Directional.l2(img, false; periodic = true)),
     ("ss", ss_theory,
-     img -> Directional.surfsurf(img, false; periodic = true,
-                                 edgemode = Utilities.EdgesFilterReflect())),
+     img -> Directional.surf2(img, false; periodic = true)),
     ("sv", sv_theory,
-     img -> Directional.surfvoid(img, false; periodic = true,
-                                 edgemode = Utilities.EdgesFilterReflect()))
+     img -> Directional.surfvoid(img, false; periodic = true))
 ]
 
 const hists = [

### 2024-01-30 paper-correlations.tex
Regroup images

@@
   \subfigure[Lineal-path correlation function]{
-    \includegraphics[width=0.3\linewidth]{images/l2.png}
+    \includegraphics[width=0.45\linewidth]{images/l2.png}
     \label{fig:l2}}
@@
   \subfigure[Two-point correlation function]{
-    \includegraphics[width=0.3\linewidth]{images/s2.png}
+    \includegraphics[width=0.45\linewidth]{images/s2.png}
     \label{fig:s2}}
-  \hfill
+  \vskip\baselineskip
   \subfigure[Surface-surface correlation function]{
-    \includegraphics[width=0.3\linewidth]{images/ss.png}
+    \includegraphics[width=0.45\linewidth]{images/ss.png}
     \label{fig:ss}}
+  \hfill
+  \subfigure[Surface-void correlation function]{
+    \includegraphics[width=0.45\linewidth]{images/sv.png}
+    \label{fig:sv}}
   \vskip\baselineskip
-  \subfigure[Surface-void correlation function]{
-    \includegraphics[width=0.3\linewidth]{images/sv.png}
-    \label{fig:sv}}
-  \hfill
   \subfigure[Pore size correlation function]{
-    \includegraphics[width=0.3\linewidth]{images/ps.png}
+    \includegraphics[width=0.45\linewidth]{images/ps.png}
     \label{fig:ps}}
@@
   \subfigure[Chord length correlation function]{
-    \includegraphics[width=0.3\linewidth]{images/cl.png}
+    \includegraphics[width=0.45\linewidth]{images/cl.png}
     \label{fig:cl}}
@@
 
-At first, we compare the three ceramic images which have somewhat different
-genesis depending on the mixture ratio of powder and binder used for firing the
-material \cite{ceramics}. As observed from \cref{fig:real-xct}, the structure of
-all three samples is visually very similar. The lineal path function supports
-this observation. The $S_2$ functions are also quite similar except for Sample 2
-having higher porosity that results in elevated curve (the tail for two-point
-probability as expected fluctuates around porosity squared). Notably, $S_2$ and
-$C_2$ are almost identical -- this indicates that pore phase represents a single
-large cluster. Recall that for $S_2$, $C_2$ and $L_2$ functions the value at
-correlation length of 0 is the porosity value. Surface functions, on the other
-hand, feel significant difference between samples in how pore-solid interface is
-organized. This is further evidenced on pore-size and chord-length graphs, with
-Ceramic 2 sample with the highest porosity having larger amount of large
-pores. Both $P$ and $p$ show very similar behavior, but for different
-correlation lengths; such behavior is attributed to quite regular pores shapes
-in all ceramics samples -- this is evident from much larger differences between
-pore-size and chord-length for SEM images considered next.
+At first, we compare the three ceramic images (\cref{fig:real-data}, at the top)
+which have somewhat different genesis depending on the mixture ratio of powder
+and binder used for firing the material \cite{ceramics}. As observed from
+\cref{fig:real-xct-cfs}, the structure of all three samples is visually very
+similar. The lineal path function supports this observation. The $S_2$ functions
+are also quite similar except for Sample 2 having higher porosity that results
+in elevated curve (the tail for two-point probability as expected fluctuates
+around porosity squared). Notably, $S_2$ and $C_2$ are almost identical -- this
+indicates that pore phase represents a single large cluster. Recall that for
+$S_2$, $C_2$ and $L_2$ functions the value at correlation length of 0 is the
+porosity value. Surface functions, on the other hand, feel significant
+difference between samples in how pore-solid interface is organized. This is
+further evidenced on pore-size and chord-length graphs, with Ceramic 2 sample
+with the highest porosity having larger amount of large pores. Both $P$ and $p$
+show very similar behavior, but for different correlation lengths; such behavior
+is attributed to quite regular pores shapes in all ceramics samples -- this is
+evident from much larger differences between pore-size and chord-length for SEM
+images considered next.
 
@@
   \vskip\baselineskip
-  \includegraphics[width=0.32\linewidth]{samples/s2-xct.png}
-  \includegraphics[width=0.32\linewidth]{samples/c2-xct.png}
-  \includegraphics[width=0.32\linewidth]{samples/l2-xct.png}
+  \subfigure[Sandstone 1]{
+    \includegraphics[width=0.3\linewidth, frame]{samples/sandstone1.png}}
+  \hfill
+  \subfigure[Sandstone 2]{
+    \includegraphics[width=0.3\linewidth, frame]{samples/sandstone2.png}}
+  \hfill
+  \subfigure[Carbonate 1]{
+    \includegraphics[width=0.3\linewidth, frame]{samples/carbonate1.png}}
+  \caption[]{Visualization of XCT (top) and SEM (bottom) images used for
+    computation of correlation functions. Different clusters of the void phase
+    on SEM samples are shown in color.}
+  \label{fig:real-data}
+\end{figure*}
+\begin{figure*}[pt]
+  \centering
+  \includegraphics[width=0.45\linewidth]{samples/s2-xct.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{samples/c2-xct.png}
   \vskip\baselineskip
-  \includegraphics[width=0.32\linewidth]{samples/surf2-xct.png}
-  \includegraphics[width=0.32\linewidth]{samples/surfvoid-xct.png}
+  \includegraphics[width=0.45\linewidth]{samples/l2-xct.png}
   \vskip\baselineskip
-  \includegraphics[width=0.32\linewidth]{samples/pore-size-xct.png}
-  \includegraphics[width=0.32\linewidth]{samples/chord-length-xct.png}
-  \caption[]{Visualization of XCT images and plots of correlation functions for
-    these images.}
-  \label{fig:real-xct}
+  \includegraphics[width=0.45\linewidth]{samples/surf2-xct.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{samples/surfvoid-xct.png}
+  \vskip\baselineskip
+  \includegraphics[width=0.45\linewidth]{samples/pore-size-xct.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{samples/chord-length-xct.png}
+  \caption[]{Plots of correlation functions for XCT samples on
+    \cref{fig:real-data}.}
+  \label{fig:real-xct-cfs}
 \end{figure*}
 
-The \cref{fig:real-sem} presents three 2D images of sandstones and carbonate
-with computed correlation functions. In this example, unlike for quite isotropic
-ceramics, we evaluated CFs in the directional manner. The $S_2$ graph
-immediately provides us with porosity values. It also highlights severe
-anisotropy in sandstone SEM images. For 2D images numerous patches of pores are
-not connected to each other and, thus, $S_2$ and $C_2$ are very
-different. Cluster functions show how connectivity decays with length, also we
-can easily observe if given pore structure percolates in a given direction -
-none of the images percolates (we highlighted the clusters to make this
-statement easily verifiable with the naked eye). Note that $C_2$ and $L_2$ were
-computed with correlations lengths equal to image dimensions explore
-connectivity -- for other CFs this leads to noised curves due to smaller number
-of sampled points (for example, see correlation functions' graphs in
-\cite{Euras2012}).  Lineal paths are close for sandstones (with lower $L_2$
-values for Sandstone 1 where large pores are occluded with clays or grain
+The \cref{fig:real-data} (at the bottom) presents three 2D images of sandstones
+and carbonate with computed correlation functions at \cref{fig:real-sem-cfs}. In
+this example, unlike for quite isotropic ceramics, we evaluated CFs in the
+directional manner. The $S_2$ graph immediately provides us with porosity
+values. It also highlights severe anisotropy in sandstone SEM images. For 2D
+images numerous patches of pores are not connected to each other and, thus,
+$S_2$ and $C_2$ are very different. Cluster functions show how connectivity
+decays with length, also we can easily observe if given pore structure
+percolates in a given direction - none of the images percolates (we highlighted
+the clusters to make this statement easily verifiable with the naked eye). Note
+that $C_2$ and $L_2$ were computed with correlations lengths equal to image
+dimensions explore connectivity -- for other CFs this leads to noised curves due
+to smaller number of sampled points (for example, see correlation functions'
+graphs in \cite{Euras2012}).  Lineal paths are close for sandstones (with lower
+$L_2$ values for Sandstone 1 where large pores are occluded with clays or grain
 fragments), but for carbonate with much smaller apertures of pores it is way
@@
 informative. For very irregular pores on 2D SEM images, $P$ and $p$ functions
-look much less similar compared to the ceramics case on \cref{fig:real-xct}. For
-2D images it is also visually easy to analyze full CF maps, as presented on
-\cref{fig:real-sem-map} for Sandstone 1 sample. Full correlation maps show
-expanded version of directional functions -- asymmetry is immediately evidenced
-from $S_2$, $F_{ss}$ and $F_{sv}$ maps. Moreover, the map for $C_2$ shows higher
-connectivity in y-direction as compared to x-axis. The interpretation of full
-correlation maps is less straightforward, but anisotropy patterns in directions
-different from those presented in \cref{fig:directions} can be spotted.
-
+look much less similar compared to the ceramics case on
+\cref{fig:real-xct-cfs}. For 2D images it is also visually easy to analyze full
+CF maps, as presented on \cref{fig:real-sem-map} for Sandstone 1 sample. Full
+correlation maps show expanded version of directional functions -- asymmetry is
+immediately evidenced from $S_2$, $F_{ss}$ and $F_{sv}$ maps. Moreover, the map
+for $C_2$ shows higher connectivity in y-direction as compared to x-axis. The
+interpretation of full correlation maps is less straightforward, but anisotropy
+patterns in directions different from those presented in \cref{fig:directions}
+can be spotted.
 \begin{figure*}[pt]
   \centering
-  \subfigure[Sandstone 1]{
-    \includegraphics[width=0.3\linewidth, frame]{samples/sandstone1.png}}
-  \hfill
-  \subfigure[Sandstone 2]{
-    \includegraphics[width=0.3\linewidth, frame]{samples/sandstone2.png}}
-  \hfill
-  \subfigure[Carbonate 1]{
-    \includegraphics[width=0.3\linewidth, frame]{samples/carbonate1.png}}
+  \includegraphics[width=0.45\linewidth]{samples/s2-sem.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{samples/c2-sem.png}
   \vskip\baselineskip
-  \includegraphics[width=0.32\linewidth]{samples/s2-sem.png}
-  \includegraphics[width=0.32\linewidth]{samples/c2-sem.png}
-  \includegraphics[width=0.32\linewidth]{samples/l2-sem.png}
+  \includegraphics[width=0.45\linewidth]{samples/l2-sem.png}
   \vskip\baselineskip
-  \includegraphics[width=0.32\linewidth]{samples/surf2-sem.png}
-  \includegraphics[width=0.32\linewidth]{samples/surfvoid-sem.png}
+  \includegraphics[width=0.45\linewidth]{samples/surf2-sem.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{samples/surfvoid-sem.png}
   \vskip\baselineskip
-  \includegraphics[width=0.32\linewidth]{samples/pore-size-sem.png}
-  \includegraphics[width=0.32\linewidth]{samples/chord-length-sem.png}
-  \caption[]{SEM images and plots of correlation functions for these
-    images. Different clusters of the void phase are shown in color.}
-  \label{fig:real-sem}
+  \includegraphics[width=0.45\linewidth]{samples/pore-size-sem.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{samples/chord-length-sem.png}
+  \caption[]{Plots of correlation functions for SEM samples on
+    \cref{fig:real-data}}
+  \label{fig:real-sem-cfs}
 \end{figure*}

### 2024-01-30 verification/plot.py
Enlarge figure 4

@@ -18,7 +18,7 @@ plt.xlabel('Correlation length $r$')
 plt.ylabel('Two point function $S_2(r)$')
 plt.legend(['CorrelationFunctions.jl (2D)', 'Theory (2D)',
             'CorrelationFunctions.jl (3D)', 'Theory (3D)'])
-plt.savefig('s2.png')
+plt.savefig('s2.png', bbox_inches = 'tight')
 
 l2_2d = np.loadtxt('l2-2d.dat')
 l2_3d = np.loadtxt('l2-3d.dat')
@@ -35,7 +35,7 @@ plt.xlabel('Correlation length $r$')
 plt.ylabel('Lineal-path function $L_2(r)$')
 plt.legend(['CorrelationFunctions.jl (2D)', 'Theory (2D)',
             'CorrelationFunctions.jl (3D)', 'Theory (3D)'])
-plt.savefig('l2.png')
+plt.savefig('l2.png', bbox_inches = 'tight')
 
 ss_2d = np.loadtxt('ss-2d.dat')
 ss_3d = np.loadtxt('ss-3d.dat')
@@ -52,7 +52,7 @@ plt.xlabel('Correlation length $r$')
 plt.ylabel('Surface-surface function $F_{ss}(r)$')
 plt.legend(['CorrelationFunctions.jl (2D)', 'Theory (2D)',
             'CorrelationFunctions.jl (3D)', 'Theory (3D)'])
-plt.savefig('ss.png')
+plt.savefig('ss.png', bbox_inches = 'tight')
 
 sv_2d = np.loadtxt('sv-2d.dat')
 sv_3d = np.loadtxt('sv-3d.dat')
@@ -69,7 +69,7 @@ plt.xlabel('Correlation length $r$')
 plt.ylabel('Surface-void function $F_{sv}(r)$')
 plt.legend(['CorrelationFunctions.jl (2D)', 'Theory (2D)',
             'CorrelationFunctions.jl (3D)', 'Theory (3D)'])
-plt.savefig('sv.png')
+plt.savefig('sv.png', bbox_inches = 'tight')
 
 ps_hist_2d = np.loadtxt('pore_size-2d-hist.dat')
 ps_prob_2d = np.loadtxt('pore_size-2d-prob.dat')
@@ -88,7 +88,7 @@ plt.xlabel('Pore size $r$')
 plt.ylabel('Pore size function $P(r)$')
 plt.legend(['Theory (2D)', 'Theory (3D)',
[…]

### 2024-01-31 paper-correlations.tex
Enlarge figure 4
added final changes
Prepare to publishing

@@
   \centering
-  \includegraphics[width=0.9\linewidth]{images/cf_1.png}
+  \includegraphics[width=0.9\linewidth]{cf_1.png}
   \caption[]{A schematic representation of a binary porous media (pores are
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{images/cf_diag.png}
+  \includegraphics[width=0.9\linewidth]{cf_diag.png}
   \caption[]{Available directions to compute directional correlation functions
@@
   \centering
-  \includegraphics[width=0.45\linewidth]{images/disks.png}
-  \includegraphics[width=0.45\linewidth]{images/balls.png}
+  \includegraphics[width=0.45\linewidth]{disks.png}
+  \includegraphics[width=0.45\linewidth]{balls.png}
   \caption[]{Images of overlapping disks and balls used for testing of our package.}
@@
   \centering
-  \subfigure[Lineal-path correlation function]{
-    \includegraphics[width=0.45\linewidth]{images/l2.png}
-    \label{fig:l2}}
-  \hfill
-  \subfigure[Two-point correlation function]{
-    \includegraphics[width=0.45\linewidth]{images/s2.png}
-    \label{fig:s2}}
+  \includegraphics[width=0.45\linewidth]{l2.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{s2.png}
   \vskip\baselineskip
-  \subfigure[Surface-surface correlation function]{
-    \includegraphics[width=0.45\linewidth]{images/ss.png}
-    \label{fig:ss}}
-  \hfill
-  \subfigure[Surface-void correlation function]{
-    \includegraphics[width=0.45\linewidth]{images/sv.png}
-    \label{fig:sv}}
+  \includegraphics[width=0.45\linewidth]{ss.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{sv.png}
   \vskip\baselineskip
-  \subfigure[Pore size correlation function]{
-    \includegraphics[width=0.45\linewidth]{images/ps.png}
-    \label{fig:ps}}
-  \hfill
-  \subfigure[Chord length correlation function]{
-    \includegraphics[width=0.45\linewidth]{images/cl.png}
-    \label{fig:cl}}
+  \includegraphics[width=0.45\linewidth]{ps.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{cl.png}
   \caption[]{A comparison of calculated and theoretical values of correlation
@@
   \subfigure[Ceramic 1]{
-    \includegraphics[width=0.3\linewidth]{samples/Ceramic1.png}}
+    \includegraphics[width=0.3\linewidth]{Ceramic1.png}}
   \hfill
   \subfigure[Ceramic 2]{
-    \includegraphics[width=0.3\linewidth]{samples/Ceramic2.png}}
+    \includegraphics[width=0.3\linewidth]{Ceramic2.png}}
   \hfill
   \subfigure[Ceramic 3]{
-    \includegraphics[width=0.3\linewidth]{samples/Ceramic3.png}}
+    \includegraphics[width=0.3\linewidth]{Ceramic3.png}}
   \vskip\baselineskip
   \subfigure[Sandstone 1]{
-    \includegraphics[width=0.3\linewidth, frame]{samples/sandstone1.png}}
+    \includegraphics[width=0.3\linewidth, frame]{sandstone1.png}}
   \hfill
   \subfigure[Sandstone 2]{
-    \includegraphics[width=0.3\linewidth, frame]{samples/sandstone2.png}}
+    \includegraphics[width=0.3\linewidth, frame]{sandstone2.png}}
   \hfill
   \subfigure[Carbonate 1]{
-    \includegraphics[width=0.3\linewidth, frame]{samples/carbonate1.png}}
+    \includegraphics[width=0.3\linewidth, frame]{carbonate1.png}}
   \caption[]{Visualization of XCT (top) and SEM (bottom) images used for
@@
   \centering
-  \includegraphics[width=0.45\linewidth]{samples/s2-xct.png}
-  \hfill
-  \includegraphics[width=0.45\linewidth]{samples/c2-xct.png}
+  \includegraphics[width=0.45\linewidth]{s2-xct.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{c2-xct.png}
   \vskip\baselineskip
-  \includegraphics[width=0.45\linewidth]{samples/l2-xct.png}
+  \includegraphics[width=0.45\linewidth]{l2-xct.png}
   \vskip\baselineskip
-  \includegraphics[width=0.45\linewidth]{samples/surf2-xct.png}
-  \hfill
-  \includegraphics[width=0.45\linewidth]{samples/surfvoid-xct.png}
+  \includegraphics[width=0.45\linewidth]{surf2-xct.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{surfvoid-xct.png}
   \vskip\baselineskip
-  \includegraphics[width=0.45\linewidth]{samples/pore-size-xct.png}
-  \hfill
-  \includegraphics[width=0.45\linewidth]{samples/chord-length-xct.png}
+  \includegraphics[width=0.45\linewidth]{pore-size-xct.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{chord-length-xct.png}
   \caption[]{Plots of correlation functions for XCT samples on
@@
   \centering
-  \includegraphics[width=0.45\linewidth]{samples/s2-sem.png}
-  \hfill
-  \includegraphics[width=0.45\linewidth]{samples/c2-sem.png}
+  \includegraphics[width=0.45\linewidth]{s2-sem.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{c2-sem.png}
   \vskip\baselineskip
-  \includegraphics[width=0.45\linewidth]{samples/l2-sem.png}
+  \includegraphics[width=0.45\linewidth]{l2-sem.png}
   \vskip\baselineskip
-  \includegraphics[width=0.45\linewidth]{samples/surf2-sem.png}
-  \hfill
-  \includegraphics[width=0.45\linewidth]{samples/surfvoid-sem.png}
+  \includegraphics[width=0.45\linewidth]{surf2-sem.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{surfvoid-sem.png}
   \vskip\baselineskip
-  \includegraphics[width=0.45\linewidth]{samples/pore-size-sem.png}
-  \hfill
-  \includegraphics[width=0.45\linewidth]{samples/chord-length-sem.png}
+  \includegraphics[width=0.45\linewidth]{pore-size-sem.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{chord-length-sem.png}
   \caption[]{Plots of correlation functions for SEM samples on
@@
   \subfigure[$S_2$]{
-    \includegraphics[width=0.45\linewidth]{samples/map-s2.png}}
+    \includegraphics[width=0.45\linewidth]{map-s2.png}}
   \hfill
   \subfigure[$C_2$]{
-    \includegraphics[width=0.45\linewidth]{samples/map-c2.png}}
+    \includegraphics[width=0.45\linewidth]{map-c2.png}}
   \vskip\baselineskip
   \subfigure[$F_{ss}$]{
-    \includegraphics[width=0.45\linewidth]{samples/map-surf2.png}}
+    \includegraphics[width=0.45\linewidth]{map-surf2.png}}
   \hfill
   \subfigure[$F_{sv}$]{
-    \includegraphics[width=0.45\linewidth]{samples/map-surfvoid.png}}
+    \includegraphics[width=0.45\linewidth]{map-surfvoid.png}}
   \caption[]{Correlation maps for Sandstone 1.}
@@
   \centering
-  \includegraphics[width=0.45\linewidth]{samples/multiphase.png}
-  \includegraphics[width=0.45\linewidth]{samples/multiphase-cc.png}
+  \includegraphics[width=0.45\linewidth]{multiphase.png}
+  \includegraphics[width=0.45\linewidth]{multiphase-cc.png}
   \caption[]{Cross-correlation functions for multiphase sample (soil) which has
@@
   \subfigure[Two-dimensional case, module \code{Directional}]{
-    \includegraphics[width=0.475\linewidth]{images/time-2d.png}
+    \includegraphics[width=0.475\linewidth]{time-2d.png}
     \label{fig:timings-2d}}
@@
   \subfigure[Three-dimensional case, module \code{Directional}]{
-    \includegraphics[width=0.475\linewidth]{images/time-3d.png}
+    \includegraphics[width=0.475\linewidth]{time-3d.png}
     \label{fig:timings-3d}}
@@
   \subfigure[Two-dimensional case, module \code{Map}, CPU]{
-    \includegraphics[width=0.475\linewidth]{images/time-2d-map.png}
+    \includegraphics[width=0.475\linewidth]{time-2d-map.png}
     \label{fig:timings-2d-map}}
@@
   \subfigure[Three-dimensional case, module \code{Map}, CPU]{
-    \includegraphics[width=0.475\linewidth]{images/time-3d-map.png}
+    \includegraphics[width=0.475\linewidth]{time-3d-map.png}
     \label{fig:timings-3d-map}}
@@
   \subfigure[Two-dimensional case, module \code{Map}, GPU]{
-    \includegraphics[width=0.475\linewidth]{images/time-2d-gpu.png}
+    \includegraphics[width=0.475\linewidth]{time-2d-gpu.png}
     \label{fig:timings-2d-gpu}}
@@
   \subfigure[Three-dimensional case, module \code{Map}, GPU]{
-    \includegraphics[width=0.475\linewidth]{images/time-3d-gpu.png}
+    \includegraphics[width=0.475\linewidth]{time-3d-gpu.png}
     \label{fig:timings-3d-gpu}}
@@
 \section{Acknowledgments}
-This research was supported by the Russian Science Foundation grant 19-72-10082.
+This research was supported by the Russian Science Foundation grant 23-74-00061.
 
@@
 Media with Pores) research group (www.porenetwork.com) and used some of its
-software.
+software. We thank our colleague Konstantin Romanenko for suggestions and administrative work.
 

### 2024-01-31 samples/calc.jl

@@ -1,47 +1,0 @@
-module SomeShit
-
-import CorrelationFunctions.Directional as D
-import CorrelationFunctions.Utilities as U
-using Statistics
-using NPZ
-using FileIO
-using Images
-
-const fns = [:s2, :l2, :c2, :surf2, :surfvoid]
-
-#=
-function read_files()
-    rawfiles = filter(readdir(".")) do name
-        splitext(name)[2] == ".raw"
-    end
-
-    return Iterators.map(rawfiles) do name
-        (splitext(name)[1], U.read_cuboid(name, 1000, 3) |> BitArray)
-    end
-end
-=#
-
-function read_files()
-    rawfiles = filter(readdir(".")) do name
-        splitext(name)[2] == ".png"
-    end
-
-    return Iterators.map(rawfiles) do name
-        (splitext(name)[1], name |> load .|> Gray |> BitArray)
-    end
-end
-
-function do_it!()
-    data = read_files()
-
-    for (name, sample) in data
-        println(name)
-        for sym in fns
-            fn = D.eval(sym)
-            a = fn(sample, true; periodic = true) |> mean
-            npzwrite("$(name)-$(sym).npy", a)
-        end
-    end
-end
-
-end

### 2024-01-31 samples/multiphase.jl

@@ -1,18 +1,0 @@
-module WTF
-import CorrelationFunctions.Utilities as U
-import CorrelationFunctions.Directional as D
-using NPZ
-using Statistics
-
-pr(array, p) = sum(array .== p) / length(array)
-
-function do_it!()
-    data = U.read_cuboid("image3d_multi_4phases.raw", 304, 3)
-
-    for (p1, p2) in [(0, 1), (0, 2), (0, 3), (1, 2), (1, 3), (2, 3)]
-        cc = D.cross_correlation(data, p1, p2; periodic = false)
-        npzwrite("multiphase-$(p1)-$(p2).npy", mean(cc) / pr(data, p1) / pr(data, p2))
-    end
-end
-
-end

### 2024-01-31 samples/multiphase.py

@@ -1,22 +1,0 @@
-#!/usr/bin/env python
-
-import numpy as np
-import matplotlib.pyplot as plt
-
-pairs = [(1, 2), (1, 3), (1, 4), (2, 3), (2, 4), (3, 4)]
-
-plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 25)
-
-for pair in pairs:
-    p1, p2 = pair
-    data = np.load('multiphase-%i-%i.npy' % (p1 - 1, p2 - 1))
-    xs = np.arange(0, data.size) * 15.0
-    plt.plot(xs, data)
-
-plt.legend(list(map(lambda x: r'$\rho_{%i%i}$' % x, pairs)))
-plt.xlabel('Correlation length, μm')
-plt.ylabel('Cross-correlation')
-plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
-#plt.show()
-plt.savefig("multiphase-cc.png", bbox_inches = 'tight')

### 2024-01-31 samples/plot.py

@@ -1,34 +1,0 @@
-#!/usr/bin/env python
-
-import numpy as np
-import matplotlib.pyplot as plt
-
-data = [
-    "Bentheimer_2d25um_binary",
-    "CastleGate_2d25um_binary",
-    "Kirby_2d25um_binary"
-]
-
-def load_data(name, fn):
-    return np.load("%s-%s.npy" % (name, fn))
-
-def plot_fn(fn, ylabel, power):
-    plt.figure(figsize = (10, 8), dpi = 300)
-    plt.rc('font', size = 25)
-
-    for n in data:
-        d = load_data(n, fn) * (1/2.25)**power
-        xs = np.arange(0, d.size) * 2.25
-        plt.plot(xs, d)
-
-    plt.legend(list(map(lambda name: name.split('_')[0], data)))
-    plt.xlabel('Correlation length, μm')
-    plt.ylabel(ylabel)
-    plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
-    plt.savefig("%s-xct.png" % fn, bbox_inches = 'tight')
-
-plot_fn('s2', '$S_2$', 0)
-plot_fn('l2', '$L_2$', 0)
-plot_fn('c2', '$C_2$', 0)
-plot_fn('surf2', '$F_{ss}, \mu m^{-2}$', 2)
-plot_fn('surfvoid', '$F_{sv}, \mu m^{-1}$', 1)

### 2024-01-31 timings/plot-timings-directional.py

@@ -1,61 +1,0 @@
-#!/usr/local/bin/python
-
-import numpy as np
-import matplotlib.pyplot as plt
-
-names2d = [
-    'chord_length-dir-2d.dat',
-    'pore_size-dir-2d.dat',
-    's2-dir-2d.dat',
-    'l2-dir-2d.dat',
-    'c2-dir-2d.dat',
-    'surf2-dir-2d.dat',
-    'surfvoid-dir-2d.dat',
-]
-
-names3d = [
-    'chord_length-dir-3d.dat',
-    'pore_size-dir-3d.dat',
-    's2-dir-3d.dat',
-    'l2-dir-3d.dat',
-    'c2-dir-3d.dat',
-    'surf2-dir-3d.dat',
-    'surfvoid-dir-3d.dat',
-]
-
-markers = [
-    '.', 'o', 's', 'p', '.', 'o', 's'
-]
-
-data2d = [np.loadtxt(name) for name in names2d]
-data3d = [np.loadtxt(name) for name in names3d]
-
-labels = [
-    'Chord length function',
-    'Pore size function',
-    'Two point function',
-    'Lineal-path function',
-    'Cluster function',
-    'Surface-surface function',
-    'Surface-void function',
-]
-
-plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 18)
-for data, marker in zip(data3d, markers):
-    plt.errorbar(data[:, 0] ** 3, data[:, 1], marker = marker, yerr = data[:, 2])
-plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
-plt.legend(labels)
-plt.xlabel('Number of voxels')
-plt.ylabel('Time of execution, seconds')
-plt.savefig('time-3d.png', bbox_inches = 'tight')
-
-plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 18)
-for data, marker in zip(data2d, markers):
-    plt.errorbar(data[:, 0] ** 2, data[:, 1], marker = marker, yerr = data[:, 2])
-plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
-plt.legend(labels)
-plt.xlabel('Number of pixels')
-plt.ylabel('Time of execution, seconds')
-plt.savefig('time-2d.png', bbox_inches = 'tight')

### 2024-01-31 timings/plot-timings-gpu.py

@@ -1,52 +1,0 @@
-#!/usr/local/bin/python
-
-import numpy as np
-import matplotlib.pyplot as plt
-
-names2d = [
-    's2-gpu-2d.dat',
-    'c2-gpu-2d.dat',
-    'surf2-gpu-2d.dat',
-    'surfvoid-gpu-2d.dat',
-]
-
-names3d = [
-    's2-gpu-3d.dat',
-    'c2-gpu-3d.dat',
-    'surf2-gpu-3d.dat',
-    'surfvoid-gpu-3d.dat',
-]
-
-markers = [
-    '.', 'o', 's', 'p'
-]
-
-data2d = [np.loadtxt(name) for name in names2d]
-data3d = [np.loadtxt(name) for name in names3d]
-
-labels = [
-    'Two point function',
-    'Cluster function',
-    'Surface-surface function',
-    'Surface-void function',
-]
-
-plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 18)
-for data, marker in zip(data3d, markers):
-    plt.errorbar(data[:, 0] ** 3, data[:, 1], marker = marker, yerr = data[:, 2])
-plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
-plt.legend(labels)
-plt.xlabel('Number of voxels')
-plt.ylabel('Time of execution, seconds')
-plt.savefig('time-3d-gpu.png', bbox_inches = 'tight')
-
-plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 18)
-for data, marker in zip(data2d, markers):
-    plt.errorbar(data[:, 0] ** 2, data[:, 1], marker = marker, yerr = data[:, 2])
-plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
-plt.legend(labels)
-plt.xlabel('Number of pixels')
-plt.ylabel('Time of execution, seconds')
-plt.savefig('time-2d-gpu.png', bbox_inches = 'tight')

### 2024-01-31 timings/plot-timings-map.py

@@ -1,52 +1,0 @@
-#!/usr/local/bin/python
-
-import numpy as np
-import matplotlib.pyplot as plt
-
-names2d = [
-    's2-map-2d.dat',
-    'c2-map-2d.dat',
-    'surf2-map-2d.dat',
-    'surfvoid-map-2d.dat',
-]
-
-names3d = [
-    's2-map-3d.dat',
-    'c2-map-3d.dat',
-    'surf2-map-3d.dat',
-    'surfvoid-map-3d.dat',
-]
-
-markers = [
-    '.', 'o', 's', 'p'
-]
-
-data2d = [np.loadtxt(name) for name in names2d]
-data3d = [np.loadtxt(name) for name in names3d]
-
-labels = [
-    'Two point function',
-    'Cluster function',
-    'Surface-surface function',
-    'Surface-void function',
-]
-
-plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 18)
-for data, marker in zip(data3d, markers):
-    plt.errorbar(data[:, 0] ** 3, data[:, 1], marker = marker, yerr = data[:, 2])
-plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
-plt.legend(labels)
-plt.xlabel('Number of voxels')
-plt.ylabel('Time of execution, seconds')
-plt.savefig('time-3d-map.png', bbox_inches = 'tight')
-
-plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 18)
-for data, marker in zip(data2d, markers):
-    plt.errorbar(data[:, 0] ** 2, data[:, 1], marker = marker, yerr = data[:, 2])
-plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
-plt.legend(labels)
-plt.xlabel('Number of pixels')
-plt.ylabel('Time of execution, seconds')
-plt.savefig('time-2d-map.png', bbox_inches = 'tight')

### 2024-01-31 timings/timings.jl

@@ -1,135 +1,0 @@
-module Timings
-
-import CorrelationFunctions.Map as M
-import CorrelationFunctions.Directional as D
-import Statistics as S
-import Distributions as Dist
-import CUDA
-using DelimitedFiles
-using NPZ
-
-function draw_balls(s)
-    array = falses(s...)
-    center1 = Iterators.repeated(0.3, length(s))
-    center2 = Iterators.repeated(0.7, length(s))
-    r = 0.2
-
-    for idx in CartesianIndices(array)
-        dist1 = sum((Tuple(idx) ./s .- center1) .^ 2)
-        dist2 = sum((Tuple(idx) ./s .- center2) .^ 2)
-        if dist1 <= r^2 || dist2 <= r^2
-            array[idx] = true
-        end
-    end
-
-    return array
-end
-
-function prepare!()
-    for side in 1000:1000:6000
-        println(side)
-        balls = draw_balls((side, side))
-        npzwrite("disks-$(side).npy", balls)
-    end
-
-    for side in 50:50:300
-        println(side)
-        balls = draw_balls((side, side, side))
-        npzwrite("balls-$(side).npy", balls)
-    end
-end
-
-struct FnSpec
-    fn   :: Function
-    name :: String
-end
-
-struct ExecResult
-    side  :: Int
-    mean  :: Float64
-    range :: Float64
-end
-
-abstract type AbstractCU end
-
-struct CPU <: AbstractCU end
-struct GPU <: AbstractCU end
-
-upload_to_cu(array, :: CPU) = array
-upload_to_cu(array, :: GPU) = CUDA.CuArray(array)
-
-s(res :: ExecResult) = res.side
-μ(res :: ExecResult) = res.mean
-r(res :: ExecResult) = res.range
-
-(fn :: FnSpec)(data) = fn.fn(data)
-
-function estimate_range(array :: AbstractArray, prob)
-    len = length(array)
-    t = Dist.TDist(len - 1)
-    # FIXME: quantile function is for one-tailed tests.
-    # Recalculate `prob` from two-tailed to one-tailed
-    α = 1 - prob
-    return Dist.quantile(t, 1 - α/2) * S.std(array) / sqrt(len)
-end
-
-function calculate_time!(fn :: FnSpec, dim, prefix, cu :: AbstractCU = CPU())
-    println(fn.name)
-    data_arrays = (dim == 2) ?
[…]

### 2024-01-31 verification/calc-cf-2d.jl

@@ -1,109 +1,0 @@
-module Shit
-using Distributions
-using Statistics
-using CorrelationFunctions
-using DelimitedFiles
-using Images
-using FileIO
-import Random
-
-function gencenters(side, λ)
-    n = (λ * side^2) |> Poisson |> rand
-    return reduce(hcat, (rand(1:side, 2) for i in 1:n))
-end
-
-function gendisks(side, R, λ)
-    spheres = zeros(Int8, (side + 2R + 1, side + 2R + 1))
-    sphere  = zeros(Int8, (2R + 1, 2R + 1))
-    centers = gencenters(side, λ)
-    for i in -R:R
-        for j in -R:R
-            dist = i^2 + j^2
-            if dist < R^2
-                sphere[j+R+1, i+R+1] = 1
-            end
-        end
-    end
-    for center in (centers[:,i] for i in 1:size(centers,2))
-        x = center[1]
-        y = center[2]
-        spheres[x:x + 2R, y:y + 2R] .|= sphere
-    end
-    return spheres[R+1:end-R-1, R+1:end-R-1]
-end
-
-s2_theory(r, R, λ) =
-    let A = 4R^2 - r^2;
-        a = (r < 2R) ? π*R^2 + r*sqrt(A)/4 - acos(r/(2R))*R^2 : π*R^2;
-        exp(-2λ*a)
-end
-
-ss_theory(r, R, λ) =
-    let A = 4R^2 - r^2;
-        a = (r < 2R) ?
-            (A*R^2*λ^2*r*(acos(r/(2R))^2 - 2π*acos(r/(2R)) + π^2) + sqrt(A)*R^2*λ)/(A*r) : (π*λ*R)^2
-        4a*s2_theory(r, R, λ)
-    end
-
-sv_theory(r, R, λ) =
-    let A = 4R^2 - r^2;
-        a = (r < 2R) ? π - acos(r/(2R)) : π
-        2R*λ*a*s2_theory(r, R, λ)
-    end
-
-l2_theory(r, R, λ) =
-    exp(-λ*(π*R^2 + 2r*R))
-
-cl_theory(r, R, λ) = 2λ*R*exp(-2λ*r*R)
-
-ps_theory(r, R, λ) = 2λ*π*(r + R)*exp(-λ*π*(r^2 + 2r*R))
-
-const fns = [
-    ("s2", s2_theory,
-     img -> Directional.s2(img, false; periodic = true)),
-    ("l2", l2_theory,
[…]

### 2024-01-31 verification/calc-cf-3d.jl

@@ -1,110 +1,0 @@
-module Shit
-using Distributions
-using Statistics
-using CorrelationFunctions
-using DelimitedFiles
-import Random
-
-function gencenters(side, λ)
-    n = (λ * side^3) |> Poisson |> rand
-    return reduce(hcat, (rand(1:side, 3) for i in 1:n))
-end
-
-function genballs(side, R, λ)
-    sphere_side = 2R + 1
-    padded_side = side + sphere_side
-    spheres = zeros(Int8, (padded_side, padded_side, padded_side))
-    sphere = zeros(Int8, (sphere_side, sphere_side, sphere_side))
-    centers = gencenters(side, λ)
-    for i in -R:R
-        for j in -R:R
-            for k in -R:R
-                dist = i^2 + j^2 + k^2
-                if dist < R^2
-                    sphere[k+R+1, j+R+1, i+R+1] = 1
-                end
-            end
-        end
-    end
-
-    for center in (centers[:,i] for i in 1:size(centers,2))
-        x = center[1]
-        y = center[2]
-        z = center[3]
-        spheres[x:x + 2R, y:y + 2R, z:z + 2R] .|= sphere
-    end
-    return spheres[R+1:end-R-1, R+1:end-R-1, R+1:end-R-1]
-end
-
-s2_theory(r, R, λ) =
-    let a = (r > 2R) ? 8/3*R^3 : (4/3*R^3 + r*R^2 - r^3/12);
-        exp(-λ*π*a)
-    end
-
-ss_theory(r, R, λ) =
-    let η = 4/3*λ*π*R^3;
-        a = (r > 2R) ? 9η^2/R^2 : (9η^2/R^2*(1/2 + r/(4R))^2 + 3η/(2r*R))
-        a*s2_theory(r, R, λ)
-    end
-
-sv_theory(r, R, λ) =
-    let η = 4/3*λ*π*R^3;
-        a = (r > 2R) ? 1 : (1/2 + r/(4R))
-        3η/R*a*s2_theory(r, R, λ)
-    end
-
-l2_theory(r, R, λ) =
-    exp(-λ*π * (4/3*R^3 + r*R^2))
-
-cl_theory(r, R, λ) = π*λ*R^2*exp(-π*λ*r*R^2)
-
-ps_theory(r, R, λ) = 4π*λ*(r + R)^2 * exp(-4/3*π*λ* (r^3 + 3r^2*R + 3r*R^2))
-
-const fns = [
[…]

### 2024-01-31 verification/plot.py

@@ -1,110 +1,0 @@
-#!/usr/bin/env python
-
-import numpy as np
-import matplotlib.pyplot as plt
-
-s2_2d = np.loadtxt('s2-2d.dat')
-s2_3d = np.loadtxt('s2-3d.dat')
-
-plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 25)
-plt.plot(s2_2d[:, 0], 'r-', linewidth = 2.0)
-plt.plot(s2_2d[:, 1], 'b-', linewidth = 2.0)
-plt.plot(s2_3d[:, 0], 'r--', linewidth = 2.0)
-plt.plot(s2_3d[:, 1], 'b--', linewidth = 2.0)
-plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
-plt.xlim([0, 130])
-plt.xlabel('Correlation length $r$')
-plt.ylabel('Two point function $S_2(r)$')
-plt.legend(['CorrelationFunctions.jl (2D)', 'Theory (2D)',
-            'CorrelationFunctions.jl (3D)', 'Theory (3D)'])
-plt.savefig('s2.png', bbox_inches = 'tight')
-
-l2_2d = np.loadtxt('l2-2d.dat')
-l2_3d = np.loadtxt('l2-3d.dat')
-
-plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 25)
-plt.plot(l2_2d[:, 0], 'r-', linewidth = 2.0)
-plt.plot(l2_2d[:, 1], 'b-', linewidth = 2.0)
-plt.plot(l2_3d[:, 0], 'r--', linewidth = 2.0)
-plt.plot(l2_3d[:, 1], 'b--', linewidth = 2.0)
-plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
-plt.xlim([0, 150])
-plt.xlabel('Correlation length $r$')
-plt.ylabel('Lineal-path function $L_2(r)$')
-plt.legend(['CorrelationFunctions.jl (2D)', 'Theory (2D)',
-            'CorrelationFunctions.jl (3D)', 'Theory (3D)'])
-plt.savefig('l2.png', bbox_inches = 'tight')
-
-ss_2d = np.loadtxt('ss-2d.dat')
-ss_3d = np.loadtxt('ss-3d.dat')
-
-plt.figure(figsize = (10, 8), dpi = 300)
[…]
